### 2019-07-29 paper.tex
initial commit

%% bare_jrnl_compsoc.tex
%% V1.4b
%% 2015/08/26
%% by Michael Shell
%% See:
%% http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
%% Computer Society journal paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/pkg/ieeetran
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall the IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. The IEEE's font choices and paper sizes can   ***
% *** trigger bugs that do not appear when using other class files.       ***                          ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

\documentclass[10pt,journal,compsoc]{IEEEtran}
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[10pt,journal,compsoc]{../sty/IEEEtran}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)
\usepackage{lipsum}

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/pkg/ifpdf
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
\ifCLASSOPTIONcompsoc
  % IEEE Computer Society needs nocompress option
  % requires cite.sty v4.0 or later (November 2003)
  \usepackage[nocompress]{cite}
\else
  % normal IEEE
  \usepackage{cite}
\fi
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of the IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 5.0 (2009-03-20) and later if using hyperref.sty.
% The latest version can be obtained at:
% http://www.ctan.org/pkg/cite
% The documentation is contained in the cite.sty file itself.
%
% Note that some packages require special options to format as the Computer
% Society requires. In particular, Computer Society  papers do not use
% compressed citation ranges as is done in typical IEEE papers
% (e.g., [1]-[4]). Instead, they list every citation separately in order
% (e.g., [1], [2], [3], [4]). To get the latter we need to load the cite
% package with the nocompress option which is supported by cite.sty v4.0
% and later. Note also the use of a CLASSOPTION conditional provided by
% IEEEtran.cls V1.7 and later.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/pkg/graphicx
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/pkg/epslatex
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
%\usepackage{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics.
%
% Note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/amsmath

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/pkg/algorithms
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/pkg/algorithmicx

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/array

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=footnotesize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a sans serif font rather
% than the serif font used in traditional IEEE formatting and thus the need
% to invoke different subfig.sty package options depending on whether
% compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/pkg/subfig

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure.
% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
% corrections already built into the system in which case a warning will
% be issued if an attempt is made to load fixltx2e.sty as it is no longer
% needed.
% The latest version and documentation can be found at:
% http://www.ctan.org/pkg/fixltx2e

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/stfloats
% Do not use the stfloats baselinefloat ability as the IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that the IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
% \usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/pkg/dblfloatfix

%\ifCLASSOPTIONcaptionsoff
%  \usepackage[nomarkers]{endfloat}
% \let\MYoriglatexcaption\caption
% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
%\fi
% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
% Axel Sommerfeldt. This package may be useful when used in conjunction with 
% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
% submissions have lists of figures/tables at the end of the paper and that
% figures/tables without any captions are placed on a page by themselves at
% the end of the document. If needed, the draftcls IEEEtran class option or
% \CLASSINPUTbaselinestretch interface can be used to increase the line
% spacing as well. Be sure and use the nomarkers option of endfloat to
% prevent endfloat from "marking" where the figures would have been placed
% in the text. The two hack lines of code above are a slight modification of
% that suggested by in the endfloat docs (section 8.4.1) to ensure that
% the full captions always appear in the list of figures/tables - even if
% the user used the short optional argument of \caption[]{}.
% IEEE papers do not typically make use of \caption[]'s optional argument,
% so this should not be an issue. A similar trick can be used to disable
% captions of packages such as subfig.sty that lack options to turn off
% the subcaptions:
% For subfig.sty:
% \let\MYorigsubfloat\subfloat
% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
% However, the above trick will not work if both optional arguments of
% the \subfloat command are used. Furthermore, there needs to be a
% description of each subfigure *somewhere* and endfloat does not add
% subfigure captions to its list of figures. Thus, the best approach is to
% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
% and instead reference/explain all the subfigures within the main caption.
% The latest version of endfloat.sty and its documentation can obtained at:
% http://www.ctan.org/pkg/endfloat
%
% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
% later in the document, say, to conditionally put the References on a 
% page by themselves.

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/url
% Basically, \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Sample \LaTeX Template for Kyoto VR MQP}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
%
%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
% lists the Computer Society journals use for "first footnote" author
% affiliations. Use \IEEEcompsocthanksitem which works much like \item
% for each affiliation group. When not in compsoc mode,
% \IEEEcompsocitemizethanks becomes like \thanks and
% \IEEEcompsocthanksitem becomes a line break with idention. This
% facilitates dual compilation, although admittedly the differences in the
% desired content of \author between the different types of papers makes a
% one-size-fits-all approach a daunting prospect. For instance, compsoc 
% journal papers have the author affiliations above the "Manuscript
% received ..."  text while in non-compsoc journals this is reversed. Sigh.

\author{William~Campbell, Cole~Granof, and Joseph~Petitti}

% note the % following the last \IEEEmembership and also \thanks - 
% these prevent an unwanted space from occurring between the last author name
% and the end of the author line. i.e., if you had this:
% 
% \author{....lastname \thanks{...} \thanks{...} }
%                     ^------------^------------^----Do not want these spaces!
%
% a space would be appended to the last name and could cause every name on that
% line to be shifted left slightly. This is one of those "LaTeX things". For
% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
% "AB" then you have to do: "\textbf{A}\textbf{B}"
% \thanks is no different in this regard, so shield the last } of each \thanks
% that ends a line with a % and do not let a space in before the next \thanks.
% Spaces after \IEEEmembership other than the last one are OK (and needed) as
% you are supposed to have spaces between the names. For what it is worth,
% this is a minor point as most people would not even notice if the said evil
% space somehow managed to creep in.

% The paper headers
\markboth{Worcester Polytechnic Institute Major Qualifying Project}%
{Sample \LaTeX Template for Kyoto VR MQP}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
% 
% *** Note that you probably will NOT want to include the author's ***
% *** name in the headers of peer review papers.                   ***
% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
% you desire.

% The publisher's ID mark at the bottom of the page is less important with
% Computer Society journal papers as those publications place the marks
% outside of the main text columns and, therefore, unlike regular IEEE
% journals, the available text space is not reduced by their presence.
% If you want to put a publisher's ID mark on the page you can do it like
% this:
%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
% or like this to get the Computer Society new two part style.
%\IEEEpubid{\makebox[\columnwidth]{\hfill 0000--0000/00/\$00.00~\copyright~2015 IEEE}%
%\hspace{\columnsep}\makebox[\columnwidth]{Published by the IEEE Computer Society\hfill}}
% Remember, if you use this you must call \IEEEpubidadjcol in the second
% column for its text to clear the IEEEpubid mark (Computer Society jorunal
% papers don't need this extra clearance.)

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\IEEEtitleabstractindextext{%
\begin{abstract}
The abstract goes here.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Computer Society, IEEE, IEEEtran, journal, \LaTeX, paper, template.
\end{IEEEkeywords}}

% make the title area
\maketitle

% To allow for easy dual compilation without having to reenter the
% abstract/keywords data, the \IEEEtitleabstractindextext text will
% not be used in maketitle, but will appear (i.e., to be "transported")
% here as \IEEEdisplaynontitleabstractindextext when the compsoc 
% or transmag modes are not selected <OR> if conference mode is selected 
% - because all conference papers position the abstract like regular
% papers do.
\IEEEdisplaynontitleabstractindextext
% \IEEEdisplaynontitleabstractindextext has no effect when using
% compsoc or transmag under a non-conference mode.

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
% Computer Society journal (but not conference!) papers do something unusual
% with the very first section heading (almost always called "Introduction").
% They place it ABOVE the main text! IEEEtran.cls does not automatically do
% this for you, but you can achieve this effect with the provided
% \IEEEraisesectionheading{} command. Note the need to keep any \label that
% is to refer to the section immediately after \section in the above as
% \IEEEraisesectionheading puts \section within a raised box.

% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps (small caps for compsoc).
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by the IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
\IEEEPARstart{T}{his} demo file is intended to serve as a ``starter file''
for IEEE Computer Society journal papers produced under \LaTeX\ using
IEEEtran.cls version 1.8b and later.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
I wish you the best of success.

\hfill mds

\hfill August 26, 2015

\subsection{Subsection Heading Here}
Subsection text here.

% needed in second column of first page if using \IEEEpubid
%\IEEEpubidadjcol

\subsubsection{Subsubsection Heading Here}
Subsubsection text here.

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure}

% Note that the IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.
% However, the Computer Society has been known to put floats at the bottom.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command,
% and the \label for the overall figure must come after \caption.
% \hfil is used as a separator to get equal spacing.
% Watch out that the combined width of all the subfigures on a 
% line do not exceed the text width or a line break will occur.
%
%\begin{figure*}[!t]
%\centering
%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
%\label{fig_second_case}}
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat[]), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.
% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
% labels, the optional argument to \subfloat must be present. If a
% subcaption is not desired, just leave its contents blank,
% e.g., \subfloat[].

% An example of a floating table. Note that, for IEEE style tables, the
% \caption command should come BEFORE the table and, given that table
% captions serve much like titles, are usually capitalized except for words
% such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
% and up, which are usually not capitalized unless they are the first or
% last word of the caption. Table text will default to \footnotesize as
% the IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

% Note that the IEEE does not put floats in the very first column
% - or typically anywhere on the first page for that matter. Also,
% in-text middle ("here") positioning is typically not used, but it
% is allowed and encouraged for Computer Society conferences (but
% not Computer Society journals). Most IEEE journals/conferences use
% top floats exclusively. 
% Note that, LaTeX2e, unlike IEEE journals/conferences, places
% footnotes above bottom floats. This can be corrected via the
% \fnbelowfloat command of the stfloats package.

\section{Conclusion}
The conclusion goes here.

% if have a single appendix:
%\appendix[Proof of the Zonklar Equations]
% or
%\appendix  % for no appendix heading
% do not use \section anymore after \appendix, only \section*
% is possibly needed

% use appendices with more than one appendix
% then use \section to start each appendix
% you must declare a \section before using any
% \subsection or using \label (\appendices by itself
% starts a section numbered zero.)
%

\appendices
\section{Proof of the First Zonklar Equation}
Appendix one text goes here.

% you can choose not to have a title for an appendix
% if you want by leaving the argument blank
\section{}
Appendix two text goes here.

% use section* for acknowledgment
\ifCLASSOPTIONcompsoc
  % The Computer Society usually uses the plural form
  \section*{Acknowledgments}
\else
  % regular IEEE prefers the singular form
  \section*{Acknowledgment}
\fi

The authors would like to thank...

% Can use something like this to put references on a page
% by themselves when using endfloat and the captionsoff option.
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}

% biography section
% 
% If you have an EPS/PDF photo (graphicx package needed) extra braces are
% needed around the contents of the optional argument to biography to prevent
% the LaTeX parser from getting confused when it sees the complicated
% \includegraphics command within an optional argument. (You could create
% your own custom macro containing the \includegraphics command to make things
% simpler here.)
%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
% or if you just want to reserve a space for a photo:

\begin{IEEEbiography}{Michael Shell}
Biography text here.
\end{IEEEbiography}

% if you will not have a photo at all:
\begin{IEEEbiographynophoto}{John Doe}
Biography text here.
\end{IEEEbiographynophoto}

% insert where needed to balance the two columns on the last page with
% biographies
%\newpage

\begin{IEEEbiographynophoto}{Jane Doe}
Biography text here.
\end{IEEEbiographynophoto}

% You can push biographies down or up by placing
% a \vfill before or after them. The appropriate
% use of \vfill depends on what kind of text is
% on the last page and whether or not the columns
% are being equalized.

%\vfill

% Can be used to pull up biographies so that the bottom of the last one
% is flush with the other column.
%\enlargethispage{-5in}

% that's all folks
\end{document}

### 2019-08-02 paper.tex
fix references

@@
 
-\subsection{Subsection Heading Here}
-Subsection text here.
+\section{Background}
+\label{sec:background}
 
-% needed in second column of first page if using \IEEEpubid
-%\IEEEpubidadjcol
+\IEEEPARstart{A}{s} smartphones and mobile technology becomes more prevalent,
+new forms of human-computer interaction are becoming mainstream. Smartphones
+allow for an unprecedented degree of connectivity with the digital world, but
+can also serve as a tool for enhancing the physical world. In this section we
+explain the origins and uses of some of this technology \cite{carroll2007}.
 
@@
 \section{Conclusion}
+\label{sec:conclusion}
 The conclusion goes here.
@@
 % http://www.michaelshell.org/tex/ieeetran/bibtex/
-%\bibliographystyle{IEEEtran}
+\bibliographystyle{IEEEtran}
 % argument is your BibTeX string definitions and bibliography database(s)
-%\bibliography{IEEEabrv,../bib/paper}
+\bibliography{IEEEabrv,references}
 %
@@
 % (used to reserve space for the reference number labels box)
-\begin{thebibliography}{1}
+%\begin{thebibliography}{1}
 
-\bibitem{IEEEhowto:kopka}
-H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
+%\bibitem{IEEEhowto:kopka}
+%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
+  %0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
 
-\end{thebibliography}
+%\end{thebibliography}
 

### 2019-08-29 paper.tex
more writing about editour and frameworks

@@
-%% bare_jrnl_compsoc.tex
-%% V1.4b
-%% 2015/08/26
-%% by Michael Shell
-%% See:
-%% http://www.michaelshell.org/
-%% for current contact information.
-%%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
-%% Computer Society journal paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/pkg/ieeetran
-%% and
-%% http://www.ieee.org/
+\documentclass[a4paper, 10pt, american, titlepage]{article}
 
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE! 
-%% User assumes all risk.
-%% In no event shall the IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
-%%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
-%%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%*************************************************************************
+% useful packages
+\usepackage[utf8]{inputenc}
+\usepackage{minted}
+\usepackage[american]{babel}
+\usepackage{csquotes}
+\usepackage{graphicx} % for images
 
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. The IEEE's font choices and paper sizes can   ***
-% *** trigger bugs that do not appear when using other class files.       ***                          ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
+\usepackage{lipsum}   % lorem-ipsum placeholder text
+\usepackage{bookmark} % links to other parts of the PDF
+%\usepackage{minted}
+% if we want to use a different style, here are some to look at
+% https://www.overleaf.com/learn/latex/Biblatex_bibliography_styles
+\usepackage[backend=biber,style=numeric]{biblatex}
+\usepackage[page, titletoc, title]{appendix}
+\usepackage[margin=1in]{geometry} % set 1in margins
+\usepackage{hyperref}      % hyperlinks
 
-\documentclass[10pt,journal,compsoc]{IEEEtran}
-%
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[10pt,journal,compsoc]{../sty/IEEEtran}
-
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
-\usepackage{lipsum}
-
-% *** MISC UTILITY PACKAGES ***
-%
-%\usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/pkg/ifpdf
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
-
-% *** CITATION PACKAGES ***
-%
-\ifCLASSOPTIONcompsoc
-  % IEEE Computer Society needs nocompress option
-  % requires cite.sty v4.0 or later (November 2003)
-  \usepackage[nocompress]{cite}
-\else
-  % normal IEEE
-  \usepackage{cite}
-\fi
-% cite.sty was written by Donald Arseneau
-% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
-% \cite{} output to follow that of the IEEE. Loading the cite package will
-% result in citation numbers being automatically sorted and properly
-% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
-% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
-% \cite will automatically add leading space, if needed. Use cite.sty's
-% noadjust option (cite.sty V3.8 and later) if you want to turn this off
-% such as if a citation ever needs to be enclosed in parenthesis.
-% cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 5.0 (2009-03-20) and later if using hyperref.sty.
-% The latest version can be obtained at:
-% http://www.ctan.org/pkg/cite
-% The documentation is contained in the cite.sty file itself.
-%
-% Note that some packages require special options to format as the Computer
-% Society requires. In particular, Computer Society  papers do not use
-% compressed citation ranges as is done in typical IEEE papers
-% (e.g., [1]-[4]). Instead, they list every citation separately in order
-% (e.g., [1], [2], [3], [4]). To get the latter we need to load the cite
-% package with the nocompress option which is supported by cite.sty v4.0
-% and later. Note also the use of a CLASSOPTION conditional provided by
-% IEEEtran.cls V1.7 and later.
-
-% *** GRAPHICS RELATED PACKAGES ***
-%
-\ifCLASSINFOpdf
-  % \usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-\else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-  % will default to the driver specified in the system graphics.cfg if no
-  % driver is specified.
-  % \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../eps/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.eps}
-\fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation
-% can be obtained at: 
-% http://www.ctan.org/pkg/graphicx
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found at:
-% http://www.ctan.org/pkg/epslatex
-%
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
-%
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
-
-% *** MATH PACKAGES ***
-%
-%\usepackage{amsmath}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics.
-%
-% Note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/amsmath
-
-% *** SPECIALIZED LIST PACKAGES ***
-%
-%\usepackage{algorithmic}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/pkg/algorithms
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/pkg/algorithmicx
-
-% *** ALIGNMENT PACKAGES ***
-%
-%\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/array
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-% *** SUBFIGURE PACKAGES ***
-%\ifCLASSOPTIONcompsoc
-%  \usepackage[caption=false,font=footnotesize,labelfont=sf,textfont=sf]{subfig}
-%\else
-%  \usepackage[caption=false,font=footnotesize]{subfig}
-%\fi
-% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
-% for subfigure.sty, the latter of which is no longer maintained and is
-% incompatible with some LaTeX packages including fixltx2e. However,
-% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
-% which will override IEEEtran.cls' handling of captions and this will result
-% in non-IEEE style figure/table captions. To prevent this problem, be sure
-% and invoke subfig.sty's "caption=false" package option (available since
-% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
-% handling of captions.
-% Note that the Computer Society format requires a sans serif font rather
-% than the serif font used in traditional IEEE formatting and thus the need
-% to invoke different subfig.sty package options depending on whether
-% compsoc mode has been enabled.
-%
-% The latest version and documentation of subfig.sty can be obtained at:
-% http://www.ctan.org/pkg/subfig
-
-% *** FLOAT PACKAGES ***
-%
-%\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure.
-% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
-% corrections already built into the system in which case a warning will
-% be issued if an attempt is made to load fixltx2e.sty as it is no longer
-% needed.
-% The latest version and documentation can be found at:
-% http://www.ctan.org/pkg/fixltx2e
-
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/stfloats
-% Do not use the stfloats baselinefloat ability as the IEEE does not allow
-% \baselineskip to stretch. Authors submitting work to the IEEE should note
-% that the IEEE rarely uses double column equations and that authors should try
-% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
-% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
-% such ways.
-% Do not attempt to use stfloats with fixltx2e as they are incompatible.
-% Instead, use Morten Hogholm'a dblfloatfix which combines the features
-% of both fixltx2e and stfloats:
-%
-% \usepackage{dblfloatfix}
-% The latest version can be found at:
-% http://www.ctan.org/pkg/dblfloatfix
-
-%\ifCLASSOPTIONcaptionsoff
-%  \usepackage[nomarkers]{endfloat}
-% \let\MYoriglatexcaption\caption
-% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
-%\fi
-% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
-% Axel Sommerfeldt. This package may be useful when used in conjunction with 
-% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
-% submissions have lists of figures/tables at the end of the paper and that
-% figures/tables without any captions are placed on a page by themselves at
-% the end of the document. If needed, the draftcls IEEEtran class option or
-% \CLASSINPUTbaselinestretch interface can be used to increase the line
-% spacing as well. Be sure and use the nomarkers option of endfloat to
-% prevent endfloat from "marking" where the figures would have been placed
-% in the text. The two hack lines of code above are a slight modification of
-% that suggested by in the endfloat docs (section 8.4.1) to ensure that
-% the full captions always appear in the list of figures/tables - even if
-% the user used the short optional argument of \caption[]{}.
-% IEEE papers do not typically make use of \caption[]'s optional argument,
-% so this should not be an issue. A similar trick can be used to disable
-% captions of packages such as subfig.sty that lack options to turn off
-% the subcaptions:
-% For subfig.sty:
-% \let\MYorigsubfloat\subfloat
-% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
-% However, the above trick will not work if both optional arguments of
-% the \subfloat command are used. Furthermore, there needs to be a
-% description of each subfigure *somewhere* and endfloat does not add
-% subfigure captions to its list of figures. Thus, the best approach is to
-% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
-% and instead reference/explain all the subfigures within the main caption.
-% The latest version of endfloat.sty and its documentation can obtained at:
-% http://www.ctan.org/pkg/endfloat
-%
-% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
-% later in the document, say, to conditionally put the References on a 
-% page by themselves.
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
-%\usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/url
-% Basically, \url{my_url_here}.
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
+% more breathing room
+\linespread{1.5}
+\setminted{fontsize=\small,baselinestretch=1}
 
@@
 
+% stuff for LaTeX to know
+\bibliography{references}
+\graphicspath{ {./images/} } % put images in here
+\title{Kyoto VR MQP Paper First Draft}
+\author{William~Campbell, Cole~Granof, and Joseph~Petitti}
+\date{\today}
+
+% call it "Table of Contents" instead of just "Contents"
+\addto{\captionsamerican}{\renewcommand*{\contentsname}{Table of Contents}}
+
 \begin{document}
-%
-% paper title
-% Titles are generally capitalized except for words such as a, an, and, as,
-% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
-% not capitalized unless they are the first or last word of the title.
-% Linebreaks \\ can be used within to get better formatting as desired.
-% Do not put math or special symbols in the title.
-\title{Sample \LaTeX Template for Kyoto VR MQP}
-%
-%
-% author names and IEEE memberships
-% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
-% a structure at a ~ so this keeps an author's name from being broken across
-% two lines.
-% use \thanks{} to gain access to the first footnote area
-% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
-% was not built to handle multiple paragraphs
-%
-%
-%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
-% lists the Computer Society journals use for "first footnote" author
-% affiliations. Use \IEEEcompsocthanksitem which works much like \item
-% for each affiliation group. When not in compsoc mode,
-% \IEEEcompsocitemizethanks becomes like \thanks and
-% \IEEEcompsocthanksitem becomes a line break with idention. This
-% facilitates dual compilation, although admittedly the differences in the
-% desired content of \author between the different types of papers makes a
-% one-size-fits-all approach a daunting prospect. For instance, compsoc 
-% journal papers have the author affiliations above the "Manuscript
-% received ..."  text while in non-compsoc journals this is reversed. Sigh.
 
-\author{William~Campbell, Cole~Granof, and Joseph~Petitti}
+% set page numbers to Roman for the forematter (before the introduction)
+\pagenumbering{roman}
 
-% note the % following the last \IEEEmembership and also \thanks - 
-% these prevent an unwanted space from occurring between the last author name
-% and the end of the author line. i.e., if you had this:
-% 
-% \author{....lastname \thanks{...} \thanks{...} }
-%                     ^------------^------------^----Do not want these spaces!
-%
-% a space would be appended to the last name and could cause every name on that
-% line to be shifted left slightly. This is one of those "LaTeX things". For
-% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
-% "AB" then you have to do: "\textbf{A}\textbf{B}"
-% \thanks is no different in this regard, so shield the last } of each \thanks
-% that ends a line with a % and do not let a space in before the next \thanks.
-% Spaces after \IEEEmembership other than the last one are OK (and needed) as
-% you are supposed to have spaces between the names. For what it is worth,
-% this is a minor point as most people would not even notice if the said evil
-% space somehow managed to creep in.
+\maketitle
 
-% The paper headers
-\markboth{Worcester Polytechnic Institute Major Qualifying Project}%
-{Sample \LaTeX Template for Kyoto VR MQP}
-% The only time the second header will appear is for the odd numbered pages
-% after the title page when using the twoside option.
-% 
-% *** Note that you probably will NOT want to include the author's ***
-% *** name in the headers of peer review papers.                   ***
-% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
-% you desire.
-
-% The publisher's ID mark at the bottom of the page is less important with
-% Computer Society journal papers as those publications place the marks
-% outside of the main text columns and, therefore, unlike regular IEEE
-% journals, the available text space is not reduced by their presence.
-% If you want to put a publisher's ID mark on the page you can do it like
-% this:
-%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
-% or like this to get the Computer Society new two part style.
-%\IEEEpubid{\makebox[\columnwidth]{\hfill 0000--0000/00/\$00.00~\copyright~2015 IEEE}%
-%\hspace{\columnsep}\makebox[\columnwidth]{Published by the IEEE Computer Society\hfill}}
-% Remember, if you use this you must call \IEEEpubidadjcol in the second
-% column for its text to clear the IEEEpubid mark (Computer Society jorunal
-% papers don't need this extra clearance.)
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
-
-% for Computer Society papers, we must declare the abstract and index terms
-% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
-% command as these need to go into the title area created by \maketitle.
-% As a general rule, do not put math, special symbols or citations
-% in the abstract or keywords.
-\IEEEtitleabstractindextext{%
 \begin{abstract}
-The abstract goes here.
 \end{abstract}
 
-% Note that keywords are not normally used for peerreview papers.
-\begin{IEEEkeywords}
-Computer Society, IEEE, IEEEtran, journal, \LaTeX, paper, template.
-\end{IEEEkeywords}}
+\section*{Acknowledgments}
+\label{sec:acknowledgements}
+\addcontentsline{toc}{section}{Acknowledgments}
 
-% make the title area
-\maketitle
+\clearpage
 
-% To allow for easy dual compilation without having to reenter the
-% abstract/keywords data, the \IEEEtitleabstractindextext text will
-% not be used in maketitle, but will appear (i.e., to be "transported")
-% here as \IEEEdisplaynontitleabstractindextext when the compsoc 
-% or transmag modes are not selected <OR> if conference mode is selected 
-% - because all conference papers position the abstract like regular
-% papers do.
-\IEEEdisplaynontitleabstractindextext
-% \IEEEdisplaynontitleabstractindextext has no effect when using
-% compsoc or transmag under a non-conference mode.
+\section*{Executive Summary}
+\label{sec:executiveSummary}
+\addcontentsline{toc}{section}{Executive Summary}
 
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
+\clearpage
 
-\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
-% Computer Society journal (but not conference!) papers do something unusual
-% with the very first section heading (almost always called "Introduction").
-% They place it ABOVE the main text! IEEEtran.cls does not automatically do
-% this for you, but you can achieve this effect with the provided
-% \IEEEraisesectionheading{} command. Note the need to keep any \label that
-% is to refer to the section immediately after \section in the above as
-% \IEEEraisesectionheading puts \section within a raised box.
+% now comes the table of contents, list of figures, and list of tables
+% these should be single spaced
+{
+\linespread{1}
 
-% The very first letter is a 2 line initial drop letter followed
-% by the rest of the first word in caps (small caps for compsoc).
-% 
-% form to use if the first word consists of a single letter:
-% \IEEEPARstart{A}{demo} file is ....
-% 
-% form to use if you need the single drop letter followed by
-% normal text (unknown if ever used by the IEEE):
-% \IEEEPARstart{A}{}demo file is ....
-% 
-% Some journals put the first two words in caps:
-% \IEEEPARstart{T}{his demo} file is ....
-% 
-% Here we have the typical use of a "T" for an initial drop letter
-% and "HIS" in caps to complete the first word.
-\IEEEPARstart{T}{his} demo file is intended to serve as a ``starter file''
-for IEEE Computer Society journal papers produced under \LaTeX\ using
-IEEEtran.cls version 1.8b and later.
-% You must have at least 2 lines in the paragraph with the drop letter
-% (should never be an issue)
-I wish you the best of success.
+% add table of contents to itself
+\addcontentsline{toc}{section}{Table of Contents}
+\tableofcontents
+\newpage
 
-\hfill mds
+\addcontentsline{toc}{section}{List of Figures}
+\listoffigures
+\newpage
 
-\hfill August 26, 2015
+% we don't have any tables yet, but uncomment this when we do
+%\addcontentsline{toc}{section}{List of Tables}
+%\listoftables
+%\newpage
+}
+
+% go back to 1.5 spacing and Arabic numbering for the rest of the paper
+\pagenumbering{arabic}
+
+\section{Introduction}
+\label{sec:introduction}
 
@@
 
-\IEEEPARstart{A}{s} smartphones and mobile technology becomes more prevalent,
+As smartphones and mobile technology becomes more prevalent,
 new forms of human-computer interaction are becoming mainstream. Smartphones
@@
 can also serve as a tool for enhancing the physical world. In this section we
-explain the origins and uses of some of this technology \cite{carroll2007}.
+explain the origins and uses of some of this technology.
 
-\subsubsection{Subsubsection Heading Here}
-Subsubsection text here.
+\subsection{What is Augmented Reality?}
+\label{sec:whatIsAugmentedReality}
 
-% An example of a floating figure using the graphicx package.
-% Note that \label must occur AFTER (or within) \caption.
-% For figures, \caption should occur after the \includegraphics.
-% Note that IEEEtran v1.7 and later has special internal code that
-% is designed to preserve the operation of \label within \caption
-% even when the captionsoff option is in effect. However, because
-% of issues like this, it may be the safest practice to put all your
-% \label just after \caption rather than within \caption{}.
-%
-% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
-% option should be used if it is desired that the figures are to be
-% displayed while in draft mode.
-%
-%\begin{figure}[!t]
-%\centering
-%\includegraphics[width=2.5in]{myfigure}
-% where an .eps filename suffix will be assumed under latex, 
-% and a .pdf suffix will be assumed for pdflatex; or what has been declared
-% via \DeclareGraphicsExtensions.
-%\caption{Simulation results for the network.}
-%\label{fig_sim}
-%\end{figure}
+Augmented Reality, or AR, is a type of human-computer interface where
+perceptions of the real world are enhanced by computer-generated information.
+This differs from Virtual Reality (VR), in that a VR experience consists
+exclusively of virtual information. In AR, virtual information is mixed with
+sensory input from the real world~\autocite{carmigniani2011}. This can enhance
+the user's perception of reality by providing information that would be
+difficult or impossible to display through traditional means.
 
-% Note that the IEEE typically puts floats only at the top, even when this
-% results in a large percentage of a column being occupied by floats.
-% However, the Computer Society has been known to put floats at the bottom.
+For example, AR can be used to display information about historical events,
+places, and objects overlaid onto images of the real world~\autocite{saenz2009}.
+This provides the user with useful information without needing to alter the real
+historic site.
 
-% An example of a double column floating figure using two subfigures.
-% (The subfig.sty package must be loaded for this to work.)
-% The subfigure \label commands are set within each subfloat command,
-% and the \label for the overall figure must come after \caption.
-% \hfil is used as a separator to get equal spacing.
-% Watch out that the combined width of all the subfigures on a 
-% line do not exceed the text width or a line break will occur.
-%
-%\begin{figure*}[!t]
-%\centering
-%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
-%\label{fig_first_case}}
-%\hfil
-%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
-%\label{fig_second_case}}
-%\caption{Simulation results for the network.}
-%\label{fig_sim}
-%\end{figure*}
-%
-% Note that often IEEE papers with subfigures do not employ subfigure
-% captions (using the optional argument to \subfloat[]), but instead will
-% reference/describe all of them (a), (b), etc., within the main caption.
-% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
-% labels, the optional argument to \subfloat must be present. If a
-% subcaption is not desired, just leave its contents blank,
-% e.g., \subfloat[].
+\subsubsection{Current Augmented Reality Technology}
+\label{sec:currentAugmentedRealityTechnology}
 
-% An example of a floating table. Note that, for IEEE style tables, the
-% \caption command should come BEFORE the table and, given that table
-% captions serve much like titles, are usually capitalized except for words
-% such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
-% and up, which are usually not capitalized unless they are the first or
-% last word of the caption. Table text will default to \footnotesize as
-% the IEEE normally uses this smaller font for tables.
-% The \label must come after \caption as always.
-%
-%\begin{table}[!t]
-%% increase table row spacing, adjust to taste
-%\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-%\caption{An Example of a Table}
-%\label{table_example}
-%\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-%\begin{tabular}{|c||c|}
-%\hline
-%One & Two\\
-%\hline
-%Three & Four\\
-%\hline
-%\end{tabular}
-%\end{table}
+While preparing for this project our team researched the current state of
+augmented reality technology. Smartphones are the most commonly used AR
+hardware by far [citation needed]. Typically smartphone AR applications make
+use of the phone's camera, accelerometer, gyroscope, and GPS sensors to
+reproduce a view of the real world with virtual information layered on top of
+it~\autocite{bonsor2018}.
 
-% Note that the IEEE does not put floats in the very first column
-% - or typically anywhere on the first page for that matter. Also,
-% in-text middle ("here") positioning is typically not used, but it
-% is allowed and encouraged for Computer Society conferences (but
-% not Computer Society journals). Most IEEE journals/conferences use
-% top floats exclusively. 
-% Note that, LaTeX2e, unlike IEEE journals/conferences, places
-% footnotes above bottom floats. This can be corrected via the
-% \fnbelowfloat command of the stfloats package.
+\subsection{Augmented Reality Use Cases}
+\label{sec:augmentedRealityUseCases}
+
+Even though it is still a developing technology, augmented reality has been used
+in many disparate disciplines, including data
+visualization~\autocite{resnick2017}, commerce~\autocite{matney2018},
+marketing~\autocite{sharma2015}, education~\autocite{stewart-smith2012}, visual
+art~\autocite{katz2018}, and even archaeology~\autocite{eve2012}.
+
+\subsection{Challenges of Augmented Reality}
+\label{sec:challengesOfAugmentedReality}
+
+\subsection{Apps for Art and Culture}
+\label{sec:appsForArtAndCulture}
+
+\subsubsection{izi.TRAVEL}
+\label{sec:iziTravel}
+
+\subsection{Platforms}
+\label{sec:platforms}
+
+\subsubsection{ARCore and ARKit}
+\label{sec:ARCoreAndARKit}
+
+ARKit and ARCore are both AR frameworks that enable apps to take advantage of
+powerful AR related features. ARKit is developed by Apple and can only be used
+by iPhones. Google's ARCore framework can deploy to both Android and iPhone.
+Many cross platform solutions will leverage the full potential of their target
+platform by using either ARKit or ARCore "under the hood". Both ViroReact and
+Vuforia use ARKit or ARCore depending on the target platform
+\autocites{vuforiaFusion}{moon2018}.
+
+ARKit 3 aims to support a wide array of new features, and will be available in
+iOS 13. Notably, one of these features is "people occlusion," which will allow
+virtual objects to be realistically obscured when someone walks in front of the
+object~\autocite{apple2019}. This kind of technology could be useful for us
+since our app uses AR in crowded places.  As of August, 2019, this feature is
+not on the horizon for Google's Android AR framework, ARCore.
+
+Both ARKit and ARCore have well-supported APIs for Unity. ARKit 3 support is
+coming to Unity, along with all of the advanced features that it
+brings~\autocite{stinson2019}.
+
+\subsubsection{Wikitude}
+\label{sec:wikitude}
+
+\subsubsection{KudanSlam}
+\label{sec:kudanSlam}
+
+\subsubsection{Unity}
+\label{sec:unity}
+
+\subsubsection{Viro AR}
+\label{sec:viroAR}
+
+Viro AR comes in two flavors: ViroReact and ViroCore. ViroCore allows
+developers to build an AR Application with Java. The disadvantage of this is
+that ViroCore only allows developers to target Android, which unfortunately
+made ViroCore not an option for our project. ViroReact is the cross-platform
+option for ViroAR. ViroReact leverages the cross-platform capabilities of
+React, which is Facebook's Javascript Library for developing user
+interfaces~\autocite{facebook2019}.
+
+Since our project is not a game, we initially wanted to avoid using a
+fully-featured game engine. Therefore, we decided to take the time to explore
+this framework since it appeared to be more tailored to our specific use case.
+Viro Media also recognizes that all developers who wish to create an app with
+3D capabilities are not necessarily game developers. Viro Media pitches Viro
+AR as ``The perfect alternative to specialized game engines, ViroAR is a
+platform for rapidly building ARKit and ARCore apps. Our platform allows
+developers to focus on what they do best by leveraging familiar tools and
+frameworks used in mobile application development''~\autocite{viro2019}.
+While the majority of our team has decent experience with writing Javascript,
+we all either have very little or no experience writing React apps.
+
+In most development scenarios, every time you wish to test your app on actual
+hardware, you must first compile your app using either Xcode or Android Studio
+depending on your platform. Once you have built the app, your device needs to
+install the app. This process can be very time consuming, especially since
+frequent tests on real hardware is important for something as intensive as
+AR.
+
+An alternative to building your app is to run your app through an emulator on
+the computer you are using for development [citation needed on what an emulator
+is]. Since an emulator uses software to emulate hardware, this poses two
+technical issues that prevent emulators from being a proper replacement for
+testing on real hardware.  Emulation is often imperfect, so glitches often
+emerge in emulation that do not manifest on the actual hardware [citation
+needed about emulator inaccuracies]. Secondly, (and most importantly for AR,)
+it is common for emulation to be much slower compared to real hardware.
+
+ViroReact offers a convenient ``test bed'' for rapidly testing your ViroReact
+app on native hardware. In the root directory of your project, you can launch
+a Node server with the command \texttt{npm start}. From here, you can input
+the provided URL into the Viro Media app. This will quickly download the code,
+graphics and 3D object files from the server and launch a functional version
+of the app \autocite{viro-testbed2019}. This allowed us to get a real AR app
+up and running on our devices much more easily than any of the other
+frameworks/engines we explored. Unfortunately, the test bed app was somewhat
+unreliable based on our experience; the test bed would frequently crash,
+or would not be able to download the files from the Node server. The most
+reliable way to test our app was to compile a binary and manually install it
+onto our devices, which completely defeats the purpose of the test bed app.
+
+\subsubsection{motive.io}
+\label{sec:motive.io}
+
+\section{Editour: The Tour Editor}
+\label{sec:editour}
+
+The goal of Editour is to allow a non-technical user to design audio tours
+through a web-app. At its core, Editour is a tool to draw arbitarily-shaped
+geographic regions onto a map. An audio file and multiple image files can be
+uploaded for each region the user defines. After naming and uploading the tour
+with the "Upload" button, our backend builds a zip containing a folder that can
+be placed directly into the Unity project.
+
+Our backend allows users to save their tours to our server, and load those same
+tours back into the editor to resume work.  The geographic area of each region
+can be adjusted by clicking and dragging. Vertices can also be added and
+deleted if the needs of the tour change over time.
+
+\subsection{The Need for an Editor}
+
+One of the goals for our project is to create a working prototype that others
+can build off of in the future [citation needed for personal communication].
+
+Similar to the app izi.TRAVEL discussed in section~\ref{sec:iziTravel}, we
+needed some way to easily define arbitrary polygons (which we call ``regions'')
+and associate media with each one, such as audio and image files.
+
+For testing purposes, we initially defined these regions directly in the C\#
+Scripts, hard-coding the coordinates. [citation needed for source used to
+write polygon detection code] Below is an example of a quadrilateral
+surrounding the Creation Core building at the Ritsumeikan Biwako-Kusatsu
+campus.
+
+\begin{minted}{csharp}
+Regions.add(new GPSPolygon(new List<GPSPoint>{
+    new GPSPoint(34.979222, 135.963628),
+    new GPSPoint(34.979187, 135.965130),
+    new GPSPoint(34.979794, 135.965053),
+    new GPSPoint(34.979754, 135.963669)
+}, "Creation Core"));
+\end{minted}
+
+Even with knowledge of C\# and Unity, inputing tour data this way is obviously
+not convenient. Atticus reminded us that, although he has a working knowledge
+of Unity, he is not a software developer [citation needed for personal
+communication.] In order to make our app prototype at all useful for the
+future, we needed to provide an easy way to ``design'' a tour.
+
+\subsection{A Complete Tour Definition}
+\label{sec:tourDefinition}
+
+In order to create a fully-functional editor for designing and exporting
+``tours,'' we had to consider how to fully define a tour purely in terms
+of text and a directory of associated media.
+
+Here is an example of the JSON metadata generated by Editour:
+
+\begin{minted}{json}
+{
+   "regions": [
+      {
+         "name": "Beautiful Place",
+         "points": [ {"lat": 23.4, "lng": 56.7}, /* list omitted for brevity */ ],
+         "audio": [ "beautiful-audio.mp3" ],
+         "images": [ "mountain.jpg", "stream.jpg" ]
+      },
+      {
+         "name": "Gorgeous Place",
+         "points": [ {"lat": 12.3, "lng": 45.6}, /* list omitted for brevity */ ],
+         "audio": [ "gorgeous-audio.mp3" ],
+         "images": [ "hill.jpg", "valley.jpg", "gorge.jpg" ]
+      }
+   ]
+}
+\end{minted}
+
+Within each object in the region list, we can see that the region has four
+properties: a name, a list of coordinates, a list of audio files, and a list of
+multiple image files. (In the current design of the app, it only makes sense to
+associate one audio file per region, but the format makes it easy to
+accommodate for multiple audio files in the future.) One disadvantage is that
+all media files have to have unique names. This is because the zip that is
+created by the editour backend contains all of the media files in a flat file
+structure. The above JSON is used to associate each media file with a region,
+meaning that the filename needs to act as a primary key. The backend will
+respond with a message if this is the case, prompting the user to have unique
+names for all files.
+
+\subsection{Editour Backend}
+\label{sec:editourBackend}
+
+The server-side backend of the Editour application is written in JavaScript for
+Node.js. This backend both serves the static frontend content and runs
+server-side scripts that process incoming API requests. When a user submits a
+new tour from the web application, the files and metadata are sent to the server
+running the Node.js scripts, which zips up the files and saves them to the
+server's disk with a timestamp. Then any application can request a particular
+tour and the backend will serve the most recent version of it.
+
+We chose Node.js as the server-side framework because of our prior experience
+with JavaScript, its high-performing asynchronous architecture, and its ease of
+development.
+
+\subsubsection{Future of Editour}
+\label{sec:futureOfEditour}
+
+In the current implementation, the tour file generated by the Editour backend
+still has to be moved manually to the Unity project folder. In the future, we
+would like the app to be able to contact our Editour server and update the tour
+info by itself. This would allow Kyoto VR to update the tours without updating
+the entire app.
+
+The design of the Editour is agnostic about how the media will be used.  For
+an app like izi.TRAVEL, the images are displayed when the associated audio
+tour is playing. For ARuku, images can be placed onto the ground plane by the
+user, which is unique compared to other audio tour guide apps. The tour files
+produced by Editour could theoretically be used by a tour guide app that does
+not incorporate AR.
+
+\section{Implementation and Technology}
+\label{sec:implementationAndTechnology}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{turtle-burger.jpg}
+	\caption{A rare but delicious turtle burger in the wild.}
+	\label{fig:turtleBurger}
+\end{figure}
+
+\section{Testing}
+\label{sec:testing}
+
+See Figure~\ref{fig:turtleBurger} for more details.
 
@@
 \label{sec:conclusion}
-The conclusion goes here.
 
-% if have a single appendix:
-%\appendix[Proof of the Zonklar Equations]
-% or
-%\appendix  % for no appendix heading
-% do not use \section anymore after \appendix, only \section*
-% is possibly needed
+\clearpage % references should be on their own page
 
-% use appendices with more than one appendix
-% then use \section to start each appendix
-% you must declare a \section before using any
-% \subsection or using \label (\appendices by itself
-% starts a section numbered zero.)
-%
+\printbibliography
+\addcontentsline{toc}{section}{References}
+
+\newpage
 
@@
 
-% you can choose not to have a title for an appendix
-% if you want by leaving the argument blank
 \section{}
@@
 
-% use section* for acknowledgment
-\ifCLASSOPTIONcompsoc
-  % The Computer Society usually uses the plural form
-  \section*{Acknowledgments}
-\else
-  % regular IEEE prefers the singular form
-  \section*{Acknowledgment}
-\fi
-
-The authors would like to thank...
-
-% Can use something like this to put references on a page
-% by themselves when using endfloat and the captionsoff option.
-\ifCLASSOPTIONcaptionsoff
-  \newpage
-\fi
-
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
-
-% references section
-
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
-\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-\bibliography{IEEEabrv,references}
-%
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
-%\begin{thebibliography}{1}
-
-%\bibitem{IEEEhowto:kopka}
-%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-  %0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
-
-%\end{thebibliography}
-
-% biography section
-% 
-% If you have an EPS/PDF photo (graphicx package needed) extra braces are
-% needed around the contents of the optional argument to biography to prevent
-% the LaTeX parser from getting confused when it sees the complicated
-% \includegraphics command within an optional argument. (You could create
-% your own custom macro containing the \includegraphics command to make things
-% simpler here.)
-%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
-% or if you just want to reserve a space for a photo:
-
-\begin{IEEEbiography}{Michael Shell}
-Biography text here.
-\end{IEEEbiography}
-
-% if you will not have a photo at all:
-\begin{IEEEbiographynophoto}{John Doe}
-Biography text here.
-\end{IEEEbiographynophoto}
-
-% insert where needed to balance the two columns on the last page with
-% biographies
-%\newpage
-
-\begin{IEEEbiographynophoto}{Jane Doe}
-Biography text here.
-\end{IEEEbiographynophoto}
-
-% You can push biographies down or up by placing
-% a \vfill before or after them. The appropriate
-% use of \vfill depends on what kind of text is
-% on the last page and whether or not the columns
-% are being equalized.
-
-%\vfill
-
-% Can be used to pull up biographies so that the bottom of the last one
-% is flush with the other column.
-%\enlargethispage{-5in}
-
-% that's all folks
 \end{document}

### 2019-08-29 paper.tex
add more use cases

@@
 % add table of contents to itself
+\tableofcontents
 \addcontentsline{toc}{section}{Table of Contents}
-\tableofcontents
 \newpage
 
+\listoffigures
 \addcontentsline{toc}{section}{List of Figures}
-\listoffigures
 \newpage
@@
 
-\subsubsection{Current Augmented Reality Technology}
+\subsection{Current Augmented Reality Technology}
 \label{sec:currentAugmentedRealityTechnology}
@@
 art~\autocite{katz2018}, and even archaeology~\autocite{eve2012}.
+
+The video game industry has readily embraced augmented reality, leading to the
+development of many AR games for smartphones and dedicated head-mounted
+displays. Perhaps the most popular AR game, \textit{Pokémon Go}, has been
+downloaded over a billion times~\autocite{webster2018}. This game makes use of
+GPS and camera data to overlay game objects (in this case fictional monsters) on
+top of images of the real world (see Figure
+\ref{fig:pokemonGo})~\autocite{concepcion2016}.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=.5\textwidth]{pokemon-go.jpg}
+	\caption{A screenshot from the AR game \textit{Pokémon
+			Go}~\autocite{vastateparks2016}.}
+	\label{fig:pokemonGo}
+\end{figure}
 
@@
 Many cross platform solutions will leverage the full potential of their target
-platform by using either ARKit or ARCore "under the hood". Both ViroReact and
+platform by using either ARKit or ARCore ``under the hood''. Both ViroReact and
 Vuforia use ARKit or ARCore depending on the target platform
@@
 ARKit 3 aims to support a wide array of new features, and will be available in
-iOS 13. Notably, one of these features is "people occlusion," which will allow
+iOS 13. Notably, one of these features is ``people occlusion,'' which will allow
 virtual objects to be realistically obscured when someone walks in front of the
@@
 uploaded for each region the user defines. After naming and uploading the tour
-with the "Upload" button, our backend builds a zip containing a folder that can
+with the ``Upload'' button, our backend builds a zip containing a folder that can
 be placed directly into the Unity project.
@@
 We chose Node.js as the server-side framework because of our prior experience
-with JavaScript, its high-performing asynchronous architecture, and its ease of
-development.
+with JavaScript, its high-performing asynchronous
+architecture~\autocite{orsini2013}, and its ease of development.
 

### 2019-08-29 paper.tex
add more editour backend info

@@
 Node.js. This backend both serves the static frontend content and runs
-server-side scripts that process incoming API requests. When a user submits a
-new tour from the web application, the files and metadata are sent to the server
-running the Node.js scripts, which zips up the files and saves them to the
-server's disk with a timestamp. Then any application can request a particular
-tour and the backend will serve the most recent version of it.
+server-side scripts that process incoming API requests.  We chose Node.js as the
+server-side framework because of our prior experience with JavaScript, its
+high-performing asynchronous architecture~\autocite{orsini2013}, and its ease of
+development.
 
-We chose Node.js as the server-side framework because of our prior experience
-with JavaScript, its high-performing asynchronous
-architecture~\autocite{orsini2013}, and its ease of development.
+When a user submits new tour from the web application, the files and metadata
+are sent to the server running the Node.js scripts, which zips up the files and
+saves them to the server's disk with a timestamp. Then any application can
+request a particular tour and the backend will serve the most recent version of
+it.
+
+Additionally, our web application allows users to edit existing tours. When the
+user requests to edit a tour on the frontend it sends a request to the backend
+server for that tour's metadata file. This file contains information about all
+regions and files in the tour. The user can then edit the regions, change names,
+upload new files, or delete existing ones without ever having to download the
+other tour files from the server, which could take a long time depending on
+their size. When the user is done editing they can upload the new metadata and
+any newly added files to the server, which intelligently collects new and old
+files required by the tour and zips them into a new tour file on the disk.
 
@@
 	\includegraphics[width=\textwidth]{turtle-burger.jpg}
-	\caption{A rare but delicious turtle burger in the wild.}
+	\caption{A rare but delicious turtle burger in the
+		wild~\autocite{harvey2002}.}
 	\label{fig:turtleBurger}

### 2019-08-30 paper.tex
add izi.TRAVEL and images

@@
 \begin{abstract}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{abstract.jpg}
+	% Note: you don't actually need the part in square brackets for the caption,
+	% but if you omit it the regular caption text will be used for the List of
+	% Figures entry.
+	\caption[\textit{Number 1, 1950 (Lavender Mist)}, Jackson Pollock]
+	{\textit{Number 1, 1950 (Lavender Mist)}, Jackson Pollock, National
+		Gallery of Art, Washington, D.C.}
+	\label{fig:abstract}
+\end{figure}
 \end{abstract}
@@
 GPS and camera data to overlay game objects (in this case fictional monsters) on
-top of images of the real world (see Figure
-\ref{fig:pokemonGo})~\autocite{concepcion2016}.
+top of images of the real world~\autocite{concepcion2016} (see Figure
+\ref{fig:pokemonGo}).
 
@@
 	\includegraphics[width=.5\textwidth]{pokemon-go.jpg}
-	\caption{A screenshot from the AR game \textit{Pokémon
-			Go}~\autocite{vastateparks2016}.}
+	\caption[A screenshot from the AR game \textit{Pokémon Go}]{A screenshot
+		from the AR game \textit{Pokémon Go}~\autocite{vastateparks2016}.}
 	\label{fig:pokemonGo}
@@
 
+To explore existing AR apps for art and culture our group researched and tested
+several games, experiences, and platforms related to our project.
+
 \subsubsection{izi.TRAVEL}
 \label{sec:iziTravel}
+
+Before our project started, Kyoto VR was already using an app with a limited
+form of AR for tours. The app, called izi.TRAVEL, allows users to create audio
+tours with audio and image files tied to specific locations in the real
+world~\autocite{izitravel2015} (see Figure \ref{fig:iziTravel}). The app is
+aimed at museums and city tours~\autocite{izitravel}, but can be used for tours
+of historic sites too.  Kyoto VR used the platform to make an audio tour of
+Kinkaku-ji, one of the most popular tourist destinations in
+Japan~\autocite{bornoff2000} and an important historic heritage
+site~\autocite{unesco}.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=.5\textwidth]{izi-travel.jpg}
+	\caption{A screenshot of the izi.TRAVEL app interface}
+	\label{fig:iziTravel}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{kinkakuji.jpg}
+	\caption[The Golden Pavilion of Kinkaku-ji, Kyoto, Japan]{The Golden
+		Pavilion of Kinkaku-ji, Kyoto, Japan~\autocite{davidson2005}}
+	\label{fig:kinkakuji}
+\end{figure}
+
+By using GPS data from the user's phone to play audio and display images at
+specific places in the real world izi.TRAVEL uses a limited form of augmented
+reality. Our group aimed to implement and extend this functionality in our own
+app. See Section \ref{sec:aruku} for more details.
 
@@
 
-\section{Editour: The Tour Editor}
+\section{Implementation and Technology}
+\label{sec:implementationAndTechnology}
+
+\subsection{Editour: The Tour Editor}
 \label{sec:editour}
@@
 
-\subsection{The Need for an Editor}
+\subsubsection{The Need for an Editor}
 
@@
 
-\subsection{A Complete Tour Definition}
+\subsubsection{A Complete Tour Definition}
 \label{sec:tourDefinition}
@@
 
-\subsection{Editour Backend}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{editour.jpg}
+	\caption{A screenshot of the Editour web app frontend}
+	\label{fig:editour}
+\end{figure}
+
+\subsubsection{Editour Backend}
 \label{sec:editourBackend}
@@
 
-\section{Implementation and Technology}
-\label{sec:implementationAndTechnology}
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=\textwidth]{turtle-burger.jpg}
-	\caption{A rare but delicious turtle burger in the
-		wild~\autocite{harvey2002}.}
-	\label{fig:turtleBurger}
-\end{figure}
+\subsection{ARuku}
+\label{sec:aruku}
 
@@
 See Figure~\ref{fig:turtleBurger} for more details.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{turtle-burger.jpg}
+	\caption[A rare but delicious turtle burger in the wild]{A rare but
+		delicious turtle burger in the wild~\autocite{harvey2002}.}
+	\label{fig:turtleBurger}
+\end{figure}
 

### 2019-09-03 paper.tex
challenges of AR development section

@@
 
-As smartphones and mobile technology becomes more prevalent,
+As smartphones and mobile technology become more prevalent,
 new forms of human-computer interaction are becoming mainstream. Smartphones
@@
 perceptions of the real world are enhanced by computer-generated information.
-This differs from Virtual Reality (VR), in that a VR experience consists
+This differs from Virtual Reality (VR) in that a VR experience consists
 exclusively of virtual information. In AR, virtual information is mixed with
@@
 \label{sec:challengesOfAugmentedReality}
+
+As we have said, AR is a new and growing field full of opportunities. But of course,
+as with anything new, our understanding of AR and how to develop for it is limited.
+And with those limitations come challenges. All sorts of different challenges and
+limitations face the development and production of AR apps. Here are some that
+we considered when working on our app.
+
+Many of the applications and use cases that exist for AR right now are, simply put,
+not very good. This means a few different things. For starters, many AR apps and
+features available on smartphones offer very little in the way of functionality or
+practicality; quite simply, they are primarily used for minor spectacles and simple
+tricks~\autocite{theappsolutions2018}. For example, one of the most popular apps
+to use AR, Pokemon GO, primarily uses it's AR feature to place a Pokemon in the
+world aroudn you through your phone camera for you to capture. But when it is in
+the world, it does not interact with anything around it. It just floats a fixed distance
+away from you, simply placed on top of your camera's video feed.
+
+Additionally, in many cases where AR is used, the task could be accomplished as well 
+or better without AR~\autocite{theappsolutions2018}. Returning to the Pokemon GO
+example, when the AR feature is left on while capturing a Pokemon, the extra power
+needed for this feature drains the device faster, makes it harder to hit the Pokemon
+with a Pokeball due to the model drifting in the environment, and can even slow app
+performance, all of which detract from the ability to play and enjoy the game.
+
+One of the biggest problems facing AR development as a whole, and one that we
+ran into as well, is limited hardware. For starters, smartphone cameras present
+a major limitation. Many smartphone cameras only capture images in 2D, which can
+make generating AR content in a 3D world difficult without the use of QR or barcode
+markers~\autocite{geospatialworld2018}. Additionally, GPS sensors on smartphones
+can also be too imprecise for good AR tracking~\autocite{geospatialworld2018}.
+
+The biggest hardware limitation comes from which platform to use. AR apps are most
+commonly designed for smartphones due to their relatively low cost and how accessible
+they are. But, as we just discussed, smartphones come with a host of hardware
+limitations that make achieving satisfying AR capabilities difficult. Additionally, AR apps
+for smartphones tend not to be very user-friendly, and oftentimes even complicate
+the task or activity they were meant to enhance~\autocite{theappsolutions2018}.
+The alternative then is to turn to dedicated hardware, like Microsoft's HoloLens. 
+But dedicated hardware like the HoloLens is very inaccessible and expensive; 
+Microsoft only offers developer editions of the HoloLens, and for the incredibly steep 
+price of \$3,500~\autocite{microsoft2019}.
+
+The challenges we faced during development mirrored these that plague the industry
+as a whole very accurately. We struggled with how exactly we would us AR for our app
+in a way that benefit the experience as a whole, but believe the way we've implemented
+it will enhance the user's experience. Hardware issues were definitely our biggest challenge.
+Only one of our phones is new enough to run AR technology at a decent level, making
+testing of our application difficult.
 

### 2019-09-04 paper.tex
Platforms intro para, Wikitude section

@@
 
-One of the biggest problems facing AR development as a whole, and one that we
+One of the major problems facing AR development as a whole, and one that we
 ran into as well, is limited hardware. For starters, smartphone cameras present
@@
 
+Before we could start working on creating our app, we first needed to decide which
+AR development platform to use. Our preliminary research had shown us that there
+are so many different platforms out there, all of which have been used to create
+great AR apps. There were a lot of things we needed to consider before finalizing
+on a platform, like what features it offered, which devices and operating systems the
+app could run on, and definitely the cost. Detailed below are some of the different
+platforms we considered.
+
 \subsubsection{ARCore and ARKit}
@@
 
+// TODO: Need a way to add Euro character to document; the way they are in now doesn't work
+
+Wikitude is another major AR development kit that is very prevalent in the world
+of AR development. It has over 130,000 registered AR developers, and is powering
+over 30,000 AR apps across smartphones, tablets, and smart glasses~\autocite{wikitude2018}.
+And it's easy to understand why Wikitude has so many registered developers
+when you see the list of features it offers. Some of the features that appealed
+most to us were their Instant Tracking, allowing for augmentation using flat surfaces;
+Image Tracking, allowing for augmentation using one or multiple 2D images; and
+Geo AR, allowing for creation of geo markers at specific locations to triggered AR
+content~\autocite{wikitude2018}.
+
+Wikitude also supports all sorts of different platforms. It supports Android, Apple,
+and Windows phones and tablets, as well as smart glasses like the Epson Moverio,
+Microsoft Hololens, and Vuzix smart glasses~\autocite{wikitude2018}. Additionally,
+many different development frameworks are capable of running Wikitude's SDK.
+According to Wikitude's website, their SDK works with Windows, Android, and iOS
+development frameworks, as well as ARCore and ARKit, Flutter, Cordova, Xamarin,
+and even Unity~\autocite{wikitude2018}.
+
+From all of this information, Wikitude certainly sounds like a fantastic AR development
+platform; it certainly did to us. But the issue we ran into was the cost. Wikitude is, in
+fact, free for eligible startups, but given the criteria they list on their site, we were not
+confident that we would qualify. Aside from this option, Wikitude offers a 30-day demo
+license for €499, which is a lot for use to pay for a license that wouldn't even last for
+our entire project. They also charge €1990 for their SDK Pro, and €2490 for their
+SDK Pro 3D~\autocite{wikitude2018}. Given these prices, and our very limited budget
+of \$0, we knew that we would have to pass on Wikitude and choose a different AR
+development platform.
+
 \subsubsection{KudanSlam}
@@
 
-\subsubsection{Unity}
-\label{sec:unity}
+\subsubsection{motive.io}
+\label{sec:motive.io}
 
@@
 
-\subsubsection{motive.io}
-\label{sec:motive.io}
+\subsubsection{Unity}
+\label{sec:unity}
 

### 2019-09-09 paper.tex
got rid of euro compile issue

@@
 \usepackage{graphicx} % for images
+\usepackage[gen]{eurosym} % for literally just the euro symbol
 
@@
 confident that we would qualify. Aside from this option, Wikitude offers a 30-day demo
-license for €499, which is a lot for use to pay for a license that wouldn't even last for
-our entire project. They also charge €1990 for their SDK Pro, and €2490 for their
+license for \euro{499}, which is a lot for use to pay for a license that would not even last for
+our entire project. They also charge \euro{1990} for their SDK Pro, and \euro{2490} for their
 SDK Pro 3D~\autocite{wikitude2018}. Given these prices, and our very limited budget

### 2019-09-09 paper.tex
got rid of euro TODO
added testing section with figures

@@
 
-// TODO: Need a way to add Euro character to document; the way they are in now doesn't work
-
 Wikitude is another major AR development kit that is very prevalent in the world
@@
 our entire project. They also charge \euro{1990} for their SDK Pro, and \euro{2490} for their
-SDK Pro 3D~\autocite{wikitude2018}. Given these prices, and our very limited budget
-of \$0, we knew that we would have to pass on Wikitude and choose a different AR
+SDK Pro 3D~\autocite{wikitude2018}. Given these prices, and our very limited budget,
+we knew that we would have to pass on Wikitude and choose a different AR
 development platform.
@@
 
-See Figure~\ref{fig:turtleBurger} for more details.
+Our first day of on-site testing with the app took place on September 6th.
+Using Editour, we rebuilt the izi.TRAVEL audio tour that Atticus already
+created. The first version of the rebuilt tour had regions that were relatively
+small; some regions were only a few meters across. This version of the tour can
+be seen in Figure~\ref{fig:kinkakujiTour}.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{kinkakuji-tour.png}
+	\caption[The original version of the Kinkakuji tour]{The original version of
+    the Kinkakuji tour with small regions}
+	\label{fig:kinkakujiTour}
+\end{figure}
+
+Due to concerns about GPS accuracy, we adapted the tour-file \texttt{kinkakuji} to
+create a second, ``chunkier'' tour.  In the tour-file \texttt{kinkakuji-chunkier},
+we expanded all of the regions to accomodate for potential GPS inaccuracies
+that could place the user outside the range of the audio-trigger region.
+Figure~\ref{fig:kinkakujiChunkierTour} depicts the tour that we used for field
+testing at Kinkakuji.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{kinkakuji-chunkier-tour.png}
+	\caption[The ``chunkier'' version of the Kinkakuji tour]{The ``chunkier'' version of
+    the Kinkakuji tour with larger regions}
+	\label{fig:kinkakujiChunkierTour}
+\end{figure}
+
+We tested using two phones at the same time: an iPhone 8 and a Samsung Galaxy
+S7. The iPhone 8 is newer, more powerful and therefore more suited for use with
+AR. We primarily used this phone to test the AR features of the app. Even
+though the Samsung Galaxy had difficulty with basic AR features such as
+ground-plane detection, it was still capable of triggering the audio track
+based on GPS position.
+
+Our previous testing involved creating a ``mock tour'' on the Ritsumeikan campus.
+While this let us know generally which features of the app were working, it was
+very difficult to know how ahead of time how well our app would work at Kinkakuji.
+
+We were surprised by how intuitively each region triggered on the first try.
+With a few exceptions, the audio started when the subject of the audio track
+was in view. During our first walkthrough of Kinkakuji, we triggered every
+region and audio track but one. The region that we missed on the first pass,
+``Final Viewpoint'', requires the user to take a right at a fork in the road
+instead of continuing along the main path. This is not necessarily a problem
+with the design of the regions; instruction provided by the audio tour could
+remedy this, directing the user toward the viewpoint that is off of the main
+path.
+
+Initially, we loaded the app onto the Samsung Galaxy S7 as a backup, since the
+app is not fully functional on a phone that old. At the same time, it was
+informative to take both phones through the tour. Initially, we made the design
+decision to update the GPS location every 60 frames. On a phone running the app
+at full speed, this should happen once every second. Because the Samsung Galaxy
+S7 was having trouble running the app at full speed, the GPS updated far less
+frequently. This was an oversight that would have been difficult to catch if we
+had not tested on hardware below the recommended specifications.
+
+Other bugs resulted from oversights that were difficult to catch with our
+on-campus testing.  For example, we noticed that we forgot to back-up the audio
+slider when entering a new region.  Because of this, when we entered a new
+region when the audio slider was past the endpoint of the new audio track, the
+audio would not play. For example, if the previous audio track were a minute
+long, and if the second track were only thirty seconds long, the app would try
+to play a thirty second audio track from the one minute mark. Since we were
+running the app on phones, we could not easily see when errors were thrown.
+Similarly, if the user were to enter a new region while thirty seconds into the
+previous audio track, the new audio track would start at the thirty second
+mark. During our on-campus testing, we were using songs rather than narration.
+Since the songs were relatively long and not always obvious when they started
+partway through, we did not catch this until we got out to Kinkakuji.  Luckily,
+this was trivial to fix.
 

### 2019-09-09 paper.tex
expanded emulator info and added more sources

@@
 An alternative to building your app is to run your app through an emulator on
-the computer you are using for development [citation needed on what an emulator
-is]. Since an emulator uses software to emulate hardware, this poses two
-technical issues that prevent emulators from being a proper replacement for
-testing on real hardware.  Emulation is often imperfect, so glitches often
-emerge in emulation that do not manifest on the actual hardware [citation
-needed about emulator inaccuracies]. Secondly, (and most importantly for AR,)
-it is common for emulation to be much slower compared to real hardware.
+the computer you are using for development.
+
+According to Techopedia, ``Emulation is the process of imitating a
+hardware/software program/platform on another program or platform. This makes
+it possible to run programs on systems not designed for
+them''~\autocite{techopedia2019}. Emulators are often very useful for speeding
+up development. Loading programs onto the Android emulator usually much faster
+than installing the APK onto the actual device. Additionally, you can mock
+almost all of the important features of an actual Android device, including
+calls, text, GPS position, device rotation and more \autocite{androidemulator}.
+
+Since an emulator uses software to emulate hardware, this poses two technical
+issues that prevent emulators from being a proper replacement for testing on
+real hardware.  Emulation is often imperfect, so glitches sometimes emerge in
+emulation that do not manifest on the actual hardware [citation needed about
+emulator inaccuracies]. Secondly, and most importantly for AR, it is common for
+emulation to be much slower compared to real hardware. In a question submitted
+to \textit{Compute!} magazine asking whether it is possible for a Commodore 64
+to emulate MS-DOS, the editor responded ``Yes, it's possible for a 64 to emulate
+an IBM PC, in the same sense that it's possible to bail out Lake Michigan with
+a teaspoon.'' The editor goes on to explain ``Emulation is a complex business,
+but here's one rule of thumb: The only way to successfully emulate a machine is
+with a much more powerful machine''~\autocite{warick1988}. In our case,
+emulating Android on a desktop operating system is closer to emulating a C64 on
+an IBM PC running MS-DOS (rather than the other way around, thankfully.) The
+moral is that the speed problem facing emulators is just as real as it was in
+1988. Considering that AR already pushes modern phone harware to the limit,
+emulation is not something is not something we wanted to struggle with. On top
+of this, our testing required us to move the camera through the world at
+various speeds and angles, which is simply cumbersome with a webcam and laptop.
 
 ViroReact offers a convenient ``test bed'' for rapidly testing your ViroReact
-app on native hardware. In the root directory of your project, you can launch
-a Node server with the command \texttt{npm start}. From here, you can input
-the provided URL into the Viro Media app. This will quickly download the code,
-graphics and 3D object files from the server and launch a functional version
-of the app \autocite{viro-testbed2019}. This allowed us to get a real AR app
-up and running on our devices much more easily than any of the other
-frameworks/engines we explored. Unfortunately, the test bed app was somewhat
-unreliable based on our experience; the test bed would frequently crash,
-or would not be able to download the files from the Node server. The most
-reliable way to test our app was to compile a binary and manually install it
-onto our devices, which completely defeats the purpose of the test bed app.
+app on native hardware without the need for an emulator. In the root directory
+of your project, you can launch a Node server with the command \texttt{npm
+start}. From here, you can input the provided URL into the Viro Media app. This
+will quickly download the code, graphics and 3D object files from the server
+and launch a functional version of the app \autocite{viro-testbed2019}. This
+allowed us to get a real AR app up and running on our devices much more easily
+than any of the other frameworks/engines we explored. Unfortunately, the test
+bed app was somewhat unreliable based on our experience; the test bed would
+frequently crash, or would not be able to download the files from the Node
+server. The most reliable way to test our app was to compile a binary and
+manually install it onto our devices, which completely defeats the purpose of
+the test bed app.
 

### 2019-09-20 paper.tex
fix prof. cuneo's suggestions
Accepted suggestions from Professor Cuneo's Sep 9 comments. Mostly removing
commas.

@@
 world~\autocite{izitravel2015} (see Figure \ref{fig:iziTravel}). The app is
-aimed at museums and city tours~\autocite{izitravel}, but can be used for tours
+aimed at museums and city tours~\autocite{izitravel} but can be used for tours
 of historic sites too.  Kyoto VR used the platform to make an audio tour of
@@
 
-ARKit 3 aims to support a wide array of new features, and will be available in
+ARKit 3 aims to support a wide array of new features and will be available in
 iOS 13. Notably, one of these features is ``people occlusion,'' which will allow
@@
 object~\autocite{apple2019}. This kind of technology could be useful for us
-since our app uses AR in crowded places.  As of August, 2019, this feature is
+since our app uses AR in crowded places.  As of August 2019, this feature is
 not on the horizon for Google's Android AR framework, ARCore.
@@
 emulation that do not manifest on the actual hardware [citation needed about
-emulator inaccuracies]. Secondly, and most importantly for AR, it is common for
-emulation to be much slower compared to real hardware. In a question submitted
-to \textit{Compute!} magazine asking whether it is possible for a Commodore 64
-to emulate MS-DOS, the editor responded ``Yes, it's possible for a 64 to emulate
-an IBM PC, in the same sense that it's possible to bail out Lake Michigan with
-a teaspoon.'' The editor goes on to explain ``Emulation is a complex business,
-but here's one rule of thumb: The only way to successfully emulate a machine is
-with a much more powerful machine''~\autocite{warick1988}. In our case,
-emulating Android on a desktop operating system is closer to emulating a C64 on
-an IBM PC running MS-DOS (rather than the other way around, thankfully.) The
-moral is that the speed problem facing emulators is just as real as it was in
-1988. Considering that AR already pushes modern phone harware to the limit,
-emulation is not something is not something we wanted to struggle with. On top
-of this, our testing required us to move the camera through the world at
-various speeds and angles, which is simply cumbersome with a webcam and laptop.
+emulator inaccuracies]. Conversely, errors that exist in the hardware version
+may not appear in the emulation. Secondly, and most importantly for AR, it is
+common for emulation to be much slower compared to real hardware.
+
+In a question submitted to \textit{Compute!} magazine asking whether it is
+possible for a Commodore 64 to emulate MS-DOS, the editor responded ``Yes, it's
+possible for a 64 to emulate an IBM PC, in the same sense that it's possible to
+bail out Lake Michigan with a teaspoon.'' The editor goes on to explain
+``Emulation is a complex business, but here's one rule of thumb: The only way to
+successfully emulate a machine is with a much more powerful
+machine''~\autocite{warick1988}. In our case, emulating Android on a desktop
+operating system is closer to emulating a C64 on an IBM PC running MS-DOS
+(rather than the other way around, thankfully). The moral is that the speed
+problem facing emulators is just as real as it was in 1988. Considering that AR
+already pushes modern phone harware to the limit, emulation is not something is
+not something we wanted to struggle with. On top of this, our testing required
+us to move the camera through the world at various speeds and angles, which is
+simply cumbersome with a webcam and laptop.
 
@@
 start}. From here, you can input the provided URL into the Viro Media app. This
-will quickly download the code, graphics and 3D object files from the server
+will quickly download the code, graphics, and 3D object files from the server
 and launch a functional version of the app \autocite{viro-testbed2019}. This
@@
 bed app was somewhat unreliable based on our experience; the test bed would
-frequently crash, or would not be able to download the files from the Node
+frequently crash or would not be able to download the files from the Node
 server. The most reliable way to test our app was to compile a binary and
@@
 
-Our backend allows users to save their tours to our server, and load those same
+Our backend allows users to save their tours to our server and load those same
 tours back into the editor to resume work.  The geographic area of each region
@@
 all media files have to have unique names. This is because the zip that is
-created by the editour backend contains all of the media files in a flat file
+created by the Editour backend contains all of the media files in a flat file
 structure. The above JSON is used to associate each media file with a region,

### 2019-09-20 paper.tex
add acknowledgments

@@
 \addcontentsline{toc}{section}{Acknowledgments}
+
+We would like to thank Atticus Sims, CEO and founder of Kyoto VR, for sponsoring
+this project and providing help and guidance throughout our time in Japan. His
+knowledge of the history of Kinkaku-ji and Kyoto in general has been invaluable
+to our experience.
+
+We would also like to thank Inoue Hikaru for his help with translations and
+researching AR technology. A special thank you to the IQP team working with
+Kyoto VR, Lewis Cook, Nicole Escobar, Ahad Fareed, and Cameron Person, for
+filming and editing the app trailer.
+
+Finally, a thank you to our advisers: Professors Joshua Cuneo and Ralph Sutter.
+Without their expert advice and feedback this project probably could not have
+been completed.
 

### 2019-09-20 paper.tex
replace izi.travel image
Replaced the old screenshot of the izi.TRAVEL app because it was full of
JPG artifacts
working on adobe xd design discussion

--- 2019-09-20 paper.tex
@@
 
-As we have said, AR is a new and growing field full of opportunities. But of course,
-as with anything new, our understanding of AR and how to develop for it is limited.
-And with those limitations come challenges. All sorts of different challenges and
-limitations face the development and production of AR apps. Here are some that
-we considered when working on our app.
+As previously discussed, AR is a new and growing field full of opportunities.
+But of course, as with anything new, our understanding of AR and how to develop
+for it is limited.  And with those limitations come challenges. All sorts of
+    different challenges and limitations face the development and production of
+    AR apps. Here are some that we considered when working on our app.
 
@@
 reality. Our group aimed to implement and extend this functionality in our own
-app. See Section \ref{sec:aruku} for more details.
+app. See Section \ref{sec:aruko} for more details.
 
@@
 
-Wikitude is another major AR development kit that is very prevalent in the world
-of AR development. It has over 130,000 registered AR developers, and is powering
-over 30,000 AR apps across smartphones, tablets, and smart glasses~\autocite{wikitude2018}.
-And it's easy to understand why Wikitude has so many registered developers
-when you see the list of features it offers. Some of the features that appealed
-most to us were their Instant Tracking, allowing for augmentation using flat surfaces;
-Image Tracking, allowing for augmentation using one or multiple 2D images; and
-Geo AR, allowing for creation of geo markers at specific locations to triggered AR
-content~\autocite{wikitude2018}.
+Wikitude is another major AR development kit that is very prevalent in the
+world of AR development. It has over 130,000 registered AR developers, and is
+powering over 30,000 AR apps across smartphones, tablets, and smart
+glasses~\autocite{wikitude2018}.  And it's easy to understand why Wikitude has
+so many registered developers when you see the list of features it offers. Some
+of the features that appealed most to us were their Instant Tracking, allowing
+for augmentation using flat surfaces; Image Tracking, allowing for augmentation
+using one or multiple 2D images; and Geo AR, allowing for creation of geo
+markers at specific locations to triggered AR content~\autocite{wikitude2018}.
 
@@
 
-From all of this information, Wikitude certainly sounds like a fantastic AR development
-platform; it certainly did to us. But the issue we ran into was the cost. Wikitude is, in
-fact, free for eligible startups, but given the criteria they list on their site, we were not
-confident that we would qualify. Aside from this option, Wikitude offers a 30-day demo
-license for \euro{499}, which is a lot for use to pay for a license that would not even last for
-our entire project. They also charge \euro{1990} for their SDK Pro, and \euro{2490} for their
-SDK Pro 3D~\autocite{wikitude2018}. Given these prices, and our very limited budget,
-we knew that we would have to pass on Wikitude and choose a different AR
-development platform.
+From all of this information, Wikitude certainly sounds like a fantastic AR
+development platform; it certainly did to us. But the issue we ran into was the
+cost. Wikitude is, in fact, free for eligible startups, but given the criteria
+they list on their site, we were not confident that we would qualify. Aside
+from this option, Wikitude offers a 30-day demo license for \euro{499}, which
+is a lot for use to pay for a license that would not even last for our entire
+project. They also charge \euro{1990} for their SDK Pro, and \euro{2490} for
+their SDK Pro 3D~\autocite{wikitude2018}. Given these prices, and our very
+limited budget, we knew that we would have to pass on Wikitude and choose a
+different AR development platform.
 
@@
 
-\subsection{ARuku}
-\label{sec:aruku}
+\subsection{ARuko}
+\label{sec:aruko}
+
+\subsubsection{Adobe XD Design}
+\label{sec:aruko}
+On September 10th, Atticus Sims presented us with a storyboard for the app
+experience. We would not be able to resume work until September 17th due to
+prior travel plans. Whether Atticus knew this or not, the design he put forth
+had ramifications that rippled throughout the entire software stack we had
+constructed up to this point. Figure~\ref{fig:adobeXdDesign} shows this design.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=1\textwidth]{adobe-xd-design.png}
+	\caption[A screenshot of the Adobe XD project designed by Atticus Sims]
+    {A screenshot of the Adobe XD project designed by Atticus Sims}
+	\label{fig:adobeXdDesign}
+\end{figure}
+
+One of the notable changes is the chapter select screen, which is the third
+screen in Figure~{fig:adobeXdDesign}. Before, we worked under the assumption
+that each geolocation-triggered region would not have to be ordered in any way.
+This assumption made its way into Editour, which did not currently have a way
+to reorder regions once they were placed. Because of this chapter selection
+screen, we needed some way to rearrange the order of regions within Editour.
+
+Another notable change can be seen in the first screen on
+Figure~\ref{fig:adobeXdDesign}. Atticus was not enthusiastic about being able
+to place images onto the ground-plane using the AR camera. Instead, he
+suggested that we have the images be viewable in a more traditional
+fashion---in 2D as part of the UI. This was disappointing to us, since we spent
+a great deal of effort projecting images into the 3D world using the AR camera;
+we felt like we figured out how to use this technology in a way that was both
+usable and fun. Ideally, we wanted to explore ways to theme the 2D images in
+the 3D world, such as by framing the images in a traditional Japanese pagoda,
+which would fit in with the environment. On the same screen, there is a
+scrollable window of text for a transcript of the audio. Because of this, the
+Editour UI and tour metadata JSON file needed to be updated to accomodate a
+transcript per region. On top of this, the C\# code that interprets the tour
+file needed to be updated to expect an audio transcript field.
+Figure~\ref{fig:editourAdditions} shows the UI elements that changed in order
+to add these new features. The arrows next to the region name can be used to
+move the "Region Card" up and down in the side bar. In the "Media" tab, there
+is also a text area to include a transcript of the uploaded audio file.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\textwidth]{editour-additions.png}
+	\caption[Additions to the editour to accommodate the new design]
+    {Additions to the editour to accommodate the new design}
+	\label{fig:editourAdditions}
+\end{figure}
+
+In Editour, the frontend alone was already around three thousand lines of
+vanilla JavaScript. Type-checking provided by Visual Studio Code and JSDoc made
+the growing code complexity more manageable. Excluding Node modules, the only
+external library we used for Editour was Leaflet, an open-source JavaScript
+library for interactive maps \autocite{leafletjs}. We did not use any libraries
+for developing frontends like Facebook's React or Google's Angular. Instead,
+all of the complex UI interactions were handled by modifying the DOM directly
+with JavaScript's built-in functionality. Furthermore, we did not use any
+advanced frontend build tools such as Rollup, webpack or Parcel. This was
+likely an appropriate decision for a JavaScript project of this scope, but if
+we were to continue to develop Editour, UI libraries and frontend build tools
+would be something to consider.
+
+With the ground-plane detection features stripped away from the main app, the
+AR focus shifted to translating the maps and signs using the camera. The fourth
+screen on Figure~\ref{fig:adobeXdDesign} shows a mock-up of this feature.
+Atticus took photographs of various signs throughout Kinkakuji for us to use as
+image targets. In this design, the AR camera superimposes an "info" button on
+top of the sign. Tapping on this button brings up a separate UI element
+containing the translation, which can be seen in Figure~\ref{fig:signTranslation}.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\textwidth]{sign-translation.png}
+	\caption[Additions to the editour to accommodate the new design]
+    {Additions to the editour to accommodate the new design}
+	\label{fig:signTranslation}
+\end{figure}
+
+ordering*
+transcripts*
+no more ground plane detection*
+many, many image targets
+thumbnails for the chapter
 

### 2019-09-20 paper.tex
worked on more sections

@@
 for it is limited.  And with those limitations come challenges. All sorts of
-    different challenges and limitations face the development and production of
-    AR apps. Here are some that we considered when working on our app.
+different challenges and limitations face the development and production of AR
+apps. Here are some that we considered when working on our app.
 
-Many of the applications and use cases that exist for AR right now are, simply put,
-not very good. This means a few different things. For starters, many AR apps and
-features available on smartphones offer very little in the way of functionality or
-practicality; quite simply, they are primarily used for minor spectacles and simple
-tricks~\autocite{theappsolutions2018}. For example, one of the most popular apps
-to use AR, Pokemon GO, primarily uses it's AR feature to place a Pokemon in the
-world aroudn you through your phone camera for you to capture. But when it is in
-the world, it does not interact with anything around it. It just floats a fixed distance
-away from you, simply placed on top of your camera's video feed.
+Many of the applications and use cases that exist for AR right now are, simply
+put, not very good. This means a few different things. For starters, many AR
+apps and features available on smartphones offer very little in the way of
+functionality or practicality; quite simply, they are primarily used for minor
+spectacles and simple tricks~\autocite{theappsolutions2018}. For example, one
+of the most popular apps to use AR, Pokemon GO, primarily uses it's AR feature
+to place a Pokemon in the world aroudn you through your phone camera for you to
+capture. But when it is in the world, it does not interact with anything around
+it. It just floats a fixed distance away from you, simply placed on top of your
+camera's video feed.
 
-Additionally, in many cases where AR is used, the task could be accomplished as well 
-or better without AR~\autocite{theappsolutions2018}. Returning to the Pokemon GO
-example, when the AR feature is left on while capturing a Pokemon, the extra power
-needed for this feature drains the device faster, makes it harder to hit the Pokemon
-with a Pokeball due to the model drifting in the environment, and can even slow app
-performance, all of which detract from the ability to play and enjoy the game.
+Additionally, in many cases where AR is used, the task could be accomplished as
+well or better without AR~\autocite{theappsolutions2018}. Returning to the
+Pokemon GO example, when the AR feature is left on while capturing a Pokemon,
+the extra power needed for this feature drains the device faster, makes it
+harder to hit the Pokemon with a Pokeball due to the model drifting in the
+environment, and can even slow app performance, all of which detract from the
+ability to play and enjoy the game.
 
-One of the major problems facing AR development as a whole, and one that we
-ran into as well, is limited hardware. For starters, smartphone cameras present
-a major limitation. Many smartphone cameras only capture images in 2D, which can
-make generating AR content in a 3D world difficult without the use of QR or barcode
-markers~\autocite{geospatialworld2018}. Additionally, GPS sensors on smartphones
-can also be too imprecise for good AR tracking~\autocite{geospatialworld2018}.
+One of the major problems facing AR development as a whole, and one that we ran
+into as well, is limited hardware. For starters, smartphone cameras present a
+major limitation. Many smartphone cameras only capture images in 2D, which can
+make generating AR content in a 3D world difficult without the use of QR or
+barcode markers~\autocite{geospatialworld2018}. Additionally, GPS sensors on
+smartphones can also be too imprecise for good AR
+tracking~\autocite{geospatialworld2018}.
 
-The biggest hardware limitation comes from which platform to use. AR apps are most
-commonly designed for smartphones due to their relatively low cost and how accessible
-they are. But, as we just discussed, smartphones come with a host of hardware
-limitations that make achieving satisfying AR capabilities difficult. Additionally, AR apps
-for smartphones tend not to be very user-friendly, and oftentimes even complicate
-the task or activity they were meant to enhance~\autocite{theappsolutions2018}.
-The alternative then is to turn to dedicated hardware, like Microsoft's HoloLens. 
-But dedicated hardware like the HoloLens is very inaccessible and expensive; 
-Microsoft only offers developer editions of the HoloLens, and for the incredibly steep 
-price of \$3,500~\autocite{microsoft2019}.
+The biggest hardware limitation comes from which platform to use. AR apps are
+most commonly designed for smartphones due to their relatively low cost and how
+accessible they are. But, as we just discussed, smartphones come with a host of
+hardware limitations that make achieving satisfying AR capabilities difficult.
+Additionally, AR apps for smartphones tend not to be very user-friendly, and
+oftentimes even complicate the task or activity they were meant to
+enhance~\autocite{theappsolutions2018}.  The alternative then is to turn to
+dedicated hardware, like Microsoft's HoloLens.  But dedicated hardware like the
+HoloLens is very inaccessible and expensive; Microsoft only offers developer
+editions of the HoloLens, and for the incredibly steep price of
+\$3,500~\autocite{microsoft2019}.
 
-The challenges we faced during development mirrored these that plague the industry
-as a whole very accurately. We struggled with how exactly we would us AR for our app
-in a way that benefit the experience as a whole, but believe the way we've implemented
-it will enhance the user's experience. Hardware issues were definitely our biggest challenge.
-Only one of our phones is new enough to run AR technology at a decent level, making
-testing of our application difficult.
+The challenges we faced during development mirrored these that plague the
+industry as a whole very accurately. We struggled with how exactly we would us
+AR for our app in a way that benefit the experience as a whole, but believe the
+way we've implemented it will enhance the user's experience. Hardware issues
+were definitely our biggest challenge.  Only one of our phones is new enough to
+run AR technology at a decent level, making testing of our application
+difficult.
 
@@
 \label{sec:motive.io}
+
+The company motive.io used to work on a product that would allow users to
+create an engaging AR experience in the style of Pokemon Go. Their service
+would have purportedly handled technical details such as hosting, storage, and
+user accounts. The promotional video shows the creation of a location-based AR
+game where the user pretends to hack into ATMs using the real-world locations
+of ATMs in a city\autocite{odom2017}.
+
+Unfortunately, it appears that the company has completely pivoted off of this
+idea, and has since moved to AR training software\autocite{motiveio}.
+
+We reached out to motive.io via email for any advice they might be willing to
+give us, but we received no response.
 
@@
 \subsubsection{Adobe XD Design}
-\label{sec:aruko}
+\label{sec:adobeXdDesign}
 On September 10th, Atticus Sims presented us with a storyboard for the app
@@
 One of the notable changes is the chapter select screen, which is the third
-screen in Figure~{fig:adobeXdDesign}. Before, we worked under the assumption
+screen in Figure~\ref{fig:adobeXdDesign}. Before, we worked under the assumption
 that each geolocation-triggered region would not have to be ordered in any way.
@@
 to add these new features. The arrows next to the region name can be used to
-move the "Region Card" up and down in the side bar. In the "Media" tab, there
+move the ``Region Card'' up and down in the side bar. In the ``Media'' tab, there
 is also a text area to include a transcript of the uploaded audio file.
@@
 vanilla JavaScript. Type-checking provided by Visual Studio Code and JSDoc made
-the growing code complexity more manageable. Excluding Node modules, the only
+the growing code complexity more manageable. Excluding Node.js modules, the only
 external library we used for Editour was Leaflet, an open-source JavaScript
@@
 we were to continue to develop Editour, UI libraries and frontend build tools
-would be something to consider.
+would be something to consider. With these changing requirements, the Editour
+was becoming onerous to maintain at this stage of the project.
 
@@
 Atticus took photographs of various signs throughout Kinkakuji for us to use as
-image targets. In this design, the AR camera superimposes an "info" button on
-top of the sign. Tapping on this button brings up a separate UI element
-containing the translation, which can be seen in Figure~\ref{fig:signTranslation}.
+image targets. Hikaru Inoue helped us by translating all of the text in these
+photos from Japanese to English. In this design, the AR camera superimposes an
+``info'' button on top of the sign. Tapping on this button brings up a separate
+UI element containing the translation, which can be seen in
+Figure~\ref{fig:signTranslation}.
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{sign-translation.png}
-	\caption[Additions to the editour to accommodate the new design]
-    {Additions to the editour to accommodate the new design}
-	\label{fig:signTranslation}
+\begin{figure}[h] \centering
+\includegraphics[width=0.5\textwidth]{sign-translation.png} \caption{Translated
+sign using AR camera} \label{fig:signTranslation}
 \end{figure}
 
-ordering*
-transcripts*
-no more ground plane detection*
-many, many image targets
-thumbnails for the chapter
+As previously mentioned, Atticus initially wanted us to explore the efficacy of
+using Vuforia's 2D image target capabilities for scanning objects outside of
+the expected use case, such as 3D landscapes or the side of a building. We had
+serious doubts about how well this would work, and our suspicions were
+confirmed after some field testing. This was the reasoning behind focusing on
+ground-plane detection instead of image targets; ground-plane detection can be
+used anywhere, and is much more reliable than treating 3D objects as 2D image
+targets.
+
+Since Adobe XD is largely a prototyping and design tool, a considerable amount
+of legwork would still need to be done to rebuild the proposed design using
+Unity's UI components. Adobe XD allowed us to export a few important UI
+elements as PNGs, such as the buttons to enter AR mode and view the map. We
+briefly explored a few solutions to automating the task of getting the Adobe XD
+project into Unity. We found one payed extension (for \$18) on the Unity Asset
+store, called ``Experience Importer - Adobe Xd files importer'', which claims
+``Transfer AdobeXd project directly to Unity. Forget about hours of positioning
+objects. They're already there! Just drag .xd file to project and... voila!''
+We suspect this sounds too good to be true because it is. As of September 20th,
+2019, there are 6 user reviews. All of the five-star reviews were have the
+caveat ``Reviewer was gifted package by publisher'' which which we interpreted
+as a warning sign. Because of this, we decided to rebuild the UI largely from
+the ground up, using the Adobe XD file to guide us.
 
@@
 
+\section{Pivots}
+\label{sec:pivots}
+
+Throughout the duration of the project, the goalposts shifted multiple times.
+This section details some of the initial plans that fell through.
+
+\section{3D Spatialized Audio Tour}
+\label{sec:3dSpatializedAudioTour}
+
 \section{Conclusion}

### 2019-09-20 paper.tex

@@
 	\centering
-	\includegraphics[width=.5\textwidth]{izi-travel.jpg}
+	\includegraphics[width=.5\textwidth]{izi-travel.png}
 	\caption{A screenshot of the izi.TRAVEL app interface}

### 2019-09-21 paper.tex
add to testing section

@@
 screen on Figure~\ref{fig:adobeXdDesign} shows a mock-up of this feature.
-Atticus took photographs of various signs throughout Kinkakuji for us to use as
+Atticus took photographs of various signs throughout Kinkaku-ji for us to use as
 image targets. Hikaru Inoue helped us by translating all of the text in these
@@
 
+\newpage
+
 \section{Testing}
 \label{sec:testing}
+
+Both pieces of our project---the Editour and ARuko---are designed to be used by
+people who aren't programmers. The Editour will be used by Atticus in the future
+to design more tours, and ARuko will be used by the general public. Because of
+this, we needed to do extensive testing to ensure not only that the products
+work as intended without bugs, but also that they would be pleasant and easy to
+use for their intended users.
+
+\subsection{Testing Editour}
+\label{sec:testingEditour}
+
+\subsection{Testing ARuko}
+\label{sec:aruko}
+
+\subsubsection{First Round of Field Testing}
+\label{sec:firstRoundOfFieldTesting}
 
@@
 	\includegraphics[width=\textwidth]{kinkakuji-tour.png}
-	\caption[The original version of the Kinkakuji tour]{The original version of
-    the Kinkakuji tour with small regions}
+	\caption[The original version of the Kinkaku-ji tour]{The original version
+		of the Kinkaku-ji tour with small regions}
 	\label{fig:kinkakujiTour}
@@
 
-Due to concerns about GPS accuracy, we adapted the tour-file \texttt{kinkakuji} to
-create a second, ``chunkier'' tour.  In the tour-file \texttt{kinkakuji-chunkier},
-we expanded all of the regions to accomodate for potential GPS inaccuracies
-that could place the user outside the range of the audio-trigger region.
-Figure~\ref{fig:kinkakujiChunkierTour} depicts the tour that we used for field
-testing at Kinkakuji.
+Due to concerns about GPS accuracy, we adapted the tour-file \texttt{kinkakuji}
+to create a second, ``chunkier'' tour.  In the tour-file
+\texttt{kinkakuji-chunkier}, we expanded all of the regions to accomodate for
+potential GPS inaccuracies that could place the user outside the range of the
+audio-trigger region.  Figure~\ref{fig:kinkakujiChunkierTour} depicts the tour
+that we used for field testing at Kinkaku-ji.
 
@@
 	\includegraphics[width=\textwidth]{kinkakuji-chunkier-tour.png}
-	\caption[The ``chunkier'' version of the Kinkakuji tour]{The ``chunkier'' version of
-    the Kinkakuji tour with larger regions}
+	\caption[The ``chunkier'' version of the Kinkaku-ji tour]{The ``chunkier''
+		version of the Kinkaku-ji tour with larger regions}
 	\label{fig:kinkakujiChunkierTour}
@@
 
-Our previous testing involved creating a ``mock tour'' on the Ritsumeikan campus.
-While this let us know generally which features of the app were working, it was
-very difficult to know how ahead of time how well our app would work at Kinkakuji.
+Our previous testing involved creating a ``mock tour'' on the Ritsumeikan
+campus. While this let us know generally which features of the app were working,
+it was very difficult to know how ahead of time how well our app would work at
+Kinkaku-ji.
 
@@
 With a few exceptions, the audio started when the subject of the audio track
-was in view. During our first walkthrough of Kinkakuji, we triggered every
+was in view. During our first walkthrough of Kinkaku-ji, we triggered every
 region and audio track but one. The region that we missed on the first pass,
@@
 Since the songs were relatively long and not always obvious when they started
-partway through, we did not catch this until we got out to Kinkakuji. Luckily,
+partway through, we did not catch this until we got out to Kinkaku-ji. Luckily,
 this was trivial to fix.

### 2019-09-22 paper.tex
add more testing

@@
 
+Because the Editour is intended only to be a tool to aid Atticus in creating
+tours, not an application for the general public, our user testing of it was less
+rigid.
+
+\subsubsection{Unit Testing the Editour Backend}
+\label{sec:unitTestingTheEditourBackend}
+
+To test the API and backend of the Editour web app we used the Mocha testing
+framework. Mocha is the most depended-upon package in the Node Package
+Manager~\autocite{tidelift2019}, and is widely used by professional software
+development teams. It has a myriad of useful features that allow developers to
+quickly write unit tests for complex Node.js projects~\autocite{mochajs2019}.
+Most importantly for us, it has good support for testing asynchronous JavaScript
+functions, since most of the backend is written asynchronously. Along with Mocha
+we also used SuperTest, a library for writing high-level end-to-end HTTP
+tests~\autocite{supertest2019}.
+
+For each of the six API endpoints that the backend responds to we wrote an
+extensive series of end-to-end tests to ensure that each step along the pipeline
+from receiving a request to sending a response worked properly. We also wrote
+many fuzz tests, to make sure the backend would respond correctly to invalid
+requests, e.g. by responding with an HTTP 400 error message~\autocite{rfc7231}.
+
+These tests were very useful in tracking down bugs and unexpected behavior in
+the backend, and also allowed us to make sure no functionality changed when
+adding new features or making changes to underlying logic later on.
+
+\subsection{Frontend Web Application Testing}
+\label{sec:frontendWebApplicationTesting}
+
 \subsection{Testing ARuko}
-\label{sec:aruko}
+\label{sec:testingARuko}
 
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=\textwidth]{turtle-burger.jpg}
-	\caption[A rare but delicious turtle burger in the wild]{A rare but
-		delicious turtle burger in the wild~\autocite{harvey2002}.}
-	\label{fig:turtleBurger}
-\end{figure}
+% \begin{figure}[h]
+%	\centering
+%	\includegraphics[width=\textwidth]{turtle-burger.jpg}
+%	\caption[A rare but delicious turtle burger in the wild]{A rare but
+%		delicious turtle burger in the wild~\autocite{harvey2002}.}
+%	\label{fig:turtleBurger}
+%\end{figure}
 

### 2019-09-22 paper.tex
added diagram

@@
 \begin{figure}[h] \centering
-\includegraphics[width=0.5\textwidth]{sign-translation.png} \caption{Translated
-sign using AR camera} \label{fig:signTranslation}
+    \includegraphics[width=0.5\textwidth]{sign-translation.png}
+    \caption{Translated sign using AR camera}
+    \label{fig:signTranslation}
 \end{figure}
@@
 adding new features or making changes to underlying logic later on.
+
+\subsubsection{Unit Testing ARuko}
+\label{sec:unitTestingARuko}
+
+The UI and AR features of the app are very important to the user experience. At
+the same time, ARuko is not as purely graphical as it may seem. There is a
+significant amount of ``business logic'' that interprets the tour from the
+Editour file. On top of this, the geometric checks to test whether the user is
+inside a particular arbitrarily-defined geographic region are very important to
+get right.  Using Unity's built-in NUnit unit-testing framework, we wrote tests
+to verify whether the tour data was being parsed correctly, and whether the tour
+would be run correctly.
+
+As a reminder, regions that trigger audio can be a set of three or more points
+that define a closed polygon. Using the user's GPS location, the app needs to
+periodically run a check to see if the user is located within one of those
+polygons, which can be either concave or convex.
+
+One decent algorithm for accomplishing this is by drawing a ray from a given
+point to infinity. Barring edge cases (which will be discussed shortly) the
+point is inside the polygon if the ray passes through an even number of line
+segments.  The point is outside of the polygon if the ray intersects an odd
+number of times. Figure~\ref{fig:intersectionsDiagram} should make it clear why
+this works. This algorithm runs in $O(n)$, where $n$ is the sum total of the
+number of vertices of all of the polygons being tested
+~\autocite{geeksforgeekspolygon}.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{intersections-diagram.png}
+	\caption{A visualization of the algorithm}
+	\label{fig:intersectionsDiagram}
+\end{figure}
+
+For this, we implemented a few mathematical functions for individual parts of
+the algorithm, such as testing for intersection. We wrote unit-tests to test
+each part of the algorithm, so we could be confident that the GPS component of
+the app would correctly place users into the correct regions.
+
+There is one edge case where this algorithm has difficulties. If the ray that
+is drawn for testing intersections passes directly through a vertex, the
+algorithm will count two intersections instead of just one. Even though this is
+highly unlikely considering our use case, we decided that our algorithm should
+be robust enough to handle this on a matter of principle. Unit-testing helped us
+catch and deal with this edge case.
 

### 2019-09-23 paper.tex
editour frontend testing section

@@
 
-\subsection{Frontend Web Application Testing}
-\label{sec:frontendWebApplicationTesting}
+\subsection{Editour Frontend Testing}
+\label{sec:editourFrontendTesting}
+
+We suspect that Editour might have a life outside of this particular use case
+for designing tours, depending on how we choose to further develop this
+software. This is why Editour is perhaps more polished than your typical tool
+purely for internal use.
+
+For the duration of the project however, Editour only had to be used by us
+three and Atticus. Therefore, the testing for the frontend of Editour was less
+systematic than other parts of the software stack. This decision also helped us
+focus our efforts on testing the reliability and user experience of ARuko. That
+being said, we were able to add many feature and get the Editour experience to
+a polished state through our own testing, using GitHub's tools to keep us
+organized.
+
+In order to test for bugs, all three of us periodically interacted with
+successive builds of the frontend. When bugs were found, we would log these as
+``Issues'' on the GitHub repo. These issues would get resolved in successive
+pull requests.
+
+Since we had to use Editour frequently to create test tours for ARuko, we were
+able to identify features that would make our own work more efficient. This
+worked as a kind of informal user testing. We kept track of feature requests
+using the same system as bug reports.
+
+Issues and feature requests alike got resolved in future pull requests. We
+resolved over thirty issues and feature requests using this workflow. The
+GitHub issues tab (which can be see in Figure~\ref{fig:issuesPageExample}) was
+very useful for making sure we made use of our user testing and bug testing.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{issues-page-example.png}
+	\caption{The GitHub issues tab for Editour}
+	\label{fig:issuesPageExample}
+\end{figure}
 

### 2019-09-23 paper.tex
another testing section and more figures

@@
 
-\subsection{Testing ARuko}
+\subsection{Testing Taking a Tour with ARuko}
 \label{sec:testingARuko}
+
+Because it was not feasible to travel to Kinkaku-ji every time we needed to
+test the GPS functionality of the app, we used Editour to design an example
+tour around the Ritsumeikan Biwako-Kusatsu campus where we worked. This allowed
+us to catch various bugs before we created a finalized prototype for
+field-testing at Kinkaku-ji. The tour represented in \ref{fig:ritsuTour} is
+what we used for testing the app. The ``C-Shaped Region'' helped us test
+concave regions. This unique region also prompted us to think about what UI
+behavior made the most sense if a user were to walk into a region, walk out and
+then in again. We decided that it was awkward if the audio restarted upon
+re-entering a region, since the audio would still be playing once a user left
+the region. The region at the bottom surrounding our domitories was added for
+our convenience, allowing us to test the app while we were away from the lab.
+As we began to implement more complex UI that changed based on GPS position in
+various ways, directly taking the tour by walking around was an invaluable way
+to test. Section~\ref{sec:adobeXdDesign} details how the UI grew in complexity
+in the late stages of the project. Having a way to regularly run field tests
+was integral to polishing the app in time before we revisited Kinkaku-ji.
+Because the Editour was flexible enough to easily swap out media and add
+regions to the tour, the Editour proved itself to be as helpful for testing as
+it was for crafting the final tour that could be taken at Kinkaku-ji.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=.5\textwidth]{ritsu-tour.png}
+	\caption{The Ritsumeikan example tour used for testing}
+	\label{fig:ritsuTour}
+\end{figure}
 

### 2019-09-23 paper.tex
start introduction

--- 2019-09-23 paper.tex
@@
 % https://www.overleaf.com/learn/latex/Biblatex_bibliography_styles
-\usepackage[backend=biber,style=numeric]{biblatex}
+\usepackage[backend=biber,style=numeric,sorting=none]{biblatex}
 \usepackage[page, titletoc, title]{appendix}
@@
 \label{sec:introduction}
+
+The field of consumer-oriented Augmented Reality (AR) technology is just coming
+into full swing, and it presents many unique opportunities for a myriad of
+fields. This budding technological platform uses digital displays to augment
+real-world information with computer-generated data. As the technology
+progresses several disparate industries have found novel uses for it, some
+becoming extremely profitable~\autocite{webster2018}. With smartphone
+manufacturers investing billions into AR technology~\autocite{mason2016}, it
+seems poised to be the next big digital interface.
+
+Tourism and art are among the fields that could gain the most from AR
+technology~\autocite{saenz2009, katz2018}.
+
+\newpage
 
@@
 \label{sec:unity}
+
+\newpage
 
@@
 
+\newpage
+
 \section{Pivots}
@@
 
+\newpage
+
 \section{3D Spatialized Audio Tour}
 \label{sec:3dSpatializedAudioTour}
+
+\newpage
 

### 2019-09-23 paper.tex
basic info about kinkakuji and updates

--- 2019-09-23 paper.tex
@@
 
+\subsection{Kinkaku-ji}
+\label{sec:kinkaku-ji}
+
+We were tasked with building an AR mobile app that enhances the experience of
+visiting Kinkaku-ji, or the Golden Pavilion. As of September 2019, Kinkaku-ji
+is the second-most visited site in Kyoto---second only to Kyoto Station
+\autocite{japanguide2019}.
+
 \section{Implementation and Technology}
@@
 through a web-app. At its core, Editour is a tool to draw arbitarily-shaped
-geographic regions onto a map. An audio file and multiple image files can be
-uploaded for each region the user defines. After naming and uploading the tour
-with the ``Upload'' button, our backend builds a zip containing a folder that can
-be placed directly into the Unity project.
+geographic regions onto a map.
+
+An audio file and multiple image files can be uploaded for each region the user
+defines. The user can also provide a text transcript of the audio file as well.
+After naming and uploading the tour with the ``Upload'' button, our backend
+builds a zip containing a folder that can be placed directly into the Unity
+project.
 
@@
          "audio": [ "beautiful-audio.mp3" ],
-         "images": [ "mountain.jpg", "stream.jpg" ]
+         "images": [ "mountain.jpg", "stream.jpg" ],
+         "transcript": "To your left, you can see a beautiful place."
       },
@@
          "audio": [ "gorgeous-audio.mp3" ],
-         "images": [ "hill.jpg", "valley.jpg", "gorge.jpg" ]
+         "images": [ "hill.jpg", "valley.jpg", "gorge.jpg" ],
+         "transcript", "To your right, you can see a gorgeous place."
       }
@@
 
-Within each object in the region list, we can see that the region has four
-properties: a name, a list of coordinates, a list of audio files, and a list of
-multiple image files. (In the current design of the app, it only makes sense to
-associate one audio file per region, but the format makes it easy to
-accommodate for multiple audio files in the future.) One disadvantage is that
-all media files have to have unique names. This is because the zip that is
-created by the Editour backend contains all of the media files in a flat file
-structure. The above JSON is used to associate each media file with a region,
-meaning that the filename needs to act as a primary key. The backend will
-respond with a message if this is the case, prompting the user to have unique
-names for all files.
+Within each object in the region list, we can see that the region has five
+properties: a name, a list of coordinates, a list of audio files, a list of
+multiple image files, and a transcript of the audio file. (In the current
+design of the app, it only makes sense to associate one audio file per region,
+but the format makes it easy to accommodate for multiple audio files in the
+future.) One disadvantage is that all media files have to have unique names.
+This is because the zip that is created by the Editour backend contains all of
+the media files in a flat file structure. The above JSON is used to associate
+each media file with a region, meaning that the filename needs to act as a
+primary key. The backend will respond with a message if this is the case,
+prompting the user to have unique names for all files.
 
@@
 
-The design of the Editour is agnostic about how the media will be used.  For
-an app like izi.TRAVEL, the images are displayed when the associated audio
-tour is playing. For ARuku, images can be placed onto the ground plane by the
-user, which is unique compared to other audio tour guide apps. The tour files
-produced by Editour could theoretically be used by a tour guide app that does
-not incorporate AR.
+The design of the Editour is agnostic about how the media will be used. For an
+app like izi.TRAVEL, the images are displayed when the associated audio tour is
+playing. The tour files produced by Editour could theoretically be used by a
+tour guide app that does not incorporate AR.
 

### 2019-09-23 paper.tex

@@
 \autocite{japanguide2019}.
+
+\newpage
 

### 2019-09-23 paper.tex
working on editour section

@@
 
-As smartphones and mobile technology become more prevalent,
-new forms of human-computer interaction are becoming mainstream. Smartphones
-allow for an unprecedented degree of connectivity with the digital world, but
-can also serve as a tool for enhancing the physical world. In this section we
-explain the origins and uses of some of this technology.
+As smartphones and mobile technology become more prevalent, new forms of
+human-computer interaction are becoming mainstream. Smartphones allow for an
+unprecedented degree of connectivity with the digital world, but can also serve
+as a tool for enhancing the physical world. In this section we explain the
+origins and uses of some of this technology.
 
@@
 For example, AR can be used to display information about historical events,
-places, and objects overlaid onto images of the real world~\autocite{saenz2009}.
-This provides the user with useful information without needing to alter the real
-historic site.
+places, and objects overlaid onto images of the real
+world~\autocite{saenz2009}.  This provides the user with useful information
+without needing to alter the real historic site.
 
@@
 us to move the camera through the world at various speeds and angles, which is
-simply cumbersome with a webcam and laptop.
-
-ViroReact offers a convenient ``test bed'' for rapidly testing your ViroReact
-app on native hardware without the need for an emulator. In the root directory
-of your project, you can launch a Node server with the command \texttt{npm
-start}. From here, you can input the provided URL into the Viro Media app. This
-will quickly download the code, graphics, and 3D object files from the server
-and launch a functional version of the app \autocite{viro-testbed2019}. This
-allowed us to get a real AR app up and running on our devices much more easily
-than any of the other frameworks/engines we explored. Unfortunately, the test
-bed app was somewhat unreliable based on our experience; the test bed would
-frequently crash or would not be able to download the files from the Node
-server. The most reliable way to test our app was to compile a binary and
-manually install it onto our devices, which completely defeats the purpose of
-the test bed app.
+simply cumbersome with a laptop webcam.
+
+As an alternative to emulation, ViroReact offers a convenient ``test bed'' for
+rapidly testing your ViroReact app on native hardware without the need for an
+emulator. In the root directory of your project, you can launch a Node server
+with the command \texttt{npm start}. From here, you can input the provided URL
+into the Viro Media app. This will quickly download the code, graphics, and 3D
+object files from the server and launch a functional version of the app
+\autocite{viro-testbed2019}. This allowed us to get a real AR app up and
+running on our devices much more easily than any of the other
+frameworks/engines we explored. Unfortunately, the test bed app was somewhat
+unreliable based on our experience; the test bed would frequently crash or
+would not be able to download the files from the Node server. The most reliable
+way to test our app was to compile a binary and manually install it onto our
+devices, which completely defeats the purpose of the test bed app.
 
@@
 We were tasked with building an AR mobile app that enhances the experience of
-visiting Kinkaku-ji, or the Golden Pavilion. As of September 2019, Kinkaku-ji
-is the second-most visited site in Kyoto---second only to Kyoto Station
-\autocite{japanguide2019}.
+visiting Kinkaku-ji, also known as the Golden Pavilion. As of September 2019,
+Kinkaku-ji is the second-most visited site in Kyoto---second only to Kyoto
+Station \autocite{japanguide2019}.
 
@@
 
+\subsubsection{Editing a Tour}
+\label{sec:editingATour}
+
+The user can easily create a new region by shift-clicking, and then clicking
+points on the map. To terminate the polygon, the user must shift-click again.
+A user can only terminate the polygon after two points have been placed to
+prevent the user from drawing a region with an area of zero. Once a region is
+created, a region card appears in the side bar. From here, the user can edit
+anything about the region. From here, the user can edit anything about the
+region.
+
+The top of the region card displays the region name in bold text. By clicking
+on the region name, the map will pan and zoom to frame the region in the center
+of the screen. This is useful if there are many regions. To the right of the
+region name, there are two arrow buttons, one pointed up and another pointed
+down. This allows the user to reorder the regions in the column. This was one
+of the features that was added late into development in order to adapt to an
+important change in the tour app, ARuko. This is discussed in
+Section~\ref{sec:adobeXdDesign}.
+
+In the region card, there are four multicolored expandable ``subcards'' that
+allow the user to edit different information about each region. Since there can
+be many region cards in the column, it was important to be able to collapse
+each section. Collapsing the subcards gives the user enough room to see
+multiple region cards at a time.
+
+The first subcard is the ``Rename'' subcard, which is fairly self-explanatory.
+This section expands to reveal a textbox, allowing the user to rename the
+region after clicking ``Okay'' or hitting the enter key. (There are multiple
+places in the UI where a textbox is immediately adjacent to a ``Confirm''
+button.  We made sure all of these can be triggered by simply hitting enter,
+since this is common when filling out forms.)
+
+The second subcard is slightly involved. Expanding the ``Media'' subcard by
+clicking on the green bar will reveal a bevy of options for augmenting the
+audio, images and text to be associated with that region of the tour. From
+here, the user can upload an audio file and multiple image files from his or
+her hard drive with the two file-select fields. If the tour has been downloaded
+as a server, the names of the files already present on the server will appear
+as cards with `X' buttons. This allows the user to remove images or audio from
+that region even after the tour has been uploaded.
+
+The third subcard is the ``Edit'' subcard. This subcard can be revealed in one
+of two ways. The first way is by clicking on the yellow bar labeled ``Edit'',
+which is the same for all subcards. Alternatively, the user can also click
+directly on the region on the map. The region will flash yellow and be scrolled
+into view to let the user know which region was clicked on. Both of these
+methods will enable editing mode, whereby the user can directly manipulate the
+vertices that make up the region. Blue circles appear on top of each vertex,
+and red circles appear at the midpoint of each edge. Clicking on a red midpoint
+will add an additional vertex at that midpoint. Dragging one of the blue
+vertices will do as you might expect---move the vertex around. The latitude and
+longitude are updated in the ``Edit'' subcard as the user drags the vertex
+around. Clicking on the vertex directly will create a blue pin-shaped marker
+that the user can also drag around. Clicking on the coordinate box in the
+subcard will also create this blue pin-shaped marker; the map will also pan to
+this coordinate. The user can also delete vertices in the same way that files
+can be deleted from the ``Media'' subcard by clicking on the `X' button. If there
+are exactly three points in a region, the `X' buttons will be ``grayed-out'',
+preventing the user from deleting any more points (since a polygon must consist
+of at least three points.)
+
+The third subcard is the ``Delete'' subcard. When revelead, another button will
+appear labeled ``Really Delete''. The action can be canceled by collapsing the
+subcard by hitting the bar now labeled ``Don't Delete!''. This prevents the user
+from accidentally deleting a region he or she did not mean to.
+
+Above all of the region cards, there are various options for uploading,
+downloading, renaming and deleting tour files on the server. Within the upload,
+download and delete cards there are message boxes to indicate the status of
+that operation. When uploading and downloading, a percentage will be displayed
+indicating the upload/download process. If a 200 or 201 is returned from the
+server, a ``Success'' message will appear. If there was some problem, the error
+message returned by the server is displayed in this box instead. Since
+uploading, downloading and deleting are all network-related operations, it
+makes sense to include this message box for each card.
+
+When the page is loaded, the frontend will request the names of the files
+stored on the server from the backend. This data is used to create a box of
+buttons, which includes one button for each tour file on the server. Clicking on
+one of these blue buttons will fill the textbox in with the correct name. Before
+this feature was implemented, the user had to correctly type the name of the
+saved tour into the textbox in order to retrieve it. The user is still free to
+do this, but the buttons make this easier and less error-prone.
+
 \begin{figure}[h]
@@
 
-In Editour, the frontend alone was already around three thousand lines of
-vanilla JavaScript. Type-checking provided by Visual Studio Code and JSDoc made
-the growing code complexity more manageable. Excluding Node.js modules, the only
-external library we used for Editour was Leaflet, an open-source JavaScript
-library for interactive maps \autocite{leafletjs}. We did not use any libraries
-for developing frontends like Facebook's React or Google's Angular. Instead,
-all of the complex UI interactions were handled by modifying the DOM directly
-with JavaScript's built-in functionality. Furthermore, we did not use any
-advanced frontend build tools such as Rollup, webpack or Parcel. This was
-likely an appropriate decision for a JavaScript project of this scope, but if
-we were to continue to develop Editour, UI libraries and frontend build tools
-would be something to consider. With these changing requirements, the Editour
-was becoming onerous to maintain at this stage of the project.
+At this point, the codebase for Editour was already around three thousand lines
+of vanilla Javascript. Type-checking provided by Visual Studio Code and JSDoc
+made the growing code complexity more manageable. Excluding Node.js modules,
+the only external library we used for Editour was Leaflet, an open-source
+JavaScript library for interactive maps \autocite{leafletjs}. We did not use
+any libraries for developing frontends like Facebook's React or Google's
+Angular. Instead, all of the complex UI interactions were handled by modifying
+the DOM directly with JavaScript's built-in functionality. Furthermore, we did
+not use any advanced frontend build tools such as Rollup, webpack or Parcel.
+This was likely an appropriate decision for a JavaScript project of this scope.
+Considering we had limited to no experience with React or Angular, it was also
+faster to develop the UI in the way we were used to from previous experience..
+But if we were to continue to develop Editour, UI libraries and frontend build
+tools would be something to consider. With these changing requirements, the
+Editour was becoming onerous to maintain at this stage of the project.
 
@@
 what we used for testing the app. The ``C-Shaped Region'' helped us test
-concave regions. This unique region also prompted us to think about what UI
-behavior made the most sense if a user were to walk into a region, walk out and
-then in again. We decided that it was awkward if the audio restarted upon
-re-entering a region, since the audio would still be playing once a user left
-the region. The region at the bottom surrounding our domitories was added for
-our convenience, allowing us to test the app while we were away from the lab.
-As we began to implement more complex UI that changed based on GPS position in
-various ways, directly taking the tour by walking around was an invaluable way
-to test. Section~\ref{sec:adobeXdDesign} details how the UI grew in complexity
-in the late stages of the project. Having a way to regularly run field tests
-was integral to polishing the app in time before we revisited Kinkaku-ji.
-Because the Editour was flexible enough to easily swap out media and add
-regions to the tour, the Editour proved itself to be as helpful for testing as
-it was for crafting the final tour that could be taken at Kinkaku-ji.
+concave regions. This uniquely shaped region also prompted us to think about
+what UI behavior made the most sense if a user were to walk into a region, walk
+out and then in again. We decided that it was awkward if the audio restarted
+upon re-entering a region, since the audio would still be playing once a user
+left the region. The region at the bottom surrounding our domitories was added
+for our convenience, allowing us to test the app while we were away from the
+lab.  As we began to implement more complex UI that changed based on GPS
+position in various ways, directly taking the tour by walking around was an
+invaluable way to test. Section~\ref{sec:adobeXdDesign} details how the UI grew
+in complexity in the late stages of the project. Having a way to regularly run
+field tests was integral to polishing the app in time before we revisited
+Kinkaku-ji.  Because the Editour was flexible enough to easily swap out media
+and add regions to the tour, the Editour proved itself to be as helpful for
+testing as it was for crafting the final tour that could be taken at
+Kinkaku-ji.
 

### 2019-09-23 paper.tex
wrapping up section on editour

@@
 points on the map.  To terminate the polygon, the user must shift-click again.
-A user can only terminate the polygon after two points have been placed to
-prevent the user from drawing a region with an area of zero. Once a region is
-created, a region card appears in the side bar. From here, the user can edit
-anything about the region. From here, the user can edit anything about the
-region.
+The ``Welcome to editour'' card provides these instructions, which should be
+enough to get started.  A user can only terminate the polygon after two points
+have been placed to prevent the user from drawing a region with an area of
+zero. Once a region is created, a region card appears in the side bar. From
+here, the user can edit anything about the region. From here, the user can edit
+anything about the region.
 
@@
 do this, but the buttons make this easier and less error-prone.
+
+We did not include a way to resolve addresses or place names, like the service
+provided by Google Maps. Instead of exploring plugins/libraries that might
+provide this functionality, we offered a simpler solution due to time
+constraints.  You can type in a latitude and longitude directly and hit the
+``Jump'' button. We also hard-coded some shortcuts for places that Atticus
+might want to design a tour for in the future, which can be accessed by
+clicking on the yellow buttons with place names.
+
+Once a tour is either uploaded or downloaded, a link to download the zip file
+will appear. The zip file contains all of the uploaded media, and a metadata
+file. The metadata is in the form of a JSON file; it contains all of the
+latitudes, longitudes, and enough information to associate all of the media
+with the correct regions. This is the file that we unzip and place into the
+Unity project before it is compiled. This also is useful if the user wants to
+check the audio and image files that were uploaded.
 

### 2019-09-24 paper.tex
continued introduction

--- 2019-09-23 paper.tex
@@
 Tourism and art are among the fields that could gain the most from AR
-technology~\autocite{saenz2009, katz2018}.
+technology~\autocite{saenz2009, katz2018}. AR technology can provide accessible
+information to tourists and art viewers that they would not be able to get any
+other way.
+
+Kinkaku-ji, the ``golden pavilion'' of Kyoto, is the perfect example of
+this~\autocite{bornoff2000}.
 
@@
 
-\subsection{Kinkaku-ji}
-\label{sec:kinkaku-ji}
-
-We were tasked with building an AR mobile app that enhances the experience of
-visiting Kinkaku-ji, or the Golden Pavilion. As of September 2019, Kinkaku-ji
-is the second-most visited site in Kyoto---second only to Kyoto Station
-\autocite{japanguide2019}.
-
 \newpage
@@
 through a web-app. At its core, Editour is a tool to draw arbitarily-shaped
-geographic regions onto a map.
-
-An audio file and multiple image files can be uploaded for each region the user
-defines. The user can also provide a text transcript of the audio file as well.
-After naming and uploading the tour with the ``Upload'' button, our backend
-builds a zip containing a folder that can be placed directly into the Unity
-project.
+geographic regions onto a map. An audio file and multiple image files can be
+uploaded for each region the user defines. After naming and uploading the tour
+with the ``Upload'' button, our backend builds a zip containing a folder that can
+be placed directly into the Unity project.
 
@@
          "audio": [ "beautiful-audio.mp3" ],
-         "images": [ "mountain.jpg", "stream.jpg" ],
-         "transcript": "To your left, you can see a beautiful place."
+         "images": [ "mountain.jpg", "stream.jpg" ]
       },
@@
          "audio": [ "gorgeous-audio.mp3" ],
-         "images": [ "hill.jpg", "valley.jpg", "gorge.jpg" ],
-         "transcript", "To your right, you can see a gorgeous place."
+         "images": [ "hill.jpg", "valley.jpg", "gorge.jpg" ]
       }
@@
 
-Within each object in the region list, we can see that the region has five
-properties: a name, a list of coordinates, a list of audio files, a list of
-multiple image files, and a transcript of the audio file. (In the current
-design of the app, it only makes sense to associate one audio file per region,
-but the format makes it easy to accommodate for multiple audio files in the
-future.) One disadvantage is that all media files have to have unique names.
-This is because the zip that is created by the Editour backend contains all of
-the media files in a flat file structure. The above JSON is used to associate
-each media file with a region, meaning that the filename needs to act as a
-primary key. The backend will respond with a message if this is the case,
-prompting the user to have unique names for all files.
+Within each object in the region list, we can see that the region has four
+properties: a name, a list of coordinates, a list of audio files, and a list of
+multiple image files. (In the current design of the app, it only makes sense to
+associate one audio file per region, but the format makes it easy to
+accommodate for multiple audio files in the future.) One disadvantage is that
+all media files have to have unique names. This is because the zip that is
+created by the Editour backend contains all of the media files in a flat file
+structure. The above JSON is used to associate each media file with a region,
+meaning that the filename needs to act as a primary key. The backend will
+respond with a message if this is the case, prompting the user to have unique
+names for all files.
 
@@
 
-The design of the Editour is agnostic about how the media will be used. For an
-app like izi.TRAVEL, the images are displayed when the associated audio tour is
-playing. The tour files produced by Editour could theoretically be used by a
-tour guide app that does not incorporate AR.
+The design of the Editour is agnostic about how the media will be used.  For
+an app like izi.TRAVEL, the images are displayed when the associated audio
+tour is playing. For ARuku, images can be placed onto the ground plane by the
+user, which is unique compared to other audio tour guide apps. The tour files
+produced by Editour could theoretically be used by a tour guide app that does
+not incorporate AR.
 

### 2019-09-24 paper.tex
added citation

--- 2019-09-23 paper.tex
@@
 
-\clearpage % references should be on their own page
+\nocite{harvey2002} % don't remove this
+
+\newpage % references should be on their own page
 

### 2019-09-24 paper.tex
edited editour section and added figures

--- 2019-09-23 paper.tex
@@
 different AR development platform.
-
-\subsubsection{KudanSlam}
-\label{sec:kudanSlam}
 
@@
 points on the map.  To terminate the polygon, the user must shift-click again.
-The ``Welcome to editour'' card provides these instructions, which should be
-enough to get started.  A user can only terminate the polygon after two points
-have been placed to prevent the user from drawing a region with an area of
-zero. Once a region is created, a region card appears in the side bar. From
-here, the user can edit anything about the region. From here, the user can edit
-anything about the region.
+The ``Welcome to Editour'' card (seen in Figure~\ref{fig:welcomeCard}) provides
+these instructions, which should be enough to get started.  A user can only
+terminate the polygon after two points have been placed to prevent the user
+from drawing a region with an area of zero. Once a region is created, a region
+card appears in the side bar. From here, the user can edit anything about the
+region. From here, the user can edit anything about the region.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.4\textwidth]{welcome-card-editour.png}
+    \caption{The ``Welcome to Editour'' card providing basic instructions to
+    get started}
+	\label{fig:welcomeCard}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\textwidth]{drawing-region-editour.png}
+    \caption{How the Editour looks when a region is being drawn, including the
+    two dotted preview lines}
+	\label{fig:drawingRegion}
+\end{figure}
 
@@
 
-The first subcard is the ``Rename'' subcard, which is fairly self-explanatory.
-This section expands to reveal a textbox, allowing the user to rename the
-region after clicking ``Okay'' or hitting the enter key. (There are multiple
-places in the UI where a textbox is immediately adjacent to a ``Confirm''
-button.  We made sure all of these can be triggered by simply hitting enter,
-since this is common when filling out forms.)
-
-The second subcard is slightly involved. Expanding the ``Media'' subcard by
-clicking on the green bar will reveal a bevy of options for augmenting the
-audio, images and text to be associated with that region of the tour. From
-here, the user can upload an audio file and multiple image files from his or
-her hard drive with the two file-select fields. If the tour has been downloaded
-as a server, the names of the files already present on the server will appear
-as cards with `X' buttons. This allows the user to remove images or audio from
-that region even after the tour has been uploaded.
+The first subcard seen in Figure~\ref{fig:renameSubcard} is the ``Rename''
+subcard, which is fairly self-explanatory.  This section expands to reveal a
+textbox, allowing the user to rename the region after clicking ``Okay'' or
+hitting the enter key. (There are multiple places in the UI where a textbox is
+immediately adjacent to a ``Confirm'' button.  We made sure all of these can be
+triggered by simply hitting enter, since this is common when filling out
+forms.)
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.4\textwidth]{rename-subcard-editour.png}
+	\caption{The ``Rename'' subcard}
+	\label{fig:renameSubcard}
+\end{figure}
+
+The second subcard seen in Figure~\ref{fig:mediaSubcard} is slightly involved.
+Expanding the ``Media'' subcard by clicking on the green bar will reveal a bevy
+of options for augmenting the audio, images and text to be associated with that
+region of the tour. From here, the user can upload an audio file and multiple
+image files from his or her hard drive with the two file-select fields. If the
+tour has been downloaded as a server, the names of the files already present on
+the server will appear as cards with `X' buttons. This allows the user to
+remove images or audio from that region even after the tour has been uploaded.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.4\textwidth]{media-subcard-editour.png}
+	\caption{The ``Media'' subcard}
+	\label{fig:mediaSubcard}
+\end{figure}
 
@@
 
-The third subcard is the ``Delete'' subcard. When revelead, another button will
-appear labeled ``Really Delete''. The action can be canceled by collapsing the
-subcard by hitting the bar now labeled ``Don't Delete!''. This prevents the user
-from accidentally deleting a region he or she did not mean to.
+\begin{figure}[h]
+	\centering
+    \includegraphics[width=\textwidth]{edit-subcard-with-map-editour.png}
+    \caption{The ``Edit'' subcard with the map showing vertices and edges that
+    can be edited}
+	\label{fig:editSubcardWithMap}
+\end{figure}
+
+The third subcard pictured in Figure~\ref{fig:deleteSubcard} is the ``Delete''
+subcard. When revealed, another button will appear labeled ``Really Delete''.
+The action can be canceled by collapsing the subcard by hitting the bar now
+labeled ``Don't Delete!''. This prevents the user from accidentally deleting a
+region he or she did not mean to.
+
+\begin{figure}[h]
+	\centering
+    \includegraphics[width=0.4\textwidth]{delete-subcard-editour.png}
+    \caption{The ``Delete'' subcard}
+	\label{fig:deleteSubcard}
+\end{figure}
 
@@
 that operation. When uploading and downloading, a percentage will be displayed
-indicating the upload/download process. If a 200 or 201 is returned from the
-server, a ``Success'' message will appear. If there was some problem, the error
-message returned by the server is displayed in this box instead. Since
-uploading, downloading and deleting are all network-related operations, it
-makes sense to include this message box for each card.
+indicating the upload/download process, which can be seen in
+Figure~\ref{ref:uploadingMessage}. If a 200 or 201 is returned from the server,
+a ``Success'' message will appear. If there was some problem, the error message
+returned by the server is displayed in this box instead. Since uploading,
+downloading and deleting are all network-related operations, it makes sense to
+include this message box for each card.
+
+\begin{figure}[h]
+	\centering
+    \includegraphics[width=0.4\textwidth]{uploading-message-editour.png}
+    \caption{The upload subcard with an upload status}
+	\label{fig:uploadingMessage}
+\end{figure}
 
@@
 stored on the server from the backend. This data is used to create a box of
-buttons, which includes one button for each tour file on the server. Clicking on
-one of these blue buttons will fill the textbox in with the correct name. Before
-this feature was implemented, the user had to correctly type the name of the
-saved tour into the textbox in order to retrieve it. The user is still free to
-do this, but the buttons make this easier and less error-prone.
+buttons, which includes one button for each tour file on the server. Clicking
+on one of these blue buttons will fill the textbox in with the correct name.
+Before this feature was implemented, the user had to correctly type the name of
+the saved tour into the textbox in order to retrieve it. The user is still free
+to do this, but the buttons make this easier and less error-prone. The download
+card containing a box filled with filenames on the server can be seen in
+Figure~\ref{download-card-editour.png}.
+
+\begin{figure}[h]
+	\centering
+    \includegraphics[width=0.4\textwidth]{download-card-editour.png}
+    \caption{The download card}
+	\label{fig:downloadCard}
+\end{figure}
 
@@
 constraints.  You can type in a latitude and longitude directly and hit the
-``Jump'' button. We also hard-coded some shortcuts for places that Atticus
+``Jump'' button. We also hard-coded a few shortcuts for places that Atticus
 might want to design a tour for in the future, which can be accessed by
 clicking on the yellow buttons with place names.
+
+\begin{figure}[h]
+	\centering
+    \includegraphics[width=0.4\textwidth]{jump-card-editour.png}
+    \caption{The jump card}
+	\label{fig:jumpCard}
+\end{figure}
 
@@
 
-Additionally, our web application allows users to edit existing tours. When the
-user requests to edit a tour on the frontend it sends a request to the backend
-server for that tour's metadata file. This file contains information about all
-regions and files in the tour. The user can then edit the regions, change names,
-upload new files, or delete existing ones without ever having to download the
-other tour files from the server, which could take a long time depending on
-their size. When the user is done editing they can upload the new metadata and
-any newly added files to the server, which intelligently collects new and old
-files required by the tour and zips them into a new tour file on the disk.
+As previously mentioned in \ref{sec:editingATour}, our web application allows
+users to edit existing tours. When the user requests to edit a tour on the
+frontend it sends a request to the backend server for that tour's metadata
+file. This file contains information about all regions and files in the tour.
+The user can then edit the regions, change names, upload new files, or delete
+existing ones without ever having to download the other tour files from the
+server, which could take a long time depending on their size. When the user is
+done editing they can upload the new metadata and any newly added files to the
+server, which intelligently collects new and old files required by the tour and
+zips them into a new tour file on the disk.
 
@@
 	\centering
-	\includegraphics[width=\textwidth]{intersections-diagram.png}
+	\includegraphics[width=0.7\textwidth]{intersections-diagram.png}
 	\caption{A visualization of the algorithm}

### 2019-09-24 paper.tex
fixed broken references

@@
 indicating the upload/download process, which can be seen in
-Figure~\ref{ref:uploadingMessage}. If a 200 or 201 is returned from the server,
+Figure~\ref{fig:uploadingMessage}. If a 200 or 201 is returned from the server,
 a ``Success'' message will appear. If there was some problem, the error message
@@
 card containing a box filled with filenames on the server can be seen in
-Figure~\ref{download-card-editour.png}.
+Figure~\ref{fig:downloadCard}.
 

### 2019-09-24 paper.tex
add API documentation appendix

@@
 \usepackage{bookmark} % links to other parts of the PDF
-%\usepackage{minted}
 % if we want to use a different style, here are some to look at
@@
 \addto{\captionsamerican}{\renewcommand*{\contentsname}{Table of Contents}}
+
+% custom environment for indenting whole paragraphs
+\newenvironment{indented}[1]%
+{\begin{list}{}%
+	{\setlength{\leftmargin}{#1}}%
+	\item[]%
+}
+{\end{list}}
 
@@
 different AR development platform.
+
+\subsubsection{KudanSlam}
+\label{sec:kudanSlam}
 
@@
 points on the map.  To terminate the polygon, the user must shift-click again.
-The ``Welcome to Editour'' card (seen in Figure~\ref{fig:welcomeCard}) provides
-these instructions, which should be enough to get started.  A user can only
-terminate the polygon after two points have been placed to prevent the user
-from drawing a region with an area of zero. Once a region is created, a region
-card appears in the side bar. From here, the user can edit anything about the
-region. From here, the user can edit anything about the region.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.4\textwidth]{welcome-card-editour.png}
-    \caption{The ``Welcome to Editour'' card providing basic instructions to
-    get started}
-	\label{fig:welcomeCard}
-\end{figure}
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{drawing-region-editour.png}
-    \caption{How the Editour looks when a region is being drawn, including the
-    two dotted preview lines}
-	\label{fig:drawingRegion}
-\end{figure}
+The ``Welcome to editour'' card provides these instructions, which should be
+enough to get started.  A user can only terminate the polygon after two points
+have been placed to prevent the user from drawing a region with an area of
+zero. Once a region is created, a region card appears in the side bar. From
+here, the user can edit anything about the region. From here, the user can edit
+anything about the region.
 
@@
 
-The first subcard seen in Figure~\ref{fig:renameSubcard} is the ``Rename''
-subcard, which is fairly self-explanatory.  This section expands to reveal a
-textbox, allowing the user to rename the region after clicking ``Okay'' or
-hitting the enter key. (There are multiple places in the UI where a textbox is
-immediately adjacent to a ``Confirm'' button.  We made sure all of these can be
-triggered by simply hitting enter, since this is common when filling out
-forms.)
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.4\textwidth]{rename-subcard-editour.png}
-	\caption{The ``Rename'' subcard}
-	\label{fig:renameSubcard}
-\end{figure}
-
-The second subcard seen in Figure~\ref{fig:mediaSubcard} is slightly involved.
-Expanding the ``Media'' subcard by clicking on the green bar will reveal a bevy
-of options for augmenting the audio, images and text to be associated with that
-region of the tour. From here, the user can upload an audio file and multiple
-image files from his or her hard drive with the two file-select fields. If the
-tour has been downloaded as a server, the names of the files already present on
-the server will appear as cards with `X' buttons. This allows the user to
-remove images or audio from that region even after the tour has been uploaded.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.4\textwidth]{media-subcard-editour.png}
-	\caption{The ``Media'' subcard}
-	\label{fig:mediaSubcard}
-\end{figure}
+The first subcard is the ``Rename'' subcard, which is fairly self-explanatory.
+This section expands to reveal a textbox, allowing the user to rename the
+region after clicking ``Okay'' or hitting the enter key. (There are multiple
+places in the UI where a textbox is immediately adjacent to a ``Confirm''
+button.  We made sure all of these can be triggered by simply hitting enter,
+since this is common when filling out forms.)
+
+The second subcard is slightly involved. Expanding the ``Media'' subcard by
+clicking on the green bar will reveal a bevy of options for augmenting the
+audio, images and text to be associated with that region of the tour. From
+here, the user can upload an audio file and multiple image files from his or
+her hard drive with the two file-select fields. If the tour has been downloaded
+as a server, the names of the files already present on the server will appear
+as cards with `X' buttons. This allows the user to remove images or audio from
+that region even after the tour has been uploaded.
 
@@
 
-\begin{figure}[h]
-	\centering
-    \includegraphics[width=\textwidth]{edit-subcard-with-map-editour.png}
-    \caption{The ``Edit'' subcard with the map showing vertices and edges that
-    can be edited}
-	\label{fig:editSubcardWithMap}
-\end{figure}
-
-The third subcard pictured in Figure~\ref{fig:deleteSubcard} is the ``Delete''
-subcard. When revealed, another button will appear labeled ``Really Delete''.
-The action can be canceled by collapsing the subcard by hitting the bar now
-labeled ``Don't Delete!''. This prevents the user from accidentally deleting a
-region he or she did not mean to.
-
-\begin{figure}[h]
-	\centering
-    \includegraphics[width=0.4\textwidth]{delete-subcard-editour.png}
-    \caption{The ``Delete'' subcard}
-	\label{fig:deleteSubcard}
-\end{figure}
+The third subcard is the ``Delete'' subcard. When revelead, another button will
+appear labeled ``Really Delete''. The action can be canceled by collapsing the
+subcard by hitting the bar now labeled ``Don't Delete!''. This prevents the user
+from accidentally deleting a region he or she did not mean to.
 
@@
 that operation. When uploading and downloading, a percentage will be displayed
-indicating the upload/download process, which can be seen in
-Figure~\ref{fig:uploadingMessage}. If a 200 or 201 is returned from the server,
-a ``Success'' message will appear. If there was some problem, the error message
-returned by the server is displayed in this box instead. Since uploading,
-downloading and deleting are all network-related operations, it makes sense to
-include this message box for each card.
-
-\begin{figure}[h]
-	\centering
-    \includegraphics[width=0.4\textwidth]{uploading-message-editour.png}
-    \caption{The upload subcard with an upload status}
-	\label{fig:uploadingMessage}
-\end{figure}
+indicating the upload/download process. If a 200 or 201 is returned from the
+server, a ``Success'' message will appear. If there was some problem, the error
+message returned by the server is displayed in this box instead. Since
+uploading, downloading and deleting are all network-related operations, it
+makes sense to include this message box for each card.
 
@@
 stored on the server from the backend. This data is used to create a box of
-buttons, which includes one button for each tour file on the server. Clicking
-on one of these blue buttons will fill the textbox in with the correct name.
-Before this feature was implemented, the user had to correctly type the name of
-the saved tour into the textbox in order to retrieve it. The user is still free
-to do this, but the buttons make this easier and less error-prone. The download
-card containing a box filled with filenames on the server can be seen in
-Figure~\ref{fig:downloadCard}.
-
-\begin{figure}[h]
-	\centering
-    \includegraphics[width=0.4\textwidth]{download-card-editour.png}
-    \caption{The download card}
-	\label{fig:downloadCard}
-\end{figure}
+buttons, which includes one button for each tour file on the server. Clicking on
+one of these blue buttons will fill the textbox in with the correct name. Before
+this feature was implemented, the user had to correctly type the name of the
+saved tour into the textbox in order to retrieve it. The user is still free to
+do this, but the buttons make this easier and less error-prone.
 
@@
 constraints.  You can type in a latitude and longitude directly and hit the
-``Jump'' button. We also hard-coded a few shortcuts for places that Atticus
+``Jump'' button. We also hard-coded some shortcuts for places that Atticus
 might want to design a tour for in the future, which can be accessed by
 clicking on the yellow buttons with place names.
-
-\begin{figure}[h]
-	\centering
-    \includegraphics[width=0.4\textwidth]{jump-card-editour.png}
-    \caption{The jump card}
-	\label{fig:jumpCard}
-\end{figure}
 
@@
 
-As previously mentioned in \ref{sec:editingATour}, our web application allows
-users to edit existing tours. When the user requests to edit a tour on the
-frontend it sends a request to the backend server for that tour's metadata
-file. This file contains information about all regions and files in the tour.
-The user can then edit the regions, change names, upload new files, or delete
-existing ones without ever having to download the other tour files from the
-server, which could take a long time depending on their size. When the user is
-done editing they can upload the new metadata and any newly added files to the
-server, which intelligently collects new and old files required by the tour and
-zips them into a new tour file on the disk.
+Additionally, our web application allows users to edit existing tours. When the
+user requests to edit a tour on the frontend it sends a request to the backend
+server for that tour's metadata file. This file contains information about all
+regions and files in the tour. The user can then edit the regions, change names,
+upload new files, or delete existing ones without ever having to download the
+other tour files from the server, which could take a long time depending on
+their size. When the user is done editing they can upload the new metadata and
+any newly added files to the server, which intelligently collects new and old
+files required by the tour and zips them into a new tour file on the disk.
 
@@
 	\centering
-	\includegraphics[width=0.7\textwidth]{intersections-diagram.png}
+	\includegraphics[width=\textwidth]{intersections-diagram.png}
 	\caption{A visualization of the algorithm}
@@
 
-% \begin{figure}[h]
-%	\centering
-%	\includegraphics[width=\textwidth]{turtle-burger.jpg}
-%	\caption[A rare but delicious turtle burger in the wild]{A rare but
-%		delicious turtle burger in the wild~\autocite{harvey2002}.}
-%	\label{fig:turtleBurger}
-%\end{figure}
-
 \newpage
@@
 \appendices
-\section{Proof of the First Zonklar Equation}
-Appendix one text goes here.
+\section{Editour API Documentation}
+
+Here is a list of API functions the Editour backend handles. The response is
+usually a JSON like this with fields called \texttt{status} and \texttt{message}
+The status is an HTTP status code like 200 (OK) or 404 (Not Found), and the
+message is a string or stringified JSON that contains the data of the response.
+
+\noindent\textbf{GET \texttt{/edit/:name}}
+
+\begin{indented}{1cm}
+	Returns the metadata file of the most recent tour with the given name. If
+	successful, it returns a status of 200 and the stringified metadata as the
+	message. If no tour with the given name is found it returns 404, and if the
+	server encounters an internal error while processing the request it returns
+	500.
+\end{indented}
+
+\noindent\textbf{GET \texttt{/tour/:name}}
+
+\begin{indented}{1cm}
+	This is the only API endpoint for which the response is not a JSON. Instead,
+	the response is the zip file of the most recent version of the tour with the
+	given name. Returns 404 if a tour with the given name isn't found or a 500
+	if there is an internal server error while processing the request.
+\end{indented}
+
+\noindent\textbf{GET \texttt{/tours}}
+
+\begin{indented}{1cm}
+	Gets a list of unique tours on the server, returning a list of their names
+	as the message of its response. Returns 200 if successful or 500 if there is
+	an internal server error while processing the request.
+\end{indented}
+
+\noindent\textbf{POST \texttt{/edit}}
+
+\begin{indented}{1cm}
+	Used for editing an existing tour. This request should contain the fields
+	\texttt{tourName}, \texttt{oldName}, and \texttt{metadata}, along with any
+	number of files.  The server will use the new metadata as well as the old
+	and new files to create a new version of an existing tour. Returns 201 if
+	the tour was edited successfully, 400 if the request was invalid, 404 if the
+	requested tour couldn't be found, or 500 if a server error occurred while
+	processing the request.
+\end{indented}
+
+\noindent\textbf{POST \texttt{/upload}}
+
+\begin{indented}{1cm}
+	Used for uploading a new tour. This request should include a
+	\texttt{tourName} field and a \texttt{metadata} field, along with any number
+	of files. It verifies the uploaded tour and creates a zip for it on the
+	server. Sends a 201 if the tour was created successfully, a 400 if the
+	request is invalid, or a 500 if a server error is encountered.
+\end{indented}
+
+\noindent\textbf{DELETE \texttt{/tour/:name}}
+
+\begin{indented}{1cm}
+	Deletes all versions of the tour with the given name from the server.
+	Returns 200 if successful, along with a message saying how many versions
+	were deleted, 404 if no tour with that name could be found, or 500 if a
+	server error was encountered.
+\end{indented}
+
+\newpage
 
 \section{}
+
 Appendix two text goes here.

### 2019-09-25 paper.tex
start deploying editour section

@@
 
-Before we could start working on creating our app, we first needed to decide which
-AR development platform to use. Our preliminary research had shown us that there
-are so many different platforms out there, all of which have been used to create
-great AR apps. There were a lot of things we needed to consider before finalizing
-on a platform, like what features it offered, which devices and operating systems the
-app could run on, and definitely the cost. Detailed below are some of the different
-platforms we considered.
+Before we could start working on creating our app, we first needed to decide
+which AR development platform to use. Our preliminary research had shown us that
+there are so many different platforms out there, all of which have been used to
+create great AR apps. There were a lot of things we needed to consider before
+finalizing on a platform, like what features it offered, which devices and
+operating systems the app could run on, and definitely the cost. Detailed below
+are some of the different platforms we considered.
 
@@
 
-Wikitude also supports all sorts of different platforms. It supports Android, Apple,
-and Windows phones and tablets, as well as smart glasses like the Epson Moverio,
-Microsoft Hololens, and Vuzix smart glasses~\autocite{wikitude2018}. Additionally,
-many different development frameworks are capable of running Wikitude's SDK.
-According to Wikitude's website, their SDK works with Windows, Android, and iOS
-development frameworks, as well as ARCore and ARKit, Flutter, Cordova, Xamarin,
-and even Unity~\autocite{wikitude2018}.
+Wikitude also supports all sorts of different platforms. It supports Android,
+Apple, and Windows phones and tablets, as well as smart glasses like the Epson
+Moverio, Microsoft Hololens, and Vuzix smart glasses~\autocite{wikitude2018}.
+Additionally, many different development frameworks are capable of running
+Wikitude's SDK.  According to Wikitude's website, their SDK works with Windows,
+Android, and iOS development frameworks, as well as ARCore and ARKit, Flutter,
+Cordova, Xamarin, and even Unity~\autocite{wikitude2018}.
 
@@
 frameworks used in mobile application development''~\autocite{viro2019}.
-While the majority of our team has decent experience with writing Javascript,
+While the majority of our team has decent experience with writing JavaScript,
 we all either have very little or no experience writing React apps.
@@
 points on the map.  To terminate the polygon, the user must shift-click again.
-The ``Welcome to editour'' card provides these instructions, which should be
+The ``Welcome to Editour'' card provides these instructions, which should be
 enough to get started.  A user can only terminate the polygon after two points
@@
 
+\subsubsection{Deploying the Editour Backend}
+\label{sec:deployingTheEditourBackend}
+
+For testing and development purposes the Editour backend was originally hosted
+on a personal server belonging to a member of our team. This was a CentOS
+virtual machine running on an old Dell rack server in Worcester, Massachusetts.
+We wrote a custom systemd service to run the Editour as a daemon and keep its
+log files organized. The Node.js backend was served by an Nginx reverse proxy
+running on the same virtual machine.
+
+While this worked well enough for testing, it was not a permanent solution. We
+asked Atticus to provide a more powerful---and geographically closer---hosting
+solution for running the Editour in the future. He obtained a domain name and
+shared hosting environment for us to use on September 23\textsuperscript{rd}.
+Unfortunately, this shared hosting environment was designed for running simple
+PHP applications like WordPress, so it took a bit of work to coerce it into
+running a Node.js application.
+
 \subsubsection{Future of Editour}
@@
 \label{sec:adobeXdDesign}
-On September 10th, Atticus Sims presented us with a storyboard for the app
-experience. We would not be able to resume work until September 17th due to
-prior travel plans. Whether Atticus knew this or not, the design he put forth
-had ramifications that rippled throughout the entire software stack we had
-constructed up to this point. Figure~\ref{fig:adobeXdDesign} shows this design.
+
+On September 10\textsuperscript{th} Atticus Sims presented us with a storyboard
+for the app experience. We would not be able to resume work until September
+17\textsuperscript{th} due to prior travel plans. Whether Atticus knew this or
+not, the design he put forth had ramifications that rippled throughout the
+entire software stack we had constructed up to this point.
+Figure~\ref{fig:adobeXdDesign} shows this design.
 
@@
 scrollable window of text for a transcript of the audio. Because of this, the
-Editour UI and tour metadata JSON file needed to be updated to accomodate a
+Editour UI and tour metadata JSON file needed to be updated to accommodate a
 transcript per region. On top of this, the C\# code that interprets the tour
@@
 	\includegraphics[width=0.5\textwidth]{editour-additions.png}
-	\caption[Additions to the editour to accommodate the new design]
-    {Additions to the editour to accommodate the new design}
+	\caption[Additions to the Editour to accommodate the new design]
+    {Additions to the Editour to accommodate the new design}
 	\label{fig:editourAdditions}
@@
 At this point, the codebase for Editour was already around three thousand lines
-of vanilla Javascript. Type-checking provided by Visual Studio Code and JSDoc
+of vanilla JavaScript. Type-checking provided by Visual Studio Code and JSDoc
 made the growing code complexity more manageable. Excluding Node.js modules,
@@
 objects. They're already there! Just drag .xd file to project and... voila!''
-We suspect this sounds too good to be true because it is. As of September 20th,
-2019, there are 6 user reviews. All of the five-star reviews were have the
-caveat ``Reviewer was gifted package by publisher'' which which we interpreted
-as a warning sign. Because of this, we decided to rebuild the UI largely from
-the ground up, using the Adobe XD file to guide us.
+We suspect this sounds too good to be true because it is. As of September
+20\textsuperscript{th}, 2019, there are 6 user reviews. All of the five-star
+reviews were have the caveat ``Reviewer was gifted package by publisher'' which
+which we interpreted as a warning sign. Because of this, we decided to rebuild
+the UI largely from the ground up, using the Adobe XD file to guide us.
 
@@
 
-Our first day of on-site testing with the app took place on September 6th.
-Using Editour, we rebuilt the izi.TRAVEL audio tour that Atticus already
-created. The first version of the rebuilt tour had regions that were relatively
-small; some regions were only a few meters across. This version of the tour can
-be seen in Figure~\ref{fig:kinkakujiTour}.
+Our first day of on-site testing with the app took place on September
+6\textsuperscript{th}. Using Editour, we rebuilt the izi.TRAVEL audio tour that
+Atticus already created. The first version of the rebuilt tour had regions that
+were relatively small; some regions were only a few meters across. This version
+of the tour can be seen in Figure~\ref{fig:kinkakujiTour}.
 

### 2019-09-25 paper.tex
added source and images

--- 2019-09-24 paper.tex
@@
 still has to be moved manually to the Unity project folder. In the future, we
-would like the app to be able to contact our Editour server and update the tour
-info by itself. This would allow Kyoto VR to update the tours without updating
-the entire app.
+would like the app to be able to contact a server running a version of the
+Editour backend and update the tour info by itself. This would allow Kyoto VR
+to update the tours without updating the entire app.
 
@@
 \label{sec:aruko}
+
+\subsubsection{GPS Functionality}
+\label{sec:gpsFunctionality}
+The core user experience of ARuko is the walking tour. By walking the given
+route, the user enters and exits specific geographic regions that invoke
+changes in the app, such as playing audio and displaying different images.
+Originally, we planned to mark regions by singular points, and trigger that
+region if the user was within a certain radius of that point.
+Implementation-wise, this would have been much simpler, but obviously limits
+possible tour designs. Consequently, we decided at an early stage to
+accommodate regions with arbitrary shape and size.  In the implementation, we
+provided support for both ``GPS Bubbles'' and ``GPS Polygons.'' In the end
+however, Editour made it trivial to use the more versatile ``GPS Polygons,'' so
+we eventually dropped support for regions triggered by distance.
 
@@
 Considering we had limited to no experience with React or Angular, it was also
-faster to develop the UI in the way we were used to from previous experience..
+faster to develop the UI in the way we were used to from previous experience.
 But if we were to continue to develop Editour, UI libraries and frontend build
@@
 
-As previously mentioned, Atticus initially wanted us to explore the efficacy of
-using Vuforia's 2D image target capabilities for scanning objects outside of
-the expected use case, such as 3D landscapes or the side of a building. We had
-serious doubts about how well this would work, and our suspicions were
-confirmed after some field testing. This was the reasoning behind focusing on
-ground-plane detection instead of image targets; ground-plane detection can be
-used anywhere, and is much more reliable than treating 3D objects as 2D image
-targets.
+Atticus initially wanted us to explore the efficacy of using Vuforia's 2D image
+target capabilities for scanning objects outside of the expected use case, such
+as 3D landscapes or the side of a building. We had serious doubts about how
+well this would work, and our suspicions were confirmed after some field
+testing. This was the reasoning behind focusing on ground-plane detection
+instead of image targets; ground-plane detection can be used anywhere, and is
+much more reliable than treating 3D objects as 2D image targets.
 
@@
 ``Transfer AdobeXd project directly to Unity. Forget about hours of positioning
-objects. They're already there! Just drag .xd file to project and... voila!''
-We suspect this sounds too good to be true because it is. As of September 20th,
-2019, there are 6 user reviews. All of the five-star reviews were have the
-caveat ``Reviewer was gifted package by publisher'' which which we interpreted
-as a warning sign. Because of this, we decided to rebuild the UI largely from
-the ground up, using the Adobe XD file to guide us.
+objects. They're already there! Just drag .xd file to project and...
+voila!''~\autocite{glasseye2019}.  We suspect this sounds too good to be true
+because it is. As of September 20th, 2019, there are 6 user reviews. All of the
+five-star reviews were have the caveat ``Reviewer was gifted package by
+publisher'' which which we interpreted as a warning sign. Because of this, we
+decided to rebuild the UI largely from the ground up, using the Adobe XD file
+to guide us.
 
@@
 
+One idea that was proposed initially was an AR audio experience using 3D
+spatialized audio.
+
 \newpage

### 2019-09-25 paper.tex

--- 2019-09-25 paper.tex
@@
 points on the map.  To terminate the polygon, the user must shift-click again.
-The ``Welcome to Editour'' card provides these instructions, which should be
-enough to get started.  A user can only terminate the polygon after two points
-have been placed to prevent the user from drawing a region with an area of
-zero. Once a region is created, a region card appears in the side bar. From
-here, the user can edit anything about the region. From here, the user can edit
-anything about the region.
+The ``Welcome to Editour'' card (seen in Figure~\ref{fig:welcomeCard}) provides
+these instructions, which should be enough to get started.  A user can only
+terminate the polygon after two points have been placed to prevent the user
+from drawing a region with an area of zero. Once a region is created, a region
+card appears in the side bar. From here, the user can edit anything about the
+region. From here, the user can edit anything about the region.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.4\textwidth]{welcome-card-editour.png}
+    \caption{The ``Welcome to Editour'' card providing basic instructions to
+    get started}
+	\label{fig:welcomeCard}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\textwidth]{drawing-region-editour.png}
+    \caption{How the Editour looks when a region is being drawn, including the
+    two dotted preview lines}
+	\label{fig:drawingRegion}
+\end{figure}
 
@@
 that operation. When uploading and downloading, a percentage will be displayed
-indicating the upload/download process. If a 200 or 201 is returned from the
-server, a ``Success'' message will appear. If there was some problem, the error
-message returned by the server is displayed in this box instead. Since
-uploading, downloading and deleting are all network-related operations, it
-makes sense to include this message box for each card.
+indicating the upload/download process, which can be seen in
+Figure~\ref{fig:uploadingMessage}. If a 200 or 201 is returned from the server,
+a ``Success'' message will appear. If there was some problem, the error message
+returned by the server is displayed in this box instead. Since uploading,
+downloading and deleting are all network-related operations, it makes sense to
+include this message box for each card.
+
+\begin{figure}[h]
+	\centering
+    \includegraphics[width=0.4\textwidth]{uploading-message-editour.png}
+    \caption{The upload subcard with an upload status}
+	\label{fig:uploadingMessage}
+\end{figure}
 
@@
 stored on the server from the backend. This data is used to create a box of
-buttons, which includes one button for each tour file on the server. Clicking on
-one of these blue buttons will fill the textbox in with the correct name. Before
-this feature was implemented, the user had to correctly type the name of the
-saved tour into the textbox in order to retrieve it. The user is still free to
-do this, but the buttons make this easier and less error-prone.
+buttons, which includes one button for each tour file on the server. Clicking
+on one of these blue buttons will fill the textbox in with the correct name.
+Before this feature was implemented, the user had to correctly type the name of
+the saved tour into the textbox in order to retrieve it. The user is still free
+to do this, but the buttons make this easier and less error-prone. The download
+card containing a box filled with filenames on the server can be seen in
+Figure~\ref{fig:downloadCard}.
+
+\begin{figure}[h]
+	\centering
+    \includegraphics[width=0.4\textwidth]{download-card-editour.png}
+    \caption{The download card}
+	\label{fig:downloadCard}
+\end{figure}
 
@@
 ``Transfer AdobeXd project directly to Unity. Forget about hours of positioning
-objects. They're already there! Just drag .xd file to project and... voila!''
-We suspect this sounds too good to be true because it is. As of September
-20\textsuperscript{th}, 2019, there are 6 user reviews. All of the five-star
-reviews were have the caveat ``Reviewer was gifted package by publisher'' which
-which we interpreted as a warning sign. Because of this, we decided to rebuild
-the UI largely from the ground up, using the Adobe XD file to guide us.
+objects. They're already there! Just drag .xd file to project and...
+voila!''~\autocite{glasseye2019}.  We suspect this sounds too good to be true
+because it is. As of September 20\textsuperscript{th}, 2019, there are 6 user
+reviews. All of the five-star reviews were have the caveat ``Reviewer was gifted
+package by publisher'' which which we interpreted as a warning sign. Because of
+this, we decided to rebuild the UI largely from the ground up, using the Adobe XD
+file to guide us.
 

### 2019-09-25 paper.tex
add more to deploying editour section

@@
 solution for running the Editour in the future. He obtained a domain name and
-shared hosting environment for us to use on September 23\textsuperscript{rd}.
-Unfortunately, this shared hosting environment was designed for running simple
-PHP applications like WordPress, so it took a bit of work to coerce it into
-running a Node.js application.
+shared hosting environment on a Red Hat Enterprise Linux (RHEL) server for us to
+use on September 23\textsuperscript{rd}. Unfortunately, this shared hosting
+environment was designed for running simple PHP applications like WordPress, so
+it took a bit of work to coerce it into running a Node.js application.
+
+We were able to get shell access to the shared hosting environment, but without
+superuser privileges. This meant we couldn't install packages, change system
+settings, or access systemctl. In order to install Node.js and npm in this
+environment we had to use Node Version Manager, a series of shell scripts that
+handles downloading and compiling various versions of Node~\autocite{nvmsh2019}.
+The only difficulty with this was finding a version of Node.js that could
+compile with the older version of GCC the RHEL server had. Fortunately the
+server already had git installed, so we were able to simply clone the backend
+from GitHub and run it with npm.
+
+However, the server already had Apache listening on port 80, and without
+superuser privileges we could not edit the Apache configuration files to change
+this. Instead we decided to configure Apache as a reverse proxy, using only the
+rules that can be put in a \texttt{.htaccess} file, since this is the only
+configuration file we could access. Using Apache's \texttt{mod\_rewrite} module
+we were able to rewrite incoming requests on port 80 to instead go to
+\texttt{localhost:3000}, the port Node.js was listening
+on~\autocite{apache2019}.
 

### 2019-09-25 paper.tex
finish deploying editour section

@@
 superuser privileges. This meant we couldn't install packages, change system
-settings, or access systemctl. In order to install Node.js and npm in this
-environment we had to use Node Version Manager, a series of shell scripts that
-handles downloading and compiling various versions of Node~\autocite{nvmsh2019}.
-The only difficulty with this was finding a version of Node.js that could
-compile with the older version of GCC the RHEL server had. Fortunately the
-server already had git installed, so we were able to simply clone the backend
-from GitHub and run it with npm.
+settings, or access \texttt{systemctl}. In order to install Node.js and npm in
+this environment we had to use Node Version Manager, a series of shell scripts
+that handles downloading and compiling various versions of
+Node~\autocite{nvmsh2019}.  The only difficulty with this was finding a version
+of Node.js that could compile with the older version of GCC the RHEL server had.
+Fortunately the server already had git installed, so we were able to simply
+clone the backend from GitHub and run it with npm.
 
@@
 we were able to rewrite incoming requests on port 80 to instead go to
-\texttt{localhost:3000}, the port Node.js was listening
-on~\autocite{apache2019}.
+\texttt{localhost:3000}, the port where Node.js was
+listening~\autocite{apache2019}.
+
+With no access to \texttt{systemctl} we could not use the custom systemd service
+we wrote to manage the server daemon. Instead, we used a custom shell script and
+an npm package called ``forever'' to handle starting and stopping it. The
+forever package runs Node.js scripts continuously, automatically restarting them
+if they crash~\autocite{robbins2019}.
 

### 2019-09-26 paper.tex
fix grammar

@@
 option for ViroAR. ViroReact leverages the cross-platform capabilities of
-React, which is Facebook's Javascript Library for developing user
+React, which is Facebook's JavaScript Library for developing user
 interfaces~\autocite{facebook2019}.
@@
 
+The backend implements a representational state transfer (REST) API, utilizing
+HTTP methods to manipulate tour data on the server. For full documentation of
+the backend's API, see Appendix~\ref{sec:editourAPIDocumentation}.
+
 \subsubsection{Deploying the Editour Backend}
@@
 the only external library we used for Editour was Leaflet, an open-source
-JavaScript library for interactive maps \autocite{leafletjs}. We did not use
+JavaScript library for interactive maps~\autocite{leafletjs}. We did not use
 any libraries for developing frontends like Facebook's React or Google's
@@
 successive builds of the frontend. When bugs were found, we would log these as
-``Issues'' on the GitHub repo. These issues would get resolved in successive
-pull requests.
+``Issues'' on the GitHub repository. These issues would get resolved in
+successive pull requests.
 
@@
 upon re-entering a region, since the audio would still be playing once a user
-left the region. The region at the bottom surrounding our domitories was added
+left the region. The region at the bottom surrounding our dormitories was added
 for our convenience, allowing us to test the app while we were away from the
@@
 to create a second, ``chunkier'' tour.  In the tour-file
-\texttt{kinkakuji-chunkier}, we expanded all of the regions to accomodate for
+\texttt{kinkakuji-chunkier}, we expanded all of the regions to accommodate for
 potential GPS inaccuracies that could place the user outside the range of the
@@
 \section{Editour API Documentation}
+\label{sec:editourAPIDocumentation}
 

### 2019-09-26 paper.tex
fix more typos

@@
 spectacles and simple tricks~\autocite{theappsolutions2018}. For example, one
-of the most popular apps to use AR, Pokemon GO, primarily uses it's AR feature
-to place a Pokemon in the world aroudn you through your phone camera for you to
+of the most popular apps to use AR, Pokémon GO, primarily uses it's AR feature
+to place a Pokémon in the world around you through your phone camera for you to
 capture. But when it is in the world, it does not interact with anything around
@@
 well or better without AR~\autocite{theappsolutions2018}. Returning to the
-Pokemon GO example, when the AR feature is left on while capturing a Pokemon,
+Pokémon GO example, when the AR feature is left on while capturing a Pokémon,
 the extra power needed for this feature drains the device faster, makes it
-harder to hit the Pokemon with a Pokeball due to the model drifting in the
+harder to hit the Pokémon with a Pokéball due to the model drifting in the
 environment, and can even slow app performance, all of which detract from the
@@
 for augmentation using flat surfaces; Image Tracking, allowing for augmentation
-using one or multiple 2D images; and Geo AR, allowing for creation of geo
-markers at specific locations to triggered AR content~\autocite{wikitude2018}.
+using one or multiple 2D images; and Geo AR, allowing for creation of
+geo-markers at specific locations to triggered AR
+content~\autocite{wikitude2018}.
 
@@
 The company motive.io used to work on a product that would allow users to
-create an engaging AR experience in the style of Pokemon Go. Their service
+create an engaging AR experience in the style of Pokémon Go. Their service
 would have purportedly handled technical details such as hosting, storage, and
@@
 problem facing emulators is just as real as it was in 1988. Considering that AR
-already pushes modern phone harware to the limit, emulation is not something is
+already pushes modern phone hardware to the limit, emulation is not something is
 not something we wanted to struggle with. On top of this, our testing required
@@
 The goal of Editour is to allow a non-technical user to design audio tours
-through a web-app. At its core, Editour is a tool to draw arbitarily-shaped
+through a web-app. At its core, Editour is a tool to draw arbitrarily-shaped
 geographic regions onto a map.
@@
 
-Even with knowledge of C\# and Unity, inputing tour data this way is obviously
+Even with knowledge of C\# and Unity, inputting tour data this way is obviously
 not convenient. Atticus reminded us that, although he has a working knowledge
@@
          "name": "Beautiful Place",
-         "points": [ {"lat": 23.4, "lng": 56.7}, /* list omitted for brevity */ ],
+         "points": [ {"lat": 34.979222, "lng": 135.963628}, ... ],
          "audio": [ "beautiful-audio.mp3" ],
@@
          "name": "Gorgeous Place",
-         "points": [ {"lat": 12.3, "lng": 45.6}, /* list omitted for brevity */ ],
+         "points": [ {"lat": 34.979754, "lng": 135.964889}, ... ],
          "audio": [ "gorgeous-audio.mp3" ],
@@
 
-The backend implements a representational state transfer (REST) API, utilizing
-HTTP methods to manipulate tour data on the server. For full documentation of
+The backend implements a representational state transfer (REST) API.
+In a ``RESTful'' service, web resources are manipulated with a predefined set of
+stateless operations~\autocite{rfc7231}. Because the REST API is operated over
+the Hypertext Transfer Protocol (HTTP), the available operations are just the
+standard HTTP methods, such as GET, POST, and DELETE. For full documentation of
 the backend's API, see Appendix~\ref{sec:editourAPIDocumentation}.
@@
 usually a JSON like this with fields called \texttt{status} and \texttt{message}
-The status is an HTTP status code like 200 (OK) or 404 (Not Found), and the
-message is a string or stringified JSON that contains the data of the response.
+The status is an HTTP status code like 200 (OK) or 404
+(Not~Found)~\autocite{rfc7231}, and the message is a string or stringified JSON
+that contains the data of the response.
 

### 2019-09-26 paper.tex
fix styling

@@
 % useful packages
-\usepackage[utf8]{inputenc}
-\usepackage{minted}
-\usepackage[american]{babel}
-\usepackage{csquotes}
+\usepackage[utf8]{inputenc} % UTF-8 support
+\usepackage{minted} % for code snippets
+\usepackage[american]{babel} % for changing particular titles
+\usepackage{csquotes} % recommended for biblatex
 \usepackage{graphicx} % for images
@@
 % https://www.overleaf.com/learn/latex/Biblatex_bibliography_styles
-\usepackage[backend=biber,style=numeric,sorting=none]{biblatex}
-\usepackage[page, titletoc, title]{appendix}
+\usepackage[backend=biber,style=numeric,sorting=none]{biblatex} % citations
+\usepackage[page, titletoc, title]{appendix} % labeled appendices
 \usepackage[margin=1in]{geometry} % set 1in margins
 \usepackage{hyperref} % hyperlinks
+\usepackage{setspace} % setting custom spacing
 
 % more breathing room
-\linespread{1.5}
 \setminted{fontsize=\small,baselinestretch=1}
@@
 \graphicspath{ {./images/} } % put images in here
-\title{Kyoto VR MQP Paper First Draft}
+\title{%
+	\huge ARuko and Editour: \\
+	\Large A Platform for Augmented Reality Tour Guide Apps}
 \author{William~Campbell, Cole~Granof, and Joseph~Petitti}
-\date{\today}
+\date{October 11, 2019}
 
@@
 
+% draw the title page
 \maketitle
 
+% more breathing room
+\setstretch{1.5}
+
 \begin{abstract}
+	% abstract goes here
 	\begin{figure}[h]
@@
 		\includegraphics[width=\textwidth]{abstract.jpg}
-	% Note: you don't actually need the part in square brackets for the caption,
-	% but if you omit it the regular caption text will be used for the List of
-	% Figures entry.
+		% Note: you don't actually need the part in square brackets for the
+		% caption, but if you omit it the regular caption text will be used for
+		% the List of Figures entry.
 		\caption[\textit{Number 1, 1950 (Lavender Mist)}, Jackson Pollock]
@@
 
-Finally, a thank you to our advisers: Professors Joshua Cuneo and Ralph Sutter.
+Finally, a thank you to our advisers, Professors Joshua Cuneo and Ralph Sutter.
 Without their expert advice and feedback this project probably could not have
@@
 
-\clearpage
+\newpage
 
@@
 % these should be single spaced
-{
-\linespread{1}
-
+\begin{singlespace}
+	\tableofcontents
 	% add table of contents to itself
-\tableofcontents
 	\addcontentsline{toc}{section}{Table of Contents}
@@
 	\newpage
+\end{singlespace}
 
@@
 %\newpage
-}
 
@@
 functionality or practicality; quite simply, they are primarily used for minor
-spectacles and simple tricks~\autocite{theappsolutions2018}. For example, one
-of the most popular apps to use AR, Pokémon GO, primarily uses it's AR feature
-to place a Pokémon in the world around you through your phone camera for you to
-capture. But when it is in the world, it does not interact with anything around
-it. It just floats a fixed distance away from you, simply placed on top of your
-camera's video feed.
+spectacles and simple tricks~\autocite{theappsolutions2018}. For example, one of
+the most popular apps to use AR, \textit{Pokémon Go}, primarily uses it's AR
+feature to place a Pokémon in the world around you through your phone camera for
+you to capture. But when it is in the world, it does not interact with anything
+around it. It just floats a fixed distance away from you, simply placed on top
+of your camera's video feed.
 
@@
 well or better without AR~\autocite{theappsolutions2018}. Returning to the
-Pokémon GO example, when the AR feature is left on while capturing a Pokémon,
-the extra power needed for this feature drains the device faster, makes it
-harder to hit the Pokémon with a Pokéball due to the model drifting in the
+\textit{Pokémon Go} example, when the AR feature is left on while capturing a
+Pokémon, the extra power needed for this feature drains the device faster, makes
+it harder to hit the Pokémon with a Pokéball due to the model drifting in the
 environment, and can even slow app performance, all of which detract from the
@@
 
-The company motive.io used to work on a product that would allow users to
-create an engaging AR experience in the style of Pokémon Go. Their service
+The company motive.io used to work on a product that would allow users to create
+an engaging AR experience in the style of \textit{Pokémon Go}. Their service
 would have purportedly handled technical details such as hosting, storage, and
 user accounts. The promotional video shows the creation of a location-based AR
-game where the user pretends to hack into ATMs using the real-world locations
-of ATMs in a city\autocite{odom2017}.
+game where the user pretends to hack into ATMs using the real-world locations of
+ATMs in a city\autocite{odom2017}.
 
@@
 use for their intended users.
+
+\nocite{harvey2002} % don't remove this
 
@@
 
-\subsubsection{First Round of Field Testing}
-\label{sec:firstRoundOfFieldTesting}
+\subsubsection{Initial Field Testing}
+\label{sec:initialFieldTesting}
 
@@
 
+\subsubsection{Final Field Testing}
+\label{sec:finalFieldTesting}
+
+On September 26\textsuperscript{th} we returned to Kinkaku-ji with a nearly
+complete version of the ARuko in order to conduct some final testing.
+
 \newpage
@@
 
-\nocite{harvey2002} % don't remove this
-
 \newpage % references should be on their own page
 
+% references should be single spaced
+\begin{singlespace}
 	\printbibliography
 	\addcontentsline{toc}{section}{References}
+\end{singlespace}
 

### 2019-09-27 paper.tex
add a lot of stuff
Add Appendix B, fix grammar, add citations, add images, add final field
testing section, add list of tables, clean up table of contents, and
rearrange some sections.

@@
 \usepackage{setspace} % setting custom spacing
+\usepackage{tabulary} % nicer tables
 
@@
 	\tableofcontents
-	% add table of contents to itself
-	\addcontentsline{toc}{section}{Table of Contents}
+	% uncomment this if you want the Table of Contents to have an entry in the
+	% table of contents
+	% \addcontentsline{toc}{section}{Table of Contents}
 	\newpage
@@
 	\listoffigures
-	\addcontentsline{toc}{section}{List of Figures}
+	% \addcontentsline{toc}{section}{List of Figures}
+	\newpage
+
+	\listoftables
+	% \addcontentsline{toc}{section}{List of Tables}
 	\newpage
 \end{singlespace}
-
-% we don't have any tables yet, but uncomment this when we do
-%\addcontentsline{toc}{section}{List of Tables}
-%\listoftables
-%\newpage
 
@@
 While preparing for this project our team researched the current state of
-augmented reality technology. Smartphones are the most commonly used AR
-hardware by far [citation needed]. Typically smartphone AR applications make
-use of the phone's camera, accelerometer, gyroscope, and GPS sensors to
-reproduce a view of the real world with virtual information layered on top of
+augmented reality technology. Smartphones are the most commonly used AR hardware
+by far~\autocite{boland2018}. Typically smartphone AR applications make use of
+the phone's camera, accelerometer, gyroscope, and GPS sensors to reproduce a
+view of the real world with virtual information layered on top of
 it~\autocite{bonsor2018}.
@@
 almost all of the important features of an actual Android device, including
-calls, text, GPS position, device rotation and more \autocite{androidemulator}.
+calls, text, GPS position, device rotation and more~\autocite{androidemulator}.
 
@@
 real hardware. Emulation is often imperfect, so glitches sometimes emerge in
-emulation that do not manifest on the actual hardware [citation needed about
-emulator inaccuracies]. Conversely, errors that exist in the hardware version
-may not appear in the emulation. Secondly, and most importantly for AR, it is
-common for emulation to be much slower compared to real hardware.
+emulation that do not manifest on the actual hardware~\autocite{alzaylaee2017}.
+Conversely, errors that exist in the hardware version may not appear in the
+emulation. Secondly, and most importantly for AR, it is common for emulation to
+be much slower compared to real hardware.
 
@@
 One of the goals for our project is to create a working prototype that others
-can build off of in the future [citation needed for personal communication].
-
-Similar to the app izi.TRAVEL discussed in section~\ref{sec:iziTravel}, we
+can build off of in the future.
+
+Similar to the app izi.TRAVEL discussed in Section~\ref{sec:iziTravel}, we
 needed some way to easily define arbitrary polygons (which we call ``regions'')
@@
 For testing purposes, we initially defined these regions directly in the C\#
-Scripts, hard-coding the coordinates. [citation needed for source used to
-write polygon detection code] Below is an example of a quadrilateral
-surrounding the Creation Core building at the Ritsumeikan Biwako-Kusatsu
-campus.
+Scripts, hard-coding the coordinates. Below is an example of a quadrilateral
+surrounding the Creation Core building at the Ritsumeikan Biwako-Kusatsu campus.
 
@@
 Even with knowledge of C\# and Unity, inputting tour data this way is obviously
-not convenient. Atticus reminded us that, although he has a working knowledge
-of Unity, he is not a software developer [citation needed for personal
-communication.] In order to make our app prototype at all useful for the
-future, we needed to provide an easy way to ``design'' a tour.
+not convenient. Atticus reminded us that, although he has a working knowledge of
+Unity, he is not a software developer. In order to make our app prototype at all
+useful for the future, we needed to provide an easy way to ``design'' a tour.
 
@@
 
+Tours are stored on the server as compressed \texttt{.zip} files, but when
+uploading or editing a tour these zips are decompressed to a temporary
+directory. To prevent the server's limited disk space from filling up with old
+temporary files we wrote a simple bash script that removes directories that
+haven't been modified in the past five days. We set up a \texttt{cron} job to
+run this script automatically once per day to clean out old temporary files that
+aren't being used any more.
+
 \subsubsection{Future of Editour}
@@
 \begin{figure}[h] \centering
-    \includegraphics[width=0.5\textwidth]{sign-translation.png}
+    \includegraphics[width=0.3\textwidth]{sign-translation.png}
     \caption{Translated sign using AR camera}
@@
 
-\subsubsection{Unit Testing ARuko}
+\subsubsection{Editour Frontend Testing}
+\label{sec:editourFrontendTesting}
+
+We suspect that Editour might have a life outside of this particular use case
+for designing tours, depending on how we choose to further develop this
+software. This is why Editour is perhaps more polished than your typical tool
+purely for internal use.
+
+For the duration of the project however, Editour only had to be used by us
+three and Atticus. Therefore, the testing for the frontend of Editour was less
+systematic than other parts of the software stack. This decision also helped us
+focus our efforts on testing the reliability and user experience of ARuko. That
+being said, we were able to add many feature and get the Editour experience to
+a polished state through our own testing, using GitHub's tools to keep us
+organized.
+
+In order to test for bugs, all three of us periodically interacted with
+successive builds of the frontend. When bugs were found, we would log these as
+``Issues'' on the GitHub repository. These issues would get resolved in
+successive pull requests.
+
+Since we had to use Editour frequently to create test tours for ARuko, we were
+able to identify features that would make our own work more efficient. This
+worked as a kind of informal user testing. We kept track of feature requests
+using the same system as bug reports.
+
+Issues and feature requests alike got resolved in future pull requests. We
+resolved over thirty issues and feature requests using this workflow. The
+GitHub issues tab (which can be see in Figure~\ref{fig:issuesPageExample}) was
+very useful for making sure we made use of our user testing and bug testing.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{issues-page-example.png}
+	\caption{The GitHub issues tab for Editour}
+	\label{fig:issuesPageExample}
+\end{figure}
+
+\subsection{Unit Testing ARuko}
 \label{sec:unitTestingARuko}
@@
 number of times. Figure~\ref{fig:intersectionsDiagram} should make it clear why
-this works. This algorithm runs in $O(n)$, where $n$ is the sum total of the
-number of vertices of all of the polygons being tested
-~\autocite{geeksforgeekspolygon}.
+this works. This algorithm's time complexity is $O(n)$, where $n$ is the sum
+total of the number of vertices of all of the polygons being
+tested~\autocite{geeksforgeekspolygon}.
 
@@
 catch and deal with this edge case.
-
-\subsection{Editour Frontend Testing}
-\label{sec:editourFrontendTesting}
-
-We suspect that Editour might have a life outside of this particular use case
-for designing tours, depending on how we choose to further develop this
-software. This is why Editour is perhaps more polished than your typical tool
-purely for internal use.
-
-For the duration of the project however, Editour only had to be used by us
-three and Atticus. Therefore, the testing for the frontend of Editour was less
-systematic than other parts of the software stack. This decision also helped us
-focus our efforts on testing the reliability and user experience of ARuko. That
-being said, we were able to add many feature and get the Editour experience to
-a polished state through our own testing, using GitHub's tools to keep us
-organized.
-
-In order to test for bugs, all three of us periodically interacted with
-successive builds of the frontend. When bugs were found, we would log these as
-``Issues'' on the GitHub repository. These issues would get resolved in
-successive pull requests.
-
-Since we had to use Editour frequently to create test tours for ARuko, we were
-able to identify features that would make our own work more efficient. This
-worked as a kind of informal user testing. We kept track of feature requests
-using the same system as bug reports.
-
-Issues and feature requests alike got resolved in future pull requests. We
-resolved over thirty issues and feature requests using this workflow. The
-GitHub issues tab (which can be see in Figure~\ref{fig:issuesPageExample}) was
-very useful for making sure we made use of our user testing and bug testing.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=\textwidth]{issues-page-example.png}
-	\caption{The GitHub issues tab for Editour}
-	\label{fig:issuesPageExample}
-\end{figure}
 
@@
 On September 26\textsuperscript{th} we returned to Kinkaku-ji with a nearly
-complete version of the ARuko in order to conduct some final testing.
-
-\newpage
+complete version of the ARuko in order to conduct some final testing. We met up
+with Atticus, the IQP group, and our intern Hikaru and installed the beta
+version of ARuko on each of their phones. With little instruction about how the
+app works we had each of them try going through Kinkaku-ji while listening to
+the tour and using the app's features. Each member of our team also installed
+the beta version so we could fuzz test it.
+
+This was our first time trying the AR image recognition on the actual signs at
+Kinkaku-ji, rather than photographs of the signs, and it worked quite well.
+Vuforia was able to recognize all of the signs, even in different lighting than
+when the reference images were taken. For image targets that were small, far
+away, or obscured by shadows image recognition was slower, but Vuforia was
+always able to recognize them eventually. We discovered that the targets that
+worked best were large, had a lot of high-contrast text, and were uniformly lit.
+
+While testing we discovered some issues with the design of the tour. One region
+was completely misplaced, so the audio played at the wrong time while walking
+through the area. Several other regions were too big, so the audio started
+playing long before the user was actually near the feature it was discussing.
+Finally, one of the image targets had the wrong text in its information pop-up.
+These were all easy bugs to fix, but if we might not have noticed them if we
+had not tested the app on site.
+
+Another major bug we discovered was that the GPS stopped updating when not on
+the main screen. This means that if you were in AR camera mode the app would not
+trigger new audio when you walked into a new region. This was caused by the GPS
+script being attached to a UI element on the main screen, so it was resolved
+simply by moving this script.
+
+After having Atticus go through the tour on his phone he also discovered several
+bugs and tweaks he wanted to make to the UI. The clickable information button on
+image targets was made larger so it is easier to see. The UI buttons in the
+bottom menu bar were also made larger and easier to press. The text ``Main'' was
+added under the central button that brings you to the screen with the images and
+transcript, so it was more clear what that button does. The header text at the
+top was too big, and sometimes overflowed onto other UI elements.
+
+Testing with Atticus revealed another user interface issue we had not
+considered.  Many modern smartphones, such as Atticus's Samsung Galaxy S10+,
+have holes or notches cut out of the screen for cameras, speakers, and other
+hardware (see Figures \ref{fig:galaxyS10Plus} and \ref{fig:iPhoneX}). We had
+been designing our UI for rectangular phone screens, so the Galaxy S10+'s ``hole
+punch'' covered some UI elements in the top right corner. To account for this
+issue we added more padding to the top of the UI.
+
+After going through Kinkaku-ji with the app twice we had each test participant
+fill out a simple survey giving their thoughts on the app. The full results of
+these surveys can be found in Appendix~\ref{sec:testingSurveyResults}.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{galaxy-s10+.jpg}
+	\caption[A Samsung Galaxy S10+ phone with distinctive ``hole punch''
+	cameras]{A Samsung Galaxy S10+ phone with distinctive ``hole punch''
+		cameras~\autocite{yoo2019}}
+	\label{fig:galaxyS10Plus}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{iphone-x.jpg}
+	\caption[An iPhone X with a large notch]{An iPhone X with a large
+		notch~\autocite{yoo2017}}
+	\label{fig:iPhoneX}
+\end{figure}
+
+\clearpage
 
@@
 
-\newpage
-
-\section{3D Spatialized Audio Tour}
+\subsection{3D Spatialized Audio Tour}
 \label{sec:3dSpatializedAudioTour}
@@
 
-\section{}
-
-Appendix two text goes here.
+\section{Testing Survey Results}
+\label{sec:testingSurveyResults}
+
+After testing a near-complete prototype of ARuko at Kinkaku-ji on September
+26\textsuperscript{th}, we had each test subject fill out a simple survey with
+their thoughts on the app. The full results are listed below.
+
+% for tabularx
+% \newcolumntype{L}{>{\raggedright\arraybackslash\footnotesize}X}%
+
+\begin{table}[h]
+\begin{singlespace}
+\begin{tabulary}{\textwidth}{ L | L | L | L | L | L }
+	I enjoyed the audio tour & The image gallery added to the audio tour & I
+	found the AR translation feature helpful & I found the AR map overlay
+	helpful & The AR features were easy to use & Do you have any other thoughts
+	on how to improve the experience? \\
+	\hline
+
+	Strongly agree & Agree & Strongly agree & Strongly agree & Agree & I thought
+	the idea about a sound playing before the audio starts is a really good
+	idea! \\
+
+	Agree & Agree & Agree & Neutral & Neutral & Add a audio queue when a new
+	track starts. Make the AR buttons bigger/easier to click. \\
+
+	Agree & Agree & Strongly agree & Neutral & Agree & Increasing GPS accuracy
+	of course. Adding a tracking "you are here" marker to the route. \\
+
+	Strongly agree & Strongly agree & Strongly agree & Strongly agree & Strongly
+	agree & Typo in the text on 4/11 towards the end \\
+
+	Agree & Agree & Strongly agree & Disagree & Neutral & Zoom in ar mode \\
+\end{tabulary}
+\end{singlespace}
+\caption{Results of final field test survey}
+\label{tab:testingSurveyResults}
+\end{table}
 

### 2019-09-27 paper.tex
add more to introduction

@@
 
-% call it "Table of Contents" instead of just "Contents"
-\addto{\captionsamerican}{\renewcommand*{\contentsname}{Table of Contents}}
+% uncomment this to call it "Table of Contents" instead of just "Contents"
+% \addto{\captionsamerican}{\renewcommand*{\contentsname}{Table of Contents}}
 
@@
 
-\newpage
+\clearpage
 
@@
 	% \addcontentsline{toc}{section}{Table of Contents}
-	\newpage
+	\clearpage
 
@@
 	% \addcontentsline{toc}{section}{List of Figures}
-	\newpage
+	\clearpage
 
@@
 	% \addcontentsline{toc}{section}{List of Tables}
-	\newpage
+	\clearpage
 \end{singlespace}
@@
 information to tourists and art viewers that they would not be able to get any
-other way.
-
-Kinkaku-ji, the ``golden pavilion'' of Kyoto, is the perfect example of
-this~\autocite{bornoff2000}.
-
-\newpage
+other way. Kinkaku-ji, the ``golden pavilion'' of Kyoto, is the perfect example
+of this~\autocite{bornoff2000}. Kinkaku-ji is a UNESCO World Heritage
+Site~\autocite{unesco} and one of the most popular tourist destinations in
+Japan~\autocite{japanguide2019}. However, much of the historic information at
+the site is lost on visitors because it is not readily available to non-Japanese
+speakers.
+
+To solve this problem and open up the peerless beauty of the Golden Pavilion to
+more people, our team created ARuko and Editour. These two tools comprise a
+complete platform for designing and experiencing AR-enhanced tours.
+
+\clearpage
 
@@
 spectacles and simple tricks~\autocite{theappsolutions2018}. For example, one of
-the most popular apps to use AR, \textit{Pokémon Go}, primarily uses it's AR
+the most popular apps to use AR, \textit{Pokémon Go}, primarily uses its AR
 feature to place a Pokémon in the world around you through your phone camera for
@@
 	\includegraphics[width=0.5\textwidth]{drawing-region-editour.png}
-    \caption{How the Editour looks when a region is being drawn, including the
-    two dotted preview lines}
+	\caption{Editour when a region is being drawn, including the two dotted
+		preview lines}
 	\label{fig:drawingRegion}
@@
 inside a particular arbitrarily-defined geographic region are very important to
-get right.  Using Unity's built-in NUnit unit-testing framework, we wrote tests
+get right.  Using Unity's built-in NUnit unit testing framework, we wrote tests
 to verify whether the tour data was being parsed correctly, and whether the tour
@@
 For this, we implemented a few mathematical functions for individual parts of
-the algorithm, such as testing for intersection. We wrote unit-tests to test
+the algorithm, such as testing for intersection. We wrote unit tests to test
 each part of the algorithm, so we could be confident that the GPS component of
@@
 
-\newpage % references should be on their own page
+\clearpage % references should be on their own page
 

### 2019-09-27 paper.tex
add more to intro

@@
 \usepackage{tabulary} % nicer tables
+\usepackage{CJKutf8} % for Japanese UTF-8 characters
 
@@
 Site~\autocite{unesco} and one of the most popular tourist destinations in
-Japan~\autocite{japanguide2019}. However, much of the historic information at
-the site is lost on visitors because it is not readily available to non-Japanese
-speakers.
+Japan~\autocite{japanguide2019}. The Golden Pavilion is a magnificent sight to
+behold, but the gardens and grounds are the true beauty of Kinkaku-ji. It is a
+living masterpiece of Zen Buddhist landscape design, expanding on the natural
+beauty of Kyoto's forests and mountains through the practice of borrowed
+scenery~\autocite{kuitert2002}.
+
+However, much of the historic information at the site is lost on visitors
+because it is not readily available to non-Japanese speakers. What few signs and
+displays exist are presented only in Japanese, and do not provide most of the
+history and context necessary to fully understand Kinkaku-ji.
 
@@
 
+ARuko, named after the Japanese word ``\begin{CJK}{UTF8}{goth}歩こ\end{CJK}''
+(\textit{aruko}), meaning ``let's walk,'' is the app we created to guide users
+through an AR-enhanced tour.
+
 \subsubsection{GPS Functionality}
 \label{sec:gpsFunctionality}
+
 The core user experience of ARuko is the walking tour. By walking the given

### 2019-09-27 paper.tex
explained more about features

@@
 
+\subsubsection{Translation Feature}
+\label{sec:translationFeature}
+
+Despite Kinkaku-ji being an incredibly popular tourist destination that draws
+crowds from all over the world, the majority of the signage is purely
+Japanese. While AR translation apps exist, the experience can be frustrating,
+and produce poor results. Google's text recognition and machine-learning
+powered translation technology is certainly impressive. At the same time, the
+translation service works better in ``scan'' mode instead of ``instant''
+mode. In ``instant'' mode, the app attempts to translate text as quickly as
+possible and superimpose the translated text onto the real world using the
+camera. In ``scan'' mode, the user takes a photo. Then, the user is prompted
+to highlight where text appears in the photo. After the translation is
+complete, the translated text appears in a separate UI element instead
+superimposed onto the photo. In most cases, it is more convenient and
+readable to have the translation appear in a separate scrollable textbox.
+This motivated the current design of the ``info buttons'' in ARuko. Instead
+of placing text directly onto signage, we place a blue button with an `i' in
+the center. By tapping on this button, a separate UI element will appear
+containing the translated text. Since this button is cast into the world
+using the AR camera, the button is intuitively placed directly onto the
+content in the real world.
+
+\subsubsection{Virtual Souvenir Feature}
+\label{sec:virtualSouveneir}
+
+When you buy a ticket to enter Kinkaku-ji, you receive a long sheet of
+printed paper with calligraphy. The tickets are large and visually appealing;
+they are souvenirs unto themselves that one might feel inclined to keep
+around. Over the course of our three month stay we visited Kinkaku-ji
+multiple times. For each visit, we received identical tickets. Seemingly, the
+design on the tickets do not change on a regular basis, if at all.
+
+Because the tickets are unlikely to change, this enables us to provide the
+user with a ``virtual souvenir'' using the AR camera. This is the only AR
+feature that is not tied directly to an image target that can only be
+accessed at Kinkaku-ji. While the image gallery and segments of the audio
+tour can be accessed at any time using the ``Chapter Select'' menu, most of 
+the AR features can only be experienced during the walking tour, pointing the 
+camera at objects physically located at the site. Augmenting the ticket
+with 3D content allows visitors to take something home, giving them a reason
+to launch the app later.
+
+We found a free untextured model of the Golden Pavilion to use for this
+feature. Using Unity's built-in capability to design materials, we created
+a shiny golden material and applied it to the model.
+
+Originally, the AR model of the Golden Pavilion was flush against the plane
+of the ticket, sitting on the paper as if it were ground. Atticus suggested
+that we re-orient the model such that the ticket served as a back plane. This
+would allow users to hold the ticket vertically, and view the Golden Pavilion
+floating in front of the ticket. This would allow users to place their hands
+under the base of the Golden Pavilion model as if they were holding it.
+Vuforia's image tracking is flexible enough such that the image target can be
+partially obscured.
+
 \subsubsection{GPS Functionality}
@@
 
+% TODO remove this
 \nocite{harvey2002} % don't remove this
@@
 On September 26\textsuperscript{th} we returned to Kinkaku-ji with a nearly
-complete version of the ARuko in order to conduct some final testing. We met up
-with Atticus, the IQP group, and our intern Hikaru and installed the beta
-version of ARuko on each of their phones. With little instruction about how the
-app works we had each of them try going through Kinkaku-ji while listening to
-the tour and using the app's features. Each member of our team also installed
-the beta version so we could fuzz test it.
-
-This was our first time trying the AR image recognition on the actual signs at
-Kinkaku-ji, rather than photographs of the signs, and it worked quite well.
-Vuforia was able to recognize all of the signs, even in different lighting than
-when the reference images were taken. For image targets that were small, far
-away, or obscured by shadows image recognition was slower, but Vuforia was
-always able to recognize them eventually. We discovered that the targets that
-worked best were large, had a lot of high-contrast text, and were uniformly lit.
-
-While testing we discovered some issues with the design of the tour. One region
-was completely misplaced, so the audio played at the wrong time while walking
-through the area. Several other regions were too big, so the audio started
-playing long before the user was actually near the feature it was discussing.
-Finally, one of the image targets had the wrong text in its information pop-up.
-These were all easy bugs to fix, but if we might not have noticed them if we
-had not tested the app on site.
+complete version of the ARuko in order to conduct some final testing. We met
+up with Atticus, the IQP group, and our friend Hikaru and installed the beta
+version of ARuko on each of their phones. With little instruction about how
+the app works we had each of them try going through Kinkaku-ji while
+listening to the tour and using the app's features. Each member of our team
+also installed the beta version so we could fuzz test it.
+
+This was our first time trying the AR image recognition on the actual signs
+at Kinkaku-ji, rather than photographs of the signs, and it worked quite
+well. Vuforia was able to recognize almost all of the signs, even in
+different lighting than when the reference images were taken. For image
+targets that were small, far away, or obscured by shadows image recognition
+was slower, but Vuforia was always able to recognize them eventually. We
+discovered that the targets that worked best were large, had a lot of
+high-contrast text, and were uniformly lit.
+
+While testing we discovered some issues with the design of the tour. One
+region was completely misplaced, so the audio played at the wrong time while
+walking through the area. Several other regions were too big, so the audio
+started playing long before the user was actually near the feature it was
+discussing. Using the Editour web-app, we were able to correct quickly these
+issues with the tour design once we returned to Atticus' office.
+
+Additionally, one of the image targets had the wrong text in its information
+pop-up. These were all easy bugs to fix, but if we might not have noticed
+them if we had not tested the app on site.
+
+Similarly, we noticed that we were only able to augment a maximum of two
+image targets at a time. In almost all cases, only two translatable signs
+were in view at once. The only scenario in which there were more than two
+image targets in view at a given time was with the four framed photos of the
+interior, arranged in a two by two grid. When standing at a distance from the
+grid, only two images would be augmented with the blue information button. By
+default, Vuforia limits the amount of image targets that the engine should
+accept simultaneously. In the Vuforia engine settings, we changed this limit
+to accommodate for four simultaneous images
 

### 2019-09-27 paper.tex
add background on kinkakuji

--- 2019-09-27 paper.tex
@@
 more people, our team created ARuko and Editour. These two tools comprise a
-complete platform for designing and experiencing AR-enhanced tours.
+complete platform for designing and experiencing AR-enhanced tours. Editour
+makes it easy to design custom audio tours including audio, text, and images,
+and ARuko allows users to seamlessly experience historic sites in an intuitive
+and novel way. The experience of walking through the site is enhanced by
+informative narration and AR pop-ups that do not alter the buildings or ground
+in real life.
 
@@
 
-We were tasked with building an AR mobile app that enhances the experience of
-visiting Kinkaku-ji, also known as the Golden Pavilion. As of September 2019,
-Kinkaku-ji is the second-most visited site in Kyoto---second only to Kyoto
-Station \autocite{japanguide2019}.
+Kinkaku-ji, the Temple of the Golden Pavilion, is undoubtedly one of Japan's
+greatest attractions.  As of September 2019, it was the second-most visited site
+in Kyoto---second only to Kyoto Station \autocite{japanguide2019}. Kinkaku-ji's
+rich history and stunning beauty bring tourists from all over the world to see
+its shining gold walls and magnificent gardens. Our project intends to enhance
+user's enjoyment and understanding of Kinkaku-ji through informative interactive
+media, teaching about the history and significance of the site.
+
+The site that is now Kinkaku-ji was originally a villa owned by poet and
+nobleman Saionji Kintsune, until the land was bought by shōgun Ashikaga
+Yoshimitsu in 1397~\autocite{noboru2013}. As Zen Buddhism was in vogue among the
+warrior class in Japan at the time, the site was converted into a Zen temple
+according to Yoshimitsu's wishes upon his death~\autocite{bornoff2000}.
+
+The main pavilion is a three-story tall building on the edge of a landscaped
+pond. The outer walls of the top two floors are completely covered in gold leaf,
+leading to the name ``Golden Pavilion'' (\begin{CJK}{UTF8}{min}金閣\end{CJK}
+\textit{kinkaku}). The grounds surrounding the Golden Pavilion are in the style
+of a Japanese strolling garden, with carefully manicured plants and paths and
+designated viewing points. The buildings and landscaping make use of a Zen
+practice called ``borrowed scenery'' (\begin{CJK}{UTF8}{min}借景\end{CJK}
+\textit{shakkei}), in which the background landscape is incorporated into the
+design of a garden~\autocite{noboru2013}.
+
+The pavilion sits on the edge of a carefully designed pond (see Figure
+\ref{fig:kinkakujiGrounds}), with small islands designed to replicate the shape
+of Japan and several other famous locations from Japanese and Chinese
+literature~\autocite{young2007}. All of these landscape features have been
+immaculately maintained and preserved through the Golden Pavilion's six hundred
+year history.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{kinkakuji-grounds.jpg}
+    \caption[Expertly landscaped islands in the Kinkaku-ji mirror pond]{Expertly
+		landscaped islands in the Kinkaku-ji mirror pond~\autocite{desousa2014}}
+	\label{fig:kinkakujiGrounds}
+\end{figure}
+
+In 1950 the pavilion was burned down by a paranoid schizophrenic monk who had
+been living at the temple~\autocite{borowitz2005}. The structure was rebuilt in
+1955, close to the original design but with more extensive gold
+leaf~\autocite{bornoff2000}. The interior was also restored later.
+
+None of this history is readily apparent to a casual tourist at Kinkaku-ji.
+There are a few signs describing different areas, but they are only available in
+Japanese and contain very little information about the history and design of the
+site. Because of this, an intuitive audio tour app with AR features would be
+very helpful to tourists at Kinkaku-ji.
 
@@
 \label{sec:implementationAndTechnology}
+
+In this section we discuss and implementation of ARuko and Editour, including
+the technologies and techniques involved in creating both of them. We also
+discuss the design decisions we made and some of the challenges we faced in
+creating these applications.
 
@@
 
-ARuko, named after the Japanese word ``\begin{CJK}{UTF8}{goth}歩こ\end{CJK}''
+ARuko, named after the Japanese word ``\begin{CJK}{UTF8}{min}歩こ\end{CJK}''
 (\textit{aruko}), meaning ``let's walk,'' is the app we created to guide users

### 2019-09-27 paper.tex
worked on various sections

--- 2019-09-27 paper.tex
@@
 
+\subsubsection{GPS Functionality}
+\label{sec:gpsFunctionality}
+
+The core user experience of ARuko is the walking tour. By walking the given
+route, the user enters and exits specific geographic regions that invoke
+changes in the app, such as playing audio and displaying different images.
+Originally, we planned to mark regions by singular points, and trigger that
+region if the user was within a certain radius of that point.
+Implementation-wise, this would have been much simpler, but obviously limits
+possible tour designs. Consequently, we decided at an early stage to
+accommodate regions with arbitrary shape and size.  In the implementation, we
+provided support for both ``GPS Bubbles'' and ``GPS Polygons.'' In the end
+however, Editour made it trivial to use the more versatile ``GPS Polygons,'' so
+we eventually dropped support for regions triggered by distance.
+
 \subsubsection{Translation Feature}
@@
 
-\subsubsection{GPS Functionality}
-\label{sec:gpsFunctionality}
-
-The core user experience of ARuko is the walking tour. By walking the given
-route, the user enters and exits specific geographic regions that invoke
-changes in the app, such as playing audio and displaying different images.
-Originally, we planned to mark regions by singular points, and trigger that
-region if the user was within a certain radius of that point.
-Implementation-wise, this would have been much simpler, but obviously limits
-possible tour designs. Consequently, we decided at an early stage to
-accommodate regions with arbitrary shape and size.  In the implementation, we
-provided support for both ``GPS Bubbles'' and ``GPS Polygons.'' In the end
-however, Editour made it trivial to use the more versatile ``GPS Polygons,'' so
-we eventually dropped support for regions triggered by distance.
-
 \subsubsection{Adobe XD Design}
@@
 
+By the end of the project, we were able to turn ARuko into an app rich with
+features and polish. However, many of these features were presented to us
+relatively late into the project. This section discusses some of our initial
+concerns when we were first given the task of bringing Atticus' experience
+design to life.
+
 On September 10\textsuperscript{th} Atticus Sims presented us with a storyboard
 for the app experience. We would not be able to resume work until September
-17\textsuperscript{th} due to prior travel plans. Whether Atticus knew this or
-not, the design he put forth had ramifications that rippled throughout the
-entire software stack we had constructed up to this point.
-Figure~\ref{fig:adobeXdDesign} shows this design.
+17\textsuperscript{th} due to prior travel plans. The design he put forth had
+ramifications that rippled throughout the entire software stack we had
+constructed up to this point.  Figure~\ref{fig:adobeXdDesign} shows the experience
+design document created in Adobe XD.
 
@@
 
+The inclusion of a ``chapter selection'' screen had other notable design
+implications as well. Initially different regions were triggered solely by your
+GPS location. Walking into a region would prompt the available images to change
+on screen. Also, a new audio track would begin to play. This forced us to
+answer certain basic questions about the chapter select screen for ourselves.
+For example, consider a user that steps into one region, triggering the audio
+and images. Then, that user selects a chapter from the chapter selection menu,
+overriding the ``true'' region the user is physically standing inside of. When
+does the GPS ``take over'' again? Should the region change back to the ``true''
+region once the audio of the selected region finishes? This might be intuitive
+and preferred for most users, but what if the user is more interested in the
+image gallery than the audio? Then, the persistence of the image gallery is
+strangely tied to the duration of the audio track playing underneath. What if a
+user selects a chapter, and then physically enters that region moments later?
+Should the audio restart to indicate that the user has arrived at the location?
+Or, will this appear as though the audio track the user was already listening
+to skipped to the beginning again for no reason? As you can imagine, this
+seemingly minor inclusion created a significant amount of discussion.
+
+Other concerns about the chapter selection feature were technical. For a long
+time, we were working under the assumption that regions would only be triggered
+by GPS location. Because of this long-standing assumption, we were uncertain
+about what bugs implementing a chapter selection feature would introduce.
+
 Another notable change can be seen in the first screen on
@@
 suggested that we have the images be viewable in a more traditional
-fashion---in 2D as part of the UI. This was disappointing to us, since we spent
-a great deal of effort projecting images into the 3D world using the AR camera;
-we felt like we figured out how to use this technology in a way that was both
-usable and fun. Ideally, we wanted to explore ways to theme the 2D images in
-the 3D world, such as by framing the images in a traditional Japanese pagoda,
-which would fit in with the environment. On the same screen, there is a
-scrollable window of text for a transcript of the audio. Because of this, the
-Editour UI and tour metadata JSON file needed to be updated to accommodate a
-transcript per region. On top of this, the C\# code that interprets the tour
-file needed to be updated to expect an audio transcript field.
-Figure~\ref{fig:editourAdditions} shows the UI elements that changed in order
-to add these new features. The arrows next to the region name can be used to
-move the ``Region Card'' up and down in the side bar. In the ``Media'' tab, there
-is also a text area to include a transcript of the uploaded audio file.
+fashion---in 2D as part of the UI.
+
+With more time, we might have been able to get the ground-plane image placement
+feature to a state where Atticus might have liked it. We wanted to explore ways
+to theme the 2D images in the 3D world, such as by framing the images in a
+traditional Japanese pagoda. We had already spent two weeks on this feature, so
+dropping this feature was a setback we had to plan around.
+
+On the same screen, there is a scrollable window of text for a transcript of
+the audio. Because of this, the Editour UI and tour metadata JSON file needed
+to be updated to accommodate one transcript per region. On top of this, the C\#
+code that interprets the tour file needed to be updated to expect an audio
+transcript field.  Figure~\ref{fig:editourAdditions} shows the UI elements that
+changed in order to add these new features. The arrows next to the region name
+can be used to move the ``Region Card'' up and down in the side bar. In the
+``Media'' tab, there is also a text area to include a transcript of the
+uploaded audio file.
 
@@
 	\includegraphics[width=0.5\textwidth]{editour-additions.png}
-	\caption[Additions to the Editour to accommodate the new design]
-    {Additions to the Editour to accommodate the new design}
+	\caption{Additions to the Editour to accommodate the new design}
 	\label{fig:editourAdditions}
@@
 tools would be something to consider. With these changing requirements, the
-Editour was becoming onerous to maintain at this stage of the project.
+Editour was becoming onerous to maintain at this stage of the project. Luckily,
+these changes were still manageable to implement.
 
@@
 screen on Figure~\ref{fig:adobeXdDesign} shows a mock-up of this feature.
-Atticus took photographs of various signs throughout Kinkaku-ji for us to use as
-image targets. Hikaru Inoue helped us by translating all of the text in these
-photos from Japanese to English. In this design, the AR camera superimposes an
-``info'' button on top of the sign. Tapping on this button brings up a separate
-UI element containing the translation, which can be seen in
-Figure~\ref{fig:signTranslation}.
+Atticus took photographs of various signs throughout Kinkaku-ji for us to use
+as image targets. Hikaru Inoue helped us by translating all of the text in
+these photos from Japanese to English. In this design, the AR camera
+superimposes an ``info'' button on top of the sign. Tapping on this button
+brings up a separate UI element containing the translation, which can be seen
+in Figure~\ref{fig:signTranslation}. The details of this feature is discussed
+more thoroughly in Section~\ref{sec:translationFeature}.
 
@@
 project into Unity. We found one payed extension (for \$18) on the Unity Asset
-store, called ``Experience Importer - Adobe Xd files importer'', which claims
-``Transfer AdobeXd project directly to Unity. Forget about hours of positioning
-objects. They're already there! Just drag .xd file to project and...
-voila!''~\autocite{glasseye2019}.  We suspect this sounds too good to be true
-because it is. As of September 20\textsuperscript{th}, 2019, there are 6 user
-reviews. All of the five-star reviews were have the caveat ``Reviewer was gifted
-package by publisher'' which which we interpreted as a warning sign. Because of
-this, we decided to rebuild the UI largely from the ground up, using the Adobe XD
-file to guide us.
+store called ``Experience Importer - Adobe Xd files importer.'' The download
+page for this extension claims ``Transfer AdobeXd project directly to Unity.
+Forget about hours of positioning objects. They're already there! Just drag .xd
+file to project and...  voila!''~\autocite{glasseye2019}.  We suspect this
+sounds too good to be true because it is. As of September
+20\textsuperscript{th}, 2019, there are 6 user reviews. All of the five-star
+reviews were have the caveat ``Reviewer was gifted package by publisher'' which
+which we interpreted as a warning sign. Because of this, we decided to rebuild
+the UI largely from the ground up, using the Adobe XD file to guide us.
+%TODO refer to the section that discusses building the ui
 
@@
 Because the Editour is intended only to be a tool to aid Atticus in creating
-tours, not an application for the general public, our user testing of it was less
-rigid.
+tours our user testing was less rigid. Even so, the frontend and backend we
+built for Editour ended up being largely reliable. The main source of
+reliability issues stemmed from the hosting provider, which was out of our
+control.
 

### 2019-09-27 paper.tex
remove whitespace
edits and comments

@@
 through a web-app. At its core, Editour is a tool to draw arbitrarily-shaped
-geographic regions onto a map.
+geographic regions onto a map, edit those regions and assign media to each of
+the drawn regions.
 
@@
 \subsubsection{The Need for an Editor}
+\label{sec:theNeedForAnEditor}
 
@@
 Despite Kinkaku-ji being an incredibly popular tourist destination that draws
-crowds from all over the world, the majority of the signage is purely
-Japanese. While AR translation apps exist, the experience can be frustrating,
-and produce poor results. Google's text recognition and machine-learning
-powered translation technology is certainly impressive. At the same time, the
-translation service works better in ``scan'' mode instead of ``instant''
-mode. In ``instant'' mode, the app attempts to translate text as quickly as
-possible and superimpose the translated text onto the real world using the
-camera. In ``scan'' mode, the user takes a photo. Then, the user is prompted
-to highlight where text appears in the photo. After the translation is
-complete, the translated text appears in a separate UI element instead
-superimposed onto the photo. In most cases, it is more convenient and
-readable to have the translation appear in a separate scrollable textbox.
-This motivated the current design of the ``info buttons'' in ARuko. Instead
-of placing text directly onto signage, we place a blue button with an `i' in
-the center. By tapping on this button, a separate UI element will appear
-containing the translated text. Since this button is cast into the world
-using the AR camera, the button is intuitively placed directly onto the
-content in the real world.
+crowds from all over the world, the majority of the signage is purely Japanese.
+While AR translation apps exist, the experience can be frustrating, and produce
+poor results. Google's text recognition and machine-learning powered
+translation technology is certainly impressive. At the same time, the
+translation service works better in ``scan'' mode instead of ``instant'' mode.
+In ``instant'' mode, the app attempts to translate text as quickly as possible,
+superimposing the translated text onto the real world using the camera. In
+``scan'' mode, the user first takes a photo. Then, the user is prompted to
+highlight where text appears in the photo. After the translation is complete,
+the translated text appears in a separate UI element instead superimposed onto
+the photo. In most cases, it is more convenient and readable to have the
+translation appear in a separate scrollable textbox. This motivated the current
+design of the ``info buttons'' in ARuko. Instead of placing text directly onto
+signage, we place a blue button with an `i' in the center. By tapping on this
+button, a separate UI element will appear containing the translated text. Since
+this button is cast into the world using the AR camera, the button is
+intuitively placed directly onto the content in the real world.
 
@@
 
-Originally, the AR model of the Golden Pavilion was flush against the plane
-of the ticket, sitting on the paper as if it were ground. Atticus suggested
-that we re-orient the model such that the ticket served as a back plane. This
-would allow users to hold the ticket vertically, and view the Golden Pavilion
-floating in front of the ticket. This would allow users to place their hands
-under the base of the Golden Pavilion model as if they were holding it.
-Vuforia's image tracking is flexible enough such that the image target can be
-partially obscured.
+Originally, the AR model of the Golden Pavilion was flush against the plane of
+the ticket, sitting on the paper as if it were ground. Atticus suggested that
+we re-orient the model such that the ticket served as a back plane. This would
+allow users to hold the ticket vertically, and view the Golden Pavilion
+floating in front of the ticket. This allows users to place their hands under
+the base of the Golden Pavilion model as if they were holding it. Vuforia's
+image tracking is flexible enough such that the image target can be partially
+obscured.
 
@@
 The inclusion of a ``chapter selection'' screen had other notable design
-implications as well. Initially different regions were triggered solely by your
+implications as well. Initially different regions were triggered solely by the
 GPS location. Walking into a region would prompt the available images to change
@@
 Should the audio restart to indicate that the user has arrived at the location?
-Or, will this appear as though the audio track the user was already listening
-to skipped to the beginning again for no reason? As you can imagine, this
-seemingly minor inclusion created a significant amount of discussion.
+Or, will this appear as though the audio track skipped to the beginning again
+for no reason? As you can imagine, this seemingly minor inclusion created a
+significant amount of discussion.
 
@@
 
+%TODO should this paragraph move somewhere else?
 Atticus initially wanted us to explore the efficacy of using Vuforia's 2D image
@@
 tours our user testing was less rigid. Even so, the frontend and backend we
-built for Editour ended up being largely reliable. The main source of
-reliability issues stemmed from the hosting provider, which was out of our
-control.
+built for Editour ended up being largely reliable. The reliability issues
+stemmed from the hosting provider, which was out of our control.
 
@@
 segments.  The point is outside of the polygon if the ray intersects an odd
-number of times. Figure~\ref{fig:intersectionsDiagram} should make it clear why
-this works. This algorithm's time complexity is $O(n)$, where $n$ is the sum
-total of the number of vertices of all of the polygons being
-tested~\autocite{geeksforgeekspolygon}.
+number of times. Figure~\ref{fig:intersectionsDiagram} does not serve as a
+proof, but should at least make it clear why this works. This algorithm's time
+complexity is $O(n)$, where $n$ is the sum total of the number of vertices of
+all of the polygons being tested~\autocite{geeksforgeekspolygon}.
 
@@
 upon re-entering a region, since the audio would still be playing once a user
-left the region. The region at the bottom surrounding our dormitories was added
+left the region. (The region at the bottom surrounding our dormitories was added
 for our convenience, allowing us to test the app while we were away from the
-lab.  As we began to implement more complex UI that changed based on GPS
+lab.) As we began to implement more complex UI that changed based on GPS
 position in various ways, directly taking the tour by walking around was an
@@
 
+If we were ever feeling too tired to test the app by walking around, we also
+mocked the GPS coordinates in software. This allowed us to simulate walking in
+a single direction without actually having to move or build to a mobile device.
+
 \begin{figure}[h]
@@
 were relatively small; some regions were only a few meters across. This version
-of the tour can be seen in Figure~\ref{fig:kinkakujiTour}.
+of the tour can be seen in Figure~\ref{fig:kinkakujiTour}. This day of testing
+prior to the redesign discussed in Section~\ref{sec:adobeXdDesign}.
 
@@
 
-Our previous testing involved creating a ``mock tour'' on the Ritsumeikan
-campus. While this let us know generally which features of the app were working,
-it was very difficult to know how ahead of time how well our app would work at
-Kinkaku-ji.
+As discussed in Section~\ref{sec:testingARuko}, our previous testing involved
+creating a ``mock tour'' on the Ritsumeikan campus. While this let us know
+generally which features of the app were working, it was very difficult to know
+how ahead of time how well our app would work at Kinkaku-ji.
 
@@
 Initially, we loaded the app onto the Samsung Galaxy S7 as a backup, since the
-app is not fully functional on a phone that old. At the same time, it was
-informative to take both phones through the tour. Initially, we made the design
-decision to update the GPS location every 60 frames. On a phone running the app
-at full speed, this should happen once every second. Because the Samsung Galaxy
-S7 was having trouble running the app at full speed, the GPS updated far less
-frequently. This was an oversight that would have been difficult to catch if we
-had not tested on hardware below the recommended specifications.
+AR features were not fully functional on a phone that old. At the same time, it
+was informative to take both phones through the tour. Initially, we made the
+design decision to update the GPS location every 60 frames. On a phone running
+the app at full speed, this should happen once every second. Because the
+Samsung Galaxy S7 was having trouble running the app at full speed, the GPS
+updated far less frequently. This was an oversight that would have been
+difficult to catch if we had not tested on hardware below the recommended
+specifications.
 
@@
 also installed the beta version so we could fuzz test it.
+% TODO check if fuzz testing is really the right word here
 
@@
 
-Similarly, we noticed that we were only able to augment a maximum of two
+We also noticed that we were only able to augment a maximum of two
 image targets at a time. In almost all cases, only two translatable signs

### 2019-09-28 paper.tex
rearrange sections
add section on editour server disk throttling

@@
 \usepackage[gen]{eurosym} % for literally just the euro symbol
-
 \usepackage{lipsum} % lorem-ipsum placeholder text
@@
 
-\subsection{Current Augmented Reality Technology}
+\subsubsection{Current Augmented Reality Technology}
 \label{sec:currentAugmentedRealityTechnology}
@@
 
-\subsection{Augmented Reality Use Cases}
+\subsubsection{Augmented Reality Use Cases}
 \label{sec:augmentedRealityUseCases}
@@
 
-\subsection{Challenges of Augmented Reality}
+\subsubsection{Challenges of Augmented Reality}
 \label{sec:challengesOfAugmentedReality}
@@
 
-\subsection{Apps for Art and Culture}
-\label{sec:appsForArtAndCulture}
-
-To explore existing AR apps for art and culture our group researched and tested
-several games, experiences, and platforms related to our project.
-
-\subsubsection{izi.TRAVEL}
+\subsection{izi.TRAVEL}
 \label{sec:iziTravel}
@@
 
-\subsection{Platforms}
+\subsection{Augmented Reality Platforms}
 \label{sec:platforms}
@@
 aren't being used any more.
+
+Unfortunately, the hosting provider Kyoto VR provided us with severely throttles
+disk write speeds. Because the backend has to write potentially large amounts of
+data to the disk every time a tour is uploaded or edited this becomes a major
+bottleneck for the web app's performance. For large tours (bigger than 50 MiB)
+this can cause an issue where the Node server takes so long to respond that
+Apache thinks it has timed out, and sends an erroneous 504 Gateway Timeout
+message~\autocite{rfc7231}. Without access to superuser permissions or a faster
+hosting provider there is nothing we can do about this bug. The Node server does
+eventually complete the request and respond correctly, so until Kyoto VR can get
+a better hosting provider we consider it a minor issue.
 

### 2019-09-28 paper.tex
add conclusion

@@
 
-\section{Conclusion}
-\label{sec:conclusion}
+\section{Conclusion and Future Work}
+\label{sec:conclusionAndFutureWork}
+
+Despite the numerous pivots this project went through, in the end we were able
+to create a useful working prototype. The Editour is fully featured with
+everything needed to build an audio tour anywhere in the world. ARuko allows
+users to experience useful AR-enhanced tours in a pleasant and intuitive way.
+Together they provide a complete platform for building augmented reality tour
+guide apps.
+
+Although the finished product works as intended, we encountered several issues
+along the way. The changing scope and goal of the project meant we spent several
+weeks researching and working on features that did not make it into the final
+product (see Section~\ref{sec:pivots}), such as displaying images in 3D AR space
+and playing spatialized audio. If we had focused only on the features that made
+it into the final app from the start we could have had more time to polish and
+refine those features.
+
+Another challenge we faced was the difficulty in actually testing the app. The
+Ritsumeikan University Biwako-Kusatsu campus we stayed at is about ninety
+minutes away from Kinkaku-ji by expensive public transport, which meant that we
+were only able to go to the site to test ARuko twice. We could test some basic
+features from Ritsumeikan, but image recognition target existed only at
+Kinkaku-ji. More extensive user testing at the actual site could have helped us
+catch bugs earlier and lead to a more polished final product.
+
+Despite these issues our team is happy with the product we delivered to Kyoto
+VR. ARuko is not quite ready to be sold on app stores yet, but with a little
+more development time it could easily be made ready. The UI could use more
+testing with real users to make sure it is intuitive and easy to use. We also
+intended to add a feature where the app could automatically download tour files
+from the Editour server and import them without having to rebuild. We were not
+able to complete this feature due to time constraints, but it could easily be
+added because all of ARuko's business logic is abstracted and generalized to
+support multiple tours. Editour also already supports requesting and downloading
+the most recent versions of tours.
+
+Editour is essentially feature complete. The most recent version, v1.3.0, can be
+found in the GitHub repository
+(\url{https://github.com/bandaloo/editour/releases/tag/v1.3.0}), and it contains
+all the features necessary to create and edit tours. In the future Kyoto VR
+should move it to a more powerful hosting provider (see
+Section~\ref{sec:deployingTheEditourBackend}), but the current solution works
+for now.
+
+Given more time and resources, the app should be augmented to include a tour
+browser that automatically downloads an unpacks tours from the Editour server.
+More historic locations around Kyoto and Japan in general should be considered
+for other tours. With the work our team has done Kyoto VR now has a complete
+platform for creating and delivering unique tours, which can easily be expanded
+upon in the future.
 

### 2019-09-28 paper.tex
executive summary and other sections

--- 2019-09-27 paper.tex
@@
 \addcontentsline{toc}{section}{Executive Summary}
+
+We built, tested and polished a mobile app to deliver an audio tour,
+incorporating various AR features to enhance the experience. In this app, which
+we call ARuko, many of the AR features were aimed at improving accessibility.
+These features included translating signs and providing additional info on the
+physical map located at the site. Other features were purely for spectacle,
+such as the ability to take an AR `souvenir' home by pointing the camera at the
+ticket.
+
+ARuko went through multiple iterations of user testing and bug testing at the
+site of the audio tour, Kinkaku-ji. Sections \ref{sec:initialFieldTesting} and
+\ref{sec:finalFieldTesting} go into detail about our two days of field testing
+on-site. From these tests, we were able to refine the user experience, and
+identify important features to add to the app. Much of the app's and
+functionality was dictated by Atticus Sims of Kyoto VR, who plans to monetize
+the app. We also worked closely with the IQP team, who has been tasked with
+exploring funding options and creating promotional content.
+
+Since our app had to deliver an audio tour supplemented by images based on your
+GPS position, we developed an internal tool to design these regions. Editour
+provides a rich editing suite for designing tours with images and audio.
+Section~\ref{sec:editingATour} goes into detail about the features of this web
+app. We also wrote a backend to manage the tour files, allowing one of us (or
+our sponsor, Atticus Sims) to download a zip file containing all of the media
+and info to reconstruct the tour. This zip can be extracted into the Unity
+project, which reconstructs the tour from the downloaded contents. We were able
+to host the backend on the server provided by Kyoto VR's hosting plan; we
+discuss the hurdles that we overcame to deploy the Editour backend with Kyoto
+VR's current setup in Section~\ref{sec:deployingTheEditourBackend}.
+
+At the end of this paper, we also discuss the alternative AR app concepts that
+were explored before development became completely focused on the tour app
+ARuko.
 
@@
 intuitively placed directly onto the content in the real world.
+
+\subsubsection{Map Overlay Feature}
+\label{sec:mapOverlayFeature}
+
+Near the entrance of Kinkaku-ji before the ticket gate, there is a large
+illustrated map. Much like the signage, there is no language on the map other
+than Japanese. Using the AR camera within the app, you can project information
+onto the map. Figure~\ref{fig:arMapFeature} shows the blue highlighted path of
+the walking tour, including a few translated labels.
+
+\begin{figure}[h] \centering
+    \includegraphics[width=0.3\textwidth]{ar-map-feature.png}
+    \caption{Map overlay displaying the path and translated labels}
+    \label{fig:arMapFeature}
+\end{figure}
 
@@
 
-This was our first time trying the AR image recognition on the actual signs
-at Kinkaku-ji, rather than photographs of the signs, and it worked quite
-well. Vuforia was able to recognize almost all of the signs, even in
-different lighting than when the reference images were taken. For image
-targets that were small, far away, or obscured by shadows image recognition
-was slower, but Vuforia was always able to recognize them eventually. We
-discovered that the targets that worked best were large, had a lot of
-high-contrast text, and were uniformly lit.
+This was our first time trying the AR image recognition on the actual signs at
+Kinkaku-ji, rather than photographs of the signs, and it worked surprisingly
+well. Vuforia was able to recognize almost all of the signs, even in different
+lighting than when the reference images were taken. For image targets that were
+small, far away, or obscured by shadows image recognition was slower, but
+Vuforia was always able to recognize them eventually. We discovered that the
+targets that worked best were large, had a lot of high-contrast text, and were
+uniformly lit.
 
@@
 
-\section{Pivots}
-\label{sec:pivots}
+\section{Alternative AR App Concepts}
+\label{sec:alternativeArAppConcepts}
 
 Throughout the duration of the project, the goalposts shifted multiple times.
-This section details some of the initial plans that fell through.
+This section details some of the initial plans that we explored before Atticus
+shifted our focus to a walking tour app with AR features.
 
@@
 One idea that was proposed initially was an AR audio experience using 3D
-spatialized audio.
+spatialized audio. Instead of traditional AR where the user is constantly
+looking through the camera, this experience would allow users to keep their
+phones in their pockets while taking the tour. Sound sources would change in
+physically based ways using motion tracking.
+
+We spent the second and third week creating demos to explore the possibility of
+a 3D spatialized audio tour. We found that this would be very difficult to do
+without the use of the camera. All of the technology for mobile AR we explored
+in Section~\ref{sec:platforms} depended heavily on the camera. If we were to
+build a 3D spatialized audio tour that ran entirely without use of the camera,
+we would not be able to take advantage of any of the useful features of the AR
+libraries we explored. Furthermore, Unity would be relegated to the simple role
+of exporting our app to multiple devices; we would not have any need to take
+advantage of its 3D capabilities.
+
+Thusly, we decided to see what was possible using the camera instead. We were
+able to get sound sources to fade in and out based on the distance to an image
+target. Naturally, if the image target were to go out of view of the camera,
+Vuforia stopped trying to estimate the camera's distance to the last known
+location of the image target. In order to make this work in the way Atticus
+imagined, we would need a way to shift to our own method of estimating distance
+to the sound source once the image target had been lost. While this might have
+been possible, it was difficult to estimate the amount of effort this would
+take, since we would essentially be implementing a feature seemingly not
+supported by current AR libraries.
+
+We explained the technical hurdles of this concept to Atticus. Ultimately, our
+focus shifted away from this idea for other logistical reasons. Initially,
+Atticus introduced the possibility of working closely with Kishi Bashi or
+Yannick Paget to produce the soundscape for the 3D spatialized audio tour.
+Yannick Paget is a French musician that became established in Japan. He is both
+conductor and composer, originally trained as a professional pianist and
+percussionist. He has written music for theater, film and orchestras around the
+world. Many of his original compositions were inspired by his experience living
+in Japan, such as Tears of Sakura
+(\begin{CJK}{UTF8}{min}サクラの涙\end{CJK})~\autocite{yannickpaget2016}. Kishi
+Bashi was born in Seattle and grew up in Virginia. Kishi Bashi has appeared at
+many major music festivals, toured the US extensively, and has even released
+his own line of coffee! His latest album, Omoiyari, was released on May
+31\textsuperscript{st}, 2019~\autocite{kishibashi2019}.
+
+\subsection{AR Art Gallery}
+\label{sec:arArtGallery}
+
+Atticus Sims proposed the idea of working with Michael Whittle. Michael Whittle
+received his PhD at the Kyoto City University of Arts in 2014. His art has
+appeared in dozens of solo exhibitions and group exhibitions across the world,
+including Kyoto, Beijing, London and New York~\autocite{michaelwhittle2019}.
+Kyoto VR has worked with Michael Whittle in the past to create a 3D scan of a
+solo exhibition, `Portraits of Thought'. This exhibition displayed diagrams
+inspired by real science and mathematics. Atticus provided us with some
+diagrams to test in the Vuforia developer portal, since Michael Whittle wanted
+to know how well certain pieces of art would work as AR image targets. All of
+images that were provided to us were ranked as ``five stars'' by Vuforia,
+indicating that those images would serve well as AR image targets.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=.7\textwidth]{exhibition-scan.png}
+    \caption{A screenshot of the 3D scan of `Portraits of Thought,' accessible
+    from the web}
+	\label{fig:exhibitionScan}
+\end{figure}
 

### 2019-09-28 paper.tex
old ui and final ui implementation

--- 2019-09-28 paper.tex
@@
 
-Unfortunately, the hosting provider Kyoto VR provided us with severely throttles
-disk write speeds. Because the backend has to write potentially large amounts of
-data to the disk every time a tour is uploaded or edited this becomes a major
-bottleneck for the web app's performance. For large tours (bigger than 50 MiB)
-this can cause an issue where the Node server takes so long to respond that
-Apache thinks it has timed out, and sends an erroneous 504 Gateway Timeout
-message~\autocite{rfc7231}. Without access to superuser permissions or a faster
-hosting provider there is nothing we can do about this bug. The Node server does
-eventually complete the request and respond correctly, so until Kyoto VR can get
-a better hosting provider we consider it a minor issue.
-
 \subsubsection{Future of Editour}
@@
 
+\subsubsection{Early UI}
+\label{sec:earlyUI}
+
+As ideas changed and ARuko became what it is today, the UI also changed
+greatly from it's early conception to the final version we used. But
+that early UI would prove just as important as the final one, because
+it was also how we learned many of the practices and skills we needed in order
+to create the UI we settled on.
+
+The early UI was very much a product of ARuko's development; many of it's
+elements were created as new features were added. But as more features were
+added, it became clear that the UI couldn't consist simply of buttons and 
+other basic features provided by Unity. We would need to learn more about 
+how to create more interesting and useful UI elements to accomodate for 
+our new functionality.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=1\textwidth]{old-ui.png}
+	\caption[A screenshot of our early UI]
+	{A screenshot of our early UI}
+	\label{fig:oldUI}
+\end{figure}
+
+Pictured in Figure~\ref{fig:oldUI} is our early UI. It was a very minimal UI,
+but still covered all of the uses for our app at the time. The top of the 
+screen had two dropdown menus. The one on the left, shown open, would
+show AR image targets in the area that users could look for and scan. The right
+dropdown would be dynamically populated in each region with buttons bearing  
+different images. These images were ones that Atticus wanted to be viewable in AR using ground plane
+detection. When tapped, each button would create a 3D Cube, with the given image
+on each face, and place it on the ground where the user was pointing.
+
+Learning to create these dropdown menus proved to be a very important lesson
+later on, since we would put that exact knowledge to use multiple times in the
+final UI. We were able to create the dynamically populated dropdown menus by 
+creating an empty vertical layout group, and then using a script to create
+buttons for each image based on which region the user is in, and then assign
+them as children of the layout group. Then, to get the smooth open/close animation,
+we used a boolean to mark the menu as open or closed and had the menu lerp to the
+corresponding position each frame until it was fully open or closed.
+
+In between these two dropdown menus is a panel that is shown empty, but in practice would
+display the name for the region the user is in at the time. The empty space
+in the middle of the screen is where the AR camera display would be shown. In this 
+implementation, the AR functionality was the focus of the app, so it made sense
+to display the AR camera feed at all times. Lastly, on the bottom is the audio slider for the audio file played in each region. 
+We learned a lot about how audio sliders work in Unity with this feature, and would
+expand a lot on that knowledge for the final version of the app in order to optimize
+the slider's functionality and usefulness.
+
+This early UI taught us a lot about how to make a UI in Unity. We learned a lot of 
+basic things, like how all of the UI elements go on the Canvas, which represents
+the phone screen, and that everything should be anchored to locations on the screen
+so that they stay in the right place despite changes in screen size. 
+We also learned more complicated skills that would help us a lot later. We learned
+how to use audio sliders, and the ins and outs of how they work. And we learned
+how to create dropdown menus that expand when opened and contract when closed, 
+creating a very smooth movement affect without needing to animate the component. 
+And we also learned how to create button functionality through script, allowing
+for UI elements that can changed between the different tours loaded into our app.
+And we would bring all of these important skills we learned into the creation
+of our final UI to help make it as useful and interesting as it is now.
+
 \subsubsection{Adobe XD Design}
@@
 %TODO refer to the section that discusses building the ui
+
+\subsubsection{Final UI Implementation}
+\label{sec:finalUI}
+
+While the newly proposed UI by Atticus was certainly a huge step up from
+our previous one, the things we had learned the first time around helped
+a lot in overcoming this rather large request in the relatively short amount
+of time we had. We had to get much more creative with how we implemented the
+UI and how everything worked together, but in the end this allowed us to 
+create a rather impressive final UI for and app that we're proud of.
+
+One of the first major challenges we had to tackle was the need to switch
+modes while keeping certain UI elements constant. So when a user goes from
+the home screen to the Route Map, or into AR Mode, we needed the mode buttons,
+audio components, and region info to remain. We went did this by splitting up
+screen space into panels, with one for the region info up top, one each for the
+mode buttons and audio components on the bottom, and one for the different 
+modes in the middle of the screen. Then, within the mode panel, each mode 
+screen would be assigned as children, and toggled active or inactive based on 
+which mode the user is in at the time. That way, on-screen content can change
+while important UI elements remain constant.
+
+Now, within the mode problem itself, there were other important things to 
+consider. One such topic was how to handle AR Mode. Previously, we had just
+left the AR camera running at all times, since it was the primary feature of 
+the app. But now, the focus was much more on the images and audio transcription
+in each region. For this, we found that we were able to disable and re-enable
+the AR camera in script, so we could turn it off while other modes were the
+focus, and back on when needed. We also weren't sure at first what to do about
+the chapter select menu, as it was also content that would occupy the space of
+the mode panel on screen, but needed to be accessible anywhere via the top 
+panel. Using our experience creating dropdown menus in the early UI, we simply
+left the chapter select menu enabled at all times, and lerped it open or closed
+as needed.
+
+Another group of challenges were created by the content of the main screen,
+which showed the images and audio transcript associated with each region. To 
+display the images, we wanted the user to be able to click through them like
+an image gallery, but weren't sure how to do so in a way that was smooth and
+looked nice. But once again, our experience with dropdown menus came in handy. 
+We created the gallery out of a horizontal layout group, populated it with 
+images dynamically in each region, and then had the buttons lerp the gallery
+to different positions in order to switch between each image in a smooth and 
+pleasing way. As for the audio transcript, we knew we needed a scrollable
+text field that could accomodate varying amounts of text, since the audio files
+varied so greatly in length. After doing some research, we found a way to use 
+a vertical layout group to create a text field that expanded vertically, within
+a predefined bounds, to fit any amount of text provided to it.
+
+At first, our route map screen was rather simple. It was just a static image
+of the map, with the route drawn on it, that the user could scroll up and down,
+since the image was too tall for the screen. But because the map was so zoomed
+out, certain features and text on the map were hard to see. This could also 
+make it hard to tell where someone is on the route. So we needed a way to zoom
+in on the map and scroll around it, even though Unity doesn't provide this 
+relatively common functionality in a standard way. After doing some research, 
+were able to write a script that used some of Unity's Input library to get
+touch input and use it to zoom in and out on the map within a predefined 
+bounds.
+
+The last major UI implementation obstacle we had to overcome was a way to keep
+audio playing with the phone in your pocket. Atticus insisted that this sort of
+feature was required so that users could listen to the audio tour without using
+any of the other functionality the app provides, like the image gallery in each
+region or the AR features. But despite how common it is for apps to play audio 
+in the background or while the phone is locked , Unity does not provide a way 
+to accomplish this either. The way we got around this was by figuring out a way
+to prevent UI elements from accidentally being triggered while the phone is 
+still unlocked and in the app in the user's pocket. We added a mode to the mode
+panel that consists of simply a high opacity black screen with a slider on it,
+and added a button to the chapter select dropdown in order to trigger this 
+mode. What this pocket mode does is that, because of where it is placed in the 
+Unity hierarchy, when it is enabled, it blocks input to all other active UI
+components. Then the slider works much like the slider on old Apple devices,
+where you slide it from one end to the other to "unlock" the app again, 
+re-enabling UI interaction. We figured that it would be rather difficult to 
+accidentally trigger the slider while the phone is in one's pocket, and even
+have the slider reset if it is only slided partially before letting go.
+
+The rest of the final UI consisted primarily of standard UI features, like 
+different basic buttons and panels in different places throughout the app. 
+We were ultimately able to replicate Atticus's Adobe XD file almost 
+perfectly, allowing us to use a great UI for this app we've worked so hard on.
 

### 2019-09-28 paper.tex
fixed unresolved reference

@@
 Although the finished product works as intended, we encountered several issues
-along the way. The changing scope and goal of the project meant we spent several
-weeks researching and working on features that did not make it into the final
-product (see Section~\ref{sec:pivots}), such as displaying images in 3D AR space
-and playing spatialized audio. If we had focused only on the features that made
-it into the final app from the start we could have had more time to polish and
-refine those features.
+along the way. The changing scope and goal of the project meant we spent
+several weeks researching and working on features that did not make it into the
+final product (see Section~\ref{sec:alternativeArAppConcepts}), such as
+displaying images in 3D AR space and playing spatialized audio. If we had
+focused only on the features that made it into the final app from the start we
+could have had more time to polish and refine those features.
 

### 2019-09-28 paper.tex
initial round of edits

@@
 Kyoto VR, Lewis Cook, Nicole Escobar, Ahad Fareed, and Cameron Person, for
-filming and editing the app trailer.
+filming and editing the app trailer, as well as providing help with testing.
 
@@
 
-We built, tested and polished a mobile app to deliver an audio tour,
-incorporating various AR features to enhance the experience. In this app, which
-we call ARuko, many of the AR features were aimed at improving accessibility.
-These features included translating signs and providing additional info on the
+Our team built, tested and polished a mobile app to deliver an audio tour,
+incorporating various augmented reality (AR) features to enhance the
+experience. Our app delivers a tour of Kinkaku-ji, or The Temple of the Golden
+Pavilion, a popular tourist destination in Kyoto. In this app, which we call
+ARuko, many of the AR features were aimed at improving accessibility. These
+features include translating signs and providing additional info on the
 physical map located at the site. Other features were purely for spectacle,
-such as the ability to take an AR `souvenir' home by pointing the camera at the
-ticket.
-
-ARuko went through multiple iterations of user testing and bug testing at the
-site of the audio tour, Kinkaku-ji. Sections \ref{sec:initialFieldTesting} and
+such as the ability to take an AR ``souvenir'' home by scanning the ticket
+to enter Kinkaku-ji.
+
+ARuko went through multiple iterations of user testing and bug testing at
+Kinkaku-ji. Sections \ref{sec:initialFieldTesting} and
 \ref{sec:finalFieldTesting} go into detail about our two days of field testing
 on-site. From these tests, we were able to refine the user experience, and
-identify important features to add to the app. Much of the app's and
-functionality was dictated by Atticus Sims of Kyoto VR, who plans to monetize
-the app. We also worked closely with the IQP team, who has been tasked with
+identify important features to add to the app. Much of the app's functionality
+was dictated by Atticus Sims, C.E.O and founder of Kyoto VR, who plans to
+monetize the app. We also worked with an IQP team, who had been tasked with
 exploring funding options and creating promotional content.
@@
 Since our app had to deliver an audio tour supplemented by images based on your
-GPS position, we developed an internal tool to design these regions. Editour
-provides a rich editing suite for designing tours with images and audio.
-Section~\ref{sec:editingATour} goes into detail about the features of this web
-app. We also wrote a backend to manage the tour files, allowing one of us (or
-our sponsor, Atticus Sims) to download a zip file containing all of the media
-and info to reconstruct the tour. This zip can be extracted into the Unity
-project, which reconstructs the tour from the downloaded contents. We were able
-to host the backend on the server provided by Kyoto VR's hosting plan; we
-discuss the hurdles that we overcame to deploy the Editour backend with Kyoto
-VR's current setup in Section~\ref{sec:deployingTheEditourBackend}.
-
-At the end of this paper, we also discuss the alternative AR app concepts that
-were explored before development became completely focused on the tour app
-ARuko.
+latitude and longitude, we developed an internal tool to design physical
+regions for each step of the tour. This tool, called Editour provides a rich
+editing suite through a simple web interface. Section~\ref{sec:editingATour}
+goes into detail about the features of this web app. We also wrote a backend to
+manage the tour files, allowing one of us (or our sponsor, Atticus Sims) to
+download a zip file containing all of the media and info to reconstruct the
+tour. This zip can be extracted into the source files for ARuko, which rebuilds
+the tour from the downloaded contents. We were able to host the backend on the
+server provided by Kyoto VR's hosting plan; we discuss the hurdles that we
+overcame to deploy the Editour backend with Kyoto VR's current setup in
+Section~\ref{sec:deployingTheEditourBackend}.
+
+In Section~\ref{sec:alternativeArAppConcepts}, we also discuss the alternative
+AR app concepts that were explored before development became completely focused
+on ARuko.
 
@@
 
-The field of consumer-oriented Augmented Reality (AR) technology is just coming
+The field of consumer-oriented augmented reality (AR) technology is just coming
 into full swing, and it presents many unique opportunities for a myriad of
@@
 real-world information with computer-generated data. As the technology
-progresses several disparate industries have found novel uses for it, some
+progresses, several disparate industries have found novel uses for it, some
 becoming extremely profitable~\autocite{webster2018}. With smartphone
@@
 Tourism and art are among the fields that could gain the most from AR
-technology~\autocite{saenz2009, katz2018}. AR technology can provide accessible
-information to tourists and art viewers that they would not be able to get any
-other way. Kinkaku-ji, the ``golden pavilion'' of Kyoto, is the perfect example
-of this~\autocite{bornoff2000}. Kinkaku-ji is a UNESCO World Heritage
-Site~\autocite{unesco} and one of the most popular tourist destinations in
-Japan~\autocite{japanguide2019}. The Golden Pavilion is a magnificent sight to
-behold, but the gardens and grounds are the true beauty of Kinkaku-ji. It is a
-living masterpiece of Zen Buddhist landscape design, expanding on the natural
-beauty of Kyoto's forests and mountains through the practice of borrowed
-scenery~\autocite{kuitert2002}.
+technology~\autocite{saenz2009, katz2018}. This technology can provide
+accessible information to tourists and art viewers that they would not be able
+to get any other way. Kinkaku-ji, the ``Golden Pavilion'' of Kyoto, is the
+perfect example of a site that would benefit from AR~\autocite{bornoff2000}.
+Kinkaku-ji is a UNESCO World Heritage Site~\autocite{unesco} and one of the
+most popular tourist destinations in Japan~\autocite{japanguide2019}. The
+Golden Pavilion is a magnificent sight to behold, but the gardens and grounds
+are the true beauty of Kinkaku-ji. It is a living masterpiece of Zen Buddhist
+landscape design, expanding on the natural beauty of Kyoto's forests and
+mountains through the practice of borrowed scenery~\autocite{kuitert2002}.
 
@@
 makes it easy to design custom audio tours including audio, text, and images,
-and ARuko allows users to seamlessly experience historic sites in an intuitive
+while ARuko allows users to seamlessly experience historic sites in an intuitive
 and novel way. The experience of walking through the site is enhanced by
@@
 
-Augmented Reality, or AR, is a type of human-computer interface where
+Augmented reality, or AR, is a type of human-computer interface where
 perceptions of the real world are enhanced by computer-generated information.
-This differs from Virtual Reality (VR) in that a VR experience consists
+This differs from virtual reality (VR) in that a VR experience consists
 exclusively of virtual information. In AR, virtual information is mixed with
@@
 world~\autocite{saenz2009}.  This provides the user with useful information
-without needing to alter the real historic site.
+without needing to alter a real historic site.
 
@@
 
-While preparing for this project our team researched the current state of
-augmented reality technology. Smartphones are the most commonly used AR hardware
-by far~\autocite{boland2018}. Typically smartphone AR applications make use of
-the phone's camera, accelerometer, gyroscope, and GPS sensors to reproduce a
-view of the real world with virtual information layered on top of
+While preparing for this project our team researched the current state of AR
+technology. Smartphones are the most commonly used AR hardware by
+far~\autocite{boland2018}. Typically smartphone AR applications make use of the
+phone's camera, accelerometer, gyroscope, and GPS sensors to reproduce a view
+of the real world with virtual information layered on top of
 it~\autocite{bonsor2018}.
@@
 
-Even though it is still a developing technology, augmented reality has been used
-in many disparate disciplines, including data
-visualization~\autocite{resnick2017}, commerce~\autocite{matney2018},
-marketing~\autocite{sharma2015}, education~\autocite{stewart-smith2012}, visual
-art~\autocite{katz2018}, and even archaeology~\autocite{eve2012}.
+Even though it is still a developing technology, AR has been used in many
+disparate disciplines, including data visualization~\autocite{resnick2017},
+commerce~\autocite{matney2018}, marketing~\autocite{sharma2015},
+education~\autocite{stewart-smith2012}, visual art~\autocite{katz2018}, and
+even archaeology~\autocite{eve2012}.
 
@@
 
-As previously discussed, AR is a new and growing field full of opportunities.
-But of course, as with anything new, our understanding of AR and how to develop
-for it is limited.  And with those limitations come challenges. All sorts of
+Many of the existing applications using AR, in our eyes, do not leverage the
+full potential of this emerging technology. As with any new field, our
+understanding of AR and how to develop for it is limited. All sorts of
 different challenges and limitations face the development and production of AR
@@
 Many of the applications and use cases that exist for AR right now are, simply
-put, not very good. This means a few different things. For starters, many AR
-apps and features available on smartphones offer very little in the way of
-functionality or practicality; quite simply, they are primarily used for minor
-spectacles and simple tricks~\autocite{theappsolutions2018}. For example, one of
-the most popular apps to use AR, \textit{Pokémon Go}, primarily uses its AR
-feature to place a Pokémon in the world around you through your phone camera for
-you to capture. But when it is in the world, it does not interact with anything
-around it. It just floats a fixed distance away from you, simply placed on top
-of your camera's video feed.
+put, not very good. Many AR apps and features available on smartphones offer
+very little in the way of functionality or practicality; quite simply, they are
+primarily used for minor spectacles and simple
+tricks~\autocite{theappsolutions2018}. For example, one of the most popular
+apps to use AR, \textit{Pokémon Go}, primarily uses its AR feature to place a
+Pokémon on top of a camera's video feed. Disappointingly, it does not interact
+with anything around it. It just floats a fixed distance away from the user.
 
@@
 \textit{Pokémon Go} example, when the AR feature is left on while capturing a
-Pokémon, the extra power needed for this feature drains the device faster, makes
-it harder to hit the Pokémon with a Pokéball due to the model drifting in the
-environment, and can even slow app performance, all of which detract from the
-ability to play and enjoy the game.
-
-One of the major problems facing AR development as a whole, and one that we ran
-into as well, is limited hardware. For starters, smartphone cameras present a
+Pokémon, the extra power needed for this feature drains the device's battery
+faster. Also, it makes it harder to hit the Pokémon with a Pokéball due to the
+model drifting in the environment. On top of all of this, the performance of
+the app suffers drastically, especially on older devices. All of these problems
+detract from the ability to play and enjoy the game.
+
+One of the major problems facing AR development as a whole---including our
+project---is limited hardware. For starters, smartphone cameras present a
 major limitation. Many smartphone cameras only capture images in 2D, which can
@@
 
-The biggest hardware limitation comes from which platform to use. AR apps are
-most commonly designed for smartphones due to their relatively low cost and how
-accessible they are. But, as we just discussed, smartphones come with a host of
+AR apps are most commonly designed for smartphones due to their relatively low
+cost and how accessible they are. However, smartphones come with a host of
 hardware limitations that make achieving satisfying AR capabilities difficult.
@@
 enhance~\autocite{theappsolutions2018}.  The alternative then is to turn to
-dedicated hardware, like Microsoft's HoloLens.  But dedicated hardware like the
-HoloLens is very inaccessible and expensive; Microsoft only offers developer
-editions of the HoloLens, and for the incredibly steep price of
-\$3,500~\autocite{microsoft2019}.
-
-The challenges we faced during development mirrored these that plague the
-industry as a whole very accurately. We struggled with how exactly we would us
-AR for our app in a way that benefit the experience as a whole, but believe the
-way we've implemented it will enhance the user's experience. Hardware issues
-were definitely our biggest challenge.  Only one of our phones is new enough to
-run AR technology at a decent level, making testing of our application
-difficult.
+dedicated hardware, like Microsoft's HoloLens. The issue is that dedicated
+hardware like the HoloLens is very inaccessible and expensive; Microsoft only
+offers developer editions of the HoloLens, and for the incredibly steep price
+of \$3,500~\autocite{microsoft2019}.
+
+The challenges we faced during development mirrored those that plague the
+industry as a whole very accurately. We struggled with how exactly we would use
+AR for our app in a way that benefited the experience as a whole. Despite our
+initial apprehension, we believe the way we have integrated AR into our app
+enhances the user experience. Hardware issues were definitely our biggest
+challenge. Only one member of our team had a phone new enough to run AR technology at a
+decent level, making testing of our application difficult.
 
@@
 
-Before our project started, Kyoto VR was already using an app with a limited
-form of AR for tours. The app, called izi.TRAVEL, allows users to create audio
-tours with audio and image files tied to specific locations in the real
+Before our project started, Kyoto VR was already using an app to deliver audio
+tours. The app, called izi.TRAVEL, allows users to create audio tours with
+audio and image files tied to specific locations in the real
 world~\autocite{izitravel2015} (see Figure \ref{fig:iziTravel}). The app is
 aimed at museums and city tours~\autocite{izitravel} but can be used for tours
-of historic sites too.  Kyoto VR used the platform to make an audio tour of
-Kinkaku-ji, one of the most popular tourist destinations in
-Japan~\autocite{bornoff2000} and an important historic heritage
-site~\autocite{unesco}.
+of historic sites too.  Kyoto VR used the platform to make a simple audio tour
+of Kinkaku-ji.
 
@@
 
-By using GPS data from the user's phone to play audio and display images at
-specific places in the real world izi.TRAVEL uses a limited form of augmented
-reality. Our group aimed to implement and extend this functionality in our own
-app. See Section \ref{sec:aruko} for more details.
+Our group aimed to implement all the functionality of izi.TRAVEL and more in
+our own app. See Section \ref{sec:aruko} for more details.
 
@@
 Before we could start working on creating our app, we first needed to decide
-which AR development platform to use. Our preliminary research had shown us that
-there are so many different platforms out there, all of which have been used to
-create great AR apps. There were a lot of things we needed to consider before
-finalizing on a platform, like what features it offered, which devices and
-operating systems the app could run on, and definitely the cost. Detailed below
-are some of the different platforms we considered.
+which AR development platform to use. Based on our preliminary research, we
+learned there are many powerful platforms available. There were many things we
+needed to consider before deciding on a platform. These considerations included
+what features the platform offered, which devices and operating systems the app
+could run on, and the cost. Detailed below are some of the different platforms
+we considered.
 
@@
 
-ARKit and ARCore are both AR frameworks that enable apps to take advantage of
+ARKit and ARCore are both frameworks that enable apps to take advantage of
 powerful AR related features. ARKit is developed by Apple and can only be used
-by iPhones. Google's ARCore framework can deploy to both Android and iPhone.
-Many cross platform solutions will leverage the full potential of their target
-platform by using either ARKit or ARCore ``under the hood''. Both ViroReact and
-Vuforia use ARKit or ARCore depending on the target platform
-\autocites{vuforiaFusion}{moon2018}.
+by iPhones~\autocite{summerson2018}. Google's ARCore framework can deploy to both
+Android and iPhone. Many cross platform solutions will leverage the full
+potential of their target platform by using either ARKit or ARCore ``under the
+hood.'' Both ViroReact and Vuforia use ARKit or ARCore depending on the target
+platform \autocites{vuforiaFusion}{moon2018}.
 
 ARKit 3 aims to support a wide array of new features and will be available in
-iOS 13. Notably, one of these features is ``people occlusion,'' which will allow
-virtual objects to be realistically obscured when someone walks in front of the
-object~\autocite{apple2019}. This kind of technology could be useful for us
-since our app uses AR in crowded places.  As of August 2019, this feature is
-not on the horizon for Google's Android AR framework, ARCore.
+iOS 13~\autocite{apple2019}. Notably, one of these features is ``people
+occlusion,'' which will allow virtual objects to be realistically obscured when
+someone walks in front of the object. This kind of technology could be useful
+for us since our app uses AR in crowded places.  As of August 2019, this
+feature is not on the horizon for ARCore.
 
 Both ARKit and ARCore have well-supported APIs for Unity. ARKit 3 support is
-coming to Unity, along with all of the advanced features that it
+coming soon to Unity, along with all of the advanced features that it
 brings~\autocite{stinson2019}.
@@
 powering over 30,000 AR apps across smartphones, tablets, and smart
-glasses~\autocite{wikitude2018}.  And it's easy to understand why Wikitude has
-so many registered developers when you see the list of features it offers. Some
-of the features that appealed most to us were their Instant Tracking, allowing
-for augmentation using flat surfaces; Image Tracking, allowing for augmentation
-using one or multiple 2D images; and Geo AR, allowing for creation of
-geo-markers at specific locations to triggered AR
-content~\autocite{wikitude2018}.
-
-Wikitude also supports all sorts of different platforms. It supports Android,
-Apple, and Windows phones and tablets, as well as smart glasses like the Epson
-Moverio, Microsoft Hololens, and Vuzix smart glasses~\autocite{wikitude2018}.
-Additionally, many different development frameworks are capable of running
-Wikitude's SDK.  According to Wikitude's website, their SDK works with Windows,
-Android, and iOS development frameworks, as well as ARCore and ARKit, Flutter,
-Cordova, Xamarin, and even Unity~\autocite{wikitude2018}.
-
-From all of this information, Wikitude certainly sounds like a fantastic AR
-development platform; it certainly did to us. But the issue we ran into was the
-cost. Wikitude is, in fact, free for eligible startups, but given the criteria
-they list on their site, we were not confident that we would qualify. Aside
-from this option, Wikitude offers a 30-day demo license for \euro{499}, which
-is a lot for use to pay for a license that would not even last for our entire
-project. They also charge \euro{1990} for their SDK Pro, and \euro{2490} for
-their SDK Pro 3D~\autocite{wikitude2018}. Given these prices, and our very
-limited budget, we knew that we would have to pass on Wikitude and choose a
-different AR development platform.
+glasses~\autocite{wikitude2018}. It is easy to understand why Wikitude has so
+many registered developers considering the list of features the platform
+offers. Some of the features that appealed most to us were their ``Instant
+Tracking,'' allowing for augmentation using flat surfaces; ``Image Tracking,''
+allowing for augmentation using one or multiple 2D images; and ``Geo AR,''
+allowing for creation of geo-markers at specific locations to trigger AR
+content.
+
+Wikitude supports Android, Apple, and Windows phones and tablets, as well as
+smart glasses like the Epson Moverio, Microsoft HoloLens, and Vuzix smart
+glasses. Additionally, many different development frameworks are capable of
+running Wikitude's software development kit (SDK). According to Wikitude's
+website, their SDK works with Windows, Android, and iOS development frameworks,
+as well as ARCore and ARKit, Flutter, Cordova, Xamarin, and even Unity.
+
+Based on this information, Wikitude was initially appealing to us. However, the
+cost was a major issue. Wikitude is free for eligible startups, but given the
+criteria they list on their site, we were not confident that we would qualify.
+Aside from this option, Wikitude offers a 30-day demo license for \euro{499},
+which was far beyond the resources available to us. They also charge
+\euro{1990} for their SDK Pro, and \euro{2490} for their SDK Pro 3D. Given
+these prices, and our very limited budget, we decided to consider other
+options.
 
@@
 
-The company motive.io used to work on a product that would allow users to create
-an engaging AR experience in the style of \textit{Pokémon Go}. Their service
-would have purportedly handled technical details such as hosting, storage, and
-user accounts. The promotional video shows the creation of a location-based AR
-game where the user pretends to hack into ATMs using the real-world locations of
-ATMs in a city\autocite{odom2017}.
+The company motive.io previously was developing a product that would allow
+users to create an engaging AR experience in the style of
+\textit{Pokémon~Go}~\autocite{odom2017}. Their service would have purportedly
+handled technical details such as hosting, storage, and user accounts. The
+promotional video shows the creation of a location-based AR game where the user
+pretends to hack into ATMs using the real-world locations of ATMs in a city.
 
 Unfortunately, it appears that the company has completely pivoted off of this
-idea, and has since moved to AR training software\autocite{motiveio}.
-
-We reached out to motive.io via email for any advice they might be willing to
-give us, but we received no response.
-
-\subsubsection{Viro AR}
+idea, and has since moved to developing AR training
+software~\autocite{motiveio}. We reached out to motive.io via email for any
+advice they might be willing to give us, but we received no response.
+
+\subsubsection{ViroAR}
 \label{sec:viroAR}
 
-Viro AR comes in two flavors: ViroReact and ViroCore. ViroCore allows
-developers to build an AR Application with Java. The disadvantage of this is
-that ViroCore only allows developers to target Android, which unfortunately
-made ViroCore not an option for our project. ViroReact is the cross-platform
-option for ViroAR. ViroReact leverages the cross-platform capabilities of
-React, which is Facebook's JavaScript Library for developing user
-interfaces~\autocite{facebook2019}.
+Viro AR comes in two flavors: ViroReact and ViroCore\autocite{facebook2019}.
+ViroCore allows developers to build an AR Application with Java. The
+disadvantage of this is that ViroCore only allows developers to target Android,
+which unfortunately made ViroCore not an option for our project. ViroReact is
+the cross-platform option for ViroAR. ViroReact leverages the cross-platform
+capabilities of React, which is Facebook's JavaScript Library for developing
+user interfaces~\autocite{facebook2019}.
 
 Since our project is not a game, we initially wanted to avoid using a
-fully-featured game engine. Therefore, we decided to take the time to explore
-this framework since it appeared to be more tailored to our specific use case.
-Viro Media also recognizes that all developers who wish to create an app with
-3D capabilities are not necessarily game developers. Viro Media pitches Viro
-AR as ``The perfect alternative to specialized game engines, ViroAR is a
-platform for rapidly building ARKit and ARCore apps. Our platform allows
-developers to focus on what they do best by leveraging familiar tools and
-frameworks used in mobile application development''~\autocite{viro2019}.
-While the majority of our team has decent experience with writing JavaScript,
-we all either have very little or no experience writing React apps.
-
-In most development scenarios, every time you wish to test your app on actual
-hardware, you must first compile your app using either Xcode or Android Studio
-depending on your platform. Once you have built the app, your device needs to
-install the app. This process can be very time consuming, especially since
-frequent tests on real hardware is important for something as intensive as
-AR.
-
-An alternative to building your app is to run your app through an emulator on
-the computer you are using for development.
+fully-featured game engine such as Unity (see Section~\ref{sec:unity}.
+Therefore, we decided to take the time to explore this framework since it
+appeared to be more tailored to our specific use case. Viro Media also
+recognizes that all developers who wish to create an app with 3D capabilities
+are not necessarily game developers. Viro Media pitches ViroAR as ``The
+perfect alternative to specialized game engines, ViroAR is a platform for
+rapidly building ARKit and ARCore apps. Our platform allows developers to focus
+on what they do best by leveraging familiar tools and frameworks used in mobile
+application development''~\autocite{viro2019}. While the majority of our team
+has decent experience with writing JavaScript, we have have very little experience
+writing React apps.
+
+In most app development scenarios, to test the app on actual hardware, it must
+be compiled using either Xcode or Android Studio depending on your platform.
+Once you have built the app, your device needs to install the app. This process
+can be very time consuming, especially when needing to run frequent tests on
+the target platform.
+
+An alternative to building an app for a physical phone is to run it through an
+emulator on a computer.
 
@@
 them''~\autocite{techopedia2019}. Emulators are often very useful for speeding
-up development. Loading programs onto the Android emulator usually much faster
-than installing the APK onto the actual device. Additionally, you can mock
-almost all of the important features of an actual Android device, including
-calls, text, GPS position, device rotation and more~\autocite{androidemulator}.
+up development. Loading programs onto the Android emulator is usually much
+faster than installing an Android package file (APK) onto the actual device.
+Additionally, emulators can mock almost all of the important features of an
+actual Android device, including calls, text, GPS position, device rotation and
+more~\autocite{androidemulator}.
 
@@
 bail out Lake Michigan with a teaspoon.'' The editor goes on to explain
-``Emulation is a complex business, but here's one rule of thumb: The only way to
-successfully emulate a machine is with a much more powerful
+``Emulation is a complex business, but here's one rule of thumb: The only way
+to successfully emulate a machine is with a much more powerful
 machine''~\autocite{warick1988}. In our case, emulating Android on a desktop
 operating system is closer to emulating a C64 on an IBM PC running MS-DOS
-(rather than the other way around, thankfully). The moral is that the speed
+(rather than the other way around, thankfully). The takeaway is that the speed
 problem facing emulators is just as real as it was in 1988. Considering that AR
-already pushes modern phone hardware to the limit, emulation is not something is
-not something we wanted to struggle with. On top of this, our testing required
-us to move the camera through the world at various speeds and angles, which is
-simply cumbersome with a laptop webcam.
+already pushes modern phone hardware to the limit, emulation is not something
+is not something we wanted to struggle with. On top of this, our testing
+required us to move the camera through the world at various speeds and angles,
+which is simply cumbersome with a laptop webcam.
 

### 2019-09-28 paper.tex
working on revisions

@@
 
-We would like to thank Atticus Sims, CEO and founder of Kyoto VR, for sponsoring
+We would like to thank Atticus Sims, CEO and founder of Kyoto~VR, for sponsoring
 this project and providing help and guidance throughout our time in Japan. His
@@
 researching AR technology. A special thank you to the IQP team working with
-Kyoto VR, Lewis Cook, Nicole Escobar, Ahad Fareed, and Cameron Person, for
+Kyoto~VR, Lewis Cook, Nicole Escobar, Ahad Fareed, and Cameron Person, for
 filming and editing the app trailer, as well as providing help with testing.
@@
 identify important features to add to the app. Much of the app's functionality
-was dictated by Atticus Sims, C.E.O and founder of Kyoto VR, who plans to
+was dictated by Atticus Sims, C.E.O and founder of Kyoto~VR, who plans to
 monetize the app. We also worked with an IQP team, who had been tasked with
@@
 the tour from the downloaded contents. We were able to host the backend on the
-server provided by Kyoto VR's hosting plan; we discuss the hurdles that we
-overcame to deploy the Editour backend with Kyoto VR's current setup in
+server provided by Kyoto~VR's hosting plan; we discuss the hurdles that we
+overcame to deploy the Editour backend with Kyoto~VR's current setup in
 Section~\ref{sec:deployingTheEditourBackend}.
@@
 
-Before our project started, Kyoto VR was already using an app to deliver audio
+Before our project started, Kyoto~VR was already using an app to deliver audio
 tours. The app, called izi.TRAVEL, allows users to create audio tours with
@@
 aimed at museums and city tours~\autocite{izitravel} but can be used for tours
-of historic sites too.  Kyoto VR used the platform to make a simple audio tour
+of historic sites too.  Kyoto~VR used the platform to make a simple audio tour
 of Kinkaku-ji.
@@
 rapidly testing your ViroReact app on native hardware without the need for an
-emulator. In the root directory of your project, you can launch a Node server
-with the command \texttt{npm start}. From here, you can input the provided URL
-into the Viro Media app. This will quickly download the code, graphics, and 3D
-object files from the server and launch a functional version of the app
-\autocite{viro-testbed2019}. This allowed us to get a real AR app up and
-running on our devices much more easily than any of the other
-frameworks/engines we explored. Unfortunately, the test bed app was somewhat
-unreliable based on our experience; the test bed would frequently crash or
-would not be able to download the files from the Node server. The most reliable
-way to test our app was to compile a binary and manually install it onto our
-devices, which completely defeats the purpose of the test bed app.
+emulator. This allowed us to get a real AR app up and running on our devices
+much more easily than any of the other frameworks/engines we explored.
+Unfortunately, the test bed app was somewhat unreliable based on our
+experience; the test bed would frequently crash or would not be able to
+download the files from the server. The most reliable way to test our app was
+to compile a binary and manually install it onto our devices, which completely
+defeated the purpose of the test bed app.
 
@@
 \label{sec:unity}
+
+%TODO write this section
+TODO: write this section
 
@@
 its shining gold walls and magnificent gardens. Our project intends to enhance
-user's enjoyment and understanding of Kinkaku-ji through informative interactive
+users' enjoyment and understanding of Kinkaku-ji through informative interactive
 media, teaching about the history and significance of the site.
@@
 1955, close to the original design but with more extensive gold
-leaf~\autocite{bornoff2000}. The interior was also restored later.
+leaf~\autocite{bornoff2000}. The interior was also restored later to match the
+original.
 
@@
 The goal of Editour is to allow a non-technical user to design audio tours
-through a web-app. At its core, Editour is a tool to draw arbitrarily-shaped
+through a web app. At its core, Editour is a tool to draw arbitrarily-shaped
 geographic regions onto a map, edit those regions and assign media to each of
@@
 After naming and uploading the tour with the ``Upload'' button, our backend
-builds a zip containing a folder that can be placed directly into the Unity
+builds a zip containing files that can be placed directly into the Unity
 project.
 
-Our backend allows users to save their tours to our server and load those same
+Our backend allows users to save their tours to a server and load those same
 tours back into the editor to resume work. The geographic area of each region
@@
 
-\subsubsection{The Need for an Editor}
-\label{sec:theNeedForAnEditor}
+\subsubsection{The Need for an Editour}
+\label{sec:theNeedForAnEditour}
 
 One of the goals for our project is to create a working prototype that others
-can build off of in the future.
-
-Similar to the app izi.TRAVEL discussed in Section~\ref{sec:iziTravel}, we
-needed some way to easily define arbitrary polygons (which we call ``regions'')
-and associate media with each one, such as audio and image files.
+can build off of in the future. Similar to the app izi.TRAVEL discussed in
+Section~\ref{sec:iziTravel}, we needed some way to easily define arbitrary
+polygons (which we call ``regions'') and associate media with each one, such as
+audio and image files.
 
 For testing purposes, we initially defined these regions directly in the C\#
-Scripts, hard-coding the coordinates. Below is an example of a quadrilateral
+scripts, hard-coding the coordinates. Below is an example of a quadrilateral
 surrounding the Creation Core building at the Ritsumeikan Biwako-Kusatsu campus.
@@
 Even with knowledge of C\# and Unity, inputting tour data this way is obviously
-not convenient. Atticus reminded us that, although he has a working knowledge of
-Unity, he is not a software developer. In order to make our app prototype at all
-useful for the future, we needed to provide an easy way to ``design'' a tour.
+cumbersome. Atticus is not a software developer, and does not want to work with
+C\# scripts. In order to make our app prototype at all useful for the future,
+we needed to provide an easy way to ``design'' a tour using a simple graphical
+interface.
 
@@
 
-Here is an example of the JSON metadata generated by Editour:
+Here is an example of a tour metadata file in JavaScript Object Notation (JSON)
+format:
 
@@
          "images": [ "hill.jpg", "valley.jpg", "gorge.jpg" ],
-         "transcript", "To your right, you can see a gorgeous place."
+         "transcript": "To your right, you can see a gorgeous place."
       }
@@
 Within each object in the region list, we can see that the region has five
-properties: a name, a list of coordinates, a list of audio files, a list of
-multiple image files, and a transcript of the audio file. (In the current
-design of the app, it only makes sense to associate one audio file per region,
-but the format makes it easy to accommodate for multiple audio files in the
-future.) One disadvantage is that all media files have to have unique names.
+properties: a name, a list of coordinates, a list of audio files,\footnote{In
+the current design of the app, it only makes sense to associate one audio file
+per region, but the format makes it easy to accommodate for multiple audio
+files in the future.} a list of multiple image files, and a transcript of the
+audio file. One disadvantage is that all media files have to have unique names.
 This is because the zip that is created by the Editour backend contains all of
@@
 each media file with a region, meaning that the filename needs to act as a
-primary key. The backend will respond with a message if this is the case,
-prompting the user to have unique names for all files.
+unique identifier. The backend will respond with a message if it finds
+duplicate filenames, prompting the user to use unique names for all files.
 
@@
 
-The user can easily create a new region by shift-clicking, and then clicking
-points on the map.  To terminate the polygon, the user must shift-click again.
-The ``Welcome to Editour'' card (seen in Figure~\ref{fig:welcomeCard}) provides
+The user can easily create a new region by shift-clicking the map, and then
+continuing to click to define more points. Figure~\ref{fig:drawingRegion} shows
+this in action. To terminate the polygon, the user must shift-click again. The
+``Welcome to Editour'' card (seen in Figure~\ref{fig:welcomeCard}) provides
 these instructions, which should be enough to get started. A user can only
@@
 card appears in the side bar. From here, the user can edit anything about the
-region. From here, the user can edit anything about the region.
+region.
 
@@
 textbox, allowing the user to rename the region after clicking ``Okay'' or
-hitting the enter key. (There are multiple places in the UI where a textbox is
-immediately adjacent to a ``Confirm'' button.  We made sure all of these can be
-triggered by simply hitting enter, since this is common when filling out
-forms.)
+hitting the enter key.\footnote{There are multiple places in the UI where a
+textbox is immediately adjacent to a ``Confirm'' button.  We made sure all of
+these can be triggered by simply hitting enter, since this is common behavior
+when filling out forms on the web.}
 
@@
 
-The second subcard seen in Figure~\ref{fig:mediaSubcard} is slightly involved.
-Expanding the ``Media'' subcard by clicking on the green bar will reveal a bevy
-of options for augmenting the audio, images and text to be associated with that
-region of the tour. From here, the user can upload an audio file and multiple
-image files from his or her hard drive with the two file-select fields. If the
-tour has been downloaded as a server, the names of the files already present on
-the server will appear as cards with `X' buttons. This allows the user to
-remove images or audio from that region even after the tour has been uploaded.
+The second subcard seen in Figure~\ref{fig:mediaSubcard} is slightly more
+involved. Expanding the ``Media'' subcard by clicking on the green bar will
+reveal a bevy of options for augmenting the audio, images, and text to be
+associated with that region of the tour. From here, the user can upload an
+audio file and multiple image files from his or her hard drive with the two
+file-select fields. If the user is editing an existing tour that has already
+been uploaded, the names of the files already present on the server will appear
+as cards with `X' buttons. This allows the user to remove images or audio from
+that region even after the tour has been uploaded.
 
@@
 
-The third subcard is the ``Edit'' subcard. This subcard can be revealed in one
-of two ways. The first way is by clicking on the yellow bar labeled ``Edit'',
-which is the same for all subcards. Alternatively, the user can also click
-directly on the region on the map. The region will flash yellow and be scrolled
-into view to let the user know which region was clicked on. Both of these
-methods will enable editing mode, whereby the user can directly manipulate the
-vertices that make up the region. Blue circles appear on top of each vertex,
-and red circles appear at the midpoint of each edge. Clicking on a red midpoint
-will add an additional vertex at that midpoint. Dragging one of the blue
-vertices will do as you might expect---move the vertex around. The latitude and
-longitude are updated in the ``Edit'' subcard as the user drags the vertex
-around. Clicking on the vertex directly will create a blue pin-shaped marker
-that the user can also drag around. Clicking on the coordinate box in the
-subcard will also create this blue pin-shaped marker; the map will also pan to
-this coordinate. The user can also delete vertices in the same way that files
-can be deleted from the ``Media'' subcard by clicking on the `X' button. If there
-are exactly three points in a region, the `X' buttons will be ``grayed-out'',
-preventing the user from deleting any more points (since a polygon must consist
-of at least three points.)
+The third subcard is the ``Points'' subcard. This subcard can be revealed in
+one of two ways. The first way is by clicking on the yellow bar labeled
+``Points'', which is the same for all subcards. Alternatively, the user can
+click directly on the region on the map. The region will flash yellow and be
+scrolled into view to let the user know which region was clicked on. Both of
+these methods will enable editing mode, whereby the user can directly
+manipulate the vertices that make up the region. Blue circles appear on top of
+each vertex, and red circles appear at the midpoint of each edge. Clicking on a
+red midpoint will add an additional vertex at that midpoint. Dragging one of
+the blue vertices will move the vertex around. The latitude and longitude are
+updated in the ``Points'' subcard as the user drags the vertex around. Clicking
+on the vertex directly will create a blue pin-shaped marker that the user can
+also drag. Clicking on the coordinate box in the subcard will also create this
+blue pin-shaped marker; the map will also pan to this coordinate. The user can
+also delete vertices in the same way that files can be deleted from the
+``Media'' subcard by clicking on the `X' button on that vertex's coordinate
+card. If there are exactly three points in a region, the `X' buttons will be
+``grayed-out,'' preventing the user from deleting any more points, since a
+polygon must consist of at least three points.
 
@@
     \includegraphics[width=\textwidth]{edit-subcard-with-map-editour.png}
-    \caption{The ``Edit'' subcard with the map showing vertices and edges that
+    \caption{The ``Points'' subcard with the map showing vertices and edges that
     can be edited}
@@
 The third subcard pictured in Figure~\ref{fig:deleteSubcard} is the ``Delete''
-subcard. When revealed, another button will appear labeled ``Really Delete''.
+subcard. When revealed, another button will appear labeled ``Really Delete.''
 The action can be canceled by collapsing the subcard by hitting the bar now
-labeled ``Don't Delete!''. This prevents the user from accidentally deleting a
-region he or she did not mean to.
+labeled ``Don't Delete!'' This prevents the user from accidentally deleting a
+region he or she did not mean to remove.
 
@@
 indicating the upload/download process, which can be seen in
-Figure~\ref{fig:uploadingMessage}. If a 200 or 201 is returned from the server,
-a ``Success'' message will appear. If there was some problem, the error message
-returned by the server is displayed in this box instead. Since uploading,
-downloading and deleting are all network-related operations, it makes sense to
-include this message box for each card.
+Figure~\ref{fig:uploadingMessage}. If an HTTP 200 (OK) or 201 (Created)
+code~\autocite{rfc7231} is returned from the server, a ``Success'' message will
+appear. If there was some problem, the error message returned by the server is
+displayed in this box instead. Since uploading, downloading, and deleting are
+all network-related operations, it makes sense to include this message box for
+each card.
 
@@
 
-When the page is loaded, the frontend will request the names of the files
+When the page is loaded, the frontend will request the names of the tour files
 stored on the server from the backend. This data is used to create a box of
@@
 the saved tour into the textbox in order to retrieve it. The user is still free
-to do this, but the buttons make this easier and less error-prone. The download
-card containing a box filled with filenames on the server can be seen in
-Figure~\ref{fig:downloadCard}.
+to do this, but the buttons make this easier and less error-prone. This feature
+can be seen in figure Figure~\ref{fig:downloadCard}. Clicking ``Download'' does
+not download the tour to the user's computer. Instead, it requests only the
+tour metadata from the server so the tour's data can be displayed in the web
+app. The user can then edit the tour and upload a new version.
 
@@
 constraints.  You can type in a latitude and longitude directly and hit the
-``Jump'' button. We also hard-coded a few shortcuts for places that Atticus
-might want to design a tour for in the future, which can be accessed by
-clicking on the yellow buttons with place names.
+``Jump'' button to pan to the specified location. We also hard-coded a few
+shortcuts for places that Atticus might want to design a tour for in the future,
+which can be accessed by clicking on the yellow buttons with place names.
 
@@
 
-Once a tour is either uploaded or downloaded, a link to download the zip file
-will appear. The zip file contains all of the uploaded media, and a metadata
-file. The metadata is in the form of a JSON file; it contains all of the
-latitudes, longitudes, and enough information to associate all of the media
-with the correct regions. This is the file that we unzip and place into the
-Unity project before it is compiled. This also is useful if the user wants to
-check the audio and image files that were uploaded.
-
+Once a tour is either uploaded or downloaded, a link to download the zip file of
+that tour will appear. The zip file contains all of the uploaded media, and a
+metadata file. The metadata is in the form of a JSON file; it contains all of
+the latitudes, longitudes, and enough information to associate all of the media
+with the correct regions. The downloaded zip file is what we decompress and
+place into the Unity project before it is compiled. This feature is also useful
+if the user wants to check the audio and image files that were uploaded.
+
+%update this figure
 \begin{figure}[h]
@@
 Node.js. This backend both serves the static frontend content and runs
-server-side scripts that process incoming API requests.  We chose Node.js as the
-server-side framework because of our prior experience with JavaScript, its
-high-performing asynchronous architecture~\autocite{orsini2013}, and its ease of
-development.
+server-side scripts that process incoming application programming interface
+(API) requests. We chose Node.js as the server-side framework because of our
+prior experience with JavaScript, its high-performing asynchronous
+architecture~\autocite{orsini2013}, and its ease of development.
 
 When a user submits new tour from the web application, the files and metadata
-are sent to the server running the Node.js scripts, which zips up the files and
-saves them to the server's disk with a timestamp. Then any application can
-request a particular tour and the backend will serve the most recent version of
-it.
-
-As previously mentioned in \ref{sec:editingATour}, our web application allows
-users to edit existing tours. When the user requests to edit a tour on the
-frontend it sends a request to the backend server for that tour's metadata
+are sent to the server running the Node.js scripts. The server zips up the files
+and saves them to the disk with a timestamp. Then any application can request a
+particular tour and the backend will serve the most recent version.
+
+As previously mentioned in Section~\ref{sec:editingATour}, our web application
+allows users to edit existing tours. When the user requests to edit a tour on
+the frontend it sends a request to the backend server for that tour's metadata
 file. This file contains information about all regions and files in the tour.
@@
 asked Atticus to provide a more powerful---and geographically closer---hosting
-solution for running the Editour in the future. He obtained a domain name and
+solution for running the Editour in the future. He obtained a domain name and a
 shared hosting environment on a Red Hat Enterprise Linux (RHEL) server for us to
@@
 We were able to get shell access to the shared hosting environment, but without
-superuser privileges. This meant we couldn't install packages, change system
-settings, or access \texttt{systemctl}. In order to install Node.js and npm in
-this environment we had to use Node Version Manager, a series of shell scripts
-that handles downloading and compiling various versions of
-Node~\autocite{nvmsh2019}.  The only difficulty with this was finding a version
-of Node.js that could compile with the older version of GCC the RHEL server had.
-Fortunately the server already had git installed, so we were able to simply
-clone the backend from GitHub and run it with npm.
+superuser privileges. This meant we could not install packages, change system
+settings, or access \texttt{systemctl}, the command that manages systemd
+services. In order to install Node.js and npm in this environment we had to use
+Node Version Manager, a series of shell scripts that handles downloading and
+compiling various versions of Node~\autocite{nvmsh2019}.  The only difficulty
+with this was finding a version of Node.js that could compile with the older
+version of GCC that the RHEL server had. After resolving this challenge, we were
+able to simply clone the backend from GitHub and run it with npm.
 
@@
 this. Instead we decided to configure Apache as a reverse proxy, using only the
-rules that can be put in a \texttt{.htaccess} file, since this is the only
-configuration file we could access. Using Apache's \texttt{mod\_rewrite} module
-we were able to rewrite incoming requests on port 80 to instead go to
-\texttt{localhost:3000}, the port where Node.js was
-listening~\autocite{apache2019}.
+rules that can be put in a \texttt{.htaccess} file,\footnote{This is a
+directory-level configuration file with limited options compared to Apache's
+global configuration files.} since this is the only configuration file we could
+access. Using Apache's \texttt{mod\_rewrite} module we were able to rewrite
+incoming requests on port 80 to instead go to \texttt{localhost:3000}, the port
+where Node.js was listening~\autocite{apache2019}.
 
@@
 
-Tours are stored on the server as compressed \texttt{.zip} files, but when
-uploading or editing a tour these zips are decompressed to a temporary
-directory. To prevent the server's limited disk space from filling up with old
-temporary files we wrote a simple bash script that removes directories that
-haven't been modified in the past five days. We set up a \texttt{cron} job to
-run this script automatically once per day to clean out old temporary files that
-aren't being used any more.
-
-Unfortunately, the hosting provider Kyoto VR provided us with severely throttles
+Tours are stored on the server as compressed zip files, but when uploading or
+editing a tour these zips are decompressed to a temporary directory. To prevent
+the server's limited disk space from filling up with old temporary files we
+wrote a simple bash script that removes directories that have not been modified
+in the past five days. We set up a cron job\footnote{The program cron allows for
+periodic scheduling of repeated commands} to run this script automatically once
+per day to clean out old temporary files that are not being used any more.
+
+Unfortunately, the hosting solution Kyoto~VR provided us with severely throttles
 disk write speeds. Because the backend has to write potentially large amounts of
@@
 hosting provider there is nothing we can do about this bug. The Node server does
-eventually complete the request and respond correctly, so until Kyoto VR can get
+eventually complete the request and respond correctly, so until Kyoto~VR can get
 a better hosting provider we consider it a minor issue.
@@
 would like the app to be able to contact a server running a version of the
-Editour backend and update the tour info by itself. This would allow Kyoto VR
+Editour backend and update the tour info by itself. This would allow Kyoto~VR
 to update the tours without updating the entire app.
@@
 While AR translation apps exist, the experience can be frustrating, and produce
-poor results. Google's text recognition and machine-learning powered
-translation technology is certainly impressive. At the same time, the
-translation service works better in ``scan'' mode instead of ``instant'' mode.
-In ``instant'' mode, the app attempts to translate text as quickly as possible,
-superimposing the translated text onto the real world using the camera. In
-``scan'' mode, the user first takes a photo. Then, the user is prompted to
-highlight where text appears in the photo. After the translation is complete,
-the translated text appears in a separate UI element instead superimposed onto
-the photo. In most cases, it is more convenient and readable to have the
-translation appear in a separate scrollable textbox. This motivated the current
-design of the ``info buttons'' in ARuko. Instead of placing text directly onto
-signage, we place a blue button with an `i' in the center. By tapping on this
-button, a separate UI element will appear containing the translated text. Since
-this button is cast into the world using the AR camera, the button is
-intuitively placed directly onto the content in the real world.
+poor results. Google's text recognition and machine-learning powered translation
+technology is certainly impressive. At the same time, the translation service
+works better in ``scan'' mode instead of ``instant'' mode. In ``instant'' mode,
+the app attempts to translate text as quickly as possible, superimposing the
+translated text onto the real world using the camera. In ``scan'' mode, the user
+first takes a photo. Then, the user is prompted to highlight where text appears
+in the photo. After the translation is complete, the translated text appears in
+a separate UI element instead superimposed onto the photo. In most cases, it is
+more convenient and readable to have the translation appear in a separate
+scrollable textbox. This motivated the current design of the ``info buttons'' in
+ARuko. Instead of placing text directly onto signage, we place a blue button
+with a stylized `i' in the center. By tapping on this button, a separate UI
+element will appear containing the translated text. Since this button is cast
+into the world using the AR camera, the button appears to be placed directly
+onto the content in the real world.
 
@@
 \begin{figure}[h] \centering
-    \includegraphics[width=0.3\textwidth]{ar-map-feature.png}
+    \includegraphics[width=0.4\textwidth]{ar-map-feature.png}
     \caption{Map overlay displaying the path and translated labels}
@@
 elements were created as new features were added. But as more features were
-added, it became clear that the UI couldn't consist simply of buttons and 
+added, it became clear that the UI could not consist simply of buttons and 
 other basic features provided by Unity. We would need to learn more about 
@@
 started playing long before the user was actually near the feature it was
-discussing. Using the Editour web-app, we were able to correct quickly these
+discussing. Using the Editour web app, we were able to correct quickly these
 issues with the tour design once we returned to Atticus' office.
@@
 including Kyoto, Beijing, London and New York~\autocite{michaelwhittle2019}.
-Kyoto VR has worked with Michael Whittle in the past to create a 3D scan of a
+Kyoto~VR has worked with Michael Whittle in the past to create a 3D scan of a
 solo exhibition, `Portraits of Thought'. This exhibition displayed diagrams
@@
 
-Despite these issues our team is happy with the product we delivered to Kyoto
-VR. ARuko is not quite ready to be sold on app stores yet, but with a little
-more development time it could easily be made ready. The UI could use more
-testing with real users to make sure it is intuitive and easy to use. We also
-intended to add a feature where the app could automatically download tour files
-from the Editour server and import them without having to rebuild. We were not
-able to complete this feature due to time constraints, but it could easily be
-added because all of ARuko's business logic is abstracted and generalized to
+Despite these issues our team is happy with the product we delivered to
+Kyoto~VR. ARuko is not quite ready to be sold on app stores yet, but with a
+little more development time it could easily be made ready. The UI could use
+more testing with real users to make sure it is intuitive and easy to use. We
+also intended to add a feature where the app could automatically download tour
+files from the Editour server and import them without having to rebuild. We were
+not able to complete this feature due to time constraints, but it could easily
+be added because all of ARuko's business logic is abstracted and generalized to
 support multiple tours. Editour also already supports requesting and downloading
@@
 (\url{https://github.com/bandaloo/editour/releases/tag/v1.3.0}), and it contains
-all the features necessary to create and edit tours. In the future Kyoto VR
+all the features necessary to create and edit tours. In the future Kyoto~VR
 should move it to a more powerful hosting provider (see
@@
 More historic locations around Kyoto and Japan in general should be considered
-for other tours. With the work our team has done Kyoto VR now has a complete
+for other tours. With the work our team has done Kyoto~VR now has a complete
 platform for creating and delivering unique tours, which can easily be expanded
@@
 	the tour was edited successfully, 400 if the request was invalid, 404 if the
-	requested tour couldn't be found, or 500 if a server error occurred while
+	requested tour could not be found, or 500 if a server error occurred while
 	processing the request.

### 2019-09-28 paper.tex
finished making last-minute edits

@@
 illustrated map. Much like the signage, there is no language on the map other
-than Japanese. Using the AR camera within the app, you can project information
+than Japanese. Using the AR camera within the app, information can be projected
 onto the map. Figure~\ref{fig:arMapFeature} shows the blue highlighted path of
@@
 
-When you buy a ticket to enter Kinkaku-ji, you receive a long sheet of
-printed paper with calligraphy. The tickets are large and visually appealing;
-they are souvenirs unto themselves that one might feel inclined to keep
-around. Over the course of our three month stay we visited Kinkaku-ji
-multiple times. For each visit, we received identical tickets. Seemingly, the
-design on the tickets do not change on a regular basis, if at all.
-
-Because the tickets are unlikely to change, this enables us to provide the
-user with a ``virtual souvenir'' using the AR camera. This is the only AR
-feature that is not tied directly to an image target that can only be
-accessed at Kinkaku-ji. While the image gallery and segments of the audio
-tour can be accessed at any time using the ``Chapter Select'' menu, most of
-the AR features can only be experienced during the walking tour, pointing the
-camera at objects physically located at the site. Augmenting the ticket
-with 3D content allows visitors to take something home, giving them a reason
-to launch the app later.
+Tickets to enter Kinkaku-ji are long sheets of printed paper with calligraphy.
+The tickets are large and visually appealing; they are souvenirs unto themselves
+that one might feel inclined to keep around. Over the course of our three month
+stay we visited Kinkaku-ji multiple times. For each visit, we received identical
+tickets. Seemingly, the design on the tickets do not change on a regular basis,
+if at all.
+
+Because the tickets are unlikely to change frequently, this enables us to
+provide the user with a ``virtual souvenir'' using the AR camera. This is the
+only AR feature that is not tied directly to an image target that can only be
+accessed at Kinkaku-ji. While the image gallery and segments of the audio tour
+can be accessed at any time using the ``Chapter Select'' menu, most of the AR
+features can only be experienced during the walking tour, pointing the camera at
+objects physically located at the site. Augmenting the ticket with 3D content
+allows visitors to take something home, giving them a reason to launch the app
+later.
 
@@
 Originally, the AR model of the Golden Pavilion was flush against the plane of
-the ticket, sitting on the paper as if it were ground. Atticus suggested that
-we re-orient the model such that the ticket served as a back plane. This would
-allow users to hold the ticket vertically, and view the Golden Pavilion
-floating in front of the ticket. This allows users to place their hands under
-the base of the Golden Pavilion model as if they were holding it. Vuforia's
-image tracking is flexible enough such that the image target can be partially
-obscured.
-
-\subsubsection{Early UI}
-\label{sec:earlyUI}
-
-As ideas changed and ARuko became what it is today, the UI also changed
-greatly from it's early conception to the final version we used. But
-that early UI would prove just as important as the final one, because
-it was also how we learned many of the practices and skills we needed in order
-to create the UI we settled on.
-
-The early UI was very much a product of ARuko's development; many of it's
-elements were created as new features were added. But as more features were
-added, it became clear that the UI could not consist simply of buttons and 
-other basic features provided by Unity. We would need to learn more about 
-how to create more interesting and useful UI elements to accomodate for 
-our new functionality.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=1\textwidth]{old-ui.png}
-	\caption[A screenshot of our early UI]
-	{A screenshot of our early UI}
+the ticket, sitting on the paper as if it were ground. Atticus suggested that we
+re-orient the model such that the ticket served as a back plane. This would
+allow users to hold the ticket vertically, and view the Golden Pavilion floating
+in front of the ticket. This allows users to place their hands under the base of
+the Golden Pavilion model as if they were holding it; Vuforia's image tracking
+is flexible enough such that the image target can be partially obscured by the
+hand.
+
+\subsubsection{Early User Interface}
+\label{sec:earlyUserInterface}
+
+As ideas changed and ARuko became what it is today, the user interface (UI) also
+changed greatly from its early conception to the final version. Still, the early
+UI was a valuable learning experience, providing us with skills that were useful
+when building the final version.
+
+The early UI was very much a product of ARuko's development; many of its
+elements were created on the fly as new features were added. As more features
+were added, it became clear that the UI could not consist simply of buttons and
+other basic features provided by Unity. We would need to learn more about how to
+create more interesting and useful UI elements to accommodate for our new
+functionality.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.4\textwidth]{old-ui.png}
+	\caption{A screenshot of our early UI}
 	\label{fig:oldUI}
@@
 Pictured in Figure~\ref{fig:oldUI} is our early UI. It was a very minimal UI,
-but still covered all of the uses for our app at the time. The top of the 
-screen had two dropdown menus. The one on the left, shown open, would
-show AR image targets in the area that users could look for and scan. The right
-dropdown would be dynamically populated in each region with buttons bearing  
-different images. These images were ones that Atticus wanted to be viewable in AR using ground plane
-detection. When tapped, each button would create a 3D Cube, with the given image
-on each face, and place it on the ground where the user was pointing.
+but still covered all of the uses for our app at the time. The top of the screen
+had two dropdown menus. The one on the left (which is open shown open in
+Figure~\ref{fig:oldUI}) shows AR image targets in the area that users could
+look for and scan. The right dropdown would be dynamically populated in each
+region with buttons bearing different images. These images were ones that
+Atticus wanted to be viewable in AR using ground plane detection. When tapped,
+each button would create a 3D Cube, with the given image on each face, and place
+it on the ground where the user was pointing. 
+%TODO provide a figure of the AR cube
+
+Atticus initially wanted us to explore the efficacy of using Vuforia's 2D image
+target capabilities for scanning objects outside of the expected use case, such
+as 3D landscapes or the side of a building. We had serious doubts about how
+well this would work, and our suspicions were confirmed after some field
+testing. This was the reasoning behind focusing on ground-plane detection
+instead of image targets; ground-plane detection can be used anywhere, and is
+much more reliable than treating 3D objects as 2D image targets.
 
@@
 final UI. We were able to create the dynamically populated dropdown menus by
-creating an empty vertical layout group, and then using a script to create
-buttons for each image based on which region the user is in, and then assign
-them as children of the layout group. Then, to get the smooth open/close animation,
-we used a boolean to mark the menu as open or closed and had the menu lerp to the
-corresponding position each frame until it was fully open or closed.
-
-In between these two dropdown menus is a panel that is shown empty, but in practice would
-display the name for the region the user is in at the time. The empty space
-in the middle of the screen is where the AR camera display would be shown. In this 
+creating an empty vertical layout group. Then, a script would create buttons for
+each image to display, and assign those images as children of the layout group.
+Then, to get the smooth open/close animation, we ``lerp'' (linearly interpolate)
+the menu to the corresponding position each frame until it is fully open or
+closed. In between these two dropdown menus is a panel that would display the
+name for the region the user is in at the time. The empty space in the middle of
+the screen is where the AR camera display would be shown. In this
 implementation, the AR functionality was the focus of the app, so it made sense
-to display the AR camera feed at all times. Lastly, on the bottom is the audio slider for the audio file played in each region. 
-We learned a lot about how audio sliders work in Unity with this feature, and would
-expand a lot on that knowledge for the final version of the app in order to optimize
-the slider's functionality and usefulness.
-
-This early UI taught us a lot about how to make a UI in Unity. We learned a lot of 
-basic things, like how all of the UI elements go on the Canvas, which represents
-the phone screen, and that everything should be anchored to locations on the screen
-so that they stay in the right place despite changes in screen size. 
-We also learned more complicated skills that would help us a lot later. We learned
-how to use audio sliders, and the ins and outs of how they work. And we learned
-how to create dropdown menus that expand when opened and contract when closed, 
-creating a very smooth movement affect without needing to animate the component. 
-And we also learned how to create button functionality through script, allowing
-for UI elements that can changed between the different tours loaded into our app.
-And we would bring all of these important skills we learned into the creation
-of our final UI to help make it as useful and interesting as it is now.
+to display the AR camera feed at all times. Lastly, on the bottom is the audio
+slider for the audio file played in each region. We learned about how audio
+sliders work in Unity with this feature, and would expand on that knowledge for
+the final version of the app in order to optimize the slider's functionality.
+
+Although most elements of the initial UI did not survive into the final product,
+it was still quite valuable as a learning tool. While crafting this prototype we
+discovered many of the intricacies of UI design in Unity. For example, all UI
+elements must be attached to a Unity canvas element, which covers the entire
+phone screen. Elements should be anchored to edges or corners of this canvas so
+that they stay in a constant location on different-size screens.
 
@@
 By the end of the project, we were able to turn ARuko into an app rich with
-features and polish. However, many of these features were presented to us
-relatively late into the project. This section discusses some of our initial
-concerns when we were first given the task of bringing Atticus' experience
-design to life.
+features and polish. However, many of these features were requested relatively
+late into the project. This section discusses some of our initial concerns when
+we were first given the task of bringing Atticus's ideas to life.
 
@@
 ramifications that rippled throughout the entire software stack we had
-constructed up to this point.  Figure~\ref{fig:adobeXdDesign} shows the experience
-design document created in Adobe XD.
+constructed up to this point. Figure~\ref{fig:adobeXdDesign} shows the
+experience design document created in Adobe XD.
 
@@
 that each geolocation-triggered region would not have to be ordered in any way.
-This assumption made its way into Editour, which did not currently have a way
+This assumption made its way into Editour, which at the time did not have a way
 to reorder regions once they were placed. Because of this chapter selection
-screen, we needed some way to rearrange the order of regions within Editour.
+screen, we needed some way to specify and rearrange the order of regions within
+Editour.
 
@@
 implications as well. Initially different regions were triggered solely by the
-GPS location. Walking into a region would prompt the available images to change
-on screen. Also, a new audio track would begin to play. This forced us to
-answer certain basic questions about the chapter select screen for ourselves.
-For example, consider a user that steps into one region, triggering the audio
-and images. Then, that user selects a chapter from the chapter selection menu,
+GPS location. Walking into a region would cause the available images to change
+on screen. Also, a new audio track would begin to play. This forced us to answer
+certain basic questions about the chapter select screen for ourselves. For
+example, consider a user that steps into one region, triggering the audio and
+images. Then, that user selects a chapter from the chapter selection menu,
 overriding the ``true'' region the user is physically standing inside of. When
@@
 user selects a chapter, and then physically enters that region moments later?
-Should the audio restart to indicate that the user has arrived at the location?
-Or, will this appear as though the audio track skipped to the beginning again
-for no reason? As you can imagine, this seemingly minor inclusion created a
-significant amount of discussion.
+Should the audio restart to indicate that the user has arrived at the location,
+or will this appear as though the audio track skipped to the beginning again for
+no reason? This seemingly minor inclusion created a significant amount of
+discussion.
 
@@
 traditional Japanese pagoda. We had already spent two weeks on this feature, so
-dropping this feature was a setback we had to plan around.
+dropping it was a setback we had to plan around.
 
@@
 transcript field.  Figure~\ref{fig:editourAdditions} shows the UI elements that
-changed in order to add these new features. The arrows next to the region name
-can be used to move the ``Region Card'' up and down in the side bar. In the
-``Media'' tab, there is also a text area to include a transcript of the
-uploaded audio file.
+changed in order to add these new features.
 
@@
 of vanilla JavaScript. Type-checking provided by Visual Studio Code and JSDoc
-made the growing code complexity more manageable. Excluding Node.js modules,
-the only external library we used for Editour was Leaflet, an open-source
-JavaScript library for interactive maps~\autocite{leafletjs}. We did not use
-any libraries for developing frontends like Facebook's React or Google's
-Angular. Instead, all of the complex UI interactions were handled by modifying
-the DOM directly with JavaScript's built-in functionality. Furthermore, we did
-not use any advanced frontend build tools such as Rollup, webpack or Parcel.
-This was likely an appropriate decision for a JavaScript project of this scope.
-Considering we had limited to no experience with React or Angular, it was also
-faster to develop the UI in the way we were used to from previous experience.
-But if we were to continue to develop Editour, UI libraries and frontend build
-tools would be something to consider. With these changing requirements, the
-Editour was becoming onerous to maintain at this stage of the project. Luckily,
-these changes were still manageable to implement.
+made the growing code complexity more manageable. Excluding Node.js modules, the
+only external library we used for Editour was Leaflet, an open-source JavaScript
+library for interactive maps~\autocite{leafletjs}. We did not use any framework
+for developing frontends like Facebook's React or Google's Angular. Instead, all
+of the complex UI interactions were handled by modifying the DOM directly with
+JavaScript's built-in functionality. Furthermore, we did not use any advanced
+frontend build tools such as Rollup, webpack or Parcel. For a JavaScript project
+of this scope, this was the correct decision. Considering we had limited
+knowledge of React or Angular, it was also faster to develop the UI in the
+way we were used to from previous experience. But if we were to continue to
+develop Editour, UI libraries and frontend build tools would be something to
+consider. With these changing requirements, the Editour was becoming onerous to
+maintain at this stage of the project. Luckily, these changes were still
+manageable to implement.
 
@@
 
-%TODO should this paragraph move somewhere else?
-Atticus initially wanted us to explore the efficacy of using Vuforia's 2D image
-target capabilities for scanning objects outside of the expected use case, such
-as 3D landscapes or the side of a building. We had serious doubts about how
-well this would work, and our suspicions were confirmed after some field
-testing. This was the reasoning behind focusing on ground-plane detection
-instead of image targets; ground-plane detection can be used anywhere, and is
-much more reliable than treating 3D objects as 2D image targets.
-
 Since Adobe XD is largely a prototyping and design tool, a considerable amount
@@
 briefly explored a few solutions to automating the task of getting the Adobe XD
-project into Unity. We found one payed extension (for \$18) on the Unity Asset
+project into Unity. We found one paid extension (for \$18) on the Unity Asset
 store called ``Experience Importer - Adobe Xd files importer.'' The download
@@
 
-While the newly proposed UI by Atticus was certainly a huge step up from
-our previous one, the things we had learned the first time around helped
-a lot in overcoming this rather large request in the relatively short amount
-of time we had. We had to get much more creative with how we implemented the
-UI and how everything worked together, but in the end this allowed us to 
-create a rather impressive final UI for and app that we're proud of.
-
-One of the first major challenges we had to tackle was the need to switch
-modes while keeping certain UI elements constant. So when a user goes from
-the home screen to the Route Map, or into AR Mode, we needed the mode buttons,
-audio components, and region info to remain. We went did this by splitting up
-screen space into panels, with one for the region info up top, one each for the
-mode buttons and audio components on the bottom, and one for the different 
-modes in the middle of the screen. Then, within the mode panel, each mode 
-screen would be assigned as children, and toggled active or inactive based on 
-which mode the user is in at the time. That way, on-screen content can change
-while important UI elements remain constant.
-
-Now, within the mode problem itself, there were other important things to 
-consider. One such topic was how to handle AR Mode. Previously, we had just
-left the AR camera running at all times, since it was the primary feature of 
-the app. But now, the focus was much more on the images and audio transcription
-in each region. For this, we found that we were able to disable and re-enable
-the AR camera in script, so we could turn it off while other modes were the
-focus, and back on when needed. We also weren't sure at first what to do about
-the chapter select menu, as it was also content that would occupy the space of
-the mode panel on screen, but needed to be accessible anywhere via the top 
-panel. Using our experience creating dropdown menus in the early UI, we simply
-left the chapter select menu enabled at all times, and lerped it open or closed
-as needed.
+The lessons we learned from the initial UI design (see
+Section~\ref{sec:earlyUserInterface}) helped us create the final design in such
+a short period of time. Although the new UI is significantly more complicated
+than the original prototype, we were able to implement all of Atticus's desired
+features within the time limit.
+
+One of the first hurdles we had to overcome was keeping certain UI elements
+constant while the user switches between the home screen, AR camera, and map
+view. The mode buttons, audio controls, and top bar need to remain on the screen
+at all times. To achieve this, we divided the screen into panels. Only one of
+the three main panels are set to ``active'' at a given time. Previously, the app
+left the AR camera running at all times, since there was only one main screen.
+In the new design, the AR camera is only set to ``active'' only when the AR
+panel is being shown. This prevents us from incurring unnecessary computational
+cost when the AR camera was not in use.
 
@@
 display the images, we wanted the user to be able to click through them like
-an image gallery, but weren't sure how to do so in a way that was smooth and
-looked nice. But once again, our experience with dropdown menus came in handy. 
+an image gallery.
+
 We created the gallery out of a horizontal layout group, populated it with
-images dynamically in each region, and then had the buttons lerp the gallery
+images dynamically in each region, and then had the buttons ``lerp'' the gallery
 to different positions in order to switch between each image in a smooth and
-pleasing way. As for the audio transcript, we knew we needed a scrollable
-text field that could accomodate varying amounts of text, since the audio files
-varied so greatly in length. After doing some research, we found a way to use 
-a vertical layout group to create a text field that expanded vertically, within
-a predefined bounds, to fit any amount of text provided to it.
-
-At first, our route map screen was rather simple. It was just a static image
-of the map, with the route drawn on it, that the user could scroll up and down,
-since the image was too tall for the screen. But because the map was so zoomed
-out, certain features and text on the map were hard to see. This could also 
-make it hard to tell where someone is on the route. So we needed a way to zoom
-in on the map and scroll around it, even though Unity doesn't provide this 
-relatively common functionality in a standard way. After doing some research, 
-were able to write a script that used some of Unity's Input library to get
-touch input and use it to zoom in and out on the map within a predefined 
-bounds.
+pleasing way. As for the audio transcript, we knew we needed a scrollable text
+field that could accomodate varying amounts of text, since the audio files
+varied so greatly in length. We created a vertical layout group to create a text
+field that expanded vertically within predefined bounds to fit an arbitrary
+amount of text.
 
@@
 any of the other functionality the app provides, like the image gallery in each
-region or the AR features. But despite how common it is for apps to play audio 
-in the background or while the phone is locked , Unity does not provide a way 
-to accomplish this either. The way we got around this was by figuring out a way
-to prevent UI elements from accidentally being triggered while the phone is 
-still unlocked and in the app in the user's pocket. We added a mode to the mode
-panel that consists of simply a high opacity black screen with a slider on it,
-and added a button to the chapter select dropdown in order to trigger this 
-mode. What this pocket mode does is that, because of where it is placed in the 
-Unity hierarchy, when it is enabled, it blocks input to all other active UI
-components. Then the slider works much like the slider on old Apple devices,
-where you slide it from one end to the other to "unlock" the app again, 
-re-enabling UI interaction. We figured that it would be rather difficult to 
-accidentally trigger the slider while the phone is in one's pocket, and even
-have the slider reset if it is only slided partially before letting go.
-
-The rest of the final UI consisted primarily of standard UI features, like 
-different basic buttons and panels in different places throughout the app. 
-We were ultimately able to replicate Atticus's Adobe XD file almost 
-perfectly, allowing us to use a great UI for this app we've worked so hard on.
+region or the AR features. Despite how common it is for apps to play audio in
+the background or while the phone is locked, Unity does not provide a way to
+accomplish this. Our workaround was to create a ``pocket mode'' that prevents UI
+elements from accidentally being triggered. The user exits pocket mode with a
+deliberate swipe to the right. If the slider is released partway through the
+action, the slider springs back to the beginning. We were ultimately able to
+replicate Atticus's Adobe XD file almost perfectly.
 
@@
 
-Both pieces of our project---the Editour and ARuko---are designed to be used by
-people who aren't programmers. The Editour will be used by Atticus in the future
-to design more tours, and ARuko will be used by the general public. Because of
+Both pieces of our project---Editour and ARuko---are designed to be used by
+people who are not programmers. Editour will be used by Atticus in the future to
+design more tours, and ARuko will be used by the general public. Because of
 this, we needed to do extensive testing to ensure not only that the products
@@
 
-Because the Editour is intended only to be a tool to aid Atticus in creating
-tours our user testing was less rigid. Even so, the frontend and backend we
-built for Editour ended up being largely reliable. The reliability issues
-stemmed from the hosting provider, which was out of our control.
+Because Editour is simply an internal tool, our user testing was less rigid.
+Even so, the frontend and backend we built for Editour ended up being reliable.
+The few reliability issues stemmed from the hosting provider, which was out of
+our control.
 
@@
 
-For each of the six API endpoints that the backend responds to we wrote an
+For each of the six API endpoints that the backend responds to, we wrote an
 extensive series of end-to-end tests to ensure that each step along the pipeline
 from receiving a request to sending a response worked properly. We also wrote
-many fuzz tests, to make sure the backend would respond correctly to invalid
-requests, e.g. by responding with an HTTP 400 error message~\autocite{rfc7231}.
+many fuzz tests to make sure the backend would respond correctly to invalid
+requests, for example, by responding with an HTTP 400 error
+message~\autocite{rfc7231}.
 
@@
 We suspect that Editour might have a life outside of this particular use case
-for designing tours, depending on how we choose to further develop this
-software. This is why Editour is perhaps more polished than your typical tool
-purely for internal use.
-
-For the duration of the project however, Editour only had to be used by us
-three and Atticus. Therefore, the testing for the frontend of Editour was less
+depending on how it is developed later on. This is why Editour is perhaps more
+polished than your typical tool purely for internal use.
+
+For the duration of the project however, Editour only had to be used our team
+and Atticus. Therefore, the testing for the frontend of Editour was less
 systematic than other parts of the software stack. This decision also helped us
-focus our efforts on testing the reliability and user experience of ARuko. That
-being said, we were able to add many feature and get the Editour experience to
-a polished state through our own testing, using GitHub's tools to keep us
+focus our efforts on testing the reliability and user experience of ARuko.
+Still, we were able to add many features and get the Editour experience to a
+polished state through our own testing, using GitHub's tools to keep us
 organized.
@@
 successive builds of the frontend. When bugs were found, we would log these as
-``Issues'' on the GitHub repository. These issues would get resolved in
-successive pull requests.
+``Issues'' on the GitHub repository.
 
@@
 Issues and feature requests alike got resolved in future pull requests. We
-resolved over thirty issues and feature requests using this workflow. The
-GitHub issues tab (which can be see in Figure~\ref{fig:issuesPageExample}) was
-very useful for making sure we made use of our user testing and bug testing.
+resolved over thirty issues and feature requests using this workflow. The GitHub
+issues tab (which can be see in Figure~\ref{fig:issuesPageExample}) was very
+useful for ensuring we made use of our user testing and bug testing.
 
@@
 significant amount of ``business logic'' that interprets the tour from the
-Editour file. On top of this, the geometric checks to test whether the user is
+Editour file. On top of this, the geometric tests to check whether the user is
 inside a particular arbitrarily-defined geographic region are very important to
@@
 
-As a reminder, regions that trigger audio can be a set of three or more points
-that define a closed polygon. Using the user's GPS location, the app needs to
-periodically run a check to see if the user is located within one of those
-polygons, which can be either concave or convex.
-
+Regions are a set of three or more points that define a closed polygon. Using
+the user's GPS location, the app needs to periodically run a check to see if the
+user is located within one of those polygons.
+
+% TODO move the stuff about the algorithm into the implementation section
 One decent algorithm for accomplishing this is by drawing a ray from a given
@@
 For this, we implemented a few mathematical functions for individual parts of
-the algorithm, such as testing for intersection. We wrote unit tests to test
-each part of the algorithm, so we could be confident that the GPS component of
-the app would correctly place users into the correct regions.
-
-There is one edge case where this algorithm has difficulties. If the ray that
-is drawn for testing intersections passes directly through a vertex, the
-algorithm will count two intersections instead of just one. Even though this is
-highly unlikely considering our use case, we decided that our algorithm should
-be robust enough to handle this on a matter of principle. Unit-testing helped us
-catch and deal with this edge case.
+the algorithm, such as one that tests to see if two lines intersect. We wrote
+unit tests to verify each part of the algorithm. This gave us confidence that
+the GPS component of the app would place users into the correct regions.
+
+There is one edge case where this algorithm has difficulties. If the ray that is
+drawn for testing intersections passes directly through a vertex, the algorithm
+will count two intersections instead of just one. Even though this is highly
+unlikely considering our use case, we decided that our algorithm should be
+robust enough to handle this on a matter of principle. We solved this by running
+a check on all vertices in the polygon to see if any were exactly colinear with
+the ray. If this is the case, one intersection count is subtracted from the
+total. Unit testing helped us catch and deal with this edge case.
 
@@
 
-Because it was not feasible to travel to Kinkaku-ji every time we needed to
-test the GPS functionality of the app, we used Editour to design an example
-tour around the Ritsumeikan Biwako-Kusatsu campus where we worked. This allowed
-us to catch various bugs before we created a finalized prototype for
-field-testing at Kinkaku-ji. The tour represented in \ref{fig:ritsuTour} is
-what we used for testing the app. The ``C-Shaped Region'' helped us test
-concave regions. This uniquely shaped region also prompted us to think about
-what UI behavior made the most sense if a user were to walk into a region, walk
-out and then in again. We decided that it was awkward if the audio restarted
-upon re-entering a region, since the audio would still be playing once a user
-left the region. (The region at the bottom surrounding our dormitories was added
-for our convenience, allowing us to test the app while we were away from the
-lab.) As we began to implement more complex UI that changed based on GPS
-position in various ways, directly taking the tour by walking around was an
-invaluable way to test. Section~\ref{sec:adobeXdDesign} details how the UI grew
-in complexity in the late stages of the project. Having a way to regularly run
-field tests was integral to polishing the app in time before we revisited
-Kinkaku-ji.  Because the Editour was flexible enough to easily swap out media
-and add regions to the tour, the Editour proved itself to be as helpful for
-testing as it was for crafting the final tour that could be taken at
-Kinkaku-ji.
+Because it was not feasible to travel to Kinkaku-ji every time we needed to test
+the GPS functionality of the app, we used Editour to design an example tour
+around the Ritsumeikan Biwako-Kusatsu campus where we worked. This allowed us to
+catch various bugs before we created a finalized prototype for field-testing at
+Kinkaku-ji. The tour represented in Figure~\ref{fig:ritsuTour} is what we used
+for testing the app. The ``C-Shaped Region'' helped us test concave regions.
+This uniquely shaped region also prompted us to think about what UI behavior
+made the most sense if a user were to walk into a region, walk out and then in
+again. We decided that it was awkward if the audio restarted upon re-entering a
+region, since the audio would still be playing once a user left the region. As
+we began to implement more complex UI that changed based on GPS position in
+various ways, directly taking the tour by walking around was an invaluable way
+to test. Section~\ref{sec:adobeXdDesign} details how the UI grew in complexity
+in the late stages of the project. Having a way to regularly run field tests was
+integral to polishing the app in time before we revisited Kinkaku-ji.  Because
+the Editour was flexible enough to easily swap out media and add regions to the
+tour, the Editour proved itself to be as helpful for testing as it was for
+crafting the final tour that could be taken at Kinkaku-ji.
 
 If we were ever feeling too tired to test the app by walking around, we also
-mocked the GPS coordinates in software. This allowed us to simulate walking in
-a single direction without actually having to move or build to a mobile device.
+mocked the GPS coordinates in software. This allowed us to simulate walking in a
+single direction without actually having to build to a mobile device or move.
 
@@
 6\textsuperscript{th}. Using Editour, we rebuilt the izi.TRAVEL audio tour that
-Atticus already created. The first version of the rebuilt tour had regions that
-were relatively small; some regions were only a few meters across. This version
-of the tour can be seen in Figure~\ref{fig:kinkakujiTour}. This day of testing
-prior to the redesign discussed in Section~\ref{sec:adobeXdDesign}.
+Atticus had created previously. The first version of the reimplemented tour had
+regions that were relatively small; some regions were only a few meters across.
+This version of the tour can be seen in Figure~\ref{fig:kinkakujiTour}. On this
+day of testing, we still had the limited UI described in
+Section~\ref{sec:earlyUserInterface}.
 
@@
 potential GPS inaccuracies that could place the user outside the range of the
-audio-trigger region.  Figure~\ref{fig:kinkakujiChunkierTour} depicts the tour
-that we used for field testing at Kinkaku-ji.
+region.  Figure~\ref{fig:kinkakujiChunkierTour} depicts the tour that we used
+for field testing at Kinkaku-ji.
 
@@
 AR. We primarily used this phone to test the AR features of the app. Even
-though the Samsung Galaxy had difficulty with basic AR features such as
+though the Galaxy S7 had difficulty with basic AR features such as
 ground-plane detection, it was still capable of triggering the audio track
@@
 generally which features of the app were working, it was very difficult to know
-how ahead of time how well our app would work at Kinkaku-ji.
+how ahead of time how well our app would work on-site.
 
@@
 region and audio track but one. The region that we missed on the first pass,
-``Final Viewpoint'', requires the user to take a right at a fork in the road
+``Final Viewpoint,'' requires the user to take a right at a fork in the road
 instead of continuing along the main path. This is not necessarily a problem
@@
 
-Initially, we loaded the app onto the Samsung Galaxy S7 as a backup, since the
-AR features were not fully functional on a phone that old. At the same time, it
-was informative to take both phones through the tour. Initially, we made the
-design decision to update the GPS location every 60 frames. On a phone running
-the app at full speed, this should happen once every second. Because the
-Samsung Galaxy S7 was having trouble running the app at full speed, the GPS
-updated far less frequently. This was an oversight that would have been
-difficult to catch if we had not tested on hardware below the recommended
-specifications.
+Initially, we loaded the app onto the Galaxy S7 as a backup, since the AR
+features were not fully functional on a phone that old. At the same time, it was
+informative to take both phones through the tour. Initially, we made the design
+decision to update the GPS location every 60 frames. On a phone running the app
+at full speed, this should happen once every second. Because the Galaxy S7 was
+having trouble running the app at full speed, the GPS updated far less
+frequently. This was an oversight that would have been difficult to catch if we
+had not tested on hardware below the recommended specifications.
 
 Other bugs resulted from oversights that were difficult to catch with our
-on-campus testing.  For example, we noticed that we forgot to back-up the audio
+on-campus testing. For example, we noticed that we forgot to reset the audio
 slider when entering a new region.  Because of this, when we entered a new
@@
 listening to the tour and using the app's features. Each member of our team
-also installed the beta version so we could fuzz test it.
-% TODO check if fuzz testing is really the right word here
+also installed the beta version so we could test it.
 
@@
 lighting than when the reference images were taken. For image targets that were
-small, far away, or obscured by shadows image recognition was slower, but
-Vuforia was always able to recognize them eventually. We discovered that the
-targets that worked best were large, had a lot of high-contrast text, and were
-uniformly lit.
+small, far away, or obscured by shadows the image recognition was slower. We
+discovered that the targets that worked best were large, had a lot of
+high-contrast text, and were uniformly lit.
 
@@
 started playing long before the user was actually near the feature it was
-discussing. Using the Editour web app, we were able to correct quickly these
-issues with the tour design once we returned to Atticus' office.
+discussing. Using the Editour web app, we were able to quickly correct these
+issues with the tour design once we returned to Atticus's office.
 
@@
 pop-up. These were all easy bugs to fix, but if we might not have noticed
-them if we had not tested the app on site.
-
-We also noticed that we were only able to augment a maximum of two
-image targets at a time. In almost all cases, only two translatable signs
-were in view at once. The only scenario in which there were more than two
-image targets in view at a given time was with the four framed photos of the
-interior, arranged in a two by two grid. When standing at a distance from the
-grid, only two images would be augmented with the blue information button. By
-default, Vuforia limits the amount of image targets that the engine should
-accept simultaneously. In the Vuforia engine settings, we changed this limit
-to accommodate for four simultaneous images
-
-Another major bug we discovered was that the GPS stopped updating when not on
-the main screen. This means that if you were in AR camera mode the app would not
-trigger new audio when you walked into a new region. This was caused by the GPS
-script being attached to a UI element on the main screen, so it was resolved
-simply by moving this script.
+them if we had not tested the app on-site.
+
+We also noticed that we were only able to augment a maximum of two image targets
+at a time. In almost all cases, only two translatable signs were in view at
+once. The only scenario in which there were more than two image targets in view
+at a given time was with the four framed photos of the interior, which were
+arranged in a two by two grid. When standing at a distance from the grid, only
+two images would be augmented with the blue information button. By default,
+Vuforia limits the amount of image targets that the engine should accept
+simultaneously. In the Vuforia engine settings, we changed this limit to
+accommodate for four simultaneous images
+
+Another major bug we discovered was that the GPS stopped updating when the main
+screen is not open. This means that in AR camera mode the app would not trigger
+new audio when you walked into a new region. This was caused by the GPS script
+being attached to a UI element on the main screen, which gets deactivated when
+switching to AR camera mode. This was easily resolved simply by moving this
+script.
 
 After having Atticus go through the tour on his phone he also discovered several
-bugs and tweaks he wanted to make to the UI. The clickable information button on
-image targets was made larger so it is easier to see. The UI buttons in the
-bottom menu bar were also made larger and easier to press. The text ``Main'' was
-added under the central button that brings you to the screen with the images and
-transcript, so it was more clear what that button does. The header text at the
-top was too big, and sometimes overflowed onto other UI elements.
+bugs and tweaks he wanted to make to the UI. The clickable information buttons
+on image targets were made larger so they are easier to see and tap. The UI
+buttons in the bottom menu bar were also made larger and easier to press. The
+text ``MAIN'' was added under the central button that opens the screen with the
+images and transcript, so it was more clear what that button does. The header
+text at the top was too big, and sometimes overflowed onto other UI elements, so
+its size was reduced and split into two lines when the text was too long.
 
@@
 punch'' covered some UI elements in the top right corner. To account for this
-issue we added more padding to the top of the UI.
+issue we used Unity's built-in function to return a safe screen space to render
+the rectangular canvas in.
 
@@
 phones in their pockets while taking the tour. Sound sources would change in
-physically based ways using motion tracking.
-
-We spent the second and third week creating demos to explore the possibility of
-a 3D spatialized audio tour. We found that this would be very difficult to do
-without the use of the camera. All of the technology for mobile AR we explored
-in Section~\ref{sec:platforms} depended heavily on the camera. If we were to
-build a 3D spatialized audio tour that ran entirely without use of the camera,
-we would not be able to take advantage of any of the useful features of the AR
-libraries we explored. Furthermore, Unity would be relegated to the simple role
-of exporting our app to multiple devices; we would not have any need to take
-advantage of its 3D capabilities.
+relation to the real world as the user moved around.
+
+We spent the second and third week of the project creating demos to explore the
+possibility of a 3D spatialized audio tour. We found that this would be very
+difficult to do without the use of the camera. All of the technology for mobile
+AR we explored in Section~\ref{sec:platforms} depended heavily on the camera. If
+we were to build a 3D spatialized audio tour that ran entirely without use of
+the camera, we would not be able to take advantage of any of the useful features
+of the AR libraries we explored. Furthermore, Unity would be relegated to the
+simple role of exporting our app to multiple devices; we would not have any need
+to take advantage of its 3D capabilities.
 
@@
 focus shifted away from this idea for other logistical reasons. Initially,
-Atticus introduced the possibility of working closely with Kishi Bashi or
-Yannick Paget to produce the soundscape for the 3D spatialized audio tour.
+Atticus introduced the possibility of working closely with artists Kishi Bashi
+or Yannick Paget to produce the soundscape for the 3D spatialized audio tour.
 Yannick Paget is a French musician that became established in Japan. He is both
@@
 Bashi was born in Seattle and grew up in Virginia. Kishi Bashi has appeared at
-many major music festivals, toured the US extensively, and has even released
-his own line of coffee! His latest album, Omoiyari, was released on May
+many major music festivals, toured the US extensively, and has even released his
+own line of coffee. His latest album, Omoiyari, was released on May
 31\textsuperscript{st}, 2019~\autocite{kishibashi2019}.
@@
 
-Atticus Sims proposed the idea of working with Michael Whittle. Michael Whittle
+Atticus Sims proposed the idea of working with Michael Whittle, a British artist
 received his PhD at the Kyoto City University of Arts in 2014. His art has
-appeared in dozens of solo exhibitions and group exhibitions across the world,
+appeared in dozens of solo and group exhibitions across the world,
 including Kyoto, Beijing, London and New York~\autocite{michaelwhittle2019}.
 Kyoto~VR has worked with Michael Whittle in the past to create a 3D scan of a
-solo exhibition, `Portraits of Thought'. This exhibition displayed diagrams
+solo exhibition, ``Portraits of Thought.'' This exhibition displayed diagrams
 inspired by real science and mathematics. Atticus provided us with some
@@
 were only able to go to the site to test ARuko twice. We could test some basic
-features from Ritsumeikan, but image recognition target existed only at
+features from Ritsumeikan, but the image recognition targets existed only at
 Kinkaku-ji. More extensive user testing at the actual site could have helped us
@@
 Kyoto~VR. ARuko is not quite ready to be sold on app stores yet, but with a
-little more development time it could easily be made ready. The UI could use
+little more development time it could easily be completed. The UI could use
 more testing with real users to make sure it is intuitive and easy to use. We
@@
 More historic locations around Kyoto and Japan in general should be considered
-for other tours. With the work our team has done Kyoto~VR now has a complete
+for other tours. With the work our team has done, Kyoto~VR now has a complete
 platform for creating and delivering unique tours, which can easily be expanded

### 2019-09-30 paper.tex
update title page
Filled out the title page with more information so it looks like other
MQPs and IQPs

@@
 
-% draw the title page
-\maketitle
+% title page
+\begin{center}
+	{\huge ARuko and Editour: \\
+		\Large A Platform for Augmented Reality Tour Guide Apps
+	}
+
+	\vfill
+
+	A Major Qualifying Project \\
+	Submitted to the faculty of \\
+	WORCESTER POLYTECHNIC INSTITUTE \\
+	In partial fulfillment of the requirements for the \\
+	Degree of Bachelor of Science \par
+
+	\vfill
+
+	By \\
+	William Campbell \\
+	Cole Granof \\
+	Joseph Petitti \par
+
+	\vfill
+
+	Date: \\
+	October 11, 2019 \par
+
+	\vfill
+
+	Report submitted to: \par
+
+	\vspace{\baselineskip}
+
+\end{center}
+\begin{flushright} % list your sponsors and advisers
+	Atticus Sims, Sponsor \\
+	Kyoto VR \par
+	\vspace{\baselineskip}
+	Professor Joshua Cuneo, Adviser \\
+	Worcester Polytechnic Institute \par
+	\vspace{\baselineskip}
+	Professor Ralph Sutter, Adviser \\
+	Worcester Polytechnic Institute \par
+\end{flushright}
+
+\vfill
+
+\clearpage
 

### 2019-09-30 paper.tex
expanding sections

--- 2019-09-28 paper.tex
@@
 GPS and camera data to overlay game objects (in this case fictional monsters) on
-top of images of the real world~\autocite{concepcion2016} (see Figure
-\ref{fig:pokemonGo}).
+top of images of the real world~\autocite{concepcion2016} (see
+Figure~\ref{fig:pokemonGo}).
 
@@
 
-%TODO write this section
-TODO: write this section
+Unity is a game engine that was originally introduced in
+2005~\autocite{axon2016}. Because of the low barrier to entry---knowledge-wise
+and price-wise---the engine quickly became incredibly popular. Ironically,
+because the engine is so accessible that, Unity has faced a degree of critism.
+Because Unity appeals to so many beginners, there are many unpolished games that
+bear the Unity logo. In response to this sentiment, Marcos Sanchez, head of
+global communications at Unity, "Democratizing development---in our minds, we
+don’t think is the wrong thing, we think it’s the right thing. You want more
+people understanding, and everyone’s gotta start somewhere." Unity CEO John
+Riccitiello made the claim at TechCrunch Disrupt San Francisco that half of all
+games are made with Unity \autocite{dillet2018}. We consider Unity's ubiquity to
+be an advantage; there is a glut of information about how to use augmented
+reality within Unity.
+%TODO citing a quotation from inside the first citation. Is this okay?
+
+Even though Unity is beginner-friendly for making games, the augmented reality
+app we planned to create was not a game. Therefore, we were somewhat concerned
+that Unity's ease-of-use would be undermined simply because we were not making a
+traditional game experience. Instead we would be using Unity to create a piece
+of software that both looked and felt like a familiar mobile app. Unity has very
+limited support for this compared to technologies that are specifically geared
+toward creating modern mobile user interfaces such as React.
+
+At the same time, Unity has excellent support for augmented reality through
+various extensions. Because we initially understood AR to be the core of the app
+experience, we chose to use Unity with the Vuforia extension for all future
+development on the mobile app.
+
+Unity is distinct from the technologies previously discussed in this section
+because it is not an AR platform unto itself. Instead, Unity can take advantage
+of AR platforms such as ARKit, ARCore, Vuforia and Wikitude through the use of
+plugins.
+%TODO provide citations that note that all of these platforms support Unity.
 
@@
 would like the app to be able to contact a server running a version of the
-Editour backend and update the tour info by itself. This would allow Kyoto~VR
-to update the tours without updating the entire app.
-
-The design of the Editour is agnostic about how the media will be used. For an
-app like izi.TRAVEL, the images are displayed when the associated audio tour is
-playing. The tour files produced by Editour could theoretically be used by a
-tour guide app that does not incorporate AR.
+Editour backend and update the tour info by itself. This would allow Kyoto~VR to
+update the tours without updating the entire app.
+
+Furthermore, we foresee Editour being a useful tool outside of the app we
+designed for Kyoto VR. The design of the Editour is agnostic about how the media
+will be used. For an app like izi.TRAVEL, the images are displayed when the
+associated audio tour is playing.
+
+The files produced by Editour could be used to power an app that does not
+incorporate AR, such as an audio guide mobile web app that runs entirely in the
+browser, using the geolocation API to access the user's location (if the user
+grants permission.) This kind of infrastructure would allow users to access an
+audio tour---supplemented by images and audio transcripts---without the need to
+download an app at all. By simply visiting a link, a user could experience a
+guided tour that changes as the user walks through the route. For example,
+colleges could distribute tour links via QR codes, which would instantly launch
+an interactive guided tour of the campus through the browser.
+
+Currently, anyone can clone the GitHub repository of Editour and deploy a
+working version on a personal server. The source code for Editour is under an
+open-source license. This allows anyone to expand the frontend and backend to
+suit their needs. With additional hardware and by extending the current
+implementation of both the frontend and backend, Editour could be used as the
+groundwork to create an entire crowd-sourced walking tour platform, allowing
+users to design tours for others to take.
+
+In summary, we want to explore the idea of creating a community-driven audio
+tour database that allows mobile users to take tours without the need to install
+an app. The open-source code we wrote for Editour empowers us (or anyone else)
+to develop and launch this platform in the future.
 
@@
 On September 26\textsuperscript{th} we returned to Kinkaku-ji with a nearly
-complete version of the ARuko in order to conduct some final testing. We met
-up with Atticus, the IQP group, and our friend Hikaru and installed the beta
-version of ARuko on each of their phones. With little instruction about how
-the app works we had each of them try going through Kinkaku-ji while
-listening to the tour and using the app's features. Each member of our team
-also installed the beta version so we could test it.
+complete version of ARuko in order to conduct some final testing. We met up with
+Atticus, the IQP group, and our friend Hikaru and installed the beta version of
+ARuko on each of their phones. With little instruction about how the app works
+we had each of them try going through Kinkaku-ji while listening to the tour and
+using the app's features. Each member of our team also installed the beta
+version so we could test it.
 
@@
 simultaneously. In the Vuforia engine settings, we changed this limit to
-accommodate for four simultaneous images
+accommodate for four simultaneous images.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=.5\textwidth]{four-i-buttons.png}
+	\caption{The result of increasing the size of the info buttons and increasing
+    the maximum image target count to four}
+	\label{fig:fourIButtons}
+\end{figure}
 
@@
 	Agree & Agree & Strongly agree & Neutral & Agree & Increasing GPS accuracy
-	of course. Adding a tracking "you are here" marker to the route. \\
+	of course. Adding a tracking ``you are here'' marker to the route. \\
 

### 2019-09-30 paper.tex
working on version control section

@@
 tickets. Seemingly, the design on the tickets do not change on a regular basis,
-if at all.
+if at all. Figure~\ref{fig:kinkakujiTicket} shows a ticket we kept from one of
+our visits to Kinkaku-ji.
+
+\begin{figure}[h] \centering
+    \includegraphics[width=0.4\textwidth]{kinkakuji-ticket.jpeg}
+    \caption{Map overlay displaying the path and translated labels}
+    \label{fig:kinkakujiTicket}
+\end{figure}
 
@@
 each button would create a 3D Cube, with the given image on each face, and place
-it on the ground where the user was pointing. 
-%TODO provide a figure of the AR cube
+it on the ground where the user was pointing. Figure~\ref{fig:floatingCube}
+shows this feature in action.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.4\textwidth]{floating-cube.png}
+	\caption{An ``art cube'' floating over the water containing a placeholder
+    programming meme}
+	\label{fig:floatingCube}
+\end{figure}
 
@@
 
+% TODO this whole section should probabyl be in the appendix
+\section{Version Control}
+\label{sec:versionControl}
+
+Over the course of the project, we had to develop multiple applications in
+different languages. In total, we opened five different repositories: the blog,
+the \LaTeX source code for our paper, the Arduino code for the heart project,
+and of course one for Editour and another for ARuko. These five repositories
+span across multiple different markup and programming languages, including C\#,
+C++, JavaScript, HTML, CSS (and the \LaTeX markup language used to typeset this
+paper.) This gave us a welcome amount of practice using git for version control,
+as well as GitHub's other features oriented around coordinating a team.
+
+All three members of the team were contributing code and updating assets such as
+graphics and sound. Code complexity grew quickly as more features were added
+across the entire software stack. Git and GitHub enabled us to view the history
+of the code and revert back to working versions when absolutely necessary. We
+researched the proper methodology of using version control in a small team,
+applying this methodology as best we could. This enabled us to work together
+efficiently, track down bugs, undo mistakes, and sometimes review each other's
+code for quality when time allowed.
+
 \begin{figure}[h]
@@
 	\label{fig:iPhoneX}
+\end{figure}
+
+\subsection{GitHub Tools}
+\label{sec:gitHubTools}
+
+Some members of our team were very excited by the workflows GitHub's tools
+enabled.
+
+Initially, we experimented with using a four-column Kanban board to keep track
+of our progress. Figure~\ref{fig:kanbanBoard} shows a screenshot of this page on
+GitHub.
+
+The Kanban technique stems from Toyota in the 1940s. Kanban means ``visual
+signal'' or ``card'' in Japanese, which describes the core component of the
+technique~\autocite{terry2019}. At Toyota, line-workers would move colored cards
+to notify other teams that parts needed for assembly work were in short supply.
+Now, Kanban boards are integral to Agile software development. Still, some teams
+use physical Kanban boards, often using sticky notes and whiteboards.
+
+The advantage of using a Kanban board is that each feature or bug that
+is being worked on can be assigned directly to a collaborator on the project. It
+is then that person's responsibility to work on those tasks and update the
+status of those tasks on the board. We abandoned this when moving onto the main
+project because we came to realize that this structure was not necessary---there
+were only three members on the team, and we were almost always in the same room
+when working on the project. For Editour, we tracked features and issues using
+the Issues page instead, which is discussed in
+Section~\ref{sec:editourFrontendTesting}.
+
+Creating ``pull requests'' through the GitHub web interface has a few advantages
+over directly merging code using git. Firstly, the pull request feature
+integrates with ``Issues'' page very well. By typing `resolves' along with the
+number associated with an issue into the description of a pull request, GitHub
+will automatically close the issue when the pull request is approved. This is
+not only remarkably convenient, but also self-documenting since the descriptions
+of pull requests would contain the issues they were resolving. Secondly,
+creating a pull request allows code to be reviewed by other members of the team
+very easily. Reviewers can view the entire diff and add comments line-by-line.
+Other collaborators can easily respond to those comments. Reviewers can also
+request certain features be changed before the branch is merged, which allowed
+us to enforce that issues with the code were actually addressed.
+% TODO explain what the heck a diff is
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{kanban-board.png}
+	\caption{A screenshot of the Kanban board we used for developing our
+    biweekly blog}
+	\label{fig:kanbanBoard}
 \end{figure}

### 2019-09-30 paper.tex
moved figures and added comments
more info about git methodology

@@
 
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{galaxy-s10+.jpg}
+	\caption[A Samsung Galaxy S10+ phone with distinctive ``hole punch''
+	cameras]{A Samsung Galaxy S10+ phone with distinctive ``hole punch''
+		cameras~\autocite{yoo2019}}
+	\label{fig:galaxyS10Plus}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{iphone-x.jpg}
+	\caption[An iPhone X with a large notch]{An iPhone X with a large
+		notch~\autocite{yoo2017}}
+	\label{fig:iPhoneX}
+\end{figure}
+
 After going through Kinkaku-ji with the app twice we had each test participant
@@
 
-% TODO this whole section should probabyl be in the appendix
+% TODO this whole section should probably be in the appendix
 \section{Version Control}
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=\textwidth]{galaxy-s10+.jpg}
-	\caption[A Samsung Galaxy S10+ phone with distinctive ``hole punch''
-	cameras]{A Samsung Galaxy S10+ phone with distinctive ``hole punch''
-		cameras~\autocite{yoo2019}}
-	\label{fig:galaxyS10Plus}
-\end{figure}
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=\textwidth]{iphone-x.jpg}
-	\caption[An iPhone X with a large notch]{An iPhone X with a large
-		notch~\autocite{yoo2017}}
-	\label{fig:iPhoneX}
-\end{figure}
-
 \subsection{GitHub Tools}
@@
 Some members of our team were very excited by the workflows GitHub's tools
-enabled.
+enabled. In this section, we will discuss some of the tools, some of which
+greatly aided in our organization and productivity.
 
@@
 
+% TODO give this paragraph some more context so it doens't seem out of place
+The way we incorporated branches into our workflow helped us collaborate in a
+way that kept us organized. In general, if one of us was working on a specific
+feature, we would create a branch with a name descriptive of that feature. This
+methodology minimized difficult-to-resolve merge conflicts.
+% TODO explain merge conflicts and cite that Atlassian thing
+
+Once we deployed Editour to a server so that Atticus could begin to use it,
+we changed the version to v1.0.0 to indicate the first release version. At this
+point, it was important that the master branch remain as stable as possible.
+Because of this, we created a ``dev'' branch where we could test experimental
+features to improve the experience and functionality of Editour. Maintaining a
+stable and experimental branch reduced the risks involved with continuing to
+iterate on the software's features post-release.
+
+In a similar vein, with ARuko we used branches to ensure we had a stable working
+version. The night before field testing at Kinkaku-ji, we would cease work on
+the most recent branch, and build the app to our phones. This way, we would
+always have an exact snapshot of the code we used for that day of testing.
+
 \begin{figure}[h]
@@
 
+% TODO is spatialized really a real word or do people just use it?
 One idea that was proposed initially was an AR audio experience using 3D
@@
 Despite these issues our team is happy with the product we delivered to
-Kyoto~VR. ARuko is not quite ready to be sold on app stores yet, but with a
-little more development time it could easily be completed. The UI could use
-more testing with real users to make sure it is intuitive and easy to use. We
-also intended to add a feature where the app could automatically download tour
-files from the Editour server and import them without having to rebuild. We were
-not able to complete this feature due to time constraints, but it could easily
-be added because all of ARuko's business logic is abstracted and generalized to
-support multiple tours. Editour also already supports requesting and downloading
-the most recent versions of tours.
+Kyoto~VR. Selling ARuko on app stores was not within the scope of our academic
+project, but we were able polish the app enough such that it would be feasible
+for Atticus to eventually sell the app. The UI could use more testing with real
+users to make sure it is intuitive and easy to use. We also intended to add a
+feature where the app could automatically download tour files from the Editour
+server and import them without having to rebuild. We were not able to complete
+this feature due to time constraints, but it could easily be added because all
+of ARuko's business logic is abstracted and generalized to support multiple
+tours. Editour also already supports requesting and downloading the most recent
+versions of tours.
 

### 2019-10-01 paper.tex

@@
 pleasing way. As for the audio transcript, we knew we needed a scrollable text
-field that could accomodate varying amounts of text, since the audio files
+field that could accommodate varying amounts of text, since the audio files
 varied so greatly in length. We created a vertical layout group to create a text

### 2019-10-01 paper.tex
ralph's comments

@@
 	% abstract goes here
-	\begin{figure}[h]
-		\centering
-		\includegraphics[width=\textwidth]{abstract.jpg}
-		% Note: you don't actually need the part in square brackets for the
-		% caption, but if you omit it the regular caption text will be used for
-		% the List of Figures entry.
-		\caption[\textit{Number 1, 1950 (Lavender Mist)}, Jackson Pollock]
-		{\textit{Number 1, 1950 (Lavender Mist)}, Jackson Pollock, National
-			Gallery of Art, Washington, D.C.}
-		\label{fig:abstract}
-	\end{figure}
+	% TODO write abstract
 \end{abstract}
@@
 
-We would like to thank Atticus Sims, CEO and founder of Kyoto~VR, for sponsoring
-this project and providing help and guidance throughout our time in Japan. His
-knowledge of the history of Kinkaku-ji and Kyoto in general has been invaluable
-to our experience.
+Our team would like to thank Atticus Sims, CEO and founder of Kyoto~VR, for
+sponsoring this project and providing help and guidance throughout our time in
+Japan. His knowledge of the history of Kinkaku-ji and Kyoto in general has been
+invaluable to our experience.
 
@@
 filming and editing the app trailer, as well as providing help with testing.
-
-Finally, a thank you to our advisers, Professors Joshua Cuneo and Ralph Sutter.
-Without their expert advice and feedback this project probably could not have
-been completed.
+Further, we are grateful to the assistance and resources provided by Ritsumeikan
+University and Professor Noma Haruo. Finally, a thank you to our advisers,
+Professors Joshua Cuneo and Ralph Sutter. Without their expert advice and
+feedback this project probably could not have been completed.
 
@@
 
-Our team built, tested and polished a mobile app to deliver an audio tour,
-incorporating various augmented reality (AR) features to enhance the
-experience. Our app delivers a tour of Kinkaku-ji, or The Temple of the Golden
-Pavilion, a popular tourist destination in Kyoto. In this app, which we call
-ARuko, many of the AR features were aimed at improving accessibility. These
-features include translating signs and providing additional info on the
-physical map located at the site. Other features were purely for spectacle,
-such as the ability to take an AR ``souvenir'' home by scanning the ticket
-to enter Kinkaku-ji.
+Our team consists of three Senior Worcester Polytechnic Institute (WPI)
+students: William Campbell, computer science and interactive media and game
+development double major; Cole Granof, computer science major; and Joseph
+Petitti, computer science major. We spent twelve weeks in Shiga, Japan
+completing the requirements for our Major Qualifying Project, a WPI graduation
+requirement in which students solve a real-world problem through practical
+project-based work. Our project was sponsored by Kyoto~VR, a startup founded in
+2016 to ``document and preserve the culture and heritage of the city and
+communicate the richness of Japan’s Old Capital to the
+world''~\autocite{kyotovr2018}.
+
+Our team worked directly under Kyoto VR founder and CEO Atticus Sims to develop
+and tested a mobile app to deliver an audio tour, incorporating various
+augmented reality (AR) features to enhance the experience. Our app delivers a
+tour of Kinkaku-ji, or The Temple of the Golden Pavilion, a popular tourist
+destination in Kyoto. In this app, which we call ARuko, many of the AR features
+were aimed at improving accessibility. These features include translating signs
+and providing additional info on the physical map located at the site. Other
+features were purely for spectacle, such as the ability to take an AR
+``souvenir'' home by scanning the ticket to enter Kinkaku-ji.
 
 ARuko went through multiple iterations of user testing and bug testing at
-Kinkaku-ji. Sections \ref{sec:initialFieldTesting} and
+Kinkaku-ji. Sections~\ref{sec:initialFieldTesting} and
 \ref{sec:finalFieldTesting} go into detail about our two days of field testing
@@
 identify important features to add to the app. Much of the app's functionality
-was dictated by Atticus Sims, C.E.O and founder of Kyoto~VR, who plans to
-monetize the app. We also worked with an IQP team, who had been tasked with
-exploring funding options and creating promotional content.
+was decided by our project sponsor, who plans to monetize the app. We also
+worked with an IQP team, who had been tasked with exploring funding options and
+creating promotional content.
 
@@
 fields. This budding technological platform uses digital displays to augment
-real-world information with computer-generated data. As the technology
-progresses, several disparate industries have found novel uses for it, some
-becoming extremely profitable~\autocite{webster2018}. With smartphone
-manufacturers investing billions into AR technology~\autocite{mason2016}, it
-seems poised to be the next big digital interface.
+real-world information with computer-generated data (see
+Figure~\ref{fig:arExample}. As the technology progresses, several disparate
+industries have found novel uses for it, some becoming extremely
+profitable~\autocite{webster2018}. With smartphone manufacturers investing
+billions into AR technology~\autocite{mason2016}, it seems poised to be the next
+big digital interface.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{ar-example.jpg}
+	% Note: you don't actually need the part in square brackets for the
+	% caption, but if you omit it the regular caption text will be used for
+	% the List of Figures entry.
+	\caption[A virtual model of the solar system projected onto the real world
+	using AR]{A virtual model of the solar system projected onto the real world
+		using augmented reality~\autocite{tedx2016}}
+	\label{fig:arExample}
+\end{figure}
 
@@
 accessible information to tourists and art viewers that they would not be able
-to get any other way. Kinkaku-ji, the ``Golden Pavilion'' of Kyoto, is the
-perfect example of a site that would benefit from AR~\autocite{bornoff2000}.
+to get any other way. Kinkaku-ji, the ``Golden Pavilion'' of Kyoto (see
+Figure~\ref{fig:kinkakuji1}, is the perfect example of a site that would benefit
+from AR~\autocite{bornoff2000}.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{kinkakuji-1.jpg}
+	\caption[The Golden Pavilion]{The Golden Pavilion~\autocite{fan2018}}
+	\label{fig:kinkakuji1}
+\end{figure}
+
 Kinkaku-ji is a UNESCO World Heritage Site~\autocite{unesco} and one of the
@@
 
-However, much of the historic information at the site is lost on visitors
-because it is not readily available to non-Japanese speakers. What few signs and
-displays exist are presented only in Japanese, and do not provide most of the
+However, much of the historic information at the site is lost on non-Japanese
+speaking visitors because it is often only available in Japanese. In addition to
+the language barrier, the information provided does not include most of the
 history and context necessary to fully understand Kinkaku-ji.
@@
 while ARuko allows users to seamlessly experience historic sites in an intuitive
-and novel way. The experience of walking through the site is enhanced by
-informative narration and AR pop-ups that do not alter the buildings or ground
-in real life.
+and novel way. Many AR apps require specific markers, like the those shown in
+Figure~\ref{fig:arMarker}. Too avoid needing to place any physical object that
+would disturb the buildings or grounds of a historic site our app does not rely
+on these markers. Instead, our ARuko recognizes images of objects that are
+already at the site, and uses them to display informative AR pop-ups. See
+Sections~\ref{sec:translationFeature} and \ref{sec:mapOverlayFeature} for
+more details.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{ar-marker.jpg}
+	\caption[Augmented reality markers]{Augmented reality
+		markers~\autocite{jeriaska2010}}
+	\label{fig:arMarker}
+\end{figure}
 
@@
 unprecedented degree of connectivity with the digital world, but can also serve
-as a tool for enhancing the physical world. In this section we explain the
-origins and uses of some of this technology.
+as a tool for digitally enhancing the physical world. In this section we explain
+the origins and uses of some of this technology.
 
@@
 This differs from virtual reality (VR) in that a VR experience consists
-exclusively of virtual information. In AR, virtual information is mixed with
-sensory input from the real world~\autocite{carmigniani2011}. This can enhance
-the user's perception of reality by providing information that would be
-difficult or impossible to display through traditional means.
+exclusively of virtual information in a virtual environment. In AR, virtual
+information is mixed with sensory input from the real
+world~\autocite{carmigniani2011}. This can enhance the user's perception of
+reality by providing information that would be difficult or impossible to
+display through traditional means.
 
@@
 places, and objects overlaid onto images of the real
-world~\autocite{saenz2009}.  This provides the user with useful information
-without needing to alter a real historic site.
+world~\autocite{saenz2009}, in a way that is more intuitive or visually
+appealing than a purely virtual environment. This provides the user with useful
+information without needing to alter a real historic site.
 
@@
 
-Many of the existing applications using AR, in our eyes, do not leverage the
+Most existing applications using AR, in our team's opinions, do not leverage the
 full potential of this emerging technology. As with any new field, our
-understanding of AR and how to develop for it is limited. All sorts of
-different challenges and limitations face the development and production of AR
-apps. Here are some that we considered when working on our app.
+understanding of AR and how to develop for it is limited. All sorts of different
+challenges and limitations face the development and production of AR apps. Here
+are some that we considered when working on our app.
 
@@
 put, not very good. Many AR apps and features available on smartphones offer
-very little in the way of functionality or practicality; quite simply, they are
-primarily used for minor spectacles and simple
-tricks~\autocite{theappsolutions2018}. For example, one of the most popular
+very little in the way of functionality or practicality; quite simply, they
+primarily primarily revolve around deploying
+gimmicks~\autocite{theappsolutions2018}. For example, one of the most popular
 apps to use AR, \textit{Pokémon Go}, primarily uses its AR feature to place a
@@
 
-Viro AR comes in two flavors: ViroReact and ViroCore\autocite{facebook2019}.
+Viro AR comes in two versions: ViroReact and ViroCore\autocite{facebook2019}.
 ViroCore allows developers to build an AR Application with Java. The
@@
 problem facing emulators is just as real as it was in 1988. Considering that AR
-already pushes modern phone hardware to the limit, emulation is not something
-is not something we wanted to struggle with. On top of this, our testing
-required us to move the camera through the world at various speeds and angles,
-which is simply cumbersome with a laptop webcam.
+already pushes modern phone hardware to the limit, emulation is not something we
+wanted to struggle with. On top of this, our testing required us to move the
+camera through the world at various speeds and angles, which is simply
+cumbersome with a laptop webcam.
 
@@
 global communications at Unity, "Democratizing development---in our minds, we
-don’t think is the wrong thing, we think it’s the right thing. You want more
-people understanding, and everyone’s gotta start somewhere." Unity CEO John
-Riccitiello made the claim at TechCrunch Disrupt San Francisco that half of all
-games are made with Unity \autocite{dillet2018}. We consider Unity's ubiquity to
-be an advantage; there is a glut of information about how to use augmented
-reality within Unity.
-%TODO citing a quotation from inside the first citation. Is this okay?
+don't think is the wrong thing, we think it's the right thing. You want more
+people understanding, and everyone’s gotta start somewhere"~\autocite{axon2016}.
+Unity CEO John Riccitiello made the claim at TechCrunch Disrupt San Francisco
+that half of all games are made with Unity \autocite{dillet2018}. We consider
+Unity's ubiquity to be an advantage; there is a glut of information about how to
+use augmented reality within Unity.
 
@@
 
-None of this history is readily apparent to a casual tourist at Kinkaku-ji.
-There are a few signs describing different areas, but they are only available in
-Japanese and contain very little information about the history and design of the
-site. Because of this, an intuitive audio tour app with AR features would be
-very helpful to tourists at Kinkaku-ji.
+None of this history is readily apparent to a typical non-Japanese speaking
+tourist at Kinkaku-ji. There are a few signs describing different areas, but
+they are only available in Japanese and contain very little information about
+the history and design of the site. Because of this, an intuitive audio tour app
+with AR features would be very helpful to tourists at Kinkaku-ji.
 
@@
 For testing and development purposes the Editour backend was originally hosted
-on a personal server belonging to a member of our team. This was a CentOS
-virtual machine running on an old Dell rack server in Worcester, Massachusetts.
-We wrote a custom systemd service to run the Editour as a daemon and keep its
-log files organized. The Node.js backend was served by an Nginx reverse proxy
-running on the same virtual machine.
+on Joseph Petitti's personal server. This was a CentOS virtual machine running
+on an old Dell rack server in Worcester, Massachusetts. We wrote a custom
+systemd service to run the Editour as a daemon and keep its log files organized.
+The Node.js backend was served by an Nginx reverse proxy running on the same
+virtual machine.
 
@@
 
-Despite Kinkaku-ji being an incredibly popular tourist destination that draws
-crowds from all over the world, the majority of the signage is purely Japanese.
-While AR translation apps exist, the experience can be frustrating, and produce
-poor results. Google's text recognition and machine-learning powered translation
+ARuko uses augmented reality to translate text at the site as well. While AR
+translation apps exist, the experience can be frustrating, and produce poor
+results. Google's text recognition and machine-learning powered translation
 technology is certainly impressive. At the same time, the translation service
@@
 more convenient and readable to have the translation appear in a separate
-scrollable textbox. This motivated the current design of the ``info buttons'' in
-ARuko. Instead of placing text directly onto signage, we place a blue button
+scrollable text box. This motivated the current design of the ``info buttons''
+in ARuko. Instead of placing text directly onto signage, we place a blue button
 with a stylized `i' in the center. By tapping on this button, a separate UI
@@
     \includegraphics[width=0.4\textwidth]{kinkakuji-ticket.jpeg}
-    \caption{Map overlay displaying the path and translated labels}
+    \caption{Kinkaku-ji ticket}
     \label{fig:kinkakujiTicket}
@@
 feature. Using Unity's built-in capability to design materials, we created
-a shiny golden material and applied it to the model.
+a shiny golden material and applied it to the model (see
+Figure~\ref{fig:souvenir}.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=.5\textwidth]{souvenir.png}
+	\caption{ARuko's virtual souvenir feature}
+	\label{fig:souvenir}
+\end{figure}
 

### 2019-10-01 paper.tex
added more info generally

--- 2019-10-01 paper.tex
@@
 toward creating modern mobile user interfaces such as React.
+
+All of Unity's scripting is done with C\#, which is a general purpose,
+object-oriented language~\autocite{ecmainternational2017}. Even though none of
+us had extensive experience with C\# prior to this project, this was not a great
+concern since C\# is similar to other object-oriented languages such as Java and
+C++. The design goals of the language were also appealing to us; C\# includes
+features important for programmer productivity such as strong type checking
+(unlike JavaScript), detection of using uninitialized variables (also unlike
+JavaScript,) range checking for array bounds (unlike C) and garbage collection.
+At the same time, our lack of familiarity with the language and Unity as a whole
+is another reason we first looked into cross-platform AR solutions that did not
+use Unity.
+%TODO see if we need more sources for this
 
@@
 
+\subsubsection{Editour Frontend Implementation}
+\label{sec:editourFrontendImplementation}
+
+The frontend was implemented as a web app, using web technologies such as HTML,
+CSS and JavaScript, with JavaScript being the vast majority. ECMAScript is the
+standard that modern JavaScript follows.
+
+Type-checking provided by Visual Studio Code and JSDoc made the growing code
+complexity more manageable~\footnote{One helpful specification of the ECMAScript
+standard in the way of programmer sanity is ``strict mode.'' By placing the
+string \texttt{"use strict"} at the top of a JavaScript source file, errors will
+be thrown in many cases where ordinary JavaScript would not complain. The
+simplest example of this is the line \texttt{a = 1;} will not throw an error
+ordinarily. In strict mode, you must at first explicitly declare the variable
+with the \texttt{let}, \texttt{var} or \texttt{const} keyword before assigning
+it, similar to Java or C++. We included the string at the beginning of every
+source file except for class declarations, which are in strict mode by
+default~\autocite[386]{ecmainternational2019}.} . Excluding Node.js modules, the
+only external library we used for Editour was Leaflet, an open-source JavaScript
+library for interactive maps~\autocite{leafletjs}. We did not use any framework
+for developing frontends like Facebook's React or Google's Angular. Instead, all
+of the complex UI interactions were handled by modifying the DOM directly with
+JavaScript's built-in functionality. Furthermore, we did not use any advanced
+frontend build tools such as Rollup, webpack or Parcel. For a JavaScript project
+of this scope, this was the correct decision. Considering we had limited
+knowledge of React or Angular, it was also faster to develop the UI in the way
+we were used to from previous experience. But if we were to continue to develop
+Editour, UI libraries and frontend build tools would be something to consider.
+
 \subsubsection{Editour Backend}
@@
 (\textit{aruko}), meaning ``let's walk,'' is the app we created to guide users
-through an AR-enhanced tour.
+through an AR-enhanced tour. The app was built with Unity, which enabled to us
+to use a single codebase for the iOS and Android versions of the apps.
 
@@
 
+At this point in the project, the codebase for Editour was already around three
+thousand lines of vanilla JavaScript. With the changing requirements, Editour
+was becoming onerous to maintain at this stage of the project. Luckily, these
+changes were still manageable to implement.
+
 With more time, we might have been able to get the ground-plane image placement
@@
 \end{figure}
-
-At this point, the codebase for Editour was already around three thousand lines
-of vanilla JavaScript. Type-checking provided by Visual Studio Code and JSDoc
-made the growing code complexity more manageable. Excluding Node.js modules, the
-only external library we used for Editour was Leaflet, an open-source JavaScript
-library for interactive maps~\autocite{leafletjs}. We did not use any framework
-for developing frontends like Facebook's React or Google's Angular. Instead, all
-of the complex UI interactions were handled by modifying the DOM directly with
-JavaScript's built-in functionality. Furthermore, we did not use any advanced
-frontend build tools such as Rollup, webpack or Parcel. For a JavaScript project
-of this scope, this was the correct decision. Considering we had limited
-knowledge of React or Angular, it was also faster to develop the UI in the
-way we were used to from previous experience. But if we were to continue to
-develop Editour, UI libraries and frontend build tools would be something to
-consider. With these changing requirements, the Editour was becoming onerous to
-maintain at this stage of the project. Luckily, these changes were still
-manageable to implement.
 
@@
 graphics and sound. Code complexity grew quickly as more features were added
-across the entire software stack. Git and GitHub enabled us to view the history
+across the entire software stack. GitHub and git enabled us to view the history
 of the code and revert back to working versions when absolutely necessary. We
@@
 feature, we would create a branch with a name descriptive of that feature. This
-methodology minimized difficult-to-resolve merge conflicts.
+methodology minimized difficult-to-resolve merge conflicts. We modeled this
+workflow off of the ``Git Feature Branch Workflow'' Atlassian
+tutorial~\autocite{atlassian}.
 % TODO explain merge conflicts and cite that Atlassian thing

### 2019-10-02 paper.tex
finish adding Ralph's suggestions
Fixed minor suggestions by Ralph, rewrote a lot of the conclusion to
separate it into three sections, and added some images. Some more images
that I don't have access to should also be added, so I created TODOs for
these

--- 2019-10-01 paper.tex
@@
 
+% TODO split up this figure into four separate figures, change references to
+% refer to the correct ones
 \begin{figure}[h]
@@
 
-If we were ever feeling too tired to test the app by walking around, we also
-mocked the GPS coordinates in software. This allowed us to simulate walking in a
-single direction without actually having to build to a mobile device or move.
+To maximize testing efforts and negate having to physically walk around we also
+simulated the GPS coordinates in software. This allowed us to simulate walking
+in a single direction without actually having to build to a mobile device or
+move.
 
@@
 using the app's features. Each member of our team also installed the beta
-version so we could test it.
+version so we could test it. % TODO add photos of us testing it
 
@@
 
-Despite the numerous pivots this project went through, in the end we were able
-to create a useful working prototype. The Editour is fully featured with
-everything needed to build an audio tour anywhere in the world. ARuko allows
-users to experience useful AR-enhanced tours in a pleasant and intuitive way.
-Together they provide a complete platform for building augmented reality tour
-guide apps.
+Our team is satisfied with the final result of this project, as we feel we have
+built a working platform that Kyoto VR will easily be able to build off of in
+the future. This section contains our final thoughts on the project and future
+work that could be done on it.
+
+\subsection{What Went Wrong}
+\label{sec:whatWentWrong}
 
@@
 
+On a similar note, the requirements and scope of the project changed greatly
+from week to week, and sometimes even within one day. We spent a lot of time
+exploring concepts and features that were completely unrelated to the final
+product. We also did not receive official specifications, such as the design of
+the GUI Atticus wanted for the app, until very late in the development process.
+
 Another challenge we faced was the difficulty in actually testing the app. The
@@
 
-Despite these issues our team is happy with the product we delivered to
-Kyoto~VR. Selling ARuko on app stores was not within the scope of our academic
+While not a disaster, we had some initial trouble getting started with Unity.
+Different versions of Unity do not play well with each other, and it often runs
+into bugs on older hardware, such as the laptops we had to work with.
+Furthermore, a stable version of the Unity editor is not available on
+GNU/Linux~\autocite{best2019}, so one of our team members had to install MacOS
+in order to use it. We were able to resolve these issues in the first weeks of
+the project, but it consumed some of our valuable time in July.
+
+\subsubsection{What Went Well}
+\label{sec:whatWentWell}
+
+Despite these issues, in the end we were able to create a useful working
+prototype. The Editour is fully featured with everything needed to build an
+audio tour anywhere in the world. ARuko allows users to experience useful
+AR-enhanced tours in a pleasant and intuitive way. Together they provide a
+complete platform for building augmented reality tour guide apps.
+
+Editour was not initially a requirement that Atticus had in mind, but it turned
+out to be a very useful tool in designing tours and allowing the app to be
+extensible. Two members of our team, Cole Granof and Joseph Petitti, had
+experience building web applications with HTML, CSS, and JavaScript, and the
+Editour allowed them to use these skills to help the project.
+
+Our team's broad range of skills made it so that each member had specific tasks
+that they were good at. This made the division of labor easier, and throughout
+the project we never had issues splitting up work.
+
+The research time we put in at the beginning of the project also proved to be
+very useful. Our decision to use Unity Vuforia based on this research made
+implementing many of the complex AR features easier later on. If we had chosen a
+less-ideal platform, we might have had to switch to a different one after
+wasting time on that poor decision.
+
+\subsubsection{Future Work}
+\label{sec:futureWork}
+
+Although selling ARuko on app stores was not within the scope of our academic
 project, but we were able polish the app enough such that it would be feasible
@@
 
-\clearpage % references should be on their own page
+\clearpage
 
@@
 
-% for tabularx
-% \newcolumntype{L}{>{\raggedright\arraybackslash\footnotesize}X}%
-
 \begin{table}[h]
 \begin{singlespace}
+\renewcommand{\arraystretch}{2.0} % add space between rows
+\footnotesize % make font smaller
 \begin{tabulary}{\textwidth}{ L | L | L | L | L | L }

### 2019-10-02 paper.tex
moved git stuff to appendix and working on heart section

--- 2019-10-01 paper.tex
@@
 
-% TODO this whole section should probably be in the appendix
-\section{Version Control}
-\label{sec:versionControl}
-
-Over the course of the project, we had to develop multiple applications in
-different languages. In total, we opened five different repositories: the blog,
-the \LaTeX source code for our paper, the Arduino code for the heart project,
-and of course one for Editour and another for ARuko. These five repositories
-span across multiple different markup and programming languages, including C\#,
-C++, JavaScript, HTML, CSS (and the \LaTeX markup language used to typeset this
-paper.) This gave us a welcome amount of practice using git for version control,
-as well as GitHub's other features oriented around coordinating a team.
-
-All three members of the team were contributing code and updating assets such as
-graphics and sound. Code complexity grew quickly as more features were added
-across the entire software stack. GitHub and git enabled us to view the history
-of the code and revert back to working versions when absolutely necessary. We
-researched the proper methodology of using version control in a small team,
-applying this methodology as best we could. This enabled us to work together
-efficiently, track down bugs, undo mistakes, and sometimes review each other's
-code for quality when time allowed.
-
-\subsection{GitHub Tools}
-\label{sec:gitHubTools}
-
-Some members of our team were very excited by the workflows GitHub's tools
-enabled. In this section, we will discuss some of the tools, some of which
-greatly aided in our organization and productivity.
-
-Initially, we experimented with using a four-column Kanban board to keep track
-of our progress. Figure~\ref{fig:kanbanBoard} shows a screenshot of this page on
-GitHub.
-
-The Kanban technique stems from Toyota in the 1940s. Kanban means ``visual
-signal'' or ``card'' in Japanese, which describes the core component of the
-technique~\autocite{terry2019}. At Toyota, line-workers would move colored cards
-to notify other teams that parts needed for assembly work were in short supply.
-Now, Kanban boards are integral to Agile software development. Still, some teams
-use physical Kanban boards, often using sticky notes and whiteboards.
-
-The advantage of using a Kanban board is that each feature or bug that
-is being worked on can be assigned directly to a collaborator on the project. It
-is then that person's responsibility to work on those tasks and update the
-status of those tasks on the board. We abandoned this when moving onto the main
-project because we came to realize that this structure was not necessary---there
-were only three members on the team, and we were almost always in the same room
-when working on the project. For Editour, we tracked features and issues using
-the Issues page instead, which is discussed in
-Section~\ref{sec:editourFrontendTesting}.
-
-Creating ``pull requests'' through the GitHub web interface has a few advantages
-over directly merging code using git. Firstly, the pull request feature
-integrates with ``Issues'' page very well. By typing `resolves' along with the
-number associated with an issue into the description of a pull request, GitHub
-will automatically close the issue when the pull request is approved. This is
-not only remarkably convenient, but also self-documenting since the descriptions
-of pull requests would contain the issues they were resolving. Secondly,
-creating a pull request allows code to be reviewed by other members of the team
-very easily. Reviewers can view the entire diff and add comments line-by-line.
-Other collaborators can easily respond to those comments. Reviewers can also
-request certain features be changed before the branch is merged, which allowed
-us to enforce that issues with the code were actually addressed.
-% TODO explain what the heck a diff is
-
-% TODO give this paragraph some more context so it doens't seem out of place
-The way we incorporated branches into our workflow helped us collaborate in a
-way that kept us organized. In general, if one of us was working on a specific
-feature, we would create a branch with a name descriptive of that feature. This
-methodology minimized difficult-to-resolve merge conflicts. We modeled this
-workflow off of the ``Git Feature Branch Workflow'' Atlassian
-tutorial~\autocite{atlassian}.
-% TODO explain merge conflicts and cite that Atlassian thing
-
-Once we deployed Editour to a server so that Atticus could begin to use it,
-we changed the version to v1.0.0 to indicate the first release version. At this
-point, it was important that the master branch remain as stable as possible.
-Because of this, we created a ``dev'' branch where we could test experimental
-features to improve the experience and functionality of Editour. Maintaining a
-stable and experimental branch reduced the risks involved with continuing to
-iterate on the software's features post-release.
-
-In a similar vein, with ARuko we used branches to ensure we had a stable working
-version. The night before field testing at Kinkaku-ji, we would cease work on
-the most recent branch, and build the app to our phones. This way, we would
-always have an exact snapshot of the code we used for that day of testing.
-
 \begin{figure}[h]
@@
 \appendices
+
+% TODO should this really go in the appendix?
+\section{Version Control}
+\label{sec:versionControl}
+
+Over the course of the project, we had to develop multiple applications in
+different languages. In total, we opened five different repositories: the blog,
+the \LaTeX source code for our paper, the Arduino code for the heart project,
+and of course one for Editour and another for ARuko. These five repositories
+span across multiple different markup and programming languages, including C\#,
+C++, JavaScript, HTML, CSS (and the \LaTeX markup language used to typeset this
+paper.) This gave us a welcome amount of practice using git for version control,
+as well as GitHub's other features oriented around coordinating a team.
+
+All three members of the team were contributing code and updating assets such as
+graphics and sound. Code complexity grew quickly as more features were added
+across the entire software stack. GitHub and git enabled us to view the history
+of the code and revert back to working versions when absolutely necessary. We
+researched the proper methodology of using version control in a small team,
+applying this methodology as best we could. This enabled us to work together
+efficiently, track down bugs, undo mistakes, and sometimes review each other's
+code for quality when time allowed.
+
+\subsection{GitHub Tools}
+\label{sec:gitHubTools}
+
+Some members of our team were very excited by the workflows GitHub's tools
+enabled. In this section, we will discuss some of the tools, some of which
+greatly aided in our organization and productivity.
+
+Initially, we experimented with using a four-column Kanban board to keep track
+of our progress. Figure~\ref{fig:kanbanBoard} shows a screenshot of this page on
+GitHub.
+
+The Kanban technique stems from Toyota in the 1940s. Kanban means ``visual
+signal'' or ``card'' in Japanese, which describes the core component of the
+technique~\autocite{terry2019}. At Toyota, line-workers would move colored cards
+to notify other teams that parts needed for assembly work were in short supply.
+Now, Kanban boards are integral to Agile software development. Still, some teams
+use physical Kanban boards, often using sticky notes and whiteboards.
+
+The advantage of using a Kanban board is that each feature or bug that
+is being worked on can be assigned directly to a collaborator on the project. It
+is then that person's responsibility to work on those tasks and update the
+status of those tasks on the board. We abandoned this when moving onto the main
+project because we came to realize that this structure was not necessary---there
+were only three members on the team, and we were almost always in the same room
+when working on the project. For Editour, we tracked features and issues using
+the Issues page instead, which is discussed in
+Section~\ref{sec:editourFrontendTesting}.
+
+Creating ``pull requests'' through the GitHub web interface has a few advantages
+over directly merging code using git. Firstly, the pull request feature
+integrates with ``Issues'' page very well. By typing `resolves' along with the
+number associated with an issue into the description of a pull request, GitHub
+will automatically close the issue when the pull request is approved. This is
+not only remarkably convenient, but also self-documenting since the descriptions
+of pull requests would contain the issues they were resolving. Secondly,
+creating a pull request allows code to be reviewed by other members of the team
+very easily. Reviewers can view the entire diff and add comments line-by-line.
+Other collaborators can easily respond to those comments. Reviewers can also
+request certain features be changed before the branch is merged, which allowed
+us to enforce that issues with the code were actually addressed.
+% TODO explain what the heck a diff is
+
+% TODO give this paragraph some more context so it doens't seem out of place
+The way we incorporated branches into our workflow helped us collaborate in a
+way that kept us organized. In general, if one of us was working on a specific
+feature, we would create a branch with a name descriptive of that feature. This
+methodology minimized difficult-to-resolve merge conflicts. We modeled this
+workflow off of the ``Git Feature Branch Workflow'' Atlassian
+tutorial~\autocite{atlassian}.
+% TODO explain merge conflicts and cite that Atlassian thing
+
+Once we deployed Editour to a server so that Atticus could begin to use it,
+we changed the version to v1.0.0 to indicate the first release version. At this
+point, it was important that the master branch remain as stable as possible.
+Because of this, we created a ``dev'' branch where we could test experimental
+features to improve the experience and functionality of Editour. Maintaining a
+stable and experimental branch reduced the risks involved with continuing to
+iterate on the software's features post-release.
+
+In a similar vein, with ARuko we used branches to ensure we had a stable working
+version. The night before field testing at Kinkaku-ji, we would cease work on
+the most recent branch, and build the app to our phones. This way, we would
+always have an exact snapshot of the code we used for that day of testing.
+
+\clearpage
+
 \section{Editour API Documentation}
@@
 
+\section{Ritsumeikan Heart Project}
+\label{sec:ritsumeikanHeartProject}
+
+\section{Supplies}
+\label{sec:supplies}
+
+\subsection{Project Goal}
+\label{sec:projectGoal}
+
+The goal of the project was to create an interactive model of a heart to teach
+heart function to non-specialists, such as students in middle school. This meant
+that the model had to be highly visual and simple to understand. Each visual
+component would have to be designed in an intuitive fashion so that students
+could begin interacting with the model without advanced knowledge of biology.
+
+\subsection{The Heart Simulation}
+\label{sec:theHeartSimulation}
+
+We were presented with a set of equations that defined the mathematical model of
+the heart we would be using to drive our physical model. Along with the
+differential equations, we were also given an analogous circuit model that could
+also be described by the same equations. The circuit and the equations can be
+seen in Figure~\ref{fig:referenceModel}. We were also provided with source code
+for an implementation of this model. We would still need to modify this code to
+calculate the output variables we would need to properly operate the physical
+model, and integrate the model into the main loop of the Arduino source code
+with the appropriate timing.
+
+\begin{figure}[h] \centering
+    \includegraphics[width=0.4\textwidth]{reference-model.png}
+    \caption{The reference model we used to implement the simulation}
+    \label{fig:referenceModel}
+\end{figure}
+
+We visited ``Den Den Town'' in Osaka in order to gather supplies we would need
+in order to construct the heart. One of the most important purchases of this
+trip was a two-meter long strip of Adafruit NeoPixel light emitting diodes
+(LEDs). The design of this reel of LEDs enabled us to cut the strip at specific
+points to create shorter strips. Each LED on the strip individually adressable,
+allowing us to set the color of any LED along the strip. This perfectly suited
+our needs for representing blood flow.
+
+We were able to program custom animations by updating the color and intensity of
+the LEDs in a rapid fashion. We represented blood flow by changing the phase of
+a sinusoidal wave over time.\footnote{For clarity, we elongated the ``troughs''
+of the sine waves, so the pattern of intensity was not a true sine wave.} Our
+design included two strips of twenty LEDs. The rate of the animation on the
+first strip of LEDs represented blood flow out of the left ventricle.
+
+\clearpage
+
 \section{Testing Survey Results}

### 2019-10-03 paper.tex
fix pull request comments

--- 2019-10-02 paper.tex
@@
 On a similar note, the requirements and scope of the project changed greatly
-from week to week, and sometimes even within one day. We spent a lot of time
-exploring concepts and features that were completely unrelated to the final
-product. We also did not receive official specifications, such as the design of
-the GUI Atticus wanted for the app, until very late in the development process.
+from week to week, and sometimes even within one day. We spent a significant
+amount of time exploring concepts and features that were completely unrelated to
+the final product. We also did not receive official specifications, such as the
+design of the GUI Atticus wanted for the app, until very late in the development
+process.
 
@@
 Furthermore, a stable version of the Unity editor is not available on
-GNU/Linux~\autocite{best2019}, so one of our team members had to install MacOS
+GNU/Linux~\autocite{best2019}, so one of our team members had to install macOS
 in order to use it. We were able to resolve these issues in the first weeks of

### 2019-10-03 paper.tex

@@
 would disturb the buildings or grounds of a historic site our app does not rely
-on these markers. Instead, our ARuko recognizes images of objects that are
-already at the site, and uses them to display informative AR pop-ups. See
-Sections~\ref{sec:translationFeature} and \ref{sec:mapOverlayFeature} for
-more details.
+on these markers. Instead, ARuko recognizes images of objects that are already
+at the site, and uses them to display informative AR pop-ups. See
+Sections~\ref{sec:translationFeature} and \ref{sec:mapOverlayFeature} for more
+details.
 
@@
 understanding of AR and how to develop for it is limited. All sorts of different
-challenges and limitations face the development and production of AR apps. Here
-are some that we considered when working on our app.
+challenges and limitations face the development and production of AR apps. In
+this section we discuss some of the challenges we faced when working on our app.
 
@@
 very little in the way of functionality or practicality; quite simply, they
-primarily primarily revolve around deploying
-gimmicks~\autocite{theappsolutions2018}. For example, one of the most popular
-apps to use AR, \textit{Pokémon Go}, primarily uses its AR feature to place a
-Pokémon on top of a camera's video feed. Disappointingly, it does not interact
-with anything around it. It just floats a fixed distance away from the user.
+primarily revolve around deploying gimmicks~\autocite{theappsolutions2018}. For
+example, one of the most popular apps to use AR, \textit{Pokémon Go}, primarily
+uses its AR feature to place a Pokémon on top of a camera's video feed.
+Disappointingly, it does not interact with anything around it. It just floats a
+fixed distance away from the user.
 
@@
 
-While not a disaster, we had some initial trouble getting started with Unity.
-Different versions of Unity do not play well with each other, and it often runs
-into bugs on older hardware, such as the laptops we had to work with.
-Furthermore, a stable version of the Unity editor is not available on
-GNU/Linux~\autocite{best2019}, so one of our team members had to install macOS
-in order to use it. We were able to resolve these issues in the first weeks of
-the project, but it consumed some of our valuable time in July.
+We had some initial trouble getting started with Unity. Different versions of
+Unity do not play well with each other. As a result, we often ran into bugs on
+older hardware, such as the laptops we had to work with. Furthermore, a stable
+version of the Unity editor is not available on GNU/Linux~\autocite{best2019},
+so one of our team members had to install macOS in order to use it. We were able
+to resolve these issues in the first weeks of the project, but it consumed some
+of our valuable time in July.
 
@@
 
+Our team's broad range of skills made it so that each member had specific tasks
+that they were good at. This made the division of labor easier, and throughout
+the project we never had issues splitting up work.
+
 Editour was not initially a requirement that Atticus had in mind, but it turned
@@
 Editour allowed them to use these skills to help the project.
-
-Our team's broad range of skills made it so that each member had specific tasks
-that they were good at. This made the division of labor easier, and throughout
-the project we never had issues splitting up work.
 

### 2019-10-03 paper.tex
working on heart section

--- 2019-10-02 paper.tex
@@
 (LEDs). The design of this reel of LEDs enabled us to cut the strip at specific
-points to create shorter strips. Each LED on the strip individually adressable,
+points to create shorter strips. Each LED on the strip individually addressable,
 allowing us to set the color of any LED along the strip. This perfectly suited
 our needs for representing blood flow.
+
+\subsection{Interactive Heart Model Design}
+\label{sec:interactiveModelDesign}
+
+The design for the interactive model is pictured in
+Figure~\ref{fig:interactiveModel}. The most prominent feature of the model is
+the plastic bottle containing the balloon. The volume of this balloon represents
+the volume of the left ventricle. Instead of inflating the balloon with the air
+compressor directly (pictured on the left of Figure~\ref{fig:interactiveModel},
+we opted to pressurize a sealed two-liter soda bottle and suspend a balloon
+inside. By pumping more air into the bottle, we could reduce the volume of the
+balloon since the external pressure would be made greater than the internal
+pressure; the balloon would shrink as a result. To accomplish switching the
+flow of air, we designed a setup involving two valves.
+% TODO do we need to cite something to explain the super simple physics of this?
+
+\begin{figure}[h] \centering
+    \includegraphics[width=0.7\textwidth]{interactive-model.png}
+    \caption{A diagram representing the physical model of the heart}
+    \label{fig:interactiveModel}
+\end{figure}
+
+Like the balloon which represents the volume of the left ventricle, the LED
+strips represent both pressure and blood flow in different parts of the body.
+Pressure is represented by color. The lower the pressure, the more blue the
+lights will appear. By the same token, red represents high pressure. The LEDs
+can display any color in between blue and red, so the light strips are often a
+pinkish hue.
 
@@
 of the sine waves, so the pattern of intensity was not a true sine wave.} Our
-design included two strips of twenty LEDs. The rate of the animation on the
-first strip of LEDs represented blood flow out of the left ventricle.
+design included two strips of twenty LEDs. The LED strips are represented by the
+red arrows on Figure~\ref{fig:interactiveModel}. The rate of the animation on
+the right strip of LEDs represents blood flow out of the left ventricle (whose
+value is $f_{1}$ in the model). The color corresponds to $P_{a}$ in the model,
+which is the pressure in the aorta. The animation speed of the LED strip leading
+back into the heart is controlled by $f_{v}$, the flow back into the ventricles.
+The pressure corresponding to the color of this strip is $P_{v}$, or venous
+pressure. In our model, this value is not an output variable. Instead, $P_{v}$
+is held constant. Consequently, the color of this LED strip does not change over
+time.
+
+The physical model also contains a digital number display, which can be seen in
+the top right corner on Figure~\ref{fig:interactiveModel}.
+
+\subsection{User Interface for Heart Model}
+\label{sec:userInterfaceForHeartModel}
+
+Our initial plan for the user interface was to control input and output
+parameters with dials. The numerical values of the input parameters would have
+been displayed on an array of digital number displays. Due to time constraints,
+we opted to support five preprogrammed scenarios that could be toggled from a
+GUI. Figure~\ref{fig:heartGui} represents the final version of the GUI we use to
+interact with the physical model.
+
+\begin{figure}[h] \centering
+    \includegraphics[width=0.7\textwidth]{heart-gui.png}
+    \caption{The GUI to enable five preprogrammed scenarios}
+    \label{fig:heartGui}
+\end{figure}
 

### 2019-10-03 paper.tex
wrote the appendix for the NOxAR app ground plane adaptation. Added a couple sources that I refer to.

--- 2019-10-03 paper.tex
@@
 
+\section{NOxAR Assignment}
+\label{sec:NOxAR}
+
+On Monday, September 9th, Atticus approached us about an additional project he 
+wanted us to tackle. He wanted us to adapt Kyoto VR's NOxAR app to use ground
+plane detection. Currently, the NOxAR app is an AR app for Microsoft Hololens
+that uses image targets with Vuforia. When viewing the correct image target,
+the app projects a 3D model of a Noh Theater\footnote{A form of Japanese 
+theater originating in the 14th century structured around song and slow 
+dancing~\autocite{japanguide2018}.} performer dancing to background 
+music~\autocite{noxar2018}. What Atticus wanted us to do was have the app use 
+ground plane detection in order to display the Noh performer so that it could 
+be displayed anywhere. Additionally, he wanted us to scale up the model so that
+when displayed in AR, the performer would appear life-sized, as if she were 
+really there dancing in the real world.
+
+For this project, Atticus sent us the original Unity project files for NOxAR.
+We then had to figure out how to turn the original project into a ground plane
+AR app. At first we tried importing the assets for the Noh performer into a new
+Unity project. We did this for a couple reasons. The first reason was because
+we didn't want all of the extra components of the original NOxAR project to
+get in the way of what we were trying to do. We also did this because the 
+original project was made with a 2017 version of Unity, so we wanted to try to
+use our more recent version so we wouldn't risk running into any depricated 
+features or functionalities. We did eventually get this method to work, but the
+model of the Noh performer was lacking a lot of the details that the original 
+model had. This was attributed to poor importation of the original assets, so 
+we decided to try making changes to the original NOxAR project instead.
+
+Per Atticus's advice, we deleted any and all unnecessary elements from the 
+scene before proceeding. We also updated the Unity version of the project to
+the 2019 version we were using, and updated the version of Vuforia to the most
+recent version, neither of which created any problems. The process of getting
+the model to appear on ground plane detection instead of image target 
+recognition was relatively simple. We simply moved the model from an image 
+target to a simulated ground plane, added a plane detector component to the
+scene, and made sure the Vuforia settings were in place for ground plane
+detection to work well. From there, we just had to test the app a few times so
+we could properly scale the model to life size. So on Tuesday, September 17th, 
+we completed the NOxAR ground plane adaptation to Atticus's saisfaction and
+sent him the final APK file for the app.
+
 \end{document}

### 2019-10-03 paper.tex
adding more to heart project section

--- 2019-10-03 paper.tex
@@
 tutorial~\autocite{atlassian}.
-% TODO explain merge conflicts and cite that Atlassian thing
+% TODO explain merge conflicts
 
@@
 
-\section{Supplies}
-\label{sec:supplies}
+Throughout our stay at Ritsumeikan, we also had the opportunity to work closely
+with other Ritsumeikan students to create build a project that involved the
+integration of hardware and software. With the help of students and professors
+alike, we were able to produce an educational physical model of a heart
+controlled by an Arduino microcomputer. Noma gave us tremendous assistance with
+hardware. He taught us how to properly use the tools around the lab, and
+purchased mechanical and electrical components we would need to complete our
+task. Amano Sensei was always available to answer questions related to biology,
+and helped us understand the mathematical model we would need to implement to
+drive the physical model with software. We worked on this project every
+Wednesday, completing the final model during the last week of our stay.
+% TODO get the full name of Amano Sensei
 
@@
 
-The goal of the project was to create an interactive model of a heart to teach
-heart function to non-specialists, such as students in middle school. This meant
-that the model had to be highly visual and simple to understand. Each visual
-component would have to be designed in an intuitive fashion so that students
-could begin interacting with the model without advanced knowledge of biology.
+The goals and requirements of this project were set out by Haruo Noma, a
+professor at Ritsumeikan University. The goal of the project was to create an
+interactive model of a heart to teach heart function to non-specialists, such as
+students in middle school. This meant that the model had to be highly visual and
+simple to understand. Each visual component would have to be designed in an
+intuitive fashion so that students could begin interacting with the model
+without advanced knowledge of biology.
 
@@
 
-We visited ``Den Den Town'' in Osaka in order to gather supplies we would need
-in order to construct the heart. One of the most important purchases of this
-trip was a two-meter long strip of Adafruit NeoPixel light emitting diodes
-(LEDs). The design of this reel of LEDs enabled us to cut the strip at specific
-points to create shorter strips. Each LED on the strip individually addressable,
-allowing us to set the color of any LED along the strip. This perfectly suited
-our needs for representing blood flow.
+\subsection{Supplies}
+\label{sec:supplies}
+
+With Noma Sensei as our guide, we visited ``Den Den Town'' in Osaka in order to
+gather supplies we would need in order to construct the heart. One of the most
+important purchases of this trip was a two-meter long strip of Adafruit NeoPixel
+light emitting diodes (LEDs). The design of this reel of LEDs enabled us to cut
+the strip at specific points to create shorter strips. Each LED on the strip
+individually addressable, allowing us to set the color of any LED along the
+strip. This perfectly suited our needs for representing blood flow.
+
+% TODO give a citation about what an Arduino is
+% TODO do we need citations about every microcomputer mentioned by name?
+Noma Sensei had various microcomputers for us to experiment with in his lab,
+including an obniz, an M5Stack, a Raspberry Pi and an Arduino. The Arduino was
+the only computer that had a ``motor shield'' component which we believed would
+be necessary for controlling the pumps.\footnote{In the end, we did not need
+this component, since we abandoned the idea of taking apart a pump to drive the
+DC motor directly.} Because of this, we chose the Arduino to be the core of the
+physical model. This microcomputer ran the simulation and output data to the
+various hardware components, such as the digital display, LED strips and switch
+to control the air valves.
 
@@
 the volume of the left ventricle. Instead of inflating the balloon with the air
-compressor directly (pictured on the left of Figure~\ref{fig:interactiveModel},
+compressor directly (pictured on the left of Figure~\ref{fig:interactiveModel}),
 we opted to pressurize a sealed two-liter soda bottle and suspend a balloon
@@
 balloon since the external pressure would be made greater than the internal
-pressure; the balloon would shrink as a result. To accomplish switching the
+pressure; the balloon would shrink as a result. To accomplish redirecting the
 flow of air, we designed a setup involving two valves.
@@
 \begin{figure}[h] \centering
-    \includegraphics[width=0.7\textwidth]{interactive-model.png}
+    \includegraphics[width=\textwidth]{interactive-model.png}
     \caption{A diagram representing the physical model of the heart}
@@
 Pressure is represented by color. The lower the pressure, the more blue the
-lights will appear. By the same token, red represents high pressure. The LEDs
-can display any color in between blue and red, so the light strips are often a
-pinkish hue.
+lights will appear. Red represents high pressure. The LEDs can display any color
+in between blue and red, so the light strips are often a pinkish hue.
 
@@
 The physical model also contains a digital number display, which can be seen in
-the top right corner on Figure~\ref{fig:interactiveModel}.
+the top right corner on Figure~\ref{fig:interactiveModel}. The display shows the
+number of the active scenario. Clicking on a scenario button in the GUI
+(discussed in Section~\ref{sec:userInterfaceForHeartModel}) will change the
+number being displayed.
 
@@
 
+The red buttons along the top of the screen allow the user to toggle between
+different scenarios. Each scenario also includes a helpful graphic below each
+button.
+
 \begin{figure}[h] \centering
-    \includegraphics[width=0.7\textwidth]{heart-gui.png}
+    \includegraphics[width=\textwidth]{heart-gui.png}
     \caption{The GUI to enable five preprogrammed scenarios}
@@
 \end{figure}
+
+Not only can the GUI communicate with the Arduino; the Arduino can relay
+information about the state of the model back to the GUI. The length of blue bar
+on the left of Figure~\ref{fig:heartGui} corresponds to $f_{v}$ in the model,
+while the blue bar on the right corresponds to $f_{1}$. On the physical model,
+these values correspond to the rate of animation of both LED strips. The size of
+the circle between the blue bars represents $V_{LV}$, the volume of the left
+ventricle. Due to limitations about the accuracy with which we could control the
+pump, the volume of the balloon does perfectly reflect the true value of
+$V_{LV}$ in the model. By contrast, the radius of the graphic on-screen can be
+set to be exactly proportional to the value of $V_{LV}$.
+
+% TODO write about the final result of the heart model and include pictures
 

### 2019-10-03 paper.tex

@@
 while ARuko allows users to seamlessly experience historic sites in an intuitive
-and novel way. The experience of walking through the site is enhanced by
-informative narration and AR pop-ups that do not alter the buildings or ground
-in real life.
+and novel way. Many AR apps require specific markers, like the those shown in
+Figure~\ref{fig:arMarker}. Too avoid needing to place any physical object that
+would disturb the buildings or grounds of a historic site our app does not rely
+on these markers. Instead, ARuko recognizes images of objects that are already
+at the site, and uses them to display informative AR pop-ups. See
+Sections~\ref{sec:translationFeature} and \ref{sec:mapOverlayFeature} for more
+details.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{ar-marker.jpg}
+	\caption[Augmented reality markers]{Augmented reality
+		markers~\autocite{jeriaska2010}}
+	\label{fig:arMarker}
+\end{figure}
 
@@
 
-Many of the existing applications using AR, in our eyes, do not leverage the
+Most existing applications using AR, in our team's opinions, do not leverage the
 full potential of this emerging technology. As with any new field, our
-understanding of AR and how to develop for it is limited. All sorts of
-different challenges and limitations face the development and production of AR
-apps. Here are some that we considered when working on our app.
+understanding of AR and how to develop for it is limited. All sorts of different
+challenges and limitations face the development and production of AR apps. In
+this section we discuss some of the challenges we faced when working on our app.
 
@@
 put, not very good. Many AR apps and features available on smartphones offer
-very little in the way of functionality or practicality; quite simply, they are
-primarily used for minor spectacles and simple
-tricks~\autocite{theappsolutions2018}. For example, one of the most popular
-apps to use AR, \textit{Pokémon Go}, primarily uses its AR feature to place a
-Pokémon on top of a camera's video feed. Disappointingly, it does not interact
-with anything around it. It just floats a fixed distance away from the user.
+very little in the way of functionality or practicality; quite simply, they
+primarily revolve around deploying gimmicks~\autocite{theappsolutions2018}. For
+example, one of the most popular apps to use AR, \textit{Pokémon Go}, primarily
+uses its AR feature to place a Pokémon on top of a camera's video feed.
+Disappointingly, it does not interact with anything around it. It just floats a
+fixed distance away from the user.
 
@@
 
+On a similar note, the requirements and scope of the project changed greatly
+from week to week, and sometimes even within one day. We spent a significant
+amount of time exploring concepts and features that were completely unrelated to
+the final product. We also did not receive official specifications, such as the
+design of the GUI Atticus wanted for the app, until very late in the development
+process.
+
 Another challenge we faced was the difficulty in actually testing the app. The
@@
 
-Despite these issues our team is happy with the product we delivered to
-Kyoto~VR. Selling ARuko on app stores was not within the scope of our academic
+We had some initial trouble getting started with Unity. Different versions of
+Unity do not play well with each other. As a result, we often ran into bugs on
+older hardware, such as the laptops we had to work with. Furthermore, a stable
+version of the Unity editor is not available on GNU/Linux~\autocite{best2019},
+so one of our team members had to install macOS in order to use it. We were able
+to resolve these issues in the first weeks of the project, but it consumed some
+of our valuable time in July.
+
+\subsubsection{What Went Well}
+\label{sec:whatWentWell}
+
+Despite these issues, in the end we were able to create a useful working
+prototype. The Editour is fully featured with everything needed to build an
+audio tour anywhere in the world. ARuko allows users to experience useful
+AR-enhanced tours in a pleasant and intuitive way. Together they provide a
+complete platform for building augmented reality tour guide apps.
+
+Our team's broad range of skills made it so that each member had specific tasks
+that they were good at. This made the division of labor easier, and throughout
+the project we never had issues splitting up work.
+
+Editour was not initially a requirement that Atticus had in mind, but it turned
+out to be a very useful tool in designing tours and allowing the app to be
+extensible. Two members of our team, Cole Granof and Joseph Petitti, had
+experience building web applications with HTML, CSS, and JavaScript, and the
+Editour allowed them to use these skills to help the project.
+
+The research time we put in at the beginning of the project also proved to be
+very useful. Our decision to use Unity Vuforia based on this research made
+implementing many of the complex AR features easier later on. If we had chosen a
+less-ideal platform, we might have had to switch to a different one after
+wasting time on that poor decision.
+
+\subsubsection{Future Work}
+\label{sec:futureWork}
+
+Although selling ARuko on app stores was not within the scope of our academic
 project, but we were able polish the app enough such that it would be feasible

### 2019-10-03 paper.tex
added section on scrapped ar use cases

--- 2019-10-03 paper.tex
@@
 
+\subsection{Alterniative Uses for AR in ARuko}
+\label{sec:alternativeARukoAR}
+
+Even once the idea for ARuko was settled on audio tour functionality with 
+additional AR components, what exactly those AR components would do was still
+undecided for a while. Atticus knew he wanted to use AR on the tour, but wasn't
+sure what to do with it. At first, we made recommendations to him based on the
+capabilities of Vuforia that we found in our research. We knew it was good at
+image recognition and ground plane recognition, so we suggested that maybe 
+displaying some sorts of 3D models in certain locations using either of these
+features might be an interesting way to expand on the tour. With these 
+recommendations in mind, Atticus expressed interest in the capability of using
+building facades as image targets. The intention then would be to tie content
+related to a specific location within Kinkaku-ji to that physical location, and
+use images of the location as targets. As previously explained, this ultimately
+did not work out due to the limitations of image recognition with Vuforia.
+
+After being initially deterred from image recognition, we thought that ground
+and mid-air plane recognition might the best way to implement AR in the app. 
+It didn't have to rely on images that meet Vuforia's criteria, and since it 
+could be triggered anywhere, it seemed like a good fit for an app focusing on
+walking around a site. Atticus explained that he primarily wanted to use AR to
+display art related to the site. So we focused our efforts with ground and 
+mid-air plane AR on ways to display 2D images. What we ended up creating first
+was a feature that allowed you to view certain images in AR, using ground plane
+detection, based on what region you were in. So when you entered a region of 
+the tour, the image menu would be dynamically populated with buttons that, when
+tapped, would create a Plane primitive in Unity with the given image displayed
+on it and place it on the ground plane.
+
+We encountered a few notable problems with this though. One problem was that 
+the Plane we made was always the same size and dimensions, and would cause 
+images to stretch to fit the plane. Further testing to change the size of the
+plane with each picture proved difficult. Additionally, using a Plane primitive
+had problematic effects on the way the object was lit in the Unity scene, as 
+well as how it appeared when not viewed head-on. If viewed from an angle, the 
+picture could become very dark and difficult to see. And if viewed from behind,
+it would actually be completely invisible. Because of these issues, we decided
+to place the images on a 3D Cube primitive instead. But after showing this
+feature to Atticus during early testing at Kinkaku-ji, he decided that he 
+wanted to move away from displaying images in AR. Looking back, the feature
+may have worked better with mid-air plane recognition so that the user could
+place the image directly in front of them.
+
+In addition to the previously mentioned use cases for AR in ARuko, Atticus also
+expressed interest in using AR to trigger video content. He was particularly
+interested in 3D videos triggerable through AR. As the scope of the project 
+grew, and time ran short, the task of including 3D videos triggered by AR 
+seemed more and more complicated, causing that idea to be phased out of the
+final project. Additionally, we never received any assets from Atticus to use
+for this feature, thus preventing us from spending time developing it.
+
 \clearpage

### 2019-10-03 paper.tex
monetization section

--- 2019-10-03 paper.tex
@@
 enhances the user experience. Hardware issues were definitely our biggest
-challenge. Only one member of our team had a phone new enough to run AR technology at a
-decent level, making testing of our application difficult.
+challenge. Only one member of our team had a phone new enough to run AR
+technology at a decent level, making testing of our application difficult.
 
@@
 
+\subsection{Monetization for ARuko}
+\label{sec:monetizationForAruko}
+
+Partway through our project, Atticus Sims let us know that he was looking to
+monetize the app we were developing for him. He also informed us that the IQP
+team would be looking for funding options in order to ``bootstrap'' the project.
+One monetization method he proposed was potentially marketing the app to hotels,
+allowing hotels to sell tours for download through in-app purchases.
+
+In order to get an app approved for the App Store or the Google Play store,
+there is sometimes a lengthy approval process. This might have been possible if
+our project had been more prescriptive from the start.
+
+We did perform some preliminary research about the monetization models Atticus
+proposed and brought forth some potential roadblocks regarding each one. We let
+Atticus know that we had logistical concerns about circumventing Apple's or
+Google's in-app purchases by locking content behind a different payment process.
+Additionally, we informed Atticus that he would have to purchase a commercial
+Vuforia license in order to deploy the app onto any
+storefront~\autocite{vuforialicense2018}, which Atticus was not willing to do at
+the time. The free version of Vuforia comes branded with a watermark in the
+bottom left corner.\footnote{The final design of our app incidentally covers up
+the watermark with our own UI elements. This does not change the fact that we
+would not be able to deploy the app without a proper commercial license for
+Vuforia.}
+
+Our concerns about focusing on monetization for Kyoto~VR were twofold. Firstly,
+we were worried that this kind of work strayed too far away from the academic
+intent of the project---the intent being to explore various ways in which AR and
+geolocation could be used in tandem to create an improved experience for
+tourists. For our purposes, the app was meant to demonstrate our discoveries in
+the form of a polished prototype. While we feel as though we achieved this goal,
+we made certain compromises in the way of experimentation in order to leave
+Kyoto~VR with a potentially marketable product. We made it clear to Atticus that
+deploying our app on the Google Play Store or App Store would not be within the
+scope of our academic project as per our advisers' advice.
+
 \clearpage
@@
 different languages. In total, we opened five different repositories: the blog,
-the \LaTeX source code for our paper, the Arduino code for the heart project,
+the \LaTeX~source code for our paper, the Arduino code for the heart project,
 and of course one for Editour and another for ARuko. These five repositories
 span across multiple different markup and programming languages, including C\#,
-C++, JavaScript, HTML, CSS (and the \LaTeX markup language used to typeset this
-paper.) This gave us a welcome amount of practice using git for version control,
+C++, JavaScript, HTML, CSS (and the \LaTeX~markup language used to typeset this
+paper.) This gave us a welcome amount of practice using Git for version control,
 as well as GitHub's other features oriented around coordinating a team.
@@
 graphics and sound. Code complexity grew quickly as more features were added
-across the entire software stack. GitHub and git enabled us to view the history
+across the entire software stack. GitHub and Git enabled us to view the history
 of the code and revert back to working versions when absolutely necessary. We
@@
 Creating ``pull requests'' through the GitHub web interface has a few advantages
-over directly merging code using git. Firstly, the pull request feature
+over directly merging code using Git. Firstly, the pull request feature
 integrates with ``Issues'' page very well. By typing `resolves' along with the

### 2019-10-03 paper.tex
wrote the abstract

--- 2019-10-03 paper.tex
@@
 \begin{abstract}
-	% abstract goes here
-	% TODO write abstract
+Kinkaku-ji, the Temple of the Golden Pavilion, is one of Kyoto's most visited
+tourist attractions. Most people who visit the site do not have the opportunity
+to experience the rich art and culture that are part of its history. We worked
+with our sponsor, Kyoto VR, to create an app that would allow visitors of 
+Kinkaku-ji to better experience these aspects of the site. We used Unity to
+create an audio tour app that provides historical insight on the location, 
+displays galleries of art throughout the visit, and offers accessibility 
+features through AR. We hope our app will enhance the experience of visiting
+Kinkaku-ji.  
 \end{abstract}
@@
 development double major; Cole Granof, computer science major; and Joseph
-Petitti, computer science major. We spent twelve weeks in Shiga, Japan
+Petitti, computer science major. We spent twelve weeks in Shiga prefecture, Japan,
 completing the requirements for our Major Qualifying Project, a WPI graduation
@@
 Our team worked directly under Kyoto VR founder and CEO Atticus Sims to develop
-and tested a mobile app to deliver an audio tour, incorporating various
+and test a mobile app to deliver an audio tour, incorporating various
 augmented reality (AR) features to enhance the experience. Our app delivers a
@@
 latitude and longitude, we developed an internal tool to design physical
-regions for each step of the tour. This tool, called Editour provides a rich
+regions for each step of the tour. This tool, called Editour, provides a rich
 editing suite through a simple web interface. Section~\ref{sec:editingATour}

### 2019-10-03 paper.tex
addressed joe's changes

--- 2019-10-03 paper.tex
@@
 
-The frontend was implemented as a web app, using web technologies such as HTML,
-CSS and JavaScript, with JavaScript being the vast majority. ECMAScript is the
-standard that modern JavaScript follows.
-
-Type-checking provided by Visual Studio Code and JSDoc made the growing code
-complexity more manageable~\footnote{One helpful specification of the ECMAScript
-standard in the way of programmer sanity is ``strict mode.'' By placing the
-string \texttt{"use strict"} at the top of a JavaScript source file, errors will
-be thrown in many cases where ordinary JavaScript would not complain. The
-simplest example of this is the line \texttt{a = 1;} will not throw an error
-ordinarily. In strict mode, you must at first explicitly declare the variable
-with the \texttt{let}, \texttt{var} or \texttt{const} keyword before assigning
-it, similar to Java or C++. We included the string at the beginning of every
-source file except for class declarations, which are in strict mode by
-default~\autocite[386]{ecmainternational2019}.} . Excluding Node.js modules, the
-only external library we used for Editour was Leaflet, an open-source JavaScript
-library for interactive maps~\autocite{leafletjs}. We did not use any framework
-for developing frontends like Facebook's React or Google's Angular. Instead, all
-of the complex UI interactions were handled by modifying the DOM directly with
-JavaScript's built-in functionality. Furthermore, we did not use any advanced
-frontend build tools such as Rollup, webpack or Parcel. For a JavaScript project
-of this scope, this was the correct decision. Considering we had limited
-knowledge of React or Angular, it was also faster to develop the UI in the way
-we were used to from previous experience. But if we were to continue to develop
-Editour, UI libraries and frontend build tools would be something to consider.
+The frontend was implemented as a web application, using web technologies such
+as HTML, CSS and JavaScript, with JavaScript being the vast majority of the
+code. Type-checking provided by Visual Studio Code and JSDoc made the growing
+code complexity more manageable.\footnote{One helpful specification of the
+ECMAScript standard in the way of programmer sanity is ``strict mode.'' By
+placing the string \texttt{"use strict"} at the top of a JavaScript source file,
+errors will be thrown in many cases where ordinary JavaScript would not
+complain. The simplest example of this is the line \texttt{a = 1;} will not
+throw an error ordinarily. In strict mode, you must at first explicitly declare
+the variable with the \texttt{let}, \texttt{var}, or \texttt{const} keyword
+before assigning it, similar to Java or C++. We included the string at the
+beginning of every source file except for class declarations, which are in
+strict mode by default~\autocite[386]{ecmainternational2019}.} Excluding Node.js
+modules, the only external library we used for Editour was Leaflet, which is
+``an open-source JavaScript library for mobile-friendly interactive maps''
+according to the official Leaflet website~\autocite{leafletjs}. We did not use
+any framework for developing frontends like Facebook's React or Google's
+Angular. Instead, all of the complex UI interactions were handled by modifying
+the DOM directly with JavaScript's built-in functionality. Furthermore, we did
+not use any advanced frontend build tools such as Rollup, webpack or Parcel. For
+a JavaScript project of this scope, this was the correct decision. Considering
+we had limited knowledge of React or Angular, it was also faster to develop the
+UI in the way we were used to from previous experience. But if we were to
+continue to develop Editour, UI libraries and frontend build tools would be
+something to consider.
 
@@
 Currently, anyone can clone the GitHub repository of Editour and deploy a
-working version on a personal server. The source code for Editour is under an
-open-source license. This allows anyone to expand the frontend and backend to
-suit their needs. With additional hardware and by extending the current
+working version on a personal server. The source code for Editour is under a
+free license. This allows anyone to expand the frontend and backend to suit
+their needs. With additional hardware and by extending the current
 implementation of both the frontend and backend, Editour could be used as the
@@
 tour database that allows mobile users to take tours without the need to install
-an app. The open-source code we wrote for Editour empowers us (or anyone else)
+an app. The free code we wrote for Editour empowers us (or anyone else)
 to develop and launch this platform in the future.
@@
 
+% TODO let's triple check the name in Japanese even makes sense
 ARuko, named after the Japanese word ``\begin{CJK}{UTF8}{min}歩こ\end{CJK}''
@@
 Over the course of the project, we had to develop multiple applications in
-different languages. In total, we opened five different repositories: the blog,
-the \LaTeX~source code for our paper, the Arduino code for the heart project,
-and of course one for Editour and another for ARuko. These five repositories
-span across multiple different markup and programming languages, including C\#,
-C++, JavaScript, HTML, CSS (and the \LaTeX~markup language used to typeset this
-paper.) This gave us a welcome amount of practice using Git for version control,
-as well as GitHub's other features oriented around coordinating a team.
+different languages. In total, we created five different repositories: the blog,
+the \LaTeX~source code for our paper, the Arduino code for the heart project
+(see Appendix~\ref{sec:ritsumeikanHeartProject}) and of course one for Editour
+and another for ARuko. These five repositories span across multiple different
+markup and programming languages, including C\#, C++, JavaScript, HTML, CSS (and
+the \LaTeX~used to typeset this paper). This gave us a welcome amount of
+practice using Git for version control, as well as GitHub's other features
+oriented around coordinating a team.
 
@@
 applying this methodology as best we could. This enabled us to work together
-efficiently, track down bugs, undo mistakes, and sometimes review each other's
-code for quality when time allowed.
+efficiently, track down bugs, undo mistakes, and review each other's code for
+quality when time allowed.
 
@@
 to notify other teams that parts needed for assembly work were in short supply.
-Now, Kanban boards are integral to Agile software development. Still, some teams
+Now, Kanban boards are integral to Agile software development. Some teams still
 use physical Kanban boards, often using sticky notes and whiteboards.
@@
 when working on the project. For Editour, we tracked features and issues using
-the Issues page instead, which is discussed in
+the ``Issues'' page instead, which is discussed in
 Section~\ref{sec:editourFrontendTesting}.
@@
 
-Once we deployed Editour to a server so that Atticus could begin to use it,
-we changed the version to v1.0.0 to indicate the first release version. At this
-point, it was important that the master branch remain as stable as possible.
-Because of this, we created a ``dev'' branch where we could test experimental
-features to improve the experience and functionality of Editour. Maintaining a
-stable and experimental branch reduced the risks involved with continuing to
-iterate on the software's features post-release.
+In order to clearly indicate new versions of the software, we use ``Semantic
+Versioning'' which is a scheme for version numbers created by Tom
+Preston-Werner, cofounder of GitHub~\autocite{prestonwerner}. In this scheme,
+the full version number consists of three integers separated by periods---in
+other words, in the form \texttt{major.minor.patch}. The major version number is
+incremented when an incompatible change is made. In our case, an incompatible
+change for Editour would entail changing the format of the metadata file used to
+construct a tour such that the frontend could not interpret older tour files.
+The exception to this rule is major version 0, where the product is not
+considered stable and incompatible changes can be made at any time. When Editour
+was in this phase of development, we changed the format of the metadata; this
+would have broken previous versions but this was allowed. The minor version
+number is incremented when functionality is added but remains backwards
+compatible with previous versions. An example of this is the ``transcript''
+field we added to the metadata. The frontend was still able to load tours made
+before this additional information was added to the metadata JSON. We added many
+other features throughout the development process without breaking existing
+functionality. The patch version number is for simple bug-fixes that also do not
+break compatibility. This number gets incremented the most frequently in
+practice.
+
+Once we deployed Editour to a server so that Atticus could begin to use it, we
+changed the version to 1.0.0 to indicate the first release version. At this
+point, we were committed to not making any backwards-incompatible change. Since
+Atticus would be interacting with Editour after the release of 1.0.0, it was
+important that the master branch remain as stable as possible. Because of this,
+we created a ``dev'' branch where we could test experimental features to improve
+the experience and functionality of Editour. Maintaining a stable branch along
+with a separate experimental branch reduced the risks involved with continuing
+to iterate on the software's features post-release.
 
@@
 alike, we were able to produce an educational physical model of a heart
-controlled by an Arduino microcomputer. Noma gave us tremendous assistance with
-hardware. He taught us how to properly use the tools around the lab, and
-purchased mechanical and electrical components we would need to complete our
-task. Amano Sensei was always available to answer questions related to biology,
-and helped us understand the mathematical model we would need to implement to
-drive the physical model with software. We worked on this project every
-Wednesday, completing the final model during the last week of our stay.
+controlled by an Arduino microcomputer. Noma Sensei gave us tremendous
+assistance with hardware. He taught us how to properly use the tools around the
+lab, and purchased mechanical and electrical components we would need to
+complete our task. Amano Sensei was always available to answer questions related
+to biology, and helped us understand the mathematical model we would need to
+implement to drive the physical model with software. We worked on this project
+every Wednesday, completing the final model during the last week of our stay.
 % TODO get the full name of Amano Sensei
@@
 seen in Figure~\ref{fig:referenceModel}. We were also provided with source code
-for an implementation of this model. We would still need to modify this code to
-calculate the output variables we would need to properly operate the physical
-model, and integrate the model into the main loop of the Arduino source code
-with the appropriate timing.
+for an implementation of this model in C. We would still need to modify this
+code to calculate the output variables we would need to properly operate the
+physical model, and integrate the model into the main loop of the Arduino source
+code with the appropriate timing.
 
@@
 
-With Noma Sensei as our guide, we visited ``Den Den Town'' in Osaka in order to
-gather supplies we would need in order to construct the heart. One of the most
-important purchases of this trip was a two-meter long strip of Adafruit NeoPixel
-light emitting diodes (LEDs). The design of this reel of LEDs enabled us to cut
-the strip at specific points to create shorter strips. Each LED on the strip
-individually addressable, allowing us to set the color of any LED along the
-strip. This perfectly suited our needs for representing blood flow.
+With Noma Sensei as our guide, we visited ``Den-Den Town'' or Nipponbashi in
+Osaka in order to gather supplies we would need in order to construct the heart.
+One of the most important purchases of this trip was a two-meter long strip of
+Adafruit NeoPixel light emitting diodes (LEDs). The design of this reel of LEDs
+enabled us to cut the strip at specific points to create shorter strips. Each
+LED on the strip individually addressable, allowing us to set the color of any
+LED along the strip. This perfectly suited our needs for representing blood
+flow.
 
@@
 
-Not only can the GUI communicate with the Arduino; the Arduino can relay
+Not only can the GUI communicate with the Arduino; the Arduino can also relay
 information about the state of the model back to the GUI. The length of blue bar

### 2019-10-03 paper.tex
added some comments for good places to put more images

--- 2019-10-03 paper.tex
@@
 the app attempts to translate text as quickly as possible, superimposing the
-translated text onto the real world using the camera. In ``scan'' mode, the user
-first takes a photo. Then, the user is prompted to highlight where text appears
-in the photo. After the translation is complete, the translated text appears in
-a separate UI element instead superimposed onto the photo. In most cases, it is
-more convenient and readable to have the translation appear in a separate
-scrollable text box. This motivated the current design of the ``info buttons''
-in ARuko. Instead of placing text directly onto signage, we place a blue button
-with a stylized `i' in the center. By tapping on this button, a separate UI
-element will appear containing the translated text. Since this button is cast
-into the world using the AR camera, the button appears to be placed directly
-onto the content in the real world.
+translated text onto the real world using the camera. %could put an image of instant mode here as an example
+In ``scan'' mode, the user first takes a photo. Then, the user is prompted to 
+highlight where text appears in the photo. %could put an example here as well
+After the translation is complete, the translated text appears in a separate UI %another example?
+element instead superimposed onto the photo. In most cases, it is more 
+convenient and readable to have the translation appear in a separate scrollable
+text box. This motivated the current design of the ``info buttons'' in ARuko. 
+Instead of placing text directly onto signage, we place a blue button with a 
+stylized `i' in the center. By tapping on this button, a separate UI element 
+will appear containing the translated text. Since this button is cast into the %example
+world using the AR camera, the button appears to be placed directly onto the 
+content in the real world.
 
@@
 audio playing with the phone in your pocket. Atticus insisted that this sort of
-feature was required so that users could listen to the audio tour without using
+feature was required so that users could listen to the audio tour without using %maybe include an image of pocket mode here
 any of the other functionality the app provides, like the image gallery in each
@@
 we didn't want all of the extra components of the original NOxAR project to
-get in the way of what we were trying to do. We also did this because the 
+get in the way of what we were trying to do. We also did this because the %could probably put an example pic here
 original project was made with a 2017 version of Unity, so we wanted to try to

### 2019-10-03 paper.tex

--- 2019-10-03 paper.tex
@@
 \end{figure}
+
+\subsection{Alterniative Uses for AR in ARuko}
+\label{sec:alternativeARukoAR}
+
+Even once the idea for ARuko was settled on audio tour functionality with 
+additional AR components, what exactly those AR components would do was still
+undecided for a while. Atticus knew he wanted to use AR on the tour, but wasn't
+sure what to do with it. At first, we made recommendations to him based on the
+capabilities of Vuforia that we found in our research. We knew it was good at
+image recognition and ground plane recognition, so we suggested that maybe 
+displaying some sorts of 3D models in certain locations using either of these
+features might be an interesting way to expand on the tour. With these 
+recommendations in mind, Atticus expressed interest in the capability of using
+building facades as image targets. The intention then would be to tie content
+related to a specific location within Kinkaku-ji to that physical location, and
+use images of the location as targets. As previously explained, this ultimately
+did not work out due to the limitations of image recognition with Vuforia.
+
+After being initially deterred from image recognition, we thought that ground
+and mid-air plane recognition might the best way to implement AR in the app. 
+It didn't have to rely on images that meet Vuforia's criteria, and since it 
+could be triggered anywhere, it seemed like a good fit for an app focusing on
+walking around a site. Atticus explained that he primarily wanted to use AR to
+display art related to the site. So we focused our efforts with ground and 
+mid-air plane AR on ways to display 2D images. What we ended up creating first
+was a feature that allowed you to view certain images in AR, using ground plane
+detection, based on what region you were in. So when you entered a region of 
+the tour, the image menu would be dynamically populated with buttons that, when
+tapped, would create a Plane primitive in Unity with the given image displayed
+on it and place it on the ground plane.
+
+We encountered a few notable problems with this though. One problem was that 
+the Plane we made was always the same size and dimensions, and would cause 
+images to stretch to fit the plane. Further testing to change the size of the
+plane with each picture proved difficult. Additionally, using a Plane primitive
+had problematic effects on the way the object was lit in the Unity scene, as 
+well as how it appeared when not viewed head-on. If viewed from an angle, the 
+picture could become very dark and difficult to see. And if viewed from behind,
+it would actually be completely invisible. Because of these issues, we decided
+to place the images on a 3D Cube primitive instead. But after showing this
+feature to Atticus during early testing at Kinkaku-ji, he decided that he 
+wanted to move away from displaying images in AR. Looking back, the feature
+may have worked better with mid-air plane recognition so that the user could
+place the image directly in front of them.
+
+In addition to the previously mentioned use cases for AR in ARuko, Atticus also
+expressed interest in using AR to trigger video content. He was particularly
+interested in 3D videos triggerable through AR. As the scope of the project 
+grew, and time ran short, the task of including 3D videos triggered by AR 
+seemed more and more complicated, causing that idea to be phased out of the
+final project. Additionally, we never received any assets from Atticus to use
+for this feature, thus preventing us from spending time developing it.
 
@@
 
+\section{NOxAR Assignment}
+\label{sec:NOxAR}
+
+On Monday, September 9th, Atticus approached us about an additional project he 
+wanted us to tackle. He wanted us to adapt Kyoto VR's NOxAR app to use ground
+plane detection. Currently, the NOxAR app is an AR app for Microsoft Hololens
+that uses image targets with Vuforia. When viewing the correct image target,
+the app projects a 3D model of a Noh Theater\footnote{A form of Japanese 
+theater originating in the 14th century structured around song and slow 
+dancing~\autocite{japanguide2018}.} performer dancing to background 
+music~\autocite{noxar2018}. What Atticus wanted us to do was have the app use 
+ground plane detection in order to display the Noh performer so that it could 
+be displayed anywhere. Additionally, he wanted us to scale up the model so that
+when displayed in AR, the performer would appear life-sized, as if she were 
+really there dancing in the real world.
+
+For this project, Atticus sent us the original Unity project files for NOxAR.
+We then had to figure out how to turn the original project into a ground plane
+AR app. At first we tried importing the assets for the Noh performer into a new
+Unity project. We did this for a couple reasons. The first reason was because
+we didn't want all of the extra components of the original NOxAR project to
+get in the way of what we were trying to do. We also did this because the %could probably put an example pic here
+original project was made with a 2017 version of Unity, so we wanted to try to
+use our more recent version so we wouldn't risk running into any depricated 
+features or functionalities. We did eventually get this method to work, but the
+model of the Noh performer was lacking a lot of the details that the original 
+model had. This was attributed to poor importation of the original assets, so 
+we decided to try making changes to the original NOxAR project instead.
+
+Per Atticus's advice, we deleted any and all unnecessary elements from the 
+scene before proceeding. We also updated the Unity version of the project to
+the 2019 version we were using, and updated the version of Vuforia to the most
+recent version, neither of which created any problems. The process of getting
+the model to appear on ground plane detection instead of image target 
+recognition was relatively simple. We simply moved the model from an image 
+target to a simulated ground plane, added a plane detector component to the
+scene, and made sure the Vuforia settings were in place for ground plane
+detection to work well. From there, we just had to test the app a few times so
+we could properly scale the model to life size. So on Tuesday, September 17th, 
+we completed the NOxAR ground plane adaptation to Atticus's saisfaction and
+sent him the final APK file for the app.
+
 \end{document}

### 2019-10-03 paper.tex
made requested changes

--- 2019-10-03 paper.tex
@@
 additional AR components, what exactly those AR components would do was still
-undecided for a while. Atticus knew he wanted to use AR on the tour, but wasn't
-sure what to do with it. At first, we made recommendations to him based on the
-capabilities of Vuforia that we found in our research. We knew it was good at
-image recognition and ground plane recognition, so we suggested that maybe 
-displaying some sorts of 3D models in certain locations using either of these
-features might be an interesting way to expand on the tour. With these 
-recommendations in mind, Atticus expressed interest in the capability of using
-building facades as image targets. The intention then would be to tie content
-related to a specific location within Kinkaku-ji to that physical location, and
-use images of the location as targets. As previously explained, this ultimately
-did not work out due to the limitations of image recognition with Vuforia.
+undecided until more details about the project crystallized. Atticus knew he 
+wanted to use AR on the tour, but was not sure what to do with it. At first, we
+made recommendations to him based on the capabilities of Vuforia that we found 
+in our research. We knew it was good at image recognition and ground plane 
+recognition, so we suggested that maybe displaying some sorts of 3D models in 
+certain locations using either of these features might be an interesting way to
+expand on the tour. With these recommendations in mind, Atticus expressed 
+interest in the capability of using building facades as image targets. The 
+intention then would be to tie content related to a specific location within 
+Kinkaku-ji to that physical location, and use images of the location as 
+targets. As previously explained, this ultimately did not work out due to the 
+limitations of image recognition with Vuforia.
 
@@
 and mid-air plane recognition might the best way to implement AR in the app. 
-It didn't have to rely on images that meet Vuforia's criteria, and since it 
+It did not have to rely on images that meet Vuforia's criteria, and since it 
 could be triggered anywhere, it seemed like a good fit for an app focusing on
 walking around a site. Atticus explained that he primarily wanted to use AR to
-display art related to the site. So we focused our efforts with ground and 
-mid-air plane AR on ways to display 2D images. What we ended up creating first
-was a feature that allowed you to view certain images in AR, using ground plane
-detection, based on what region you were in. So when you entered a region of 
-the tour, the image menu would be dynamically populated with buttons that, when
-tapped, would create a Plane primitive in Unity with the given image displayed
-on it and place it on the ground plane.
+display art related to the site. With this in mind, we focused our efforts with
+ground and mid-air plane AR on ways to display 2D images. What we ended up 
+creating first was a feature that allowed users to view certain images in AR, 
+using ground plane detection, based on what region you were in. When users 
+entered a region of the tour, the image menu would be dynamically populated 
+with buttons that, when tapped, would create a Plane primitive in Unity with 
+the given image displayed on it and place it on the ground plane.
 
@@
 well as how it appeared when not viewed head-on. If viewed from an angle, the 
-picture could become very dark and difficult to see. And if viewed from behind,
-it would actually be completely invisible. Because of these issues, we decided
-to place the images on a 3D Cube primitive instead. But after showing this
-feature to Atticus during early testing at Kinkaku-ji, he decided that he 
-wanted to move away from displaying images in AR. Looking back, the feature
-may have worked better with mid-air plane recognition so that the user could
-place the image directly in front of them.
+picture could become very dark and difficult to see. If viewed from behind,
+back-face culling would take effect and the plane would become completely 
+invisible. Because of these issues, we decided to place the images on a 3D Cube
+primitive instead. But after showing this feature to Atticus during early 
+testing at Kinkaku-ji, he decided that he wanted to move away from displaying 
+images in AR. Looking back, the feature may have worked better with mid-air 
+plane recognition so that the user could place the image directly in front of 
+them.
 
@@
 
-On Monday, September 9th, Atticus approached us about an additional project he 
+On Monday, September 9\textsuperscript{th}, Atticus approached us about an additional project he 
 wanted us to tackle. He wanted us to adapt Kyoto VR's NOxAR app to use ground
@@
 that uses image targets with Vuforia. When viewing the correct image target,
-the app projects a 3D model of a Noh Theater\footnote{A form of Japanese 
+the app projects a 3D model of a noh theater\footnote{A form of Japanese 
 theater originating in the 14th century structured around song and slow 
 dancing~\autocite{japanguide2018}.} performer dancing to background 
-music~\autocite{noxar2018}. What Atticus wanted us to do was have the app use 
-ground plane detection in order to display the Noh performer so that it could 
+music~\autocite{noxar2018}. What Atticus wanted was to have the app use 
+ground plane detection in order to display the noh performer so that it could 
 be displayed anywhere. Additionally, he wanted us to scale up the model so that
-when displayed in AR, the performer would appear life-sized, as if she were 
-really there dancing in the real world.
+when displayed in AR, the performer would appear life-sized.
 
@@
 We then had to figure out how to turn the original project into a ground plane
-AR app. At first we tried importing the assets for the Noh performer into a new
+AR app. At first we tried importing the assets for the noh performer into a new
 Unity project. We did this for a couple reasons. The first reason was because
-we didn't want all of the extra components of the original NOxAR project to
+we did not want all of the extra components of the original NOxAR project to
 get in the way of what we were trying to do. We also did this because the %could probably put an example pic here
 original project was made with a 2017 version of Unity, so we wanted to try to
-use our more recent version so we wouldn't risk running into any depricated 
+use our more recent version so we would not risk running into any depricated 
 features or functionalities. We did eventually get this method to work, but the
-model of the Noh performer was lacking a lot of the details that the original 
+model of the noh performer was lacking a lot of the details that the original 
 model had. This was attributed to poor importation of the original assets, so 
@@
 detection to work well. From there, we just had to test the app a few times so
-we could properly scale the model to life size. So on Tuesday, September 17th, 
+we could properly scale the model to life size. On Tuesday, September 17th, 
 we completed the NOxAR ground plane adaptation to Atticus's saisfaction and

### 2019-10-03 paper.tex
up to page 22 of minor edits

@@
 displays galleries of art throughout the visit, and offers accessibility
-features through AR. We hope our app will enhance the experience of visiting
+features through AR. We also developed a tool to aid in the design and creation
+of audio tours. We hope our app will enhance the experience of visiting
 Kinkaku-ji.  
@@
 
+% TODO is starting with "A special thank you" a complete clause?
 We would also like to thank Inoue Hikaru for his help with translations and
@@
 
-Since our app had to deliver an audio tour supplemented by images based on your
-latitude and longitude, we developed an internal tool to design physical
+Since our app had to deliver an audio tour supplemented by images based on the
+user's latitude and longitude, we developed an internal tool to design physical
 regions for each step of the tour. This tool, called Editour, provides a rich
@@
 and novel way. Many AR apps require specific markers, like the those shown in
-Figure~\ref{fig:arMarker}. Too avoid needing to place any physical object that
-would disturb the buildings or grounds of a historic site our app does not rely
+Figure~\ref{fig:arMarker}. To avoid the need to place any physical object that
+would disturb the buildings or grounds of a historic site, our app does not rely
 on these markers. Instead, ARuko recognizes images of objects that are already
@@
 as a tool for digitally enhancing the physical world. In this section we explain
-the origins and uses of some of this technology.
+the origins and uses of this technology.
 
@@
 appealing than a purely virtual environment. This provides the user with useful
-information without needing to alter a real historic site.
+information without needing to alter the physical historic site.
 
@@
 
-Even though it is still a developing technology, AR has been used in many
+Even though AR is still a developing technology, it has been used in many
 disparate disciplines, including data visualization~\autocite{resnick2017},
@@
 uses its AR feature to place a Pokémon on top of a camera's video feed.
-Disappointingly, it does not interact with anything around it. It just floats a
-fixed distance away from the user.
+Disappointingly, the Pokémon does not interact with anything around it. It just
+floats a fixed distance away from the user.
 
@@
 hardware like the HoloLens is very inaccessible and expensive; Microsoft only
-offers developer editions of the HoloLens, and for the incredibly steep price
-of \$3,500~\autocite{microsoft2019}.
+offers developer editions of the HoloLens, and for the steep price of
+\$3,500~\autocite{microsoft2019}.
 
@@
 initial apprehension, we believe the way we have integrated AR into our app
-enhances the user experience. Hardware issues were definitely our biggest
-challenge. Only one member of our team had a phone new enough to run AR
-technology at a decent level, making testing of our application difficult.
+enhances the user experience. One of our largest challenges came from the lack
+of hardware on which to test. Only one member of our team had a phone new enough
+to run AR technology at a decent level, making testing of our application
+difficult.
 
@@
 
-Before our project started, Kyoto~VR was already using an app to deliver audio
+Before our project had begun, Kyoto~VR was already using an app to deliver audio
 tours. The app, called izi.TRAVEL, allows users to create audio tours with
@@
 learned there are many powerful platforms available. There were many things we
-needed to consider before deciding on a platform. These considerations included
-what features the platform offered, which devices and operating systems the app
-could run on, and the cost. Detailed below are some of the different platforms
-we considered.
+needed to consider before deciding on a platform---considerations such as what
+features the platform offered, which devices and operating systems the app could
+run on, and the cost. Detailed below are some of the different platforms and
+technologies we considered.
 
@@
 many registered developers considering the list of features the platform
-offers. Some of the features that appealed most to us were their ``Instant
+offers. Some of the features that most appealing to us were their ``Instant
 Tracking,'' allowing for augmentation using flat surfaces; ``Image Tracking,''
@@
 website, their SDK works with Windows, Android, and iOS development frameworks,
-as well as ARCore and ARKit, Flutter, Cordova, Xamarin, and even Unity.
+as well as ARCore and ARKit, Flutter, Cordova, Xamarin, and Unity.
 
@@
 
-Viro AR comes in two versions: ViroReact and ViroCore\autocite{facebook2019}.
+Viro AR comes in two versions: ViroReact and ViroCore~\autocite{viro2019}.
 ViroCore allows developers to build an AR Application with Java. The
 disadvantage of this is that ViroCore only allows developers to target Android,
-which unfortunately made ViroCore not an option for our project. ViroReact is
-the cross-platform option for ViroAR. ViroReact leverages the cross-platform
-capabilities of React, which is Facebook's JavaScript Library for developing
-user interfaces~\autocite{facebook2019}.
+which unfortunately made ViroCore not an option for our project; one of the
+requirements from our sponsor was that the app had to be cross-platform.
+ViroReact is the cross-platform option for ViroAR. ViroReact leverages the
+cross-platform capabilities of React, which is Facebook's JavaScript Library for
+developing user interfaces~\autocite{facebook2019}.
 
@@
 application development''~\autocite{viro2019}. While the majority of our team
-has decent experience with writing JavaScript, we have have very little experience
-writing React apps.
+has decent experience with writing JavaScript, we have have very little
+experience writing React apps.
 
@@
 An alternative to building an app for a physical phone is to run it through an
-emulator on a computer.
-
-According to Techopedia, ``Emulation is the process of imitating a
-hardware/software program/platform on another program or platform. This makes
-it possible to run programs on systems not designed for
+emulator on a computer. According to Techopedia, ``Emulation is the process of
+imitating a hardware/software program/platform on another program or platform.
+This makes it possible to run programs on systems not designed for
 them''~\autocite{techopedia2019}. Emulators are often very useful for speeding
@@
 emulation. Secondly, and most importantly for AR, it is common for emulation to
-be much slower compared to real hardware.
-
-In a question submitted to \textit{Compute!} magazine asking whether it is
-possible for a Commodore 64 to emulate MS-DOS, the editor responded ``Yes, it's
-possible for a 64 to emulate an IBM PC, in the same sense that it's possible to
-bail out Lake Michigan with a teaspoon.'' The editor goes on to explain
-``Emulation is a complex business, but here's one rule of thumb: The only way
-to successfully emulate a machine is with a much more powerful
-machine''~\autocite{warick1988}. In our case, emulating Android on a desktop
-operating system is closer to emulating a C64 on an IBM PC running MS-DOS
-(rather than the other way around, thankfully). The takeaway is that the speed
-problem facing emulators is just as real as it was in 1988. Considering that AR
-already pushes modern phone hardware to the limit, emulation is not something we
-wanted to struggle with. On top of this, our testing required us to move the
-camera through the world at various speeds and angles, which is simply
-cumbersome with a laptop webcam.
-
-As an alternative to emulation, ViroReact offers a convenient ``test bed'' for
-rapidly testing your ViroReact app on native hardware without the need for an
-emulator. This allowed us to get a real AR app up and running on our devices
-much more easily than any of the other frameworks/engines we explored.
-Unfortunately, the test bed app was somewhat unreliable based on our
-experience; the test bed would frequently crash or would not be able to
-download the files from the server. The most reliable way to test our app was
-to compile a binary and manually install it onto our devices, which completely
-defeated the purpose of the test bed app.
+be much slower compared to real hardware.\footnote{In a question submitted to
+\textit{Compute!} magazine asking whether it is possible for a Commodore 64 to
+emulate MS-DOS, the editor responded ``Yes, it's possible for a 64 to emulate an
+IBM PC, in the same sense that it's possible to bail out Lake Michigan with a
+teaspoon.'' The editor goes on to explain ``Emulation is a complex business, but
+here's one rule of thumb: The only way to successfully emulate a machine is with
+a much more powerful machine''~\autocite{warick1988}. In our case, emulating
+Android on a desktop operating system is closer to emulating a C64 on an IBM PC
+running MS-DOS (rather than the other way around, thankfully). The takeaway is
+that the speed problem facing emulators is just as real as it was in 1988.}
+Considering that AR already pushes modern phone hardware to the limit, emulation
+is not something we wanted to struggle with. On top of this, our testing
+required us to move the camera through the world at various speeds and angles,
+which is simply cumbersome with a laptop webcam.
+
+As an alternative to emulation or compiling a native binary, ViroReact offers a
+convenient ``test bed'' for rapidly testing your ViroReact app on native
+hardware without the need for an emulator. This allowed us to launch a working
+AR app on our devices much more easily than any of the other frameworks or
+engines we explored. Unfortunately, the test bed app was somewhat unreliable
+based on our experience; the test bed would frequently crash or would not be
+able to download the files from the server. The most reliable way to test our
+app was to compile a binary and manually install it onto our devices, which
+completely defeated the purpose of the test bed app.
 
@@
 Unity is a game engine that was originally introduced in
-2005~\autocite{axon2016}. Because of the low barrier to entry---knowledge-wise
+2005~\autocite{axon2016}. Because of the low barrier to entry---experience-wise
 and price-wise---the engine quickly became incredibly popular. Ironically,
-because the engine is so accessible that, Unity has faced a degree of critism.
+because the engine is so accessible, Unity has faced a degree of critism.
 Because Unity appeals to so many beginners, there are many unpolished games that
 bear the Unity logo. In response to this sentiment, Marcos Sanchez, head of
-global communications at Unity, "Democratizing development---in our minds, we
-don't think is the wrong thing, we think it's the right thing. You want more
+global communications at Unity, said "Democratizing development---in our minds,
+we don't think is the wrong thing, we think it's the right thing. You want more
 people understanding, and everyone’s gotta start somewhere"~\autocite{axon2016}.
@@
 object-oriented language~\autocite{ecmainternational2017}. Even though none of
-us had extensive experience with C\# prior to this project, this was not a great
-concern since C\# is similar to other object-oriented languages such as Java and
-C++. The design goals of the language were also appealing to us; C\# includes
-features important for programmer productivity such as strong type checking
-(unlike JavaScript), detection of using uninitialized variables (also unlike
-JavaScript,) range checking for array bounds (unlike C) and garbage collection.
-At the same time, our lack of familiarity with the language and Unity as a whole
-is another reason we first looked into cross-platform AR solutions that did not
-use Unity.
+us had extensive experience with C\# prior to this project, this was not of
+great concern since C\# is similar to other object-oriented languages such as
+Java and C++. The design goals of the language were also appealing to us; C\#
+includes features important for programmer productivity such as strong type
+checking (unlike JavaScript), detection of using uninitialized variables (also
+unlike normal JavaScript,) range checking for array bounds (unlike C) and
+garbage collection. At the same time, our lack of familiarity with the language
+and Unity as a whole is another reason we first looked into cross-platform AR
+solutions that did not use Unity.
 %TODO see if we need more sources for this
@@
 
-In this section we discuss and implementation of ARuko and Editour, including
-the technologies and techniques involved in creating both of them. We also
-discuss the design decisions we made and some of the challenges we faced in
+In this section we discuss the implementation of ARuko and Editour, which are
+the names for the mobile AR mobile app and web-based tour editor respectively.
+We also discuss the technologies and techniques involved in creating both of
+them, along with the the design decisions we made and challenges we faced in
 creating these applications.
@@
 The first subcard seen in Figure~\ref{fig:renameSubcard} is the ``Rename''
-subcard, which is fairly self-explanatory.  This section expands to reveal a
-textbox, allowing the user to rename the region after clicking ``Okay'' or
-hitting the enter key.\footnote{There are multiple places in the UI where a
-textbox is immediately adjacent to a ``Confirm'' button.  We made sure all of
-these can be triggered by simply hitting enter, since this is common behavior
-when filling out forms on the web.}
+subcard. This section expands to reveal a textbox, allowing the user to rename
+the region after clicking ``Okay'' or hitting the enter key.\footnote{There are
+multiple places in the UI where a textbox is immediately adjacent to a
+``Confirm'' button.  We made sure all of these can be triggered by simply
+hitting enter, since this is common behavior when filling out forms on the web.}
 
@@
 
-The second subcard seen in Figure~\ref{fig:mediaSubcard} is slightly more
-involved. Expanding the ``Media'' subcard by clicking on the green bar will
-reveal a bevy of options for augmenting the audio, images, and text to be
-associated with that region of the tour. From here, the user can upload an
-audio file and multiple image files from his or her hard drive with the two
-file-select fields. If the user is editing an existing tour that has already
-been uploaded, the names of the files already present on the server will appear
-as cards with `X' buttons. This allows the user to remove images or audio from
-that region even after the tour has been uploaded.
+The second subcard seen in Figure~\ref{fig:mediaSubcard} is more involved.
+Expanding the ``Media'' subcard by clicking on the green bar will reveal a bevy
+of options for augmenting the audio, images, and text to be associated with that
+region of the tour. From here, the user can upload an audio file and multiple
+image files from the user's hard drive with the two file-select fields. If the
+user is editing an existing tour that has already been uploaded, the names of
+the files already present on the server will appear as cards with `X' buttons.
+This allows the user to remove images or audio from that region even after the
+tour has been uploaded.
 
@@
 
-The third subcard is the ``Points'' subcard. This subcard can be revealed in
-one of two ways. The first way is by clicking on the yellow bar labeled
-``Points'', which is the same for all subcards. Alternatively, the user can
-click directly on the region on the map. The region will flash yellow and be
-scrolled into view to let the user know which region was clicked on. Both of
-these methods will enable editing mode, whereby the user can directly
-manipulate the vertices that make up the region. Blue circles appear on top of
-each vertex, and red circles appear at the midpoint of each edge. Clicking on a
-red midpoint will add an additional vertex at that midpoint. Dragging one of
-the blue vertices will move the vertex around. The latitude and longitude are
-updated in the ``Points'' subcard as the user drags the vertex around. Clicking
-on the vertex directly will create a blue pin-shaped marker that the user can
-also drag. Clicking on the coordinate box in the subcard will also create this
-blue pin-shaped marker; the map will also pan to this coordinate. The user can
-also delete vertices in the same way that files can be deleted from the
-``Media'' subcard by clicking on the `X' button on that vertex's coordinate
-card. If there are exactly three points in a region, the `X' buttons will be
-``grayed-out,'' preventing the user from deleting any more points, since a
-polygon must consist of at least three points.
+The third subcard is the ``Points'' subcard. This subcard can be revealed in one
+of two ways. The first way is by clicking on the yellow bar labeled ``Points'',
+which is the same for all subcards. Alternatively, the user can click directly
+on the region on the map. The region will flash yellow and be scrolled into view
+to let the user know which region was clicked on. Both of these methods will
+enable editing mode, whereby the user can directly manipulate the vertices that
+make up the region. Blue circles appear on top of each vertex, and red circles
+appear at the midpoint of each edge. Clicking on a red midpoint will add an
+additional vertex at that midpoint. Dragging one of the blue vertices will move
+the vertex around. The latitude and longitude are updated in the ``Points''
+subcard as the user moves the vertex. Clicking on the vertex directly will
+create a blue pin-shaped marker that the user can also drag. Clicking on the
+coordinate box in the subcard will also create this blue pin-shaped marker; the
+map will also pan to this coordinate. The user can also delete vertices in the
+same way that files can be deleted from the ``Media'' subcard by clicking on the
+`X' button on that vertex's coordinate card. If there are exactly three points
+in a region, the `X' buttons will be ``grayed-out,'' preventing the user from
+deleting any more points, since a polygon must consist of at least three points.
 
@@
 labeled ``Don't Delete!'' This prevents the user from accidentally deleting a
-region he or she did not mean to remove.
+region unintentionally.
 
@@
 
-%update this figure
+% TODO update this figure
 \begin{figure}[h]
@@
 we had limited knowledge of React or Angular, it was also faster to develop the
-UI in the way we were used to from previous experience. But if we were to
+UI in the way we were used to from previous experience, but if we were to
 continue to develop Editour, UI libraries and frontend build tools would be
@@
 
+% TODO explain what stateless operations are
 The backend implements a representational state transfer (REST) API.
@@
 browser, using the geolocation API to access the user's location (if the user
-grants permission.) This kind of infrastructure would allow users to access an
+grants permission). This kind of infrastructure would allow users to access an
 audio tour---supplemented by images and audio transcripts---without the need to
@@
 working version on a personal server. The source code for Editour is under a
-free license. This allows anyone to expand the frontend and backend to suit
-their needs. With additional hardware and by extending the current
-implementation of both the frontend and backend, Editour could be used as the
-groundwork to create an entire crowd-sourced walking tour platform, allowing
-users to design tours for others to take.
+free license, namely the GNU General Public License. This allows anyone to
+expand the frontend and backend to suit their needs. With additional hardware
+and by extending the current implementation of both the frontend and backend,
+Editour could be used as the groundwork to create an entire crowd-sourced
+walking tour platform, allowing users to design tours for others to take.
 
@@
 
+% TODO include photos of the google translation app including our own app
 ARuko uses augmented reality to translate text at the site as well. While AR
@@
 the app attempts to translate text as quickly as possible, superimposing the
-translated text onto the real world using the camera. %could put an image of instant mode here as an example
-In ``scan'' mode, the user first takes a photo. Then, the user is prompted to 
-highlight where text appears in the photo. %could put an example here as well
-After the translation is complete, the translated text appears in a separate UI %another example?
-element instead superimposed onto the photo. In most cases, it is more 
-convenient and readable to have the translation appear in a separate scrollable
-text box. This motivated the current design of the ``info buttons'' in ARuko. 
-Instead of placing text directly onto signage, we place a blue button with a 
-stylized `i' in the center. By tapping on this button, a separate UI element 
-will appear containing the translated text. Since this button is cast into the %example
-world using the AR camera, the button appears to be placed directly onto the 
-content in the real world.
+translated text onto the real world using the camera. In ``scan'' mode, the user
+first takes a photo. Then, the user is prompted to highlight where text appears
+in the photo. After the translation is complete, the translated text appears in
+a separate UI element instead superimposed onto the photo. In most cases, it is
+more convenient and readable to have the translation appear in a separate
+scrollable text box. This motivated the current design of the ``info buttons''
+in ARuko. Instead of placing text directly onto signage, we place a blue button
+with a stylized `i' in the center. By tapping on this button, a separate UI
+element will appear containing the translated text. Since this button is cast
+into the world using the AR camera, the button appears to be placed directly
+onto the content in the real world.
 
@@
 
+\clearpage
+
 \section{NOxAR Assignment}
@@
 
-On Monday, September 9\textsuperscript{th}, Atticus approached us about an additional project he 
-wanted us to tackle. He wanted us to adapt Kyoto VR's NOxAR app to use ground
-plane detection. Currently, the NOxAR app is an AR app for Microsoft Hololens
-that uses image targets with Vuforia. When viewing the correct image target,
-the app projects a 3D model of a noh theater\footnote{A form of Japanese 
-theater originating in the 14th century structured around song and slow 
-dancing~\autocite{japanguide2018}.} performer dancing to background 
-music~\autocite{noxar2018}. What Atticus wanted was to have the app use 
-ground plane detection in order to display the noh performer so that it could 
-be displayed anywhere. Additionally, he wanted us to scale up the model so that
+On Monday, September 9\textsuperscript{th}, Atticus approached us about an
+additional project he wanted us to tackle. He wanted us to adapt Kyoto VR's
+NOxAR app to use ground plane detection. Currently, the NOxAR app is an AR app
+for Microsoft Hololens that uses image targets with Vuforia. When viewing the
+correct image target, the app projects a 3D model of a noh theater\footnote{A
+form of Japanese theater originating in the 14th century structured around song
+and slow dancing~\autocite{japanguide2018}.} performer dancing to background
+music~\autocite{noxar2018}. What Atticus wanted was to have the app use ground
+plane detection in order to display the noh performer so that it could be
+displayed anywhere. Additionally, he wanted us to scale up the model so that
 when displayed in AR, the performer would appear life-sized.

### 2019-10-03 paper.tex
fixed most appealing

@@
 
-Wikitude is another major AR development kit that is very prevalent in the
-world of AR development. It has over 130,000 registered AR developers, and is
-powering over 30,000 AR apps across smartphones, tablets, and smart
+Wikitude is another major AR development kit that is very prevalent in the world
+of AR development. It has over 130,000 registered AR developers, and is powering
+over 30,000 AR apps across smartphones, tablets, and smart
 glasses~\autocite{wikitude2018}. It is easy to understand why Wikitude has so
-many registered developers considering the list of features the platform
-offers. Some of the features that most appealing to us were their ``Instant
+many registered developers considering the list of features the platform offers.
+Some of the features that were most appealing to us were their ``Instant
 Tracking,'' allowing for augmentation using flat surfaces; ``Image Tracking,''

### 2019-10-03 paper.tex
fixed HoloLens
added nbs to kyoto vr

@@
 
-Our team worked directly under Kyoto VR founder and CEO Atticus Sims to develop
+Our team worked directly under Kyoto~VR founder and CEO Atticus Sims to develop
 and test a mobile app to deliver an audio tour, incorporating various
@@
 Furthermore, we foresee Editour being a useful tool outside of the app we
-designed for Kyoto VR. The design of the Editour is agnostic about how the media
+designed for Kyoto~VR. The design of the Editour is agnostic about how the media
 will be used. For an app like izi.TRAVEL, the images are displayed when the
@@
 Our team is satisfied with the final result of this project, as we feel we have
-built a working platform that Kyoto VR will easily be able to build off of in
+built a working platform that Kyoto~VR will easily be able to build off of in
 the future. This section contains our final thoughts on the project and future
@@
 On Monday, September 9\textsuperscript{th}, Atticus approached us about an
-additional project he wanted us to tackle. He wanted us to adapt Kyoto VR's
+additional project he wanted us to tackle. He wanted us to adapt Kyoto~VR's
 NOxAR app to use ground plane detection. Currently, the NOxAR app is an AR app
-for Microsoft Hololens that uses image targets with Vuforia. When viewing the
+for Microsoft HoloLens that uses image targets with Vuforia. When viewing the
 correct image target, the app projects a 3D model of a noh theater\footnote{A

### 2019-10-03 paper.tex
finish second draft

@@
 \title{%
-	\huge ARuko and Editour: \\
-	\Large A Platform for Augmented Reality Tour Guide Apps}
+	ARuko and Editour: \\
+	A Platform for Augmented Reality Tour Guide Apps}
 \author{William~Campbell, Cole~Granof, and Joseph~Petitti}
@@
 	{\huge ARuko and Editour: \\
+		\vspace{.5\baselineskip}
 		\Large A Platform for Augmented Reality Tour Guide Apps
@@
 was decided by our project sponsor, who plans to monetize the app. We also
-worked with an IQP team, who had been tasked with exploring funding options and
-creating promotional content.
+worked with an Interactive Qualifying Project (IQP) team, who had been tasked
+with exploring funding options and creating promotional content.
 
@@
 In most app development scenarios, to test the app on actual hardware, it must
-be compiled using either Xcode or Android Studio depending on your platform.
-Once you have built the app, your device needs to install the app. This process
-can be very time consuming, especially when needing to run frequent tests on
-the target platform.
+be compiled using either Xcode or Android Studio depending on the target
+platform. Once you have built the app, it must be installed on the device. This
+process can be very time consuming, especially when needing to run frequent
+tests on the target platform.
 
@@
 As an alternative to emulation or compiling a native binary, ViroReact offers a
-convenient ``test bed'' for rapidly testing your ViroReact app on native
+convenient ``test bed'' for rapidly testing ViroReact apps on native
 hardware without the need for an emulator. This allowed us to launch a working
@@
 on an old Dell rack server in Worcester, Massachusetts. We wrote a custom
-systemd service to run the Editour as a daemon and keep its log files organized.
-The Node.js backend was served by an Nginx reverse proxy running on the same
-virtual machine.
+systemd service to run Editour as a daemon and keep its log files organized. The
+Node.js backend was served by an Nginx reverse proxy running on the same virtual
+machine.
 
@@
 asked Atticus to provide a more powerful---and geographically closer---hosting
-solution for running the Editour in the future. He obtained a domain name and a
+solution for running Editour in the future. He obtained a domain name and a
 shared hosting environment on a Red Hat Enterprise Linux (RHEL) server for us to
@@
 Furthermore, we foresee Editour being a useful tool outside of the app we
-designed for Kyoto~VR. The design of the Editour is agnostic about how the media
+designed for Kyoto~VR. The design of Editour is agnostic about how the media
 will be used. For an app like izi.TRAVEL, the images are displayed when the
@@
 through an AR-enhanced tour. The app was built with Unity, which enabled to us
-to use a single codebase for the iOS and Android versions of the apps.
+to use a single codebase for the iOS and Android versions of the app.
 
@@
 we eventually dropped support for regions triggered by distance.
+% TODO add a picture that shows how having only circular regions limits possible
+% tour designs
 
@@
 
-% TODO include photos of the google translation app including our own app
-ARuko uses augmented reality to translate text at the site as well. While AR
-translation apps exist, the experience can be frustrating, and produce poor
-results. Google's text recognition and machine-learning powered translation
-technology is certainly impressive. At the same time, the translation service
-works better in ``scan'' mode instead of ``instant'' mode. In ``instant'' mode,
-the app attempts to translate text as quickly as possible, superimposing the
-translated text onto the real world using the camera. In ``scan'' mode, the user
-first takes a photo. Then, the user is prompted to highlight where text appears
-in the photo. After the translation is complete, the translated text appears in
-a separate UI element instead superimposed onto the photo. In most cases, it is
-more convenient and readable to have the translation appear in a separate
-scrollable text box. This motivated the current design of the ``info buttons''
-in ARuko. Instead of placing text directly onto signage, we place a blue button
-with a stylized `i' in the center. By tapping on this button, a separate UI
+ARuko uses augmented reality to translate text at the site of the tour as well.
+While AR translation apps exist, the experience can be frustrating, and produce
+poor results. Google~Translate's text recognition and machine-learning powered
+translation technology is certainly impressive. At the same time, the
+translation service works better in ``scan'' mode instead of ``instant'' mode.
+In ``instant'' mode, the app attempts to translate text as quickly as possible,
+superimposing the translated text onto the real world using the camera. In
+``scan'' mode, the user first takes a photo. Then, the user is prompted to
+highlight where text appears in the photo. After the translation is complete,
+the translated text appears in a separate UI element. In most cases, it is more
+convenient and readable to have the translation appear in a separate scrollable
+text box. This motivated the current design of the ``info buttons'' in ARuko.
+Instead of placing text directly onto signage, we place a blue button with a
+stylized ``\textit{i}'' in the center. By tapping on this button, a separate UI
 element will appear containing the translated text. Since this button is cast
 into the world using the AR camera, the button appears to be placed directly
-onto the content in the real world.
+on top of the content.
+% TODO images for this section
 
@@
 onto the map. Figure~\ref{fig:arMapFeature} shows the blue highlighted path of
-the walking tour, including a few translated labels.
-
-\begin{figure}[h] \centering
-    \includegraphics[width=0.4\textwidth]{ar-map-feature.png}
+the walking tour, including a few translated labels. The blue path and English
+text are not part of the physical map. These are superimposed on the image by
+ARuko.
+
+\begin{figure}[p]
+	\centering
+    \includegraphics[width=0.8\textwidth]{ar-map-feature.png}
     \caption{Map overlay displaying the path and translated labels}
@@
 
-Tickets to enter Kinkaku-ji are long sheets of printed paper with calligraphy.
+Tickets to enter Kinkaku-ji are long sheets of paper printed with calligraphy.
 The tickets are large and visually appealing; they are souvenirs unto themselves
 that one might feel inclined to keep around. Over the course of our three month
-stay we visited Kinkaku-ji multiple times. For each visit, we received identical
+stay we visited Kinkaku-ji thrice. For each visit, we received identical
 tickets. Seemingly, the design on the tickets do not change on a regular basis,
@@
 
-Because the tickets are unlikely to change frequently, this enables us to
-provide the user with a ``virtual souvenir'' using the AR camera. This is the
-only AR feature that is not tied directly to an image target that can only be
-accessed at Kinkaku-ji. While the image gallery and segments of the audio tour
-can be accessed at any time using the ``Chapter Select'' menu, most of the AR
-features can only be experienced during the walking tour, pointing the camera at
-objects physically located at the site. Augmenting the ticket with 3D content
-allows visitors to take something home, giving them a reason to launch the app
-later.
-
-We found a free untextured model of the Golden Pavilion to use for this
-feature. Using Unity's built-in capability to design materials, we created
-a shiny golden material and applied it to the model (see
-Figure~\ref{fig:souvenir}.
+Because the tickets are unlikely to change frequently, we are able to provide
+the user with a ``virtual souvenir'' using the AR camera. This is the only AR
+feature that is not tied directly to an image target that can only be accessed
+at Kinkaku-ji. While the image gallery and segments of the audio tour can be
+accessed at any time using the ``Chapter Select'' menu, most of the AR features
+can only be experienced during the walking tour, pointing the camera at objects
+physically located at the site. Augmenting the ticket with 3D content allows
+visitors to take something home, giving them a reason to launch the app later.
+
+We found a free untextured model of the Golden Pavilion to use for this feature
+on Thingiverse, a site for sharing user-created 3D
+models~\autocite{baichtal2008}. Using Unity's built-in capability to design
+materials, we created a shiny golden material and applied it to the model (see
+Figure~\ref{fig:souvenir}).
 
@@
 UI was a valuable learning experience, providing us with skills that were useful
-when building the final version.
-
-The early UI was very much a product of ARuko's development; many of its
-elements were created on the fly as new features were added. As more features
-were added, it became clear that the UI could not consist simply of buttons and
-other basic features provided by Unity. We would need to learn more about how to
-create more interesting and useful UI elements to accommodate for our new
-functionality.
+when building the finished product.
+
+The early UI was purely functional with no bells or whistles; many of its
+elements were created on the fly as new features were added. As the app grew,
+it became clear that the UI could not consist simply of buttons and other basic
+features provided by Unity.
 
@@
 
-Pictured in Figure~\ref{fig:oldUI} is our early UI. It was a very minimal UI,
-but still covered all of the uses for our app at the time. The top of the screen
-had two dropdown menus. The one on the left (which is open shown open in
-Figure~\ref{fig:oldUI}) shows AR image targets in the area that users could
-look for and scan. The right dropdown would be dynamically populated in each
-region with buttons bearing different images. These images were ones that
-Atticus wanted to be viewable in AR using ground plane detection. When tapped,
-each button would create a 3D Cube, with the given image on each face, and place
-it on the ground where the user was pointing. Figure~\ref{fig:floatingCube}
-shows this feature in action.
+Pictured in Figure~\ref{fig:oldUI} is our early UI. It was very minimal, but
+still covered all of the uses for our app at the time. The top of the screen had
+two drop-down menus. The one on the left (which is shown open in
+Figure~\ref{fig:oldUI}) shows AR image targets users could look for and scan.
+The right drop-down would be dynamically populated in each region with buttons
+bearing different images. These images were ones that Atticus wanted to be
+viewable in AR using ground plane detection. When tapped, each button would
+create a cube, with the given image on each face, and place it on the ground
+where the user was pointing. Figure~\ref{fig:floatingCube} shows this feature in
+action.
 
@@
 Atticus initially wanted us to explore the efficacy of using Vuforia's 2D image
-target capabilities for scanning objects outside of the expected use case, such
+target capabilities for scanning objects outside of the supported use case, such
 as 3D landscapes or the side of a building. We had serious doubts about how
@@
 
-Learning to create these dropdown menus proved to be a very important lesson
+Learning to create these drop-down menus proved to be a very important lesson
 later on, since we would put that exact knowledge to use multiple times in the
-final UI. We were able to create the dynamically populated dropdown menus by
+final UI. We were able to create the dynamically populated drop-down menus by
 creating an empty vertical layout group. Then, a script would create buttons for
 each image to display, and assign those images as children of the layout group.
-Then, to get the smooth open/close animation, we ``lerp'' (linearly interpolate)
-the menu to the corresponding position each frame until it is fully open or
-closed. In between these two dropdown menus is a panel that would display the
+To get the smooth open/close animation, we ``lerp'' (linearly interpolate)
+the menu to the corresponding position each frame until it is fully opened or
+closed. In between these two drop-down menus is a panel that would display the
 name for the region the user is in at the time. The empty space in the middle of
@@
 implementation, the AR functionality was the focus of the app, so it made sense
-to display the AR camera feed at all times. Lastly, on the bottom is the audio
-slider for the audio file played in each region. We learned about how audio
-sliders work in Unity with this feature, and would expand on that knowledge for
-the final version of the app in order to optimize the slider's functionality.
+to display the AR camera feed at all times. Lastly, on the bottom is a slider
+that controls the playback position of the audio file played in each region. We
+learned about how audio sliders work in Unity with this feature, and would
+expand on that knowledge for the final version of the app in order to optimize
+the slider's functionality.
 
 Although most elements of the initial UI did not survive into the final product,
-it was still quite valuable as a learning tool. While crafting this prototype we
-discovered many of the intricacies of UI design in Unity. For example, all UI
-elements must be attached to a Unity canvas element, which covers the entire
-phone screen. Elements should be anchored to edges or corners of this canvas so
-that they stay in a constant location on different-size screens.
+this original phase was still quite valuable as a learning tool. While crafting
+this prototype we discovered many of the intricacies of UI design in Unity. For
+example, all UI elements must be attached to a Unity canvas element, which
+covers the entire phone screen. Elements should be anchored to edges or corners
+of this canvas so that they stay in a constant location on screens of different
+sizes.
 
@@
 	\includegraphics[width=0.5\textwidth]{editour-additions.png}
-	\caption{Additions to the Editour to accommodate the new design}
+	\caption{Additions to Editour to accommodate the new design}
 	\label{fig:editourAdditions}
@@
 The last major UI implementation obstacle we had to overcome was a way to keep
-audio playing with the phone in your pocket. Atticus insisted that this sort of
-feature was required so that users could listen to the audio tour without using %maybe include an image of pocket mode here
-any of the other functionality the app provides, like the image gallery in each
-region or the AR features. Despite how common it is for apps to play audio in
-the background or while the phone is locked, Unity does not provide a way to
-accomplish this. Our workaround was to create a ``pocket mode'' that prevents UI
-elements from accidentally being triggered. The user exits pocket mode with a
-deliberate swipe to the right. If the slider is released partway through the
-action, the slider springs back to the beginning. We were ultimately able to
-replicate Atticus's Adobe XD file almost perfectly.
+audio playing with the phone in a pocket. Atticus desired this sort of feature
+so that users could listen to the audio tour without using any of the other
+functionality the app provides, such as the image gallery or the AR
+features. Despite how common it is for apps to play audio in the background or
+while the phone is locked, Unity does not provide a way to accomplish this. Our
+workaround was to create a ``pocket mode'' that prevents UI elements from
+accidentally being triggered. The user exits pocket mode with a deliberate swipe
+to the right. If the slider is released partway through the action, the slider
+springs back to the its original position.
+% TODO maybe include an image of pocket mode here
 
@@
 this, we needed to do extensive testing to ensure not only that the products
-work as intended without bugs, but also that they would be pleasant and easy to
-use for their intended users.
-
-% TODO remove this
+work as intended without bugs, but also that they are pleasant and easy to use
+for their intended users.
+
 \nocite{harvey2002} % don't remove this
@@
 depending on how it is developed later on. This is why Editour is perhaps more
-polished than your typical tool purely for internal use.
+polished than typical internal tools.
 
@@
 integral to polishing the app in time before we revisited Kinkaku-ji. Because
-the Editour was flexible enough to easily swap out media and add regions to the
-tour, the Editour proved itself to be as helpful for testing as it was for
+Editour was flexible enough to easily swap out media and add regions to the
+tour, Editour proved itself to be as helpful for testing as it was for
 crafting the final tour that could be taken at Kinkaku-ji.
@@
 	\includegraphics[width=.5\textwidth]{four-i-buttons.png}
-	\caption{The result of increasing the size of the info buttons and increasing
-    the maximum image target count to four}
+	\caption{Tracking four image targets at once with improved info buttons.}
 	\label{fig:fourIButtons}
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=\textwidth]{kanban-board.png}
-	\caption{A screenshot of the Kanban board we used for developing our
-    biweekly blog}
-	\label{fig:kanbanBoard}
-\end{figure}
-
 \clearpage
@@
 
-We spent the second and third week of the project creating demos to explore the
-possibility of a 3D spatialized audio tour. We found that this would be very
-difficult to do without the use of the camera. All of the technology for mobile
-AR we explored in Section~\ref{sec:platforms} depended heavily on the camera. If
-we were to build a 3D spatialized audio tour that ran entirely without use of
-the camera, we would not be able to take advantage of any of the useful features
-of the AR libraries we explored. Furthermore, Unity would be relegated to the
-simple role of exporting our app to multiple devices; we would not have any need
-to take advantage of its 3D capabilities.
-
-Thusly, we decided to see what was possible using the camera instead. We were
+We spent the second and third week of the project creating demonstrations to
+explore the possibility of a 3D spatialized audio tour. We found that this would
+be very difficult to do without the use of the camera. All of the technology for
+mobile AR we explored in Section~\ref{sec:platforms} depended heavily on the
+camera. If we were to build a 3D spatialized audio tour that ran entirely
+without use of the camera, we would not be able to take advantage of any of the
+useful features of the AR libraries we explored. Furthermore, Unity would be
+relegated to the simple role of exporting our app to multiple devices; we would
+not have any need to take advantage of its 3D capabilities.
+
+Therefore, we decided to see what was possible using the camera instead. We were
 able to get sound sources to fade in and out based on the distance to an image
@@
 imagined, we would need a way to shift to our own method of estimating distance
-to the sound source once the image target had been lost. While this might have
-been possible, it was difficult to estimate the amount of effort this would
-take, since we would essentially be implementing a feature seemingly not
+to the sound source once the image target had been lost. It was difficult to
+estimate the amount of effort this would take (and whether it was even
+possible), since we would essentially be implementing a feature seemingly not
 supported by current AR libraries.
@@
 	\includegraphics[width=.7\textwidth]{exhibition-scan.png}
-    \caption{A screenshot of the 3D scan of `Portraits of Thought,' accessible
+    \caption{A screenshot of the 3D scan of ``Portraits of Thought,'' accessible
     from the web}
@@
 
-\subsection{Alterniative Uses for AR in ARuko}
+\subsection{Alternative Uses for AR in ARuko}
 \label{sec:alternativeARukoAR}
 
-Even once the idea for ARuko was settled on audio tour functionality with 
-additional AR components, what exactly those AR components would do was still
+Even after the core functionality of ARuko was finalized as an audio tour with
+additional AR components, the exact nature of those AR components was still
 undecided until more details about the project crystallized. Atticus knew he
 wanted to use AR on the tour, but was not sure what to do with it. At first, we
-made recommendations to him based on the capabilities of Vuforia that we found 
-in our research. We knew it was good at image recognition and ground plane 
-recognition, so we suggested that maybe displaying some sorts of 3D models in 
-certain locations using either of these features might be an interesting way to
-expand on the tour. With these recommendations in mind, Atticus expressed 
-interest in the capability of using building facades as image targets. The 
-intention then would be to tie content related to a specific location within 
-Kinkaku-ji to that physical location, and use images of the location as 
-targets. As previously explained, this ultimately did not work out due to the 
-limitations of image recognition with Vuforia.
+made recommendations to him based on the capabilities of Vuforia. We knew that
+image recognition and ground plane recognition were two of its strengths, so we
+suggested that displaying 3D models in certain locations using either of these
+features would be an interesting way to expand on the tour. With these
+recommendations in mind, Atticus expressed interest in using building facades as
+image targets. The intention then would be to tie content to a physical location
+in Kinkaku-ji, and use images of the location as targets. As explained in
+Section~\ref{sec:earlyUserInterface}, this ultimately did not work out due to
+the limitations of Vuforia's image recognition.
 
 After being initially deterred from image recognition, we thought that ground
-and mid-air plane recognition might the best way to implement AR in the app. 
-It did not have to rely on images that meet Vuforia's criteria, and since it 
-could be triggered anywhere, it seemed like a good fit for an app focusing on
+and mid-air plane recognition might the best way to implement AR in the app. It
+did not have to rely on images that meet Vuforia's criteria, and since it could
+be triggered anywhere, it appeared to be a good fit for an app focusing on
 walking around a site. Atticus explained that he primarily wanted to use AR to
@@
 using ground plane detection, based on what region you were in. When users
-entered a region of the tour, the image menu would be dynamically populated 
-with buttons that, when tapped, would create a Plane primitive in Unity with 
-the given image displayed on it and place it on the ground plane.
-
-We encountered a few notable problems with this though. One problem was that 
-the Plane we made was always the same size and dimensions, and would cause 
-images to stretch to fit the plane. Further testing to change the size of the
-plane with each picture proved difficult. Additionally, using a Plane primitive
-had problematic effects on the way the object was lit in the Unity scene, as 
-well as how it appeared when not viewed head-on. If viewed from an angle, the 
-picture could become very dark and difficult to see. If viewed from behind,
-back-face culling would take effect and the plane would become completely 
-invisible. Because of these issues, we decided to place the images on a 3D Cube
-primitive instead. But after showing this feature to Atticus during early 
-testing at Kinkaku-ji, he decided that he wanted to move away from displaying 
-images in AR. Looking back, the feature may have worked better with mid-air 
-plane recognition so that the user could place the image directly in front of 
-them.
+entered a region of the tour, the image menu would be dynamically populated with
+buttons that, when tapped, would create a Plane primitive in Unity with the
+given image displayed on it and place it on the ground plane.
+
+We encountered a few notable problems with this. Using a Plane primitive had
+deleterious effects on the way the object was lit in the Unity scene, as well as
+how it appeared when not viewed head-on. If viewed from an angle, the picture
+could become very dark and difficult to see. If viewed from behind, back-face
+culling would take effect and the plane would become completely invisible.
+Because of these issues, we decided to place the images on a Cube primitive
+instead. After showing this feature to Atticus during early testing at
+Kinkaku-ji, he decided that he wanted to move away from displaying images in AR.
+Looking back, the feature may have worked better with mid-air plane recognition
+so that the user could place the image directly in front of them.
 
@@
 expressed interest in using AR to trigger video content. He was particularly
-interested in 3D videos triggerable through AR. As the scope of the project 
+interested in triggering 3D videos through AR. As the scope of the project 
 grew, and time ran short, the task of including 3D videos triggered by AR 
@@
 final project. Additionally, we never received any assets from Atticus to use
-for this feature, thus preventing us from spending time developing it.
+for this feature, preventing us from spending time developing it.
 
@@
 team would be looking for funding options in order to ``bootstrap'' the project.
-One monetization method he proposed was potentially marketing the app to hotels,
+One monetization method he proposed was marketing the app to hotels,
 allowing hotels to sell tours for download through in-app purchases.
 
-In order to get an app approved for the App Store or the Google Play store,
-there is sometimes a lengthy approval process. This might have been possible if
-our project had been more prescriptive from the start.
+Getting an app approved to launch on the App Store or Google Play has many
+specific requirements and can be a very lengthy process. This might have been
+possible if our project had been more prescriptive from the start and we had
+more time.
 
@@
 Atticus know that we had logistical concerns about circumventing Apple's or
-Google's in-app purchases by locking content behind a different payment process.
-Additionally, we informed Atticus that he would have to purchase a commercial
-Vuforia license in order to deploy the app onto any
+Google's in-app purchases by locking content behind a different payment process
+as he suggested. Additionally, we informed Atticus that he would have to
+purchase a commercial Vuforia license in order to publish the app on any
 storefront~\autocite{vuforialicense2018}, which Atticus was not willing to do at
@@
 the watermark with our own UI elements. This does not change the fact that we
-would not be able to deploy the app without a proper commercial license for
-Vuforia.}
+would not legally be able to deploy the app without a proper commercial license
+for Vuforia.}
 
@@
 we were worried that this kind of work strayed too far away from the academic
-intent of the project---the intent being to explore various ways in which AR and
-geolocation could be used in tandem to create an improved experience for
-tourists. For our purposes, the app was meant to demonstrate our discoveries in
-the form of a polished prototype. While we feel as though we achieved this goal,
-we made certain compromises in the way of experimentation in order to leave
-Kyoto~VR with a potentially marketable product. We made it clear to Atticus that
-deploying our app on the Google Play Store or App Store would not be within the
-scope of our academic project as per our advisers' advice.
+intent of the project---to explore various ways in which AR and geolocation
+could be used in tandem to create an improved experience for tourists. For our
+purposes, the app was meant to demonstrate our discoveries in the form of a
+polished prototype. While we feel as though we achieved this goal, we restricted
+our experimentation in order to leave Kyoto~VR with a potentially marketable
+product. We made it clear to Atticus that deploying our app on Google Play
+or the App Store would not be within the scope of our academic project as per
+our advisers' guidance.
 
@@
 the future. This section contains our final thoughts on the project and future
-work that could be done on it.
+work that could be done.
 
@@
 the final product. We also did not receive official specifications, such as the
-design of the GUI Atticus wanted for the app, until very late in the development
-process.
+design of the graphical user interface (GUI) Atticus wanted for the app, until
+very late in the development process.
 
@@
 
-\subsubsection{What Went Well}
+\subsection{What Went Well}
 \label{sec:whatWentWell}
@@
 Despite these issues, in the end we were able to create a useful working
-prototype. The Editour is fully featured with everything needed to build an
+prototype. Editour is fully featured with everything needed to build an
 audio tour anywhere in the world. ARuko allows users to experience useful
@@
 
-Our team's broad range of skills made it so that each member had specific tasks
-that they were good at. This made the division of labor easier, and throughout
-the project we never had issues splitting up work.
+Our team had broad range of skills. This made the division of labor easier, and
+throughout the project we never had issues splitting up work. For example,
+William Campbell was the only Interactive Media and Game Design (IMGD) major on
+our team, so he was the most familiar with game engines including Unity. Because
+of this, he primarily worked on ARuko in Unity.
 
 Editour was not initially a requirement that Atticus had in mind, but it turned
-out to be a very useful tool in designing tours and allowing the app to be
+out to be a very useful tool for designing tours, allowing the app to be
 extensible. Two members of our team, Cole Granof and Joseph Petitti, had
-experience building web applications with HTML, CSS, and JavaScript, and the
-Editour allowed them to use these skills to help the project.
+experience building web applications with HTML, CSS, and JavaScript, and Editour
+allowed them to use these skills to help the project.
 
 The research time we put in at the beginning of the project also proved to be
-very useful. Our decision to use Unity Vuforia based on this research made
+very useful. Our decision to use Unity and Vuforia based on this research made
 implementing many of the complex AR features easier later on. If we had chosen a
@@
 
-\subsubsection{Future Work}
+\subsection{Future Work}
 \label{sec:futureWork}
@@
 Although selling ARuko on app stores was not within the scope of our academic
-project, but we were able polish the app enough such that it would be feasible
-for Atticus to eventually sell the app. The UI could use more testing with real
+project, we were able polish the app enough that it would be feasible for
+Atticus to eventually sell it. The UI could use more testing with real
 users to make sure it is intuitive and easy to use. We also intended to add a
@@
 
-Editour is essentially feature complete. The most recent version, v1.3.0, can be
+Editour is essentially feature complete. The most recent version, 1.3.0, can be
 found in the GitHub repository
 (\url{https://github.com/bandaloo/editour/releases/tag/v1.3.0}), and it contains
-all the features necessary to create and edit tours. In the future Kyoto~VR
+all the features necessary to create and edit tours. In the future, Kyoto~VR
 should move it to a more powerful hosting provider (see
@@
 
-Given more time and resources, the app should be augmented to include a tour
+Given more time and resources, the app could be augmented to include a tour
 browser that automatically downloads an unpacks tours from the Editour server.
@@
 and another for ARuko. These five repositories span across multiple different
-markup and programming languages, including C\#, C++, JavaScript, HTML, CSS (and
-the \LaTeX~used to typeset this paper). This gave us a welcome amount of
+markup and programming languages, including C\#, C++, JavaScript, HTML, CSS, and
+the \LaTeX~used to typeset this paper. This gave us a welcome amount of
 practice using Git for version control, as well as GitHub's other features
@@
 
-The Kanban technique stems from Toyota in the 1940s. Kanban means ``visual
-signal'' or ``card'' in Japanese, which describes the core component of the
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{kanban-board.png}
+	\caption{A screenshot of the Kanban board we used for developing our
+    biweekly blog}
+	\label{fig:kanbanBoard}
+\end{figure}
+
+The Kanban technique originates from Toyota in the 1940s. Kanban
+(\begin{CJK}{UTF8}{min}看板\end{CJK}) means ``visual signal'' or ``card'' in
+Japanese, which describes the core component of the
 technique~\autocite{terry2019}. At Toyota, line-workers would move colored cards
@@
 Creating ``pull requests'' through the GitHub web interface has a few advantages
-over directly merging code using Git. Firstly, the pull request feature
-integrates with ``Issues'' page very well. By typing `resolves' along with the
-number associated with an issue into the description of a pull request, GitHub
-will automatically close the issue when the pull request is approved. This is
-not only remarkably convenient, but also self-documenting since the descriptions
-of pull requests would contain the issues they were resolving. Secondly,
-creating a pull request allows code to be reviewed by other members of the team
-very easily. Reviewers can view the entire diff and add comments line-by-line.
-Other collaborators can easily respond to those comments. Reviewers can also
-request certain features be changed before the branch is merged, which allowed
-us to enforce that issues with the code were actually addressed.
-% TODO explain what the heck a diff is
+over directly merging code using Git. First, the pull request feature integrates
+with the ``Issues'' page very well. By typing ``resolves'' along with the number
+associated with an issue into the description of a pull request, GitHub will
+automatically close the issue when the pull request is approved. This is not
+only remarkably convenient, but also self-documenting since the descriptions of
+pull requests would contain the issues they were resolving. Secondly, creating a
+pull request allows code to be reviewed by other members of the team very
+easily. Reviewers can view the entire diff file\footnote{A ``diff'' is a file
+generated by Git that shows the differences between two files.} and add comments
+line-by-line. Other collaborators can easily respond to those comments.
+Reviewers can also request certain features be changed before the branch is
+merged, which allowed us to enforce that issues with the code were actually
+addressed.
 
@@
 In order to clearly indicate new versions of the software, we use ``Semantic
-Versioning'' which is a scheme for version numbers created by Tom
+Versioning,'' which is a scheme for version numbers created by Tom
 Preston-Werner, cofounder of GitHub~\autocite{prestonwerner}. In this scheme,
-the full version number consists of three integers separated by periods---in
-other words, in the form \texttt{major.minor.patch}. The major version number is
-incremented when an incompatible change is made. In our case, an incompatible
-change for Editour would entail changing the format of the metadata file used to
-construct a tour such that the frontend could not interpret older tour files.
-The exception to this rule is major version 0, where the product is not
-considered stable and incompatible changes can be made at any time. When Editour
-was in this phase of development, we changed the format of the metadata; this
-would have broken previous versions but this was allowed. The minor version
-number is incremented when functionality is added but remains backwards
-compatible with previous versions. An example of this is the ``transcript''
-field we added to the metadata. The frontend was still able to load tours made
-before this additional information was added to the metadata JSON. We added many
-other features throughout the development process without breaking existing
-functionality. The patch version number is for simple bug-fixes that also do not
-break compatibility. This number gets incremented the most frequently in
-practice.
+the full version number consists of three integers separated by periods in the
+form \texttt{major.minor.patch}. The major version number is incremented when an
+incompatible change is made. In our case, an incompatible change for Editour
+would entail changing the format of the metadata file used to construct a tour
+such that the frontend could not interpret older tour files. The exception to
+this rule is major version 0, where the product is not considered stable and
+incompatible changes can be made at any time. When Editour was in this phase of
+development, we changed the format of the metadata; this would have broken
+previous versions but this was allowed because it was still in an unstable beta
+version. The minor version number is incremented when functionality is added but
+remains backwards compatible with previous versions. An example of this is the
+``transcript'' field we added to the metadata. The frontend was still able to
+load tours made before this additional information was added to the metadata
+JSON. We added many other features throughout the development process without
+breaking existing functionality. The patch version number is for simple
+bug-fixes that also do not break compatibility. This number gets incremented the
+most frequently in practice.
 
@@
 
-Throughout our stay at Ritsumeikan, we also had the opportunity to work closely
-with other Ritsumeikan students to create build a project that involved the
+Throughout our stay at Ritsumeikan University, we had the opportunity to work
+closely with other students to build a project that involved the
 integration of hardware and software. With the help of students and professors
 alike, we were able to produce an educational physical model of a heart
-controlled by an Arduino microcomputer. Noma Sensei gave us tremendous
+controlled by an Arduino microcomputer. Professor Noma Haruo gave us tremendous
 assistance with hardware. He taught us how to properly use the tools around the
 lab, and purchased mechanical and electrical components we would need to
-complete our task. Amano Sensei was always available to answer questions related
-to biology, and helped us understand the mathematical model we would need to
-implement to drive the physical model with software. We worked on this project
-every Wednesday, completing the final model during the last week of our stay.
+complete our task. Professor Amano was always available to answer questions
+related to biology, and helped us understand the mathematical model we would
+need to implement to drive the physical model with software. We worked on this
+project every Wednesday, completing the final model during the last week of our
+stay.
 % TODO get the full name of Amano Sensei
@@
 
-The goals and requirements of this project were set out by Haruo Noma, a
+The goals and requirements of this project were set out by Professor Noma, a
 professor at Ritsumeikan University. The goal of the project was to create an
-interactive model of a heart to teach heart function to non-specialists, such as
-students in middle school. This meant that the model had to be highly visual and
-simple to understand. Each visual component would have to be designed in an
+interactive model of a heart to teach heart functions to non-specialists, such
+as students in middle school. This meant that the model had to be highly visual
+and simple to understand. Each visual component would have to be designed in an
 intuitive fashion so that students could begin interacting with the model
@@
 \begin{figure}[h] \centering
-    \includegraphics[width=0.4\textwidth]{reference-model.png}
+    \includegraphics[width=0.8\textwidth]{reference-model.png}
     \caption{The reference model we used to implement the simulation}
@@
 
-With Noma Sensei as our guide, we visited ``Den-Den Town'' or Nipponbashi in
-Osaka in order to gather supplies we would need in order to construct the heart.
-One of the most important purchases of this trip was a two-meter long strip of
-Adafruit NeoPixel light emitting diodes (LEDs). The design of this reel of LEDs
-enabled us to cut the strip at specific points to create shorter strips. Each
-LED on the strip individually addressable, allowing us to set the color of any
-LED along the strip. This perfectly suited our needs for representing blood
-flow.
+With Professor Noma as our guide, we visited ``Den-Den Town,'' or Nipponbashi,
+in Osaka in order to gather supplies we would need in order to construct the
+heart. One of the most important purchases of this trip was a two-meter long
+strip of Adafruit NeoPixel light emitting diodes (LEDs). The design of this reel
+of LEDs enabled us to cut the strip at specific points to create shorter strips.
+Each LED on the strip was individually addressable, allowing us to set the color
+of any LED along the strip. This perfectly suited our needs for representing
+blood flow.
 
 % TODO give a citation about what an Arduino is
-% TODO do we need citations about every microcomputer mentioned by name?
-Noma Sensei had various microcomputers for us to experiment with in his lab,
-including an obniz, an M5Stack, a Raspberry Pi and an Arduino. The Arduino was
+Professor Noma had various microcomputers for us to experiment with in his lab,
+including an obniz, an M5Stack, a Raspberry Pi, and an Arduino. The Arduino was
 the only computer that had a ``motor shield'' component which we believed would
@@
 
-Like the balloon which represents the volume of the left ventricle, the LED
+Like the balloon, which represents the volume of the left ventricle, the LED
 strips represent both pressure and blood flow in different parts of the body.
@@
 Our initial plan for the user interface was to control input and output
-parameters with dials. The numerical values of the input parameters would have
+parameters with dials. The numeric values of the input parameters would have
 been displayed on an array of digital number displays. Due to time constraints,
@@
 ventricle. Due to limitations about the accuracy with which we could control the
-pump, the volume of the balloon does perfectly reflect the true value of
+pump, the volume of the balloon does not perfectly reflect the true value of
 $V_{LV}$ in the model. By contrast, the radius of the graphic on-screen can be
@@
 additional project he wanted us to tackle. He wanted us to adapt Kyoto~VR's
-NOxAR app to use ground plane detection. Currently, the NOxAR app is an AR app
-for Microsoft HoloLens that uses image targets with Vuforia. When viewing the
+NOxAR app to use ground plane detection. Currently, NOxAR is an AR app for
+Microsoft HoloLens that uses image targets with Vuforia. When viewing the
 correct image target, the app projects a 3D model of a noh theater\footnote{A
@@
 and slow dancing~\autocite{japanguide2018}.} performer dancing to background
-music~\autocite{noxar2018}. What Atticus wanted was to have the app use ground
-plane detection in order to display the noh performer so that it could be
-displayed anywhere. Additionally, he wanted us to scale up the model so that
-when displayed in AR, the performer would appear life-sized.
+music~\autocite{noxar2018}. Atticus wanted to have the app use ground plane
+detection in order to display the noh performer so that it could be displayed
+anywhere. Additionally, he wanted us to scale up the model so that when
+displayed in AR, the performer would appear life-sized.
 
@@
 AR app. At first we tried importing the assets for the noh performer into a new
-Unity project. We did this for a couple reasons. The first reason was because
+Unity project. We did this two reasons. First,
 we did not want all of the extra components of the original NOxAR project to
-get in the way of what we were trying to do. We also did this because the %could probably put an example pic here
+get in the way of what we were trying to do. We also did this because the
 original project was made with a 2017 version of Unity, so we wanted to try to
-use our more recent version so we would not risk running into any depricated 
-features or functionalities. We did eventually get this method to work, but the
-model of the noh performer was lacking a lot of the details that the original 
-model had. This was attributed to poor importation of the original assets, so 
-we decided to try making changes to the original NOxAR project instead.
-
-Per Atticus's advice, we deleted any and all unnecessary elements from the 
-scene before proceeding. We also updated the Unity version of the project to
-the 2019 version we were using, and updated the version of Vuforia to the most
-recent version, neither of which created any problems. The process of getting
-the model to appear on ground plane detection instead of image target 
-recognition was relatively simple. We simply moved the model from an image 
-target to a simulated ground plane, added a plane detector component to the
-scene, and made sure the Vuforia settings were in place for ground plane
-detection to work well. From there, we just had to test the app a few times so
-we could properly scale the model to life size. On Tuesday, September 17th, 
-we completed the NOxAR ground plane adaptation to Atticus's saisfaction and
-sent him the final APK file for the app.
+import it into the most recent version so we would not risk running into any
+deprecated features or functionalities. We did eventually get this method to
+work, but the model of the noh performer was lacking a lot of the details that
+the original model had. This was attributed to errors while importing the
+original assets, so we decided to try making changes to the original NOxAR
+project instead. 
+% TODO could probably put an example pic here
+
+Per Atticus's advice, we deleted any and all unnecessary elements from the scene
+before proceeding. We also updated the Unity version of the project to the 2019
+version we were using, and updated the version of Vuforia to the most recent
+version, neither of which created any problems. The process of getting the model
+to appear on ground plane detection instead of image target recognition was
+relatively easy. We simply moved the model from an image target to a simulated
+ground plane, added a plane detector component to the scene, and made sure the
+Vuforia settings were in place for ground plane detection to work well. From
+there, we just had to test the app a few times so we could properly scale the
+model to life size. On Tuesday, September 17\textsuperscript{th}, we completed
+the NOxAR ground plane adaptation to Atticus's satisfaction and sent him the
+final APK file for the app.
 

### 2019-10-04 paper.tex
more figures and added to sections

@@
 geographic regions onto a map, edit those regions and assign media to each of
-the drawn regions.
+the drawn regions. Figure~\ref{fig:editour} shows a screenshot of the web
+interface used to design tours.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{updated-editour.png}
+	\caption{A screenshot of the Editour web app frontend}
+	\label{fig:editour}
+\end{figure}
 
@@
 
-% TODO update this figure
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=\textwidth]{editour.jpg}
-	\caption{A screenshot of the Editour web app frontend}
-	\label{fig:editour}
-\end{figure}
-
-\subsubsection{Editour Frontend Implementation}
+\subsubsection{Editour Frontend Implementation and Design}
 \label{sec:editourFrontendImplementation}
@@
 
+The look and feel of the Editour frontend was inspired from multiple sources.
+The color scheme of the UI was inspired by the Super Famicom controller, which
+can be seen in Figure~\ref{fig:superFamicomController}. The shape of the
+``cards'' within the sidebar were inspired by the GitHub Kanban board on the
+``Projects'' tab of a GitHub repo (which can be seen in
+Figure~\ref{fig:kanbanBoard} in the Appendix).
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\textwidth]{super-famicom-controller.jpg}
+    \caption[A Japanese Super Famicom controller.]{The inspiration for the
+    colorscheme: a Japanese Super Famicom controller~\autocite{amos2017}.}
+    \label{fig:superFamicomController}
+\end{figure}
+
+Since the frontend of Editour was implemented using basic web technologies, we
+had access to the full power of CSS to style each element of the GUI. The
+classes within CSS were designed so they could be reused easily and composed
+with one another. If, for example, we needed to change the font of every element
+that was styled like a button, we could do so by simply changing the
+\texttt{font-family} attribute in a single CSS class. Consider the green bar
+pictured in Figure~\ref{fig:mediaSubcard}. Multiple CSS classes were composed in
+order to inherit the visual descriptions of other UI elements. The four CSS
+classes on this bar are \texttt{button}, \texttt{greenbutton},
+\texttt{outlinebutton}, and \texttt{revealer}. The class \texttt{button} styles
+elements as the slightly raised, rounded rectangle that can be seen throughout
+the UI. Additionally, all elements with the \texttt{button} class will have a
+subtle ``press'' animation when being clicked on, since key frame animations can
+also be defined in CSS. The default color of the button is red; the bottom of
+the button is a slightly darker shade to give a 3D effect. Both of these colors
+are conveniently stored as custom CSS variables, \texttt{--bg-color} and
+\texttt{--bottom-color}. This allows another class to easily override these
+colors. This is what the class \texttt{greenbutton} does; an HTML element with
+the \texttt{button} class and either \texttt{greenbutton}, \texttt{orangebutton}
+or \texttt{bluebutton} will be styled like a button and have a new color palette
+applied. In order to differentiate the buttons that reveal subcards, the
+\texttt{outlinebutton} class is used. This class takes the custom
+\texttt{--bg-color} property and applies it to the border, drop shadow and text
+color instead of the background. This class was also applied to the buttons that
+can be seen in Figures~\ref{fig:jumpCard}~and~\ref{fig:downloadCard}. Finally,
+the \texttt{revealer} class changes the text from centered to left-justified
+among other minor formatting adjustments. CSS allowed us to define the look and
+feel programmatically with the need to create graphical assets using image
+editing software. This means that anyone using the codebase of Editour for
+different purposes can easily change the look and feel of the frontend by
+changing the CSS.\footnote{This is allowed since Editour is free software, which
+is discussed briefly in Section~\ref{sec:futureOfEditour}.}
+
 \subsubsection{Editour Backend}
@@
 update the tours without updating the entire app.
+
+Currently, there is no way to download a previous version of a tour directly
+from the UI, despite the fact that the backend automatically saves timestamped
+backups of tours as they are uploaded. Our team is able to recover backups by
+copying files directly from the server. However, we would like to design an
+intuitive version browser in the frontend so that any user can recover previous
+versions of their tour.
 
@@
 superimposing the translated text onto the real world using the camera. In
-``scan'' mode, the user first takes a photo. Then, the user is prompted to
-highlight where text appears in the photo. After the translation is complete,
-the translated text appears in a separate UI element. In most cases, it is more
-convenient and readable to have the translation appear in a separate scrollable
-text box. This motivated the current design of the ``info buttons'' in ARuko.
-Instead of placing text directly onto signage, we place a blue button with a
-stylized ``\textit{i}'' in the center. By tapping on this button, a separate UI
-element will appear containing the translated text. Since this button is cast
-into the world using the AR camera, the button appears to be placed directly
-on top of the content.
-% TODO images for this section
+``scan'' mode, the user first takes a photo. This will sometimes produce
+useless results, as seen in Figure~\ref{fig:translateInstant}. Then, the user
+is prompted to highlight where text appears in the photo by dragging lines onto
+the screen where text appears, as seen in Figure~\ref{fig:translateScan}. After
+the translation is complete, the translated text appears in a separate UI
+element, which can be seen in Figure~\ref{fig:translateFinalCard}. In most
+cases, it is more convenient and readable to have the translation appear in a
+separate scrollable text box. This motivated the current design of the ``info
+buttons'' in ARuko. Instead of placing text directly onto signage, we place a
+blue button with a stylized ``\textit{i}'' in the center. By tapping on this
+button, a separate UI element will appear containing the translated text. Since
+this button is cast into the world using the AR camera, the button appears to
+be placed directly on top of the content.
+
+% TODO make it so these images don't appear so far away (thank you LaTeX)
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=0.8\textwidth]{translate-instant.jpg}
+	\caption{Google Translate camera feature in ``instant'' mode.}
+	\label{fig:translateInstant}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=0.8\textwidth]{translate-scan.jpg}
+	\caption{Google Translate camera feature in ``scan'' mode}
+	\label{fig:translateScan}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=0.8\textwidth]{translate-final-card.png}
+	\caption{The final page seen after using ``scan'' mode in Google Translate}
+	\label{fig:translateFinalCard}
+\end{figure}
+
+Additionally, we would not try to use any text recognition or translation APIs
+to automate the translation. Figure~\ref{fig:translateInstant} demonstrates
+that this kind of technology needs to mature before it is completely usable,
+especially for Japanese. Instead, we had Atticus share a Google Sheets
+spreadsheet. Hikaru Inoue manually translated each sign and provided notes about
+his decision making process about each translation. Once this time-intensive
+labor was completed, we took each field of translated text from the spreadsheet
+and implemented it directly into the app, associating each translation with the
+correct image target.
 
@@
 Originally, the AR model of the Golden Pavilion was flush against the plane of
-the ticket, sitting on the paper as if it were ground. Atticus suggested that we
-re-orient the model such that the ticket served as a back plane. This would
-allow users to hold the ticket vertically, and view the Golden Pavilion floating
-in front of the ticket. This allows users to place their hands under the base of
-the Golden Pavilion model as if they were holding it; Vuforia's image tracking
-is flexible enough such that the image target can be partially obscured by the
-hand.
+the ticket, sitting on the paper as if it were ground, as depicted in
+Figure~\ref{fig:kinkakujiHorizontal}. Atticus suggested that we re-orient the
+model such that the ticket served as a back plane, as pictured in
+Figure~\ref{fig:souvenir}. This would allow users to hold the ticket vertically,
+and view the Golden Pavilion floating in front of the ticket. This allows users
+to place their hands under the base of the Golden Pavilion model as if they were
+holding it; Vuforia's image tracking is flexible enough such that the image
+target can be partially obscured by the hand.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=.5\textwidth]{kinkakuji-horizontal.png}
+	\caption{Untextured Golden Pavilion model sitting horizontally on ticket}
+	\label{fig:kinkakujiHorizontal}
+\end{figure}
 
@@
 project instead.
-% TODO could probably put an example pic here
 
@@
 the NOxAR ground plane adaptation to Atticus's satisfaction and sent him the
-final APK file for the app.
+final APK file for the app. Figure~\ref{fig:noArWorking} shows how the final
+working version of the NOxAR app.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.7\textwidth]{no-ar-working.jpg}
+	\caption{Noh artist dancing on the ground plane of the scene}
+	\label{fig:noArWorking}
+\end{figure}
 

### 2019-10-05 paper.tex
edits to send in before ralph reads this over weekend

@@
 Since the frontend of Editour was implemented using basic web technologies, we
-had access to the full power of CSS to style each element of the GUI. The
-classes within CSS were designed so they could be reused easily and composed
-with one another. If, for example, we needed to change the font of every element
-that was styled like a button, we could do so by simply changing the
-\texttt{font-family} attribute in a single CSS class. Consider the green bar
-pictured in Figure~\ref{fig:mediaSubcard}. Multiple CSS classes were composed in
-order to inherit the visual descriptions of other UI elements. The four CSS
-classes on this bar are \texttt{button}, \texttt{greenbutton},
+had access to the full power of cascading style sheets (CSS) to style each
+element of the GUI. CSS is a style sheet language, meaning that it works in
+tandem with markup languages like HTML, which define the structure of content on
+the page~\autocite{mozillahtml2019}. CSS allows developers to define a set of
+rules that describes how the content will look~\autocite{mozillacss2019}.
+
+The classes within CSS were designed so they could be reused
+easily and composed with one another. If, for example, we needed to change the
+font of every element that was styled like a button, we could do so by simply
+changing the \texttt{font-family} attribute in a single CSS class. Consider the
+green bar pictured in Figure~\ref{fig:mediaSubcard}. Multiple CSS classes were
+composed in order to inherit the visual descriptions of other UI elements. The
+four CSS classes on this bar are \texttt{button}, \texttt{greenbutton},
 \texttt{outlinebutton}, and \texttt{revealer}. The class \texttt{button} styles
@@
 are sent to the server running the Node.js scripts. The server zips up the files
-and saves them to the disk with a timestamp. Then any application can request a
+and saves them to the disk with a time stamp. Then any application can request a
 particular tour and the backend will serve the most recent version.
@@
 Another notable change can be seen in the first screen on
-Figure~\ref{fig:adobeXdDesign}. Atticus was not enthusiastic about being able
-to place images onto the ground-plane using the AR camera. Instead, he
-suggested that we have the images be viewable in a more traditional
-fashion---in 2D as part of the UI.
+Figure~\ref{fig:adobeXdDesign} and Figure~\ref{fig:galleryZoomed}. Atticus was
+not enthusiastic about being able to place images onto the ground-plane using
+the AR camera. Instead, he suggested that we have the images be viewable in a
+more traditional fashion---in 2D as part of the UI.
 
@@
 
+% "scrollable" is for sure a neologism but let's normalize it through usage
 On the same screen, there is a scrollable window of text for a transcript of
@@
 
-With the ground-plane detection features stripped away from the main app, the
-AR focus shifted to translating the maps and signs using the camera. The fourth
-screen on Figure~\ref{fig:adobeXdDesign} shows a mock-up of this feature.
-Atticus took photographs of various signs throughout Kinkaku-ji for us to use
-as image targets. Hikaru Inoue helped us by translating all of the text in
-these photos from Japanese to English. In this design, the AR camera
-superimposes an ``info'' button on top of the sign. Tapping on this button
-brings up a separate UI element containing the translation, which can be seen
-in Figure~\ref{fig:signTranslation}. The details of this feature is discussed
-more thoroughly in Section~\ref{sec:translationFeature}.
-
-\begin{figure}[h] \centering
-    \includegraphics[width=0.3\textwidth]{sign-translation.png}
-    \caption{Translated sign using AR camera}
-    \label{fig:signTranslation}
-\end{figure}
+With the ground-plane detection features stripped away from the main app, the AR
+focus shifted to translating the maps and signs using the camera. The fourth
+screen on Figure~\ref{fig:adobeXdDesign} and Figure~\ref{fig:infoZoomed} shows a
+mock-up of this feature. Atticus took photographs of various signs throughout
+Kinkaku-ji for us to use as image targets. Hikaru Inoue helped us by translating
+all of the text in these photos from Japanese to English. In this design, the AR
+camera superimposes an ``info'' button on top of the sign. Tapping on this
+button brings up a separate UI element containing the translation, which can be
+seen in Figure~\ref{fig:translationZoomed}. The details of this feature is
+discussed more thoroughly in Section~\ref{sec:translationFeature}.
 
@@
 of legwork would still need to be done to rebuild the proposed design using
-Unity's UI components. Adobe XD allowed us to export a few important UI
-elements as PNGs, such as the buttons to enter AR mode and view the map. We
-briefly explored a few solutions to automating the task of getting the Adobe XD
-project into Unity. We found one paid extension (for \$18) on the Unity Asset
-store called ``Experience Importer - Adobe Xd files importer.'' The download
-page for this extension claims ``Transfer AdobeXd project directly to Unity.
-Forget about hours of positioning objects. They're already there! Just drag .xd
-file to project and...  voila!''~\autocite{glasseye2019}.  We suspect this
-sounds too good to be true because it is. As of September
-20\textsuperscript{th}, 2019, there are 6 user reviews. All of the five-star
-reviews were have the caveat ``Reviewer was gifted package by publisher'' which
-which we interpreted as a warning sign. Because of this, we decided to rebuild
-the UI largely from the ground up, using the Adobe XD file to guide us.
+Unity's UI components. Adobe XD allowed us to export a few important UI elements
+as PNGs, such as the buttons to enter AR mode and view the map. We briefly
+explored a few solutions to automating the task of getting the Adobe XD project
+into Unity. We found one paid extension (for \$18) on the Unity Asset store
+called ``Experience Importer - Adobe Xd files importer.'' The download page for
+this extension claims ``Transfer AdobeXd project directly to Unity. Forget about
+hours of positioning objects. They're already there! Just drag .xd file to
+project and... voila!''~\autocite{glasseye2019}.\footnote{``Adobe XD'' is
+stylized incorrectly with ``AdobeXd'' in the description of the Unity
+package. This is also different from ``Adobe Xd'', the way in which it is
+stylized in the title.} We suspect this sounds too good to be true because it
+is. As of September 20\textsuperscript{th}, 2019, there are 6 user reviews. All
+of the five-star reviews were have the caveat ``Reviewer was gifted package by
+publisher'' which which we interpreted as a warning sign. Because of this, we
+decided to rebuild the UI largely from the ground up, using the Adobe XD file to
+guide us.
 %TODO refer to the section that discusses building the ui
+
+\begin{figure}[p] \centering
+    \includegraphics[width=0.6\textwidth]{chapters-zoomed.png}
+    \caption{Larger screenshot of the chapter selection screen mock-up}
+    \label{fig:chaptersZoomed}
+\end{figure}
+
+\begin{figure}[p] \centering
+    \includegraphics[width=0.6\textwidth]{gallery-zoomed.png}
+    \caption{Larger screenshot of the transcript and image gallery mock-up}
+    \label{fig:galleryZoomed}
+\end{figure}
+
+\begin{figure}[p] \centering
+    \includegraphics[width=0.6\textwidth]{info-zoomed.png}
+    \caption{Larger screenshot of the info button mock-up}
+    \label{fig:infoZoomed}
+\end{figure}
+
+\begin{figure}[p] \centering
+    \includegraphics[width=0.6\textwidth]{map-zoomed.png}
+    \caption{Larger screenshot of the route screen mock-up}
+    \label{fig:mapZoomed}
+\end{figure}
+
+\begin{figure}[p] \centering
+    \includegraphics[width=0.6\textwidth]{translation-zoomed.png}
+    \caption{Larger screenshot of the translation window mock-up}
+    \label{fig:translationZoomed}
+\end{figure}
 
@@
 code to calculate the output variables we would need to properly operate the
-physical model, and integrate the model into the main loop of the Arduino source
+physical model and integrate the model into the main loop of the Arduino source
 code with the appropriate timing.

### 2019-10-06 paper.tex
it takes a long paper...

@@
-\documentclass[a4paper, 10pt, american, titlepage]{article}
+\documentclass[8pt, american, titlepage]{article}
 
@@
 \usepackage{CJKutf8} % for Japanese UTF-8 characters
+\usepackage{morefloats}
 
@@
 \hyphenation{op-tical net-works semi-conduc-tor}
+
+\geometry{paperwidth=340mm, paperheight=16383pt, marginparsep=20pt, marginparwidth=100pt, textheight=16263pt, footskip=40pt}
+
+\setcounter{totalnumber}{100}
 
@@
 
-	\vfill
+	%\vfill
 
@@
 
-\vfill
-
-\clearpage
-
-% more breathing room
-\setstretch{1.5}
-
-\begin{abstract}
+%\vfill
+
+%\clearpage
+
+%\begin{abstract}
+\section*{Abstract}
+
 Kinkaku-ji, the Temple of the Golden Pavilion, is one of Kyoto's most visited
@@
 Kinkaku-ji.  
-\end{abstract}
+%\end{abstract}
 
@@
 
-\clearpage
+%\clearpage
 
@@
 
-\clearpage
+%\clearpage
 
 % now comes the table of contents, list of figures, and list of tables
-% these should be single spaced
-\begin{singlespace}
 \tableofcontents
@@
 % \addcontentsline{toc}{section}{Table of Contents}
-	\clearpage
+%\clearpage
 
@@
 % \addcontentsline{toc}{section}{List of Figures}
-	\clearpage
+%\clearpage
 
@@
 % \addcontentsline{toc}{section}{List of Tables}
-	\clearpage
-\end{singlespace}
+%\clearpage
 
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=\textwidth]{ar-example.jpg}
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=0.2\textwidth]{ar-example.jpg}
 	% Note: you don't actually need the part in square brackets for the
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=\textwidth]{kinkakuji-1.jpg}
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=0.2\textwidth]{kinkakuji-1.jpg}
 	\caption[The Golden Pavilion]{The Golden Pavilion~\autocite{fan2018}}
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=\textwidth]{ar-marker.jpg}
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=0.2\textwidth]{ar-marker.jpg}
 	\caption[Augmented reality markers]{Augmented reality
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=.5\textwidth]{pokemon-go.jpg}
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=0.2\textwidth]{pokemon-go.jpg}
 	\caption[A screenshot from the AR game \textit{Pokémon Go}]{A screenshot
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=.5\textwidth]{izi-travel.png}
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=0.2\textwidth]{izi-travel.png}
 	\caption{A screenshot of the izi.TRAVEL app interface}
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=\textwidth]{kinkakuji.jpg}
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=0.2\textwidth]{kinkakuji.jpg}
 	\caption[The Golden Pavilion of Kinkaku-ji, Kyoto, Japan]{The Golden
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=\textwidth]{kinkakuji-grounds.jpg}
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=0.2\textwidth]{kinkakuji-grounds.jpg}
     \caption[Expertly landscaped islands in the Kinkaku-ji mirror pond]{Expertly
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=\textwidth]{updated-editour.png}
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=0.2\textwidth]{updated-editour.png}
 	\caption{A screenshot of the Editour web app frontend}
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.4\textwidth]{welcome-card-editour.png}
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=0.2\textwidth]{welcome-card-editour.png}
     \caption{The ``Welcome to Editour'' card providing basic instructions to
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{drawing-region-editour.png}
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=0.2\textwidth]{drawing-region-editour.png}
 	\caption{Editour when a region is being drawn, including the two dotted
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.4\textwidth]{rename-subcard-editour.png}
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=0.2\textwidth]{rename-subcard-editour.png}
 	\caption{The ``Rename'' subcard}
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.4\textwidth]{media-subcard-editour.png}
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=0.2\textwidth]{media-subcard-editour.png}
 	\caption{The ``Media'' subcard}
@@
 
-\begin{figure}[h]
-	\centering
-    \includegraphics[width=\textwidth]{edit-subcard-with-map-editour.png}
+\begin{figure}[p]
+	\centering
+    \includegraphics[width=0.2\textwidth]{edit-subcard-with-map-editour.png}
     \caption{The ``Points'' subcard with the map showing vertices and edges that
@@
 
-\begin{figure}[h]
-	\centering
-    \includegraphics[width=0.4\textwidth]{delete-subcard-editour.png}
+\begin{figure}[p]
+	\centering
+    \includegraphics[width=0.2\textwidth]{delete-subcard-editour.png}
     \caption{The ``Delete'' subcard}
@@
 
-\begin{figure}[h]
-	\centering
-    \includegraphics[width=0.4\textwidth]{uploading-message-editour.png}
+\begin{figure}[p]
+	\centering
+    \includegraphics[width=0.2\textwidth]{uploading-message-editour.png}
     \caption{The upload subcard with an upload status}
@@
 
-\begin{figure}[h]
-	\centering
-    \includegraphics[width=0.4\textwidth]{download-card-editour.png}
+\begin{figure}[p]
+	\centering
+    \includegraphics[width=0.2\textwidth]{download-card-editour.png}
     \caption{The download card}
@@
 
-\begin{figure}[h]
-	\centering
-    \includegraphics[width=0.4\textwidth]{jump-card-editour.png}
+\begin{figure}[p]
+	\centering
+    \includegraphics[width=0.2\textwidth]{jump-card-editour.png}
     \caption{The jump card}
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{super-famicom-controller.jpg}
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=0.2\textwidth]{super-famicom-controller.jpg}
     \caption[A Japanese Super Famicom controller.]{The inspiration for the
@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{translate-instant.jpg}
+	\includegraphics[width=0.2\textwidth]{translate-instant.jpg}
 	\caption{Google Translate camera feature in ``instant'' mode.}
@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{translate-scan.jpg}
+	\includegraphics[width=0.2\textwidth]{translate-scan.jpg}
 	\caption{Google Translate camera feature in ``scan'' mode}
@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{translate-final-card.png}
+	\includegraphics[width=0.2\textwidth]{translate-final-card.png}
 	\caption{The final page seen after using ``scan'' mode in Google Translate}
@@
 	\centering
-    \includegraphics[width=0.8\textwidth]{ar-map-feature.png}
+    \includegraphics[width=0.2\textwidth]{ar-map-feature.png}
     \caption{Map overlay displaying the path and translated labels}
@@
 
-\begin{figure}[h] \centering
-    \includegraphics[width=0.4\textwidth]{kinkakuji-ticket.jpeg}
+\begin{figure}[p] \centering
+    \includegraphics[width=0.2\textwidth]{kinkakuji-ticket.jpeg}
     \caption{Kinkaku-ji ticket}
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=.5\textwidth]{souvenir.png}
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=0.2\textwidth]{souvenir.png}
 	\caption{ARuko's virtual souvenir feature}
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=.5\textwidth]{kinkakuji-horizontal.png}
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=0.2\textwidth]{kinkakuji-horizontal.png}
 	\caption{Untextured Golden Pavilion model sitting horizontally on ticket}
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.4\textwidth]{old-ui.png}
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=0.2\textwidth]{old-ui.png}
 	\caption{A screenshot of our early UI}
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.4\textwidth]{floating-cube.png}
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=0.2\textwidth]{floating-cube.png}
 	\caption{An ``art cube'' floating over the water containing a placeholder
@@
 % refer to the correct ones
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=1\textwidth]{adobe-xd-design.png}
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=0.2\textwidth]{adobe-xd-design.png}
 	\caption[A screenshot of the Adobe XD project designed by Atticus Sims]
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{editour-additions.png}
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=0.2\textwidth]{editour-additions.png}
 	\caption{Additions to Editour to accommodate the new design}
@@
 \begin{figure}[p] \centering
-    \includegraphics[width=0.6\textwidth]{chapters-zoomed.png}
+    \includegraphics[width=0.2\textwidth]{chapters-zoomed.png}
     \caption{Larger screenshot of the chapter selection screen mock-up}
@@
 \begin{figure}[p] \centering
-    \includegraphics[width=0.6\textwidth]{gallery-zoomed.png}
+    \includegraphics[width=0.2\textwidth]{gallery-zoomed.png}
     \caption{Larger screenshot of the transcript and image gallery mock-up}
@@
 \begin{figure}[p] \centering
-    \includegraphics[width=0.6\textwidth]{info-zoomed.png}
+    \includegraphics[width=0.2\textwidth]{info-zoomed.png}
     \caption{Larger screenshot of the info button mock-up}
@@
 \begin{figure}[p] \centering
-    \includegraphics[width=0.6\textwidth]{map-zoomed.png}
+    \includegraphics[width=0.2\textwidth]{map-zoomed.png}
     \caption{Larger screenshot of the route screen mock-up}
@@
 \begin{figure}[p] \centering
-    \includegraphics[width=0.6\textwidth]{translation-zoomed.png}
+    \includegraphics[width=0.2\textwidth]{translation-zoomed.png}
     \caption{Larger screenshot of the translation window mock-up}
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=\textwidth]{issues-page-example.png}
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=0.2\textwidth]{issues-page-example.png}
 	\caption{The GitHub issues tab for Editour}
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.7\textwidth]{intersections-diagram.png}
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=0.2\textwidth]{intersections-diagram.png}
 	\caption{A visualization of the algorithm}
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=.5\textwidth]{ritsu-tour.png}
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=0.2\textwidth]{ritsu-tour.png}
 	\caption{The Ritsumeikan example tour used for testing}
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=\textwidth]{kinkakuji-tour.png}
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=0.2\textwidth]{kinkakuji-tour.png}
 	\caption[The original version of the Kinkaku-ji tour]{The original version
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=\textwidth]{kinkakuji-chunkier-tour.png}
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=0.2\textwidth]{kinkakuji-chunkier-tour.png}
 	\caption[The ``chunkier'' version of the Kinkaku-ji tour]{The ``chunkier''
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=.5\textwidth]{four-i-buttons.png}
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=0.2\textwidth]{four-i-buttons.png}
 	\caption{Tracking four image targets at once with improved info buttons.}
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=\textwidth]{galaxy-s10+.jpg}
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=0.2\textwidth]{galaxy-s10+.jpg}
 	\caption[A Samsung Galaxy S10+ phone with distinctive ``hole punch''
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=\textwidth]{iphone-x.jpg}
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=0.2\textwidth]{iphone-x.jpg}
 	\caption[An iPhone X with a large notch]{An iPhone X with a large
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=.7\textwidth]{exhibition-scan.png}
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=0.2\textwidth]{exhibition-scan.png}
     \caption{A screenshot of the 3D scan of ``Portraits of Thought,'' accessible
@@
 
-\clearpage
-
-% references should be single spaced
-\begin{singlespace}
+%\clearpage
+
 \printbibliography
 \addcontentsline{toc}{section}{References}
-\end{singlespace}
-
-\clearpage
+
+%\clearpage
 
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=\textwidth]{kanban-board.png}
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=0.2\textwidth]{kanban-board.png}
 	\caption{A screenshot of the Kanban board we used for developing our
@@
 
-\begin{figure}[h] \centering
-    \includegraphics[width=0.8\textwidth]{reference-model.png}
+\begin{figure}[p] \centering
+    \includegraphics[width=0.2\textwidth]{reference-model.png}
     \caption{The reference model we used to implement the simulation}
@@
 
-\begin{figure}[h] \centering
-    \includegraphics[width=\textwidth]{interactive-model.png}
+\begin{figure}[p] \centering
+    \includegraphics[width=0.2\textwidth]{interactive-model.png}
     \caption{A diagram representing the physical model of the heart}
@@
 
-\begin{figure}[h] \centering
-    \includegraphics[width=\textwidth]{heart-gui.png}
+\begin{figure}[p] \centering
+    \includegraphics[width=0.2\textwidth]{heart-gui.png}
     \caption{The GUI to enable five preprogrammed scenarios}
@@
 \begin{table}[h]
-\begin{singlespace}
 \renewcommand{\arraystretch}{2.0} % add space between rows
@@
 \end{tabulary}
-\end{singlespace}
 \caption{Results of final field test survey}
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.7\textwidth]{no-ar-working.jpg}
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=0.2\textwidth]{no-ar-working.jpg}
 	\caption{Noh artist dancing on the ground plane of the scene}

### 2019-10-08 paper.tex

--- 2019-10-05 paper.tex
@@
 
-The field of consumer-oriented augmented reality (AR) technology is just coming
-into full swing, and it presents many unique opportunities for a myriad of
-fields. This budding technological platform uses digital displays to augment
-real-world information with computer-generated data (see
-Figure~\ref{fig:arExample}. As the technology progresses, several disparate
-industries have found novel uses for it, some becoming extremely
-profitable~\autocite{webster2018}. With smartphone manufacturers investing
-billions into AR technology~\autocite{mason2016}, it seems poised to be the next
-big digital interface.
+Consumer-oriented augmented reality (AR) technology is just coming into full
+swing, and it presents many unique opportunities for a myriad of fields. This
+budding technological platform uses digital displays to augment real-world
+information with computer-generated data (see Figure~\ref{fig:arExample}). As
+the technology progresses, several disparate industries have found novel uses
+for it, some becoming extremely profitable~\autocite{webster2018}. With
+smartphone manufacturers investing billions into AR
+technology~\autocite{mason2016}, it seems poised to be the next big digital
+interface.
 
@@
 to get any other way. Kinkaku-ji, the ``Golden Pavilion'' of Kyoto (see
-Figure~\ref{fig:kinkakuji1}, is the perfect example of a site that would benefit
+Figure~\ref{fig:kinkakuji1}), is the perfect example of a site that would benefit
 from AR~\autocite{bornoff2000}.
@@
 complete platform for designing and experiencing AR-enhanced tours. Editour
-makes it easy to design custom audio tours including audio, text, and images,
+makes it easy to design custom audio tours including sound, text, and images,
 while ARuko allows users to seamlessly experience historic sites in an intuitive
@@
 on these markers. Instead, ARuko recognizes images of objects that are already
-at the site, and uses them to display informative AR pop-ups. See
+at the site and uses them to display informative AR pop-ups. See
 Sections~\ref{sec:translationFeature} and \ref{sec:mapOverlayFeature} for more
@@
 human-computer interaction are becoming mainstream. Smartphones allow for an
-unprecedented degree of connectivity with the digital world, but can also serve
+unprecedented degree of connectivity with the digital world but can also serve
 as a tool for digitally enhancing the physical world. In this section we explain
@@
 places, and objects overlaid onto images of the real
-world~\autocite{saenz2009}, in a way that is more intuitive or visually
+world~\autocite{saenz2009} in a way that is more intuitive or visually
 appealing than a purely virtual environment. This provides the user with useful
@@
 One of the major problems facing AR development as a whole---including our
-project---is limited hardware. For starters, smartphone cameras present a
+project---is hardware. For starters, smartphone cameras present a
 major limitation. Many smartphone cameras only capture images in 2D, which can
@@
 hardware limitations that make achieving satisfying AR capabilities difficult.
-Additionally, AR apps for smartphones tend not to be very user-friendly, and
+Additionally, AR apps for smartphones tend not to be very user-friendly and
 oftentimes even complicate the task or activity they were meant to
@@
 hardware like the HoloLens is very inaccessible and expensive; Microsoft only
-offers developer editions of the HoloLens, and for the steep price of
+offers developer editions of the HoloLens and for the steep price of
 \$3,500~\autocite{microsoft2019}.
@@
 Wikitude is another major AR development kit that is very prevalent in the world
-of AR development. It has over 130,000 registered AR developers, and is powering
+of AR development. It has over 130,000 registered AR developers and is powering
 over 30,000 AR apps across smartphones, tablets, and smart
@@
 which was far beyond the resources available to us. They also charge
-\euro{1990} for their SDK Pro, and \euro{2490} for their SDK Pro 3D. Given
+\euro{1990} for their SDK Pro and \euro{2490} for their SDK Pro 3D. Given
 these prices, and our very limited budget, we decided to consider other
@@
 Unfortunately, it appears that the company has completely pivoted off of this
-idea, and has since moved to developing AR training
-software~\autocite{motiveio}. We reached out to motive.io via email for any
-advice they might be willing to give us, but we received no response.
+idea and has since moved to developing AR training software~\autocite{motiveio}.
+We reached out to motive.io via email for any advice they might be willing to
+give us, but we received no response.
 
@@
 Since our project is not a game, we initially wanted to avoid using a
-fully-featured game engine such as Unity (see Section~\ref{sec:unity}.
+fully-featured game engine such as Unity (see Section~\ref{sec:unity}).
 Therefore, we decided to take the time to explore this framework since it
@@
 \textit{Compute!} magazine asking whether it is possible for a Commodore 64 to
-emulate MS-DOS, the editor responded ``Yes, it's possible for a 64 to emulate an
-IBM PC, in the same sense that it's possible to bail out Lake Michigan with a
-teaspoon.'' The editor goes on to explain ``Emulation is a complex business, but
-here's one rule of thumb: The only way to successfully emulate a machine is with
-a much more powerful machine''~\autocite{warick1988}. In our case, emulating
-Android on a desktop operating system is closer to emulating a C64 on an IBM PC
-running MS-DOS (rather than the other way around, thankfully). The takeaway is
-that the speed problem facing emulators is just as real as it was in 1988.}
-Considering that AR already pushes modern phone hardware to the limit, emulation
-is not something we wanted to struggle with. On top of this, our testing
-required us to move the camera through the world at various speeds and angles,
-which is simply cumbersome with a laptop webcam.
+emulate MS-DOS, the editor responded, ``Yes, it's possible for a 64 to emulate
+an IBM PC, in the same sense that it's possible to bail out Lake Michigan with a
+teaspoon.'' The editor goes on to explain, ``Emulation is a complex business,
+but here's one rule of thumb: The only way to successfully emulate a machine is
+with a much more powerful machine''~\autocite{warick1988}. In our case,
+emulating Android on a desktop operating system is closer to emulating a C64 on
+an IBM PC running MS-DOS (rather than the other way around, thankfully). The
+takeaway is that the speed problem facing emulators is just as real as it was in
+1988.} Considering that AR already pushes modern phone hardware to the limit,
+emulation is not something we wanted to struggle with. On top of this, our
+testing required us to move the camera through the world at various speeds and
+angles, which is simply cumbersome with a laptop webcam.
 
@@
 checking (unlike JavaScript), detection of using uninitialized variables (also
-unlike normal JavaScript,) range checking for array bounds (unlike C) and
+unlike normal JavaScript) range checking for array bounds (unlike C), and
 garbage collection. At the same time, our lack of familiarity with the language
@@
 because it is not an AR platform unto itself. Instead, Unity can take advantage
-of AR platforms such as ARKit, ARCore, Vuforia and Wikitude through the use of
+of AR platforms such as ARKit, ARCore, Vuforia, and Wikitude through the use of
 plugins.
@@
 An audio file and multiple image files can be uploaded for each region the user
-defines. The user can also provide a text transcript of the audio file as well.
-After naming and uploading the tour with the ``Upload'' button, our backend
-builds a zip containing files that can be placed directly into the Unity
-project.
+defines. The user can also provide a text transcript of the audio file. After
+naming and uploading the tour with the ``Upload'' button, our backend builds a
+zip containing files that can be placed directly into the Unity project.
 
@@
 Even with knowledge of C\# and Unity, inputting tour data this way is obviously
-cumbersome. Atticus is not a software developer, and does not want to work with
+cumbersome. Atticus is not a software developer and does not want to work with
 C\# scripts. In order to make our app prototype at all useful for the future,
@@
 In order to create a fully-functional editor for designing and exporting
-``tours,'' we had to consider how to fully define a tour purely in terms
-of text and a directory of associated media.
-
-Here is an example of a tour metadata file in JavaScript Object Notation (JSON)
-format:
+``tours,'' we had to consider how to fully define a tour purely in terms of text
+and a directory of associated media. Here is an example of a tour metadata file
+in JavaScript Object Notation (JSON) format:
 
@@
 
-The user can easily create a new region by shift-clicking the map, and then
+The user can easily create a new region by shift-clicking the map and then
 continuing to click to define more points. Figure~\ref{fig:drawingRegion} shows
@@
 these instructions, which should be enough to get started. A user can only
-terminate the polygon after two points have been placed to prevent the user
-from drawing a region with an area of zero. Once a region is created, a region
-card appears in the side bar. From here, the user can edit anything about the
-region.
+terminate the polygon with a third point after two points have already been
+placed to prevent the user from drawing a region with an area of zero. Once a
+region is created, a region card appears in the side bar. From here, the user
+can edit anything about the region.
 
@@
 Once a tour is either uploaded or downloaded, a link to download the zip file of
-that tour will appear. The zip file contains all of the uploaded media, and a
+that tour will appear. The zip file contains all of the uploaded media and a
 metadata file. The metadata is in the form of a JSON file; it contains all of
@@
 The frontend was implemented as a web application, using web technologies such
-as HTML, CSS and JavaScript, with JavaScript being the vast majority of the
+as HTML, CSS, and JavaScript, with JavaScript being the vast majority of the
 code. Type-checking provided by Visual Studio Code and JSDoc made the growing
@@
 the DOM directly with JavaScript's built-in functionality. Furthermore, we did
-not use any advanced frontend build tools such as Rollup, webpack or Parcel. For
-a JavaScript project of this scope, this was the correct decision. Considering
-we had limited knowledge of React or Angular, it was also faster to develop the
-UI in the way we were used to from previous experience, but if we were to
-continue to develop Editour, UI libraries and frontend build tools would be
-something to consider.
+not use any advanced frontend build tools such as Rollup, webpack, or Parcel.
+For a JavaScript project of this scope, this was the correct decision.
+Considering we had limited knowledge of React or Angular, it was also faster to
+develop the UI in the way we were used to from previous experience, but if we
+were to continue to develop Editour, UI libraries and frontend build tools would
+be something to consider.
 
@@
 
-The classes within CSS were designed so they could be reused
-easily and composed with one another. If, for example, we needed to change the
-font of every element that was styled like a button, we could do so by simply
-changing the \texttt{font-family} attribute in a single CSS class. Consider the
-green bar pictured in Figure~\ref{fig:mediaSubcard}. Multiple CSS classes were
-composed in order to inherit the visual descriptions of other UI elements. The
-four CSS classes on this bar are \texttt{button}, \texttt{greenbutton},
+The classes within CSS were designed so they could be reused easily and composed
+with one another. If, for example, we needed to change the font of every element
+that was styled like a button, we could do so by simply changing the
+\texttt{font-family} attribute in a single CSS class. Consider the green bar
+pictured in Figure~\ref{fig:mediaSubcard}. Multiple CSS classes were composed in
+order to inherit the visual descriptions of other UI elements. The four CSS
+classes on this bar are \texttt{button}, \texttt{greenbutton},
 \texttt{outlinebutton}, and \texttt{revealer}. The class \texttt{button} styles
@@
 colors. This is what the class \texttt{greenbutton} does; an HTML element with
-the \texttt{button} class and either \texttt{greenbutton}, \texttt{orangebutton}
-or \texttt{bluebutton} will be styled like a button and have a new color palette
-applied. In order to differentiate the buttons that reveal subcards, the
-\texttt{outlinebutton} class is used. This class takes the custom
-\texttt{--bg-color} property and applies it to the border, drop shadow and text
-color instead of the background. This class was also applied to the buttons that
-can be seen in Figures~\ref{fig:jumpCard}~and~\ref{fig:downloadCard}. Finally,
-the \texttt{revealer} class changes the text from centered to left-justified
-among other minor formatting adjustments. CSS allowed us to define the look and
-feel programmatically with the need to create graphical assets using image
-editing software. This means that anyone using the codebase of Editour for
-different purposes can easily change the look and feel of the frontend by
-changing the CSS.\footnote{This is allowed since Editour is free software, which
-is discussed briefly in Section~\ref{sec:futureOfEditour}.}
+the \texttt{button} class and either \texttt{greenbutton},
+\texttt{orangebutton}, or \texttt{bluebutton} will be styled like a button and
+have a new color palette applied. In order to differentiate the buttons that
+reveal subcards, the \texttt{outlinebutton} class is used. This class takes the
+custom \texttt{--bg-color} property and applies it to the border, drop shadow,
+and text color instead of the background. This class was also applied to the
+buttons that can be seen in
+Figures~\ref{fig:jumpCard}~and~\ref{fig:downloadCard}. Finally, the
+\texttt{revealer} class changes the text from centered to left-justified among
+other minor formatting adjustments. CSS allowed us to define the look and feel
+programmatically with the need to create graphical assets using image editing
+software. This means that anyone using the codebase of Editour for different
+purposes can easily change the look and feel of the frontend by changing the
+CSS.\footnote{This is allowed since Editour is free software, which is discussed
+briefly in Section~\ref{sec:futureOfEditour}.}
 
@@
 and saves them to the disk with a time stamp. Then any application can request a
-particular tour and the backend will serve the most recent version.
+particular tour, and the backend will serve the most recent version.
 
@@
 allows users to edit existing tours. When the user requests to edit a tour on
-the frontend it sends a request to the backend server for that tour's metadata
+the frontend, it sends a request to the backend server for that tour's metadata
 file. This file contains information about all regions and files in the tour.
@@
 
-For testing and development purposes the Editour backend was originally hosted
-on Joseph Petitti's personal server. This was a CentOS virtual machine running
-on an old Dell rack server in Worcester, Massachusetts. We wrote a custom
-systemd service to run Editour as a daemon and keep its log files organized. The
-Node.js backend was served by an Nginx reverse proxy running on the same virtual
+For testing and development purposes, Editour backend was originally hosted on
+Joseph Petitti's personal server. This was a CentOS virtual machine running on
+an old Dell rack server in Worcester, Massachusetts. We wrote a custom systemd
+service to run Editour as a daemon and keep its log files organized. The Node.js
+backend was served by an Nginx reverse proxy running on the same virtual
 machine.
@@
 this can cause an issue where the Node server takes so long to respond that
-Apache thinks it has timed out, and sends an erroneous 504 Gateway Timeout
+Apache thinks it has timed out and sends an erroneous 504 Gateway Timeout
 message~\autocite{rfc7231}. Without access to superuser permissions or a faster
@@
 incorporate AR, such as an audio guide mobile web app that runs entirely in the
-browser, using the geolocation API to access the user's location (if the user
+browser, and uses the geolocation API to access the user's location (if the user
 grants permission). This kind of infrastructure would allow users to access an
@@
 Currently, anyone can clone the GitHub repository of Editour and deploy a
-working version on a personal server. The source code for Editour is under a
-free license, namely the GNU General Public License. This allows anyone to
-expand the frontend and backend to suit their needs. With additional hardware
-and by extending the current implementation of both the frontend and backend,
-Editour could be used as the groundwork to create an entire crowd-sourced
-walking tour platform, allowing users to design tours for others to take.
+working version on a personal server. The source code for Editour is under the
+GNU General Public License. This is a free license that allows anyone to expand
+the frontend and backend to suit their needs. With additional hardware and by
+extending the current implementation of both the frontend and backend, Editour
+could be used as the groundwork to create an entire crowd-sourced walking tour
+platform, allowing users to design tours for others to take.
 
@@
 The core user experience of ARuko is the walking tour. By walking the given
-route, the user enters and exits specific geographic regions that invoke
-changes in the app, such as playing audio and displaying different images.
-Originally, we planned to mark regions by singular points, and trigger that
-region if the user was within a certain radius of that point.
-Implementation-wise, this would have been much simpler, but obviously limits
-possible tour designs. Consequently, we decided at an early stage to
-accommodate regions with arbitrary shape and size.  In the implementation, we
-provided support for both ``GPS Bubbles'' and ``GPS Polygons.'' In the end
-however, Editour made it trivial to use the more versatile ``GPS Polygons,'' so
-we eventually dropped support for regions triggered by distance.
+route, the user enters and exits specific geographic regions that invoke changes
+in the app, such as playing audio and displaying different images. Originally,
+we planned to mark regions by singular points and trigger that region if the
+user was within a certain radius of that point. Implementation-wise, this would
+have been much simpler but obviously limits possible tour designs.
+Consequently, we decided at an early stage to accommodate regions with arbitrary
+shape and size.  In the implementation, we provided support for both ``GPS
+Bubbles'' and ``GPS Polygons.'' In the end however, Editour made it trivial to
+use the more versatile ``GPS Polygons,'' so we eventually dropped support for
+regions triggered by distance.
 % TODO add a picture that shows how having only circular regions limits possible
@@
 ARuko uses augmented reality to translate text at the site of the tour as well.
-While AR translation apps exist, the experience can be frustrating, and produce
-poor results. Google~Translate's text recognition and machine-learning powered
-translation technology is certainly impressive. At the same time, the
+While AR translation apps exist, the experience can be frustrating and can
+produce poor results. Google~Translate's text recognition and machine-learning
+powered translation technology is certainly impressive. At the same time, the
 translation service works better in ``scan'' mode instead of ``instant'' mode.
@@
 superimposing the translated text onto the real world using the camera. In
-``scan'' mode, the user first takes a photo. This will sometimes produce
-useless results, as seen in Figure~\ref{fig:translateInstant}. Then, the user
-is prompted to highlight where text appears in the photo by dragging lines onto
-the screen where text appears, as seen in Figure~\ref{fig:translateScan}. After
-the translation is complete, the translated text appears in a separate UI
-element, which can be seen in Figure~\ref{fig:translateFinalCard}. In most
-cases, it is more convenient and readable to have the translation appear in a
-separate scrollable text box. This motivated the current design of the ``info
-buttons'' in ARuko. Instead of placing text directly onto signage, we place a
-blue button with a stylized ``\textit{i}'' in the center. By tapping on this
-button, a separate UI element will appear containing the translated text. Since
-this button is cast into the world using the AR camera, the button appears to
-be placed directly on top of the content.
+``scan'' mode, the user first takes a photo. This will sometimes produce useless
+results, as seen in Figure~\ref{fig:translateInstant}. Then, the user is
+prompted to highlight where text appears in the photo by dragging lines onto the
+screen where text appears, as seen in Figure~\ref{fig:translateScan}. After the
+translation is complete, the translated text appears in a separate UI element,
+which can be seen in Figure~\ref{fig:translateFinalCard}. In most cases, it is
+more convenient and readable to have the translation appear in a separate
+scrollable text box. This motivated the current design of the ``info buttons''
+in ARuko. Instead of placing text directly onto signage, we place a blue button
+with a stylized ``\textit{i}'' in the center. By tapping on this button, a
+separate UI element will appear containing the translated text. Since this
+button is cast into the world using the AR camera, the button appears to be
+placed directly on top of the content.
 
@@
 spreadsheet. Hikaru Inoue manually translated each sign and provided notes about
-his decision making process about each translation. Once this time-intensive
+his decision-making process about each translation. Once this time-intensive
 labor was completed, we took each field of translated text from the spreadsheet
@@
 model such that the ticket served as a back plane, as pictured in
-Figure~\ref{fig:souvenir}. This would allow users to hold the ticket vertically,
+Figure~\ref{fig:souvenir}. This would allow users to hold the ticket vertically
 and view the Golden Pavilion floating in front of the ticket. This allows users
@@
 
-Pictured in Figure~\ref{fig:oldUI} is our early UI. It was very minimal, but
+Pictured in Figure~\ref{fig:oldUI} is our early UI. It was very minimal but
 still covered all of the uses for our app at the time. The top of the screen had
@@
 viewable in AR using ground plane detection. When tapped, each button would
-create a cube, with the given image on each face, and place it on the ground
+create a cube with the given image on each face and place it on the ground
 where the user was pointing. Figure~\ref{fig:floatingCube} shows this feature in
@@
 target capabilities for scanning objects outside of the supported use case, such
-as 3D landscapes or the side of a building. We had serious doubts about how
-well this would work, and our suspicions were confirmed after some field
-testing. This was the reasoning behind focusing on ground-plane detection
-instead of image targets; ground-plane detection can be used anywhere, and is
-much more reliable than treating 3D objects as 2D image targets.
+as 3D landscapes or the side of a building. We had serious doubts about how well
+this would work, and our suspicions were confirmed after some field testing.
+This was the reasoning behind focusing on ground-plane detection instead of
+image targets; ground-plane detection can be used anywhere and is much more
+reliable than treating 3D objects as 2D image targets.
 
@@
 creating an empty vertical layout group. Then, a script would create buttons for
-each image to display, and assign those images as children of the layout group.
-To get the smooth open/close animation, we ``lerp'' (linearly interpolate)
-the menu to the corresponding position each frame until it is fully opened or
+each image to display and assign those images as children of the layout group.
+To get the smooth open/close animation, we ``lerp'' (linearly interpolate) the
+menu to the corresponding position in each frame until it is fully opened or
 closed. In between these two drop-down menus is a panel that would display the
@@
 that controls the playback position of the audio file played in each region. We
-learned about how audio sliders work in Unity with this feature, and would
+learned about how audio sliders work in Unity with this feature, and would we
 expand on that knowledge for the final version of the app in order to optimize
@@
 strangely tied to the duration of the audio track playing underneath. What if a
-user selects a chapter, and then physically enters that region moments later?
+user selects a chapter and then physically enters that region moments later?
 Should the audio restart to indicate that the user has arrived at the location,
@@
 project and... voila!''~\autocite{glasseye2019}.\footnote{``Adobe XD'' is
-stylized incorrectly with ``AdobeXd'' in the description of the Unity
-package. This is also different from ``Adobe Xd'', the way in which it is
-stylized in the title.} We suspect this sounds too good to be true because it
-is. As of September 20\textsuperscript{th}, 2019, there are 6 user reviews. All
-of the five-star reviews were have the caveat ``Reviewer was gifted package by
-publisher'' which which we interpreted as a warning sign. Because of this, we
+stylized incorrectly with ``AdobeXd'' in the description of the Unity package.
+This is also different from ``Adobe Xd'', the way in which it is stylized in the
+title.} As of September 20\textsuperscript{th}, 2019, there are 6 user reviews.
+All of the five-star reviews were have the caveat ``Reviewer was gifted package
+by publisher'' which which we interpreted as a warning sign. Because of this, we
 decided to rebuild the UI largely from the ground up, using the Adobe XD file to
@@
 We created the gallery out of a horizontal layout group, populated it with
-images dynamically in each region, and then had the buttons ``lerp'' the gallery
+images dynamically in each region, and had the buttons ``lerp'' the gallery
 to different positions in order to switch between each image in a smooth and
@@
 framework. Mocha is the most depended-upon package in the Node Package
-Manager~\autocite{tidelift2019}, and is widely used by professional software
+Manager~\autocite{tidelift2019} and is widely used by professional software
 development teams. It has a myriad of useful features that allow developers to
@@
 These tests were very useful in tracking down bugs and unexpected behavior in
-the backend, and also allowed us to make sure no functionality changed when
+the backend, and they also allowed us to make sure no functionality changed when
 adding new features or making changes to underlying logic later on.
@@
 
-For the duration of the project however, Editour only had to be used our team
+For the duration of the project, however, Editour only had to be used our team
 and Atticus. Therefore, the testing for the frontend of Editour was less
@@
 get right.  Using Unity's built-in NUnit unit testing framework, we wrote tests
-to verify whether the tour data was being parsed correctly, and whether the tour
+to verify whether the tour data was being parsed correctly and whether the tour
 would be run correctly.
@@
 segments.  The point is outside of the polygon if the ray intersects an odd
-number of times. Figure~\ref{fig:intersectionsDiagram} does not serve as a
-proof, but should at least make it clear why this works. This algorithm's time
+number of times. Figure~\ref{fig:intersectionsDiagram} does not serve as a proof
+but should at least make it clear why this works. This algorithm's time
 complexity is $O(n)$, where $n$ is the sum total of the number of vertices of
@@
 This uniquely shaped region also prompted us to think about what UI behavior
-made the most sense if a user were to walk into a region, walk out and then in
-again. We decided that it was awkward if the audio restarted upon re-entering a
-region, since the audio would still be playing once a user left the region. As
-we began to implement more complex UI that changed based on GPS position in
-various ways, directly taking the tour by walking around was an invaluable way
-to test. Section~\ref{sec:adobeXdDesign} details how the UI grew in complexity
-in the late stages of the project. Having a way to regularly run field tests was
-integral to polishing the app in time before we revisited Kinkaku-ji. Because
-Editour was flexible enough to easily swap out media and add regions to the
-tour, Editour proved itself to be as helpful for testing as it was for
-crafting the final tour that could be taken at Kinkaku-ji.
+made the most sense if a user were to walk into a region, walk out, and then
+walk in again. We decided that it was awkward if the audio restarted upon
+re-entering a region, since the audio would still be playing once a user left
+the region. As we began to implement more complex UI that changed based on GPS
+position in various ways, directly taking the tour by walking around was an
+invaluable way to test. Section~\ref{sec:adobeXdDesign} details how the UI grew
+in complexity in the late stages of the project. Having a way to regularly run
+field tests was integral to polishing the app in time before we revisited
+Kinkaku-ji. Because Editour was flexible enough to easily swap out media and add
+regions to the tour, Editour proved itself to be as helpful for testing as it
+was for crafting the final tour that could be taken at Kinkaku-ji.
 
@@
 We tested using two phones at the same time: an iPhone 8 and a Samsung Galaxy
-S7. The iPhone 8 is newer, more powerful and therefore more suited for use with
-AR. We primarily used this phone to test the AR features of the app. Even
-though the Galaxy S7 had difficulty with basic AR features such as
-ground-plane detection, it was still capable of triggering the audio track
-based on GPS position.
+S7. The iPhone 8 is newer and more powerful. Therefore it is more suited for use
+with AR. We primarily used this phone to test the AR features of the app. Even
+though the Galaxy S7 had difficulty with basic AR features such as ground-plane
+detection, it was still capable of triggering the audio track based on GPS
+position.
 
@@
 Atticus, the IQP group, and our friend Hikaru and installed the beta version of
-ARuko on each of their phones. With little instruction about how the app works
-we had each of them try going through Kinkaku-ji while listening to the tour and
-using the app's features. Each member of our team also installed the beta
-version so we could test it. % TODO add photos of us testing it
+ARuko on each of their phones. Providing them with little instruction about how
+the app works, we had each of them try going through Kinkaku-ji while listening
+to the tour and using the app's features. Each member of our team also installed
+the beta version so we could test it.
+% TODO add photos of us testing it
 
@@
 lighting than when the reference images were taken. For image targets that were
-small, far away, or obscured by shadows the image recognition was slower. We
+small, far away, or obscured by shadows, the image recognition was slower. We
 discovered that the targets that worked best were large, had a lot of
@@
 Additionally, one of the image targets had the wrong text in its information
-pop-up. These were all easy bugs to fix, but if we might not have noticed
-them if we had not tested the app on-site.
+pop-up. These were all easy bugs to fix, but we might not have noticed them if
+we had not tested the app on-site.
 
@@
 Another major bug we discovered was that the GPS stopped updating when the main
-screen is not open. This means that in AR camera mode the app would not trigger
+screen was not open. This meant that in AR camera mode the app would not trigger
 new audio when you walked into a new region. This was caused by the GPS script
@@
 images and transcript, so it was more clear what that button does. The header
-text at the top was too big, and sometimes overflowed onto other UI elements, so
+text at the top was too big and sometimes overflowed onto other UI elements, so
 its size was reduced and split into two lines when the text was too long.
@@
 appeared in dozens of solo and group exhibitions across the world,
-including Kyoto, Beijing, London and New York~\autocite{michaelwhittle2019}.
+including Kyoto, Beijing, London, and New York~\autocite{michaelwhittle2019}.
 Kyoto~VR has worked with Michael Whittle in the past to create a 3D scan of a
@@
 undecided until more details about the project crystallized. Atticus knew he
-wanted to use AR on the tour, but was not sure what to do with it. At first, we
+wanted to use AR on the tour but was not sure what to do with it. At first, we
 made recommendations to him based on the capabilities of Vuforia. We knew that
@@
 image targets. The intention then would be to tie content to a physical location
-in Kinkaku-ji, and use images of the location as targets. As explained in
+in Kinkaku-ji and use images of the location as targets. As explained in
 Section~\ref{sec:earlyUserInterface}, this ultimately did not work out due to
@@
 We encountered a few notable problems with this. Using a Plane primitive had
-deleterious effects on the way the object was lit in the Unity scene, as well as
+deleterious effects on the way the object was lit in the Unity scene as well as
 how it appeared when not viewed head-on. If viewed from an angle, the picture
 could become very dark and difficult to see. If viewed from behind, back-face
-culling would take effect and the plane would become completely invisible.
+culling would take effect, and the plane would become completely invisible.
 Because of these issues, we decided to place the images on a Cube primitive
@@
 expressed interest in using AR to trigger video content. He was particularly
-interested in triggering 3D videos through AR. As the scope of the project 
-grew, and time ran short, the task of including 3D videos triggered by AR 
-seemed more and more complicated, causing that idea to be phased out of the
-final project. Additionally, we never received any assets from Atticus to use
-for this feature, preventing us from spending time developing it.
+interested in triggering 3D videos through AR. As the scope of the project grew,
+and time ran short, the task of including 3D videos triggered by AR was phased
+out of the final project. Additionally, we never received any assets to use for
+this feature, preventing us from developing it.
 
@@
 On a similar note, the requirements and scope of the project changed greatly
-from week to week, and sometimes even within one day. We spent a significant
+from week to week and sometimes even within one day. We spent a significant
 amount of time exploring concepts and features that were completely unrelated to
@@
 extensible. Two members of our team, Cole Granof and Joseph Petitti, had
-experience building web applications with HTML, CSS, and JavaScript, and Editour
+experience building web applications with HTML, CSS, and JavaScript, so Editour
 allowed them to use these skills to help the project.
@@
 implementing many of the complex AR features easier later on. If we had chosen a
-less-ideal platform, we might have had to switch to a different one after
-wasting time on that poor decision.
+less-ideal platform, we might have had to switch to a different one, costing us
+valuable development time.
 
@@
 Although selling ARuko on app stores was not within the scope of our academic
-project, we were able polish the app enough that it would be feasible for
-Atticus to eventually sell it. The UI could use more testing with real
-users to make sure it is intuitive and easy to use. We also intended to add a
-feature where the app could automatically download tour files from the Editour
-server and import them without having to rebuild. We were not able to complete
-this feature due to time constraints, but it could easily be added because all
-of ARuko's business logic is abstracted and generalized to support multiple
-tours. Editour also already supports requesting and downloading the most recent
+project, we were able to polish the app enough that it would be feasible for
+Atticus to eventually sell it. The UI could use more testing with real users to
+make sure it is intuitive and easy to use. We also intended to add a feature
+where the app could automatically download tour files from the Editour server
+and import them without having to rebuild. We were not able to complete this
+feature due to time constraints, but it could easily be added because all of
+ARuko's business logic is abstracted and generalized to support multiple tours.
+Editour also already supports requesting and downloading the most recent
 versions of tours.
@@
 Given more time and resources, the app could be augmented to include a tour
-browser that automatically downloads an unpacks tours from the Editour server.
+browser that automatically downloads and unpacks tours from the Editour server.
 More historic locations around Kyoto and Japan in general should be considered
@@
 the \LaTeX~source code for our paper, the Arduino code for the heart project
-(see Appendix~\ref{sec:ritsumeikanHeartProject}) and of course one for Editour
+(see Appendix~\ref{sec:ritsumeikanHeartProject}), and of course one for Editour
 and another for ARuko. These five repositories span across multiple different
 markup and programming languages, including C\#, C++, JavaScript, HTML, CSS, and
-the \LaTeX~used to typeset this paper. This gave us a welcome amount of
-practice using Git for version control, as well as GitHub's other features
-oriented around coordinating a team.
+the \LaTeX~used to typeset this paper. This gave us a welcome amount of practice
+using Git for version control as well as GitHub's features oriented around
+coordinating a team.
 
@@
 Now, Kanban boards are integral to Agile software development. Some teams still
-use physical Kanban boards, often using sticky notes and whiteboards.
+use physical Kanban boards, often consisting of sticky notes and whiteboards.
 
@@
 automatically close the issue when the pull request is approved. This is not
-only remarkably convenient, but also self-documenting since the descriptions of
-pull requests would contain the issues they were resolving. Secondly, creating a
+only remarkably convenient but also self-documenting, since the descriptions of
+pull requests would contain the issues they were resolving. Second, creating a
 pull request allows code to be reviewed by other members of the team very
@@
 version. The night before field testing at Kinkaku-ji, we would cease work on
-the most recent branch, and build the app to our phones. This way, we would
+the most recent branch and build the app to our phones. This way, we would
 always have an exact snapshot of the code we used for that day of testing.
@@
 assistance with hardware. He taught us how to properly use the tools around the
-lab, and purchased mechanical and electrical components we would need to
+lab, and he purchased mechanical and electrical components we would need to
 complete our task. Professor Amano was always available to answer questions
-related to biology, and helped us understand the mathematical model we would
+related to biology, and he helped us understand the mathematical model we would
 need to implement to drive the physical model with software. We worked on this
@@
 before proceeding. We also updated the Unity version of the project to the 2019
-version we were using, and updated the version of Vuforia to the most recent
+version we were using, and we updated the version of Vuforia to the most recent
 version, neither of which created any problems. The process of getting the model

### 2019-10-08 paper.tex
addressed cuneo's other comments

@@
 	\label{fig:iziTravel}
-\end{figure}
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=\textwidth]{kinkakuji.jpg}
-	\caption[The Golden Pavilion of Kinkaku-ji, Kyoto, Japan]{The Golden
-		Pavilion of Kinkaku-ji, Kyoto, Japan~\autocite{davidson2005}}
-	\label{fig:kinkakuji}
 \end{figure}
@@
 we wrote to manage the server daemon. Instead, we used a custom shell script and
-an npm package called ``forever'' to handle starting and stopping it. The
+an npm package called \texttt{forever} to handle starting and stopping it. The
 forever package runs Node.js scripts continuously, automatically restarting them
@@
 wrote a simple bash script that removes directories that have not been modified
-in the past five days. We set up a cron job\footnote{The program cron allows for
-periodic scheduling of repeated commands} to run this script automatically once
-per day to clean out old temporary files that are not being used any more.
+in the past five days. We set up a \texttt{cron} job\footnote{The program
+\texttt{cron} allows for periodic scheduling of repeated commands} to run this
+script automatically once per day to clean out old temporary files that are not
+being used any more.
 
@@
 Additionally, we would not try to use any text recognition or translation APIs
-to automate the translation. Figure~\ref{fig:translateInstant} demonstrates
-that this kind of technology needs to mature before it is completely usable,
+to automate the translation. Figure~\ref{fig:translateInstant} demonstrates that
+this kind of technology needs to mature before it is completely usable,
 especially for Japanese. Instead, we had Atticus share a Google Sheets
-spreadsheet. Hikaru Inoue manually translated each sign and provided notes about
-his decision-making process about each translation. Once this time-intensive
-labor was completed, we took each field of translated text from the spreadsheet
-and implemented it directly into the app, associating each translation with the
-correct image target.
+spreadsheet. A Japanese student and acquaintance of Atticus Sims, Hikaru Inoue,
+manually translated each sign and provided notes about his decision-making
+process about each translation. Once this time-intensive labor was completed, we
+took each field of translated text from the spreadsheet and implemented it
+directly into the app, associating each translation with the correct image
+target.
 
@@
 At this point in the project, the codebase for Editour was already around three
-thousand lines of vanilla JavaScript. With the changing requirements, Editour
-was becoming onerous to maintain at this stage of the project. Luckily, these
-changes were still manageable to implement.
+thousand lines of vanilla JavaScript. The growing code complexity meant that
+adding features required nontrivial amounts of retesting and refactoring.
+Luckily, these changes were still manageable to implement.
 
@@
 
-% TODO remove this
-\nocite{harvey2002} % don't remove this
-
 \subsection{Testing Editour}
@@
 point to infinity. Barring edge cases (which will be discussed shortly) the
-point is inside the polygon if the ray passes through an even number of line
-segments.  The point is outside of the polygon if the ray intersects an odd
+point is inside the polygon if the ray passes through an odd number of line
+segments.  The point is outside of the polygon if the ray intersects an even
 number of times. Figure~\ref{fig:intersectionsDiagram} does not serve as a proof
@@
 Throughout the duration of the project, the goalposts shifted multiple times.
-This section details some of the initial plans that we explored before Atticus
-shifted our focus to a walking tour app with AR features.
+This section details some of the initial plans that we explored before the
+specifications provided to us by Kyoto~VR helped focus the design on a walking
+tour app with AR features.
 
@@
 own line of coffee. His latest album, Omoiyari, was released on May
-31\textsuperscript{st}, 2019~\autocite{kishibashi2019}.
+31\textsuperscript{st}, 2019~\autocite{kishibashi2019}. While the prospect of
+working with either of these artists had us excited, Kyoto~VR was not able to
+find an arrangement.
 
@@
 Kyoto~VR has worked with Michael Whittle in the past to create a 3D scan of a
-solo exhibition, ``Portraits of Thought.'' This exhibition displayed diagrams
+solo exhibition, \textit{Portraits of Thought}. This exhibition displayed diagrams
 inspired by real science and mathematics. Atticus provided us with some
@@
 	\includegraphics[width=.7\textwidth]{exhibition-scan.png}
-    \caption{A screenshot of the 3D scan of ``Portraits of Thought,'' accessible
-    from the web}
+    \caption{A screenshot of the 3D scan of \textit{Portraits of Thought},
+    accessible from the web}
 	\label{fig:exhibitionScan}

### 2019-10-08 paper.tex
fix image positions

@@
 	\vspace{\baselineskip}
-	Professor Joshua Cuneo, Adviser \\
+	Professor Ralph Sutter, Adviser \\
 	Worcester Polytechnic Institute \par
 	\vspace{\baselineskip}
-	Professor Ralph Sutter, Adviser \\
+	Professor Joshua Cuneo, Adviser \\
 	Worcester Polytechnic Institute \par
@@
 	\centering
+	\includegraphics[width=0.5\textwidth]{drawing-region-editour.png}
+	\caption{Editour when a region is being drawn, including the two dotted
+		preview lines}
+	\label{fig:drawingRegion}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
 	\includegraphics[width=0.4\textwidth]{welcome-card-editour.png}
@@
 	\label{fig:welcomeCard}
-\end{figure}
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{drawing-region-editour.png}
-	\caption{Editour when a region is being drawn, including the two dotted
-		preview lines}
-	\label{fig:drawingRegion}
 \end{figure}
@@
 
-\begin{figure}[h]
+\begin{figure}[p]
 	\centering
@@
 	\label{fig:renameSubcard}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=0.4\textwidth]{media-subcard-editour.png}
+	\caption{The ``Media'' subcard}
+	\label{fig:mediaSubcard}
 \end{figure}
@@
 tour has been uploaded.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.4\textwidth]{media-subcard-editour.png}
-	\caption{The ``Media'' subcard}
-	\label{fig:mediaSubcard}
-\end{figure}
 
@@
 subcard as the user moves the vertex. Clicking on the vertex directly will
-create a blue pin-shaped marker that the user can also drag. Clicking on the
-coordinate box in the subcard will also create this blue pin-shaped marker; the
-map will also pan to this coordinate. The user can also delete vertices in the
-same way that files can be deleted from the ``Media'' subcard by clicking on the
-`X' button on that vertex's coordinate card. If there are exactly three points
-in a region, the `X' buttons will be ``grayed-out,'' preventing the user from
-deleting any more points, since a polygon must consist of at least three points.
+create a blue pin-shaped marker that the user can also drag (see
+Figure~\ref{fig:editSubcardWithMap}). Clicking on the coordinate box in the
+subcard will also create this blue pin-shaped marker; the map will also pan to
+this coordinate. The user can also delete vertices in the same way that files
+can be deleted from the ``Media'' subcard by clicking on the `X' button on that
+vertex's coordinate card. If there are exactly three points in a region, the `X'
+buttons will be ``grayed-out,'' preventing the user from deleting any more
+points, since a polygon must consist of at least three points.
 
@@
 to do this, but the buttons make this easier and less error-prone. This feature
-can be seen in figure Figure~\ref{fig:downloadCard}. Clicking ``Download'' does
+can be seen in Figure~\ref{fig:downloadCard}. Clicking ``Download'' does
 not download the tour to the user's computer. Instead, it requests only the
@@
 We did not include a way to resolve addresses or place names, like the service
-provided by Google Maps. Instead of exploring plugins/libraries that might
+provided by Google Maps. Instead of exploring plugins or libraries that might
 provide this functionality, we offered a simpler solution due to time
@@
 which can be accessed by clicking on the yellow buttons with place names.
-
-\begin{figure}[h]
-	\centering
-    \includegraphics[width=0.4\textwidth]{jump-card-editour.png}
-    \caption{The jump card}
-	\label{fig:jumpCard}
-\end{figure}
 
@@
 ``Projects'' tab of a GitHub repo (which can be seen in
-Figure~\ref{fig:kanbanBoard} in the Appendix).
+Figure~\ref{fig:kanbanBoard} in Appendix~\ref{sec:versionControl}).
 
@@
 
+\begin{figure}[h]
+	\centering
+    \includegraphics[width=0.4\textwidth]{jump-card-editour.png}
+    \caption{The jump card}
+	\label{fig:jumpCard}
+\end{figure}
+
 \subsubsection{Editour Backend}
@@
 screen where text appears, as seen in Figure~\ref{fig:translateScan}. After the
-translation is complete, the translated text appears in a separate UI element,
-which can be seen in Figure~\ref{fig:translateFinalCard}. In most cases, it is
-more convenient and readable to have the translation appear in a separate
-scrollable text box. This motivated the current design of the ``info buttons''
-in ARuko. Instead of placing text directly onto signage, we place a blue button
-with a stylized ``\textit{i}'' in the center. By tapping on this button, a
-separate UI element will appear containing the translated text. Since this
-button is cast into the world using the AR camera, the button appears to be
-placed directly on top of the content.
-
-% TODO make it so these images don't appear so far away (thank you LaTeX)
-\begin{figure}[p]
-	\centering
-	\includegraphics[width=0.8\textwidth]{translate-instant.jpg}
+translation is complete, the translated text appears in a separate UI element.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.4\textwidth]{translate-instant.jpg}
 	\caption{Google Translate camera feature in ``instant'' mode.}
@@
 
-\begin{figure}[p]
-	\centering
-	\includegraphics[width=0.8\textwidth]{translate-scan.jpg}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.4\textwidth]{translate-scan.jpg}
 	\caption{Google Translate camera feature in ``scan'' mode}
@@
 
-\begin{figure}[p]
-	\centering
-	\includegraphics[width=0.8\textwidth]{translate-final-card.png}
-	\caption{The final page seen after using ``scan'' mode in Google Translate}
-	\label{fig:translateFinalCard}
-\end{figure}
+In most cases, it is more convenient and readable to have the translation appear
+in a separate scrollable text box. This motivated the current design of the
+``info buttons'' in ARuko. Instead of placing text directly onto signage, we
+place a blue button with a stylized ``\textit{i}'' in the center. By tapping on
+this button, a separate UI element will appear containing the translated text.
+Since this button is cast into the world using the AR camera, the button appears
+to be placed directly on top of the content.
 
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=.5\textwidth]{souvenir.png}
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=.8\textwidth]{souvenir.png}
 	\caption{ARuko's virtual souvenir feature}
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=.5\textwidth]{kinkakuji-horizontal.png}
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=.8\textwidth]{kinkakuji-horizontal.png}
 	\caption{Untextured Golden Pavilion model sitting horizontally on ticket}
@@
 features provided by Unity.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.4\textwidth]{old-ui.png}
-	\caption{A screenshot of our early UI}
-	\label{fig:oldUI}
-\end{figure}
 
@@
 action.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.4\textwidth]{old-ui.png}
+	\caption{A screenshot of our early UI}
+	\label{fig:oldUI}
+\end{figure}
 
@@
 One of the notable changes is the chapter select screen, which is the third
-screen in Figure~\ref{fig:adobeXdDesign}. Before, we worked under the assumption
-that each geolocation-triggered region would not have to be ordered in any way.
-This assumption made its way into Editour, which at the time did not have a way
-to reorder regions once they were placed. Because of this chapter selection
-screen, we needed some way to specify and rearrange the order of regions within
-Editour.
+screen in Figure~\ref{fig:adobeXdDesign} and in Figure~\ref{fig:chaptersZoomed}.
+Before, we worked under the assumption that each geolocation-triggered region
+would not have to be ordered in any way. This assumption made its way into
+Editour, which at the time did not have a way to reorder regions once they were
+placed. Because of this chapter selection screen, we needed some way to specify
+and rearrange the order of regions within Editour.
+
+\begin{figure}[h] \centering
+    \includegraphics[width=0.4\textwidth]{chapters-zoomed.png}
+    \caption{Larger screenshot of the chapter selection screen mock-up}
+    \label{fig:chaptersZoomed}
+\end{figure}
 
@@
 
+\begin{figure}[h] \centering
+    \includegraphics[width=0.4\textwidth]{gallery-zoomed.png}
+    \caption{Larger screenshot of the transcript and image gallery mock-up}
+    \label{fig:galleryZoomed}
+\end{figure}
+
 At this point in the project, the codebase for Editour was already around three
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{editour-additions.png}
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=0.3\textwidth]{editour-additions.png}
 	\caption{Additions to Editour to accommodate the new design}
@@
 focus shifted to translating the maps and signs using the camera. The fourth
-screen on Figure~\ref{fig:adobeXdDesign} and Figure~\ref{fig:infoZoomed} shows a
-mock-up of this feature. Atticus took photographs of various signs throughout
+screen on Figure~\ref{fig:adobeXdDesign} and
+Figure~\ref{fig:infoTranslationZoomed} shows a mock-up of this feature.
+
+\begin{figure}[p] \centering
+    \includegraphics[width=0.8\textwidth]{info-translation-zoomed.png}
+    \caption{Larger screenshot of the info button and translation mock-up}
+    \label{fig:infoTranslationZoomed}
+\end{figure}
+
+Atticus took photographs of various signs throughout
 Kinkaku-ji for us to use as image targets. Hikaru Inoue helped us by translating
@@
 button brings up a separate UI element containing the translation, which can be
-seen in Figure~\ref{fig:translationZoomed}. The details of this feature is
+seen in Figure~\ref{fig:infoTranslationZoomed}. The details of this feature is
 discussed more thoroughly in Section~\ref{sec:translationFeature}.
+
+Another feature that was added was the ability for the user to preview the
+route. Figure~\ref{fig:mapZoomed} shows the map screen of the app. The map
+screen is simply a static image that can be pinched and zoomed.
+
+\begin{figure}[h] \centering
+    \includegraphics[width=0.4\textwidth]{map-zoomed.png}
+    \caption{Larger screenshot of the route screen mock-up}
+    \label{fig:mapZoomed}
+\end{figure}
 
@@
 
-\begin{figure}[p] \centering
-    \includegraphics[width=0.6\textwidth]{chapters-zoomed.png}
-    \caption{Larger screenshot of the chapter selection screen mock-up}
-    \label{fig:chaptersZoomed}
-\end{figure}
-
-\begin{figure}[p] \centering
-    \includegraphics[width=0.6\textwidth]{gallery-zoomed.png}
-    \caption{Larger screenshot of the transcript and image gallery mock-up}
-    \label{fig:galleryZoomed}
-\end{figure}
-
-\begin{figure}[p] \centering
-    \includegraphics[width=0.6\textwidth]{info-zoomed.png}
-    \caption{Larger screenshot of the info button mock-up}
-    \label{fig:infoZoomed}
-\end{figure}
-
-\begin{figure}[p] \centering
-    \includegraphics[width=0.6\textwidth]{map-zoomed.png}
-    \caption{Larger screenshot of the route screen mock-up}
-    \label{fig:mapZoomed}
-\end{figure}
-
-\begin{figure}[p] \centering
-    \includegraphics[width=0.6\textwidth]{translation-zoomed.png}
-    \caption{Larger screenshot of the translation window mock-up}
-    \label{fig:translationZoomed}
-\end{figure}
-
 \subsubsection{Final UI Implementation}
@@
 simultaneously. In the Vuforia engine settings, we changed this limit to
-accommodate for four simultaneous images.
+accommodate for four simultaneous images (see Figure~\ref{fig:fourIButtons}).
 
@@
 received his PhD at the Kyoto City University of Arts in 2014. His art has
-appeared in dozens of solo and group exhibitions across the world,
-including Kyoto, Beijing, London, and New York~\autocite{michaelwhittle2019}.
-Kyoto~VR has worked with Michael Whittle in the past to create a 3D scan of a
-solo exhibition, \textit{Portraits of Thought}. This exhibition displayed diagrams
-inspired by real science and mathematics. Atticus provided us with some
-diagrams to test in the Vuforia developer portal, since Michael Whittle wanted
-to know how well certain pieces of art would work as AR image targets. All of
-images that were provided to us were ranked as ``five stars'' by Vuforia,
-indicating that those images would serve well as AR image targets.
+appeared in dozens of solo and group exhibitions across the world, including
+Kyoto, Beijing, London, and New York~\autocite{michaelwhittle2019}. Kyoto~VR has
+worked with Michael Whittle in the past to create a 3D scan of a solo
+exhibition, \textit{Portraits of Thought} (Figure~\ref{fig:exhibitionScan}).
+This exhibition displayed diagrams inspired by real science and mathematics.
+Atticus provided us with some diagrams to test in the Vuforia developer portal,
+since Michael Whittle wanted to know how well certain pieces of art would work
+as AR image targets. All of images that were provided to us were ranked as
+``five stars'' by Vuforia, indicating that those images would serve well as AR
+image targets.
 

### 2019-10-08 paper.tex
addressed rest of cuneo's comments

@@
 the \LaTeX~source code for our paper, the Arduino code for the heart project
-(see Appendix~\ref{sec:ritsumeikanHeartProject}), and of course one for Editour
-and another for ARuko. These five repositories span across multiple different
-markup and programming languages, including C\#, C++, JavaScript, HTML, CSS, and
-the \LaTeX~used to typeset this paper. This gave us a welcome amount of practice
-using Git for version control as well as GitHub's features oriented around
-coordinating a team.
+(see Appendix~\ref{sec:ritsumeikanHeartProject}), and of course one repository
+for Editour and another for ARuko. These five repositories span across multiple
+different markup and programming languages, including C\#, C++, JavaScript,
+HTML, CSS, and the \LaTeX~used to typeset this paper. This gave us a welcome
+amount of practice using Git for version control as well as GitHub's features
+oriented around coordinating a team.
 
@@
 pull request allows code to be reviewed by other members of the team very
-easily. Reviewers can view the entire diff file\footnote{A ``diff'' is a file
-generated by Git that shows the differences between two files.} and add comments
-line-by-line. Other collaborators can easily respond to those comments.
+easily. Reviewers can view the entire \texttt{diff} file\footnote{A ``diff'' is
+a file generated by Git that shows the differences between two files.} and add
+comments line-by-line. Other collaborators can easily respond to those comments.
 Reviewers can also request certain features be changed before the branch is
@@
 (Not~Found)~\autocite{rfc7231}, and the message is a string or stringified JSON
-that contains the data of the response.
+that contains the data of the response. \vspace*{0.5\baselineskip}
 
@@
 seen in Figure~\ref{fig:referenceModel}. We were also provided with source code
-for an implementation of this model in C. We would still need to modify this
-code to calculate the output variables we would need to properly operate the
-physical model and integrate the model into the main loop of the Arduino source
-code with the appropriate timing.
+for an implementation of this model in C.
+
+We would still need to modify this code to calculate the output variables we
+would need to properly operate the physical model. Additionally, we would need
+to integrate the model into the main loop of the Arduino source code with the
+appropriate timing.
 
